### 2022-05-19 manuscript.Rmd
Added manuscript file

---
title: "manuscript"
author: "Federico Segala, Aurelio Bruno, Alex Wade, Daniel Baker"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

## Introduction

## Methods

### Participants

### Apparatus & Stimuli

Probably wants a figure here showing example stimuli, maybe some sine waves, and perhaps some stills of large and small pupils taken through the eyetracker (I think we used these on the ECVP poster last year).

### Procedure

### Data analysis

## Results

### Experiment 1

I'd suggest the following figures:

Summary of the pupillometry data with Fourier spectra, maybe an average waveform, and contrast response functions

Summary of the first harmonic EEG data showing the same as for the pupils, maybe with embedded scalp plots inset in the Fourier spectrum

Summary of the second harmonic EEG data showing the same as for the pupils, again with embedded scalp plots inset in the Fourier spectrum

```{r}

# example of how to embed R code in the markdown document

a <- 1

```

### Experiment 2

Figure showing summary of data from the experiment with different temporal frequencies

### Experiment 3

Figure summarising the matching results (probably averaged across participants)

### Computational modelling

Probably makes sense to explain the modelling after presenting the data. We might plot the model curves in the figures above, but then here have a summary figure with the posterior distributions of the interocular suppression parameter across four data sets.

## Discussion

## References

### 2022-05-20 manuscript.Rmd
testing

@@
 date: "`r Sys.Date()`"
-output: html_document
+output:
+  word_document: default
+  html_document: default
+  pdf_document: default
 ---
@@
 ### Experiment 1
-
+nonsense
 I'd suggest the following figures:

### 2022-09-11 manuscript.Rmd
Update manuscript.Rmd

--- 2022-05-19 manuscript.Rmd
@@
 ---
-title: "manuscript"
-author: "Federico Segala, Aurelio Bruno, Alex Wade, Daniel Baker"
+title: "Different rules for binocular combination of luminance in cortical and subcortical pathways"
+author: "Federico G. Segala, Aurelio Bruno, Alex R. Wade &  Daniel H. Baker"
 date: "`r Sys.Date()`"
-output: html_document
+output:
+  bookdown::pdf_document2:
+    fig_caption: yes
+    toc: no
+    keep_tex: yes
+  word_document: default
+  pdf_document:
+    toc: no
+  html_document: default
+bibliography: references.bib
+csl: elife.csl
 ---
@@
 ```{r setup, include=FALSE}
+
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+# 0 - do no processing, generate the pdf using existing versions of all figures
+# 1 - generate figures using the processed group data (requires XGB of storage)
+# 2 - average data across participants, do bootstrapping and modelling
+# 3 - download all raw data and analyse (requires XGB of storage)
+
+# reasonably compact code to check which packages are installed, install the missing ones, and activate all
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot') # list of CRAN packages
+missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
+if (length(missingpackages)>0){install.packages(missingpackages)}
+if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
+if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
+packagelist <- c(packagelist,'osfr','FourierStats')
+toinstall <- packagelist[which(!packagelist %in% (.packages()))]
+invisible(lapply(toinstall,library,character.only=TRUE))
+
 knitr::opts_chunk$set(echo = TRUE)
-```
 
-## Abstract
+# helper function to make colours transparent
+addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
 
-## Introduction
+v4Interp <- function(df, xo, yo, rmax = .75, gridRes = 67) {
+  ## Create a function to perform Matlab's v4 interpolation.
+  ## Takes as input a data-frame with columns x, y, and z (x co-ordinates, y co-ordinates, and amplitude)
+  ## and variables xo and yo, the co-ordinates which will be use to create a grid for interpolation
+  xo <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+  yo <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+  xy <- df$x + df$y*sqrt(as.complex(-1))
+  d <- matrix(rep(xy,length(xy)),nrow = length(xy), ncol = length(xy))
+  d <- abs(d - t(d))
+  diag(d) <- 1
+  g <- (d^2) * (log(d)-1)   # Green's function.
+  diag(g) <- 0
+  weights <- qr.solve(g,df$z)
+  xy <- t(xy)
+  outmat <- matrix(nrow = gridRes,ncol = gridRes)
+  for (i in 1:gridRes){
+    for (j in 1:gridRes) {
+      test4 <- abs((xo[i,j] + sqrt(as.complex(-1))*yo[i,j]) - xy)
+      g <- (test4^2) * (log(test4)-1)
+      outmat[i,j] <- g %*% weights}}
+  outDf <- data.frame(x = xo[,1],outmat)
+  names(outDf)[1:length(yo[1,])+1] <- yo[1,]
+  return(outDf)}
 
-## Methods
+colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
+targetelectrodes <- c('Oz','POz','O1','O2')
 
-### Participants
+localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
+if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
+rawdir <- 'local/rawdata/'
+if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
+matchdir <- 'local/Matching/'
+if (!file.exists(matchdir)){dir.create(matchdir)}   # create a local directory to store matching data
+TFdir <- 'local/TFdata/'
+if (!file.exists(TFdir)){dir.create(TFdir)}   # create a local directory to store  data from the temporal frequency experiment
+figdir <- 'local/Figures/'
+if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
+datadir <- 'local/Data/'
+if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
 
-### Apparatus & Stimuli
-
-Probably wants a figure here showing example stimuli, maybe some sine waves, and perhaps some stills of large and small pupils taken through the eyetracker (I think we used these on the ECVP poster last year).
-
-### Procedure
-
-### Data analysis
-
-## Results
-
-### Experiment 1
-
-I'd suggest the following figures:
-
-Summary of the pupillometry data with Fourier spectra, maybe an average waveform, and contrast response functions
-
-Summary of the first harmonic EEG data showing the same as for the pupils, maybe with embedded scalp plots inset in the Fourier spectrum
-
-Summary of the second harmonic EEG data showing the same as for the pupils, again with embedded scalp plots inset in the Fourier spectrum
-
-```{r}
-
-# example of how to embed R code in the markdown document
-
-a <- 1
+# cut off for data inclusion (Mahalanobis distance for complex data)
+SDthresh <- 3
+nbootstraps <- 1000
 
@@
 
-### Experiment 2
+# Abstract
+
+# Introduction
+
+# Methods
+
+## Participants
+
+## Apparatus & Stimuli
+
+## Procedure
+
+## Data analysis
+
+@Baker2021
+
+# Results
+
+## Experiment 1
+
+```{r include=FALSE, results='hide'}
+
+# (download and) analyse individual participant data for experiment 1
+
+if (processdata > 2){
+
+legaltriggers <- 1
+
+timeseq <- seq(1/120,10,length.out=120*10)
+timeseq2 <- seq(1/120,14,length.out=120*14)
+EEGtimes <- seq(1/1000,10,1/1000)
+targetindex <- (2*10)+1
+maskindex <- (1.6*10)+1
+targetindex2 <- (2*2*10)+1
+maskindex2 <- (2*1.6*10)+1
+
+  for (participant in 1:30){
+
+    # only download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',100+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',100+participant))){
+        dir.create(paste0(rawdir,'P',100+participant))
+
+       d <- dir(paste0(rawdir,'P',100+participant))
+
+       if (length(d)==0){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(rawdir,'P',100+participant,'.tar'))){
+           # download it from OSF
+
+         }
+
+         # then unzip the tar file
+         untar(paste0(rawdir,'P',100+participant,'.tar'),exdir=paste0(rawdir,'P',100+participant))
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(rawdir,'P',100+participant,'.tar'))
+       }
+
+      d <- dir(paste0(rawdir,'P',100+participant),full.names=TRUE)
+
+      pupiltargets <- array(0,dim=c(3,2,60))
+pupilmasks <- pupiltargets
+pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
+pupilspectra <- array(0,dim=c(3,2,60,300))
+EEGtargets <- array(0,dim=c(3,64,60))
+EEGmasks <- EEGtargets
+EEGtargets2 <- EEGtargets
+EEGmasks2 <- EEGtargets
+EEGwaveforms <- array(0,dim=c(3,64,60,1000*14))
+EEGspectra <- array(0,dim=c(3,64,60,300))
+
+psychopyfiles <- dir(path=paste0(rawdir,'P',100+participant),pattern=paste0('P',100+participant,'_CRFstudy'), full.names = TRUE)
+infofiles <- dir(path=paste0(rawdir,'P',100+participant),pattern='*_info.csv', full.names = TRUE)
+EEGfiles <- dir(path=paste0(rawdir,'P',100+participant),pattern='*_EEG.csv.gz', full.names = TRUE)
+pupilfiles <- dir(path=paste0(rawdir,'P',100+participant),pattern='*_pupil_positions.csv', full.names = TRUE)
+
+for (block in 1:length(EEGfiles)){
+
+    infofile <- read.csv(infofiles[block])
+  pupilstarttime <- as.numeric(as.character(infofile[4,2]))
+  localstarttime <- as.numeric(as.character(infofile[5,2]))
+
+  psychoutput <- read.csv(psychopyfiles[block])
+
+  trialtimes <- psychoutput$trialonset - pupilstarttime
+  condorder <- psychoutput$condition
+
+    EEGdata <- read.csv(EEGfiles[block])
+  electrodes <- colnames(EEGdata)
+
+      triggertimes <- NULL
+    counter <- 0
+    lasttrigger <- -10000
+    for (n in 1:nrow(EEGdata)){
+      if(EEGdata$Trigger[n] %in% legaltriggers){
+        if(n>(lasttrigger+10000)){
+        counter <- counter + 1
+        triggertimes[counter] <- n
+        lasttrigger <- n
+      }}
+    }
+
+    for (cond in 1:60){
+      for (ch in 1:64){
+        trial <- EEGdata[(triggertimes[cond]+(2001:12000)),ch+2]
+        fspec <- (fft(trial)/length(trial))
+        EEGtargets[block,ch,condorder[cond]] <- fspec[targetindex]
+        EEGmasks[block,ch,condorder[cond]] <- fspec[maskindex]
+        EEGtargets2[block,ch,condorder[cond]] <- fspec[targetindex2]
+        EEGmasks2[block,ch,condorder[cond]] <- fspec[maskindex2]
+        EEGspectra[block,ch,condorder[cond],1:300] <- fspec[1:300]
+
+        trial <- EEGdata[(triggertimes[cond]+(-999:13000)),ch+2]
+        EEGwaveforms[block,ch,condorder[cond],] <- trial - mean(trial[1:1000])
+      }}
+
+  pdata <- read.csv(pupilfiles[block])
+  pdata2 <- pdata[,c(1,3,4,14)]
+  pdata2[,1] <- pdata2[,1] - localstarttime
+  pdata2 <- pdata2[which(pdata2[,3]>0.0),]
+
+  for (eye in 1:2){
+    eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]
+    for (cond in 1:60){
+      a <- which(eyedata[,1]>trialtimes[cond]+2)
+      b <- which(eyedata[,1]<(trialtimes[cond]+12))
+      i <- intersect(a,b)
+      trial <- eyedata[i,]
+      trial[,1] <- trial[,1] - trial[1,1]
+      if (nrow(trial)>3){
+        resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
+        fspec <- (fft(resampled)/length(resampled))
+        pupiltargets[block,eye,condorder[cond]] <- fspec[targetindex]
+        pupilmasks[block,eye,condorder[cond]] <- fspec[maskindex]
+        pupilspectra[block,eye,condorder[cond],1:300] <- fspec[1:300]
+      }
+
+      a <- which(eyedata[,1]>(trialtimes[cond]-1))
+      b <- which(eyedata[,1]<(trialtimes[cond]+13))
+      i <- intersect(a,b)
+      trial <- eyedata[i,]
+      trial[,1] <- trial[,1] - trial[1,1]
+      if (nrow(trial)>3){
+        resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
+        pupilwaveforms[block,eye,condorder[cond],] <- resampled - mean(resampled[1:120])
+      }
+
+      }}
+
+}
+
+cleanmeansP <- matrix(0,nrow=6,ncol=5)
+cleanmasksP <- matrix(0,nrow=6,ncol=5)
+cleanmeansE <- array(0,dim=c(64,6,5))
+cleanmasksE <- array(0,dim=c(64,6,5))
+cleanmeansE2 <- array(0,dim=c(64,6,5))
+cleanmasksE2 <- array(0,dim=c(64,6,5))
+
+for (cond in 1:6){
+  startindex <- (10*(cond-1))
+  for (level in 1:5){
+    temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
+        cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    cleanmeansP[cond,level] <- mean(temp[i])}
+
+    temp <- c(pupilmasks[,,startindex+level],pupiltargets[,,startindex+level+5])
+        cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    cleanmasksP[cond,level] <- mean(temp[i])}
+
+    for (ch in 1:64){
+    temp <- c(EEGtargets[,ch,startindex+level],EEGtargets[,ch,startindex+level+5])
+            cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    cleanmeansE[ch,cond,level] <- mean(temp[i])}
+
+    temp <- c(EEGmasks[,ch,startindex+level],EEGmasks[,ch,startindex+level+5])
+                cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    cleanmasksE[ch,cond,level] <- mean(temp[i])}
+
+    temp <- c(EEGtargets2[,ch,startindex+level],EEGtargets2[,ch,startindex+level+5])
+                cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    cleanmeansE2[ch,cond,level] <- mean(temp[i])}
+
+    temp <- c(EEGmasks2[,ch,startindex+level],EEGmasks2[,ch,startindex+level+5])
+                cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    cleanmasksE2[ch,cond,level] <- mean(temp[i])}   
+    }
+
+  }
+}
+
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
+meanwavesE <- apply(EEGwaveforms[,electrodeindices,c(15,20),],4,mean,na.rm=TRUE)
+meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
+meanspectraE <- apply(EEGspectra[,electrodeindices,c(15,20),],4,mean,na.rm=TRUE)
+save(file=paste(datadir,'P',100+participant,'summary.RData',sep=''),list=c('cleanmeansP','cleanmeansE','cleanmeansE2','cleanmasksP','cleanmasksE','cleanmasksE2','meanspectraP','meanspectraE','meanwavesP','meanwavesE','electrodes'))
+
+      }
+
+      }
+
+    }
+  }
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# load in individual participant data and average, save group data
+
+if (processdata > 1){
+
+hdata <- read.csv(paste0(EEGdir,'headerfile.csv'))
+
+d <- dir(datadir,pattern='*summaryC.RData',full.names=TRUE)
+
+tempmasksP <- array(0,dim=c(length(d),6,5))
+tempmeansP <- tempmasksP
+tempmasksE <- array(0,dim=c(length(d),64,6,5))
+tempmeansE <- tempmasksE
+tempmeansE2 <- tempmeansE
+tempmasksE2 <- tempmasksE
+tempspectraP <- array(0,dim=c(length(d),300))
+tempspectraE <- array(0,dim=c(length(d),300))
+tempwavesP <- array(0,dim=c(length(d),1680))
+tempwavesE <- array(0,dim=c(length(d),14000))
+
+  for (s in 1:length(d)){
+
+    load(d[s])
+
+  tempmasksP[s,,] <- cleanmasksP
+  tempmeansP[s,,] <- cleanmeansP
+  tempspectraP[s,] <- meanspectraP
+  tempspectraE[s,] <- meanspectraE
+  tempwavesP[s,] <- meanwavesP
+  tempwavesE[s,] <- meanwavesE
+  tempmeansE[s,,,] <- cleanmeansE
+  tempmasksE[s,,,] <- cleanmasksE
+  tempmeansE2[s,,,] <- cleanmeansE2
+  tempmasksE2[s,,,] <- cleanmasksE2
+
+  }
+
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
+
+cleanmeansP <- matrix(0,nrow=6,ncol=5)
+cleanmeansPCI <- array(0,c(2,6,5))
+cleanmasksP <- matrix(0,nrow=6,ncol=5)
+cleanmasksPCI <- array(0,c(2,6,5))
+cleanmeansEav <- matrix(0,nrow=6,ncol=5)
+cleanmeansEavCI <- array(0,c(2,6,5))
+cleanmasksEav <- matrix(0,nrow=6,ncol=5)
+cleanmasksEavCI <- array(0,c(2,6,5))
+cleanmeansE2av <- matrix(0,nrow=6,ncol=5)
+cleanmeansE2avCI <- array(0,c(2,6,5))
+cleanmasksE2av <- matrix(0,nrow=6,ncol=5)
+cleanmasksE2avCI <- array(0,c(2,6,5))
+cleanmeansE <- array(0,dim=c(64,6,5))
+cleanmeansECI <- array(0,c(2,64,6,5))
+cleanmasksE <- array(0,dim=c(64,6,5))
+cleanmasksECI <- array(0,c(2,64,6,5))
+cleanmeansE2 <- array(0,dim=c(64,6,5))
+cleanmeansE2CI <- array(0,c(2,64,6,5))
+cleanmasksE2 <- array(0,dim=c(64,6,5))
+cleanmasksE2CI <- array(0,c(2,64,6,5))
+
+for (cond in 1:6){
+  for (level in 1:5){
+
+    temp <- tempmeansP[,cond,level]
+    cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmeansP[cond,level] <- mbs$meanamp
+    cleanmeansPCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansPCI[2,cond,level] <- mbs$upperCI
+    }
+
+    temp <- tempmasksP[,cond,level]
+    cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh)
+
+          mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmasksP[cond,level] <- mbs$meanamp
+    cleanmasksPCI[1,cond,level] <- mbs$lowerCI
+    cleanmasksPCI[2,cond,level] <- mbs$upperCI
+}
+
+      temp <- apply(tempmeansE[,electrodeindices,cond,level],1,mean)
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmeansEav[cond,level] <- mbs$meanamp
+    cleanmeansEavCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansEavCI[2,cond,level] <- mbs$upperCI
+      }
+
+temp <- apply(tempmasksE[,electrodeindices,cond,level],1,mean)
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmasksEav[cond,level] <- mbs$meanamp
+    cleanmasksEavCI[1,cond,level] <- mbs$lowerCI
+    cleanmasksEavCI[2,cond,level] <- mbs$upperCI
+        }
+
+temp <- apply(tempmeansE2[,electrodeindices,cond,level],1,mean)
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmeansE2av[cond,level] <- mbs$meanamp
+    cleanmeansE2avCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
+        }
+
+      temp <- apply(tempmasksE2[,electrodeindices,cond,level],1,mean)
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmasksE2av[cond,level] <- mbs$meanamp
+    cleanmasksE2avCI[1,cond,level] <- mbs$lowerCI
+    cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
+        }
+
+    for (ch in 1:64){
+
+      temp <- tempmeansE[,ch,cond,level]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmeansE[ch,cond,level] <- mbs$meanamp
+    cleanmeansECI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
+}
+
+      temp <- tempmasksE[,ch,cond,level]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmasksE[ch,cond,level] <- mbs$meanamp
+    cleanmasksECI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
+        }
+
+      temp <- tempmeansE2[,ch,cond,level]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmeansE2[ch,cond,level] <- mbs$meanamp
+    cleanmeansE2CI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
+        }
+
+      temp <- tempmasksE2[,ch,cond,level]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    cleanmasksE2[ch,cond,level] <- mbs$meanamp
+    cleanmasksE2CI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
+        }
+
+    }}}
+
+meanspectraP <- NULL
+meanspectraE <- NULL
+meanspectraPCI <- array(0,c(2,300))
+meanspectraECI <- array(0,c(2,300))
+
+for (f in 1:300){
+
+mbs <- amperrors(tempspectraP[,f],method='boot',quantiles=95,nresamples=nbootstraps)
+meanspectraP[f] <- mbs$meanamp
+meanspectraPCI[1,f] <- mbs$lowerCI
+meanspectraPCI[2,f] <- mbs$upperCI
+
+mbs <- amperrors(tempspectraE[,f],method='boot',quantiles=95,nresamples=nbootstraps)
+meanspectraE[f] <- mbs$meanamp
+meanspectraECI[1,f] <- mbs$lowerCI
+meanspectraECI[2,f] <- mbs$upperCI
+
+}
+
+meanwavesP <- apply(tempwavesP,2,mean)
+meanwavesE <- apply(tempwavesE,2,mean)
+meanwavesPCI <- array(0,dim=c(2,length(meanwavesP)))
+meanwavesECI <- array(0,dim=c(2,length(meanwavesE)))
+nsubjs <- dim(tempwavesP)[1]
+for (t in 1:length(meanwavesP)){
+  bspop <- NULL
+  for (s in 1:nbootstraps){bspop[s] <- mean(sample(tempwavesP[,t],nsubjs,replace=TRUE))}
+  meanwavesPCI[,t] <- quantile(bspop,c(0.025,0.975))
+}
+for (t in 1:length(meanwavesE)){
+  bspop <- NULL
+  for (s in 1:nbootstraps){bspop[s] <- mean(sample(tempwavesE[,t],nsubjs,replace=TRUE))}
+  meanwavesECI[,t] <- quantile(bspop,c(0.025,0.975))
+}
+
+save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes'))
+
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# generate plot showing the group pupillometry data
+
+if (processdata > 0){
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+load(file=paste0(datadir,'Averagedata.RData'))
+
+plotlims <- c(12,40,0,0.03)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(19,0.03,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.028,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+condlist <- c(1,5,6)
+pointlist <- c(21,24,25)
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
+  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(19,0.03,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.028,'(d)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1.6Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (cond in 4:6){
+  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
+  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
+  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
+}
+legend(19,0.03,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.028,'(e)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+frequencies <- (0:299)/10
+
+plotlims <- c(1,6,0,0.03) 
+ticklocsx <- seq(1,6,1)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+polygon(frequencies[c(11:61,61:11)],c(meanspectraPCI[1,11:61],meanspectraPCI[2,61:11]),col=colpal[2],border=NA)
+
+lines(frequencies[11:61],abs(meanspectraP[11:61]), col=colpal[2], lwd=3, cex=0.5)
+
+text(1.1,0.028,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+times <- seq((1/120)-1,13,1/120)
+sinewave <- sin(2*times * 2*pi)
+sinewave[1:120] <- 0
+sinewave[1560:1680] <- 0
+
+plotlims <- c(-1,13,-1,1) 
+ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,1,1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+# polygon(frequencies[c(11:51,51:11)],c(meanspectraPCI[1,11:51],meanspectraPCI[2,51:11]),col=colpal[2],border=NA)
+
+lines(times, sinewave, col='black', lwd=3)
+
+text(-0.7,0.88,'(a)',adj=0.5,cex=2.5)
+
+dev.off()
+
+  PostScriptTrace('CRF1p.ps')
+  p1 <- readPicture('CRF1p.ps.xml')
+  PostScriptTrace('CRF2p.ps')
+  p2 <- readPicture('CRF2p.ps.xml')
+  PostScriptTrace('CRF3p.ps')
+  p3 <- readPicture('CRF3p.ps.xml')
+  PostScriptTrace('SpecP.ps')
+  p4 <- readPicture('SpecP.ps.xml')
+  PostScriptTrace('timecourseP.ps')
+  p5 <- readPicture('timecourseP.ps.xml')
+
+    for (n in 1:length(p4@paths)){
+    temp <- class(p4@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p4@paths[n]$path@rgb))<765){p4@paths[n]$path@rgb <- addalpha(p4@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf(paste0(figdir,"pupildata.pdf"), bg="transparent", height = 10, width = 15)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  grid.picture(p1,x=0.17,y=0.25,width=0.32,height=1)
+  grid.picture(p2,x=0.5,y=0.25,width=0.32,height=1)
+  grid.picture(p3,x=0.83,y=0.25,width=0.32,height=1)
+  grid.picture(p5,x=0.25,y=0.7,width=0.5,height=1)
+  grid.picture(p4,x=0.75,y=0.7,width=0.5,height=1)
+
+  text(0.5,0.98,'Pupillometry',cex=4)
+
+  dev.off()
+
+  file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','SpecP.ps','timecourseP.ps'))
+  file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','SpecP.ps.xml','timecourseP.ps.xml'))
+
+}
+
+```
+
+```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation, with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum.
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Shaded regions and error bars indicate bootstrapped 95 percent confidence intervals.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('local/Figures/pupildata.pdf')
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# generate plot showing the group EEG data
+
+if (processdata > 0){
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+load(file=paste0(datadir,'Averagedata.RData'))
+
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+plotlims <- c(12,40,0,0.8)  
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("CRF1e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansEav[cond,]),contrastsdB,cleanmeansEavCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansEav[cond,]),contrastsdB,cleanmeansEavCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(19,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.75,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF2e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
+title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,5,6)
+pointlist <- c(21,24,25)
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansEav[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
+  arrows(contrastsdB,abs(cleanmeansEav[condlist[cond],]),contrastsdB,cleanmeansEavCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansEav[condlist[cond],]),contrastsdB,cleanmeansEavCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansEav[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(19,0.8,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.75,'(d)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF3e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV) at 1.6Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 4:6){
+  lines(contrastsdB,abs(cleanmasksEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
+  arrows(contrastsdB,abs(cleanmasksEav[cond,]),contrastsdB,cleanmasksEavCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksEav[cond,]),contrastsdB,cleanmasksEavCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksEav[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
+}
+legend(19,0.8,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.75,'(e)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF1e2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansE2av[cond,]),contrastsdB,cleanmeansE2avCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  if (cond!=2){
+  arrows(contrastsdB,abs(cleanmeansE2av[cond,]),contrastsdB,cleanmeansE2avCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)}
+
+  # plot an arrow for the final binocular target contrast level that is above 0.8
+  if (cond==2){
+  arrows(contrastsdB[1:4],abs(cleanmeansE2av[cond,1:4]),contrastsdB[1:4],cleanmeansE2avCI[2,cond,1:4],lwd=3,col=colpal[cond],length=0.05,angle=90)   
+  arrows(contrastsdB[5],abs(cleanmeansE2av[cond,5]),contrastsdB[5],0.8,lwd=3,col=colpal[cond],length=0.05,angle=45)    
+  }
+
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(19,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.75,'(f)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF2e2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
+title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,5,6)
+pointlist <- c(21,24,25)
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansE2av[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
+  arrows(contrastsdB,abs(cleanmeansE2av[condlist[cond],]),contrastsdB,cleanmeansE2avCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansE2av[condlist[cond],]),contrastsdB,cleanmeansE2avCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansE2av[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(19,0.8,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.75,'(g)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF3e2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV) at 3.2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 4:6){
+  lines(contrastsdB,abs(cleanmasksE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
+  arrows(contrastsdB,abs(cleanmasksE2av[cond,]),contrastsdB,cleanmasksE2avCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksE2av[cond,]),contrastsdB,cleanmasksE2avCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksE2av[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
+}
+legend(19,0.8,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(14,0.75,'(h)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("SpecE.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+frequencies <- (0:299)/10
+
+plotlims <- c(1,6,0,1) 
+ticklocsx <- seq(1,6,1)    # locations of tick marks on x axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+polygon(frequencies[c(11:61,61:11)],c(meanspectraECI[1,11:61],meanspectraECI[2,61:11]),col=colpal[2],border=NA)
+
+lines(frequencies[11:61],abs(meanspectraE[11:61]), col=colpal[2], lwd=3, cex=0.5)
+
+text(1.1,0.95,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("timecourseE.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+times <- seq((1/1000)-1,13,1/1000)
+sinewave <- sin(2*times * 2*pi)
+sinewave[1:1000] <- 0
+sinewave[13001:14000] <- 0
+
+plotlims <- c(-1,13,-1,1) 
+ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,1,1)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+# polygon(frequencies[c(11:51,51:11)],c(meanspectraPCI[1,11:51],meanspectraPCI[2,51:11]),col=colpal[2],border=NA)
+
+lines(times, sinewave, col='black', lwd=3)
+
+text(-0.7,0.88,'(a)',adj=0.5,cex=2.5)
+
+dev.off()
+
+xpos <- 1:64
+ypos <- 1:64
+montageE <- toupper(as.character(hdata$Electrode))
+for (ch in 1:64){
+  i <- match(toupper(electrodes[ch+2]),montageE)
+  xpos[ch] <- hdata$X_position[i]
+  ypos[ch] <- hdata$Y_position[i]
+}
+
+ramp2 <- colorRamp(c("white",colpal[2]))  # create a ramp from one colour to another
+colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
+
+## Create data frame to be used for interpolation - the function needs columns labelled x, y, and z
+rmax <- 0.55   #specify a maximum boundary for the grid
+gridRes <- 100 #specify the interpolation grid resolution
+
+toplot <- abs(cleanmeansE[,2,5])
+toplot[which(is.na(toplot))] <- 0
+testDat<- data.frame(x = xpos, y = -ypos, z = toplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+
+tiff("head1.tiff", height = 600, width = 600, units="px", bg="white")
+
+plotlims <- c(-rmax,rmax,-rmax,rmax) 
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,1),add=TRUE,useRaster=TRUE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match(toupper(targetelectrodes),toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=2)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+dev.off()
+
+toplot <- abs(cleanmeansE2[,2,5])
+toplot[which(is.na(toplot))] <- 0
+testDat<- data.frame(x = xpos, y = -ypos, z = toplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+zo2[which(zo2>1)] <- 1
+
+tiff("head2.tiff", height = 600, width = 600, units="px", bg="white")
+
+plotlims <- c(-rmax,rmax,-rmax,rmax) 
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,1),add=TRUE,useRaster=TRUE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match(toupper(targetelectrodes),toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=2)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+dev.off()
+
+  PostScriptTrace('CRF1e.ps')
+  p1 <- readPicture('CRF1e.ps.xml')
+  PostScriptTrace('CRF2e.ps')
+  p2 <- readPicture('CRF2e.ps.xml')
+  PostScriptTrace('CRF3e.ps')
+  p3 <- readPicture('CRF3e.ps.xml')
+  PostScriptTrace('SpecE.ps')
+  p4 <- readPicture('SpecE.ps.xml')
+  PostScriptTrace('timecourseE.ps')
+  p5 <- readPicture('timecourseE.ps.xml')
+  PostScriptTrace('CRF1e2.ps')
+  p6 <- readPicture('CRF1e2.ps.xml')
+  PostScriptTrace('CRF2e2.ps')
+  p7 <- readPicture('CRF2e2.ps.xml')
+  PostScriptTrace('CRF3e2.ps')
+  p8 <- readPicture('CRF3e2.ps.xml')
+
+    for (n in 1:length(p4@paths)){
+    temp <- class(p4@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p4@paths[n]$path@rgb))<765){p4@paths[n]$path@rgb <- addalpha(p4@paths[n]$path@rgb,alpha=0.2)}}}
+
+  h1 <- readTIFF('head1.tiff')
+  h2 <- readTIFF('head2.tiff')
+
+  pdf(paste0(figdir,"EEGdata.pdf"), bg="transparent", height = 15, width = 15)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  # insert the head plots first so the white border doesn't overlap the other graphs
+    aspratio <- 1  # this is the aspect ratio of the output pdf
+  imwidth <- 0.16
+  xstart <- 0.65
+  ystart <- 0.82
+  rasterImage(h1,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth) 
+  xstart <- 0.82
+  ystart <- 0.82
+  rasterImage(h2,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  grid.picture(p5,x=0.25,y=0.8,width=0.5,height=1)
+  grid.picture(p4,x=0.75,y=0.8,width=0.5,height=1)
+  grid.picture(p1,x=0.17,y=0.5,width=0.32,height=1)
+  grid.picture(p2,x=0.5,y=0.5,width=0.32,height=1)
+  grid.picture(p3,x=0.83,y=0.5,width=0.32,height=1)
+  grid.picture(p6,x=0.17,y=0.175,width=0.32,height=1)
+  grid.picture(p7,x=0.5,y=0.175,width=0.32,height=1)
+  grid.picture(p8,x=0.83,y=0.175,width=0.32,height=1)
+
+    text(0.5,1,'Electroencephalography',cex=4)
+
+  dev.off()
+
+  file.remove(c('CRF1e.ps','CRF2e.ps','CRF3e.ps','CRF1e2.ps','CRF2e2.ps','CRF3e2.ps','SpecE.ps','timecourseE.ps','head1.tiff','head2.tiff'))
+  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF3e.ps.xml','CRF1e2.ps.xml','CRF2e2.ps.xml','CRF3e2.ps.xml','SpecE.ps.xml','timecourseE.ps.xml'))
+
+}
+
+```
+
+```{r EEGdata, fig.cap="Summary of EEG results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation, with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
+Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Panels (f-h) are in the same format but for the second harmonic responses.
+Shaded regions and error bars indicate bootstrapped 95 percent confidence intervals.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('local/Figures/EEGdata.pdf')
+
+```
+
+## Experiment 2
 
@@
 
-### Experiment 3
+## Experiment 3
 
@@
 
-### Computational modelling
+## Computational modelling
 
-Probably makes sense to explain the modelling after presenting the data.
-We might plot the model curves in the figures above, but then here have a summary figure with the posterior distributions of the interocular suppression parameter across four data sets.
+Figure showing model behaviour (four panels) and posterior weight distributions.
 
-## Discussion
+# Discussion
 
-## References
+# References

### 2022-09-11 renameandupload.R
Working on manuscript

@@ -1,127 +1,26 @@
-# script to collate the various files and upload to OSF
-# checks which files already exist and which need to be uploaded
-# important to run the matlab script to convert EEG data first
 
-participant <- 'P310'
-sourcedir <- '~/Desktop/Pupildata/'
+# packagelist <- c('remotes','tictoc','utils')
+# missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
+# if (length(missingpackages)>0){install.packages(missingpackages)}
+# if (packagelist[!'osfr' %in% installed.packages()[,1]]){remotes::install_github("centerforopenscience/osfr")}
+# packagelist <- c(packagelist,'osfr')
+# toinstall <- packagelist[which(!packagelist %in% (.packages()))]
+# invisible(lapply(toinstall,library,character.only=TRUE))
 
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
-EEGdir <- 'local/EEG/'
-if (!file.exists(EEGdir)){dir.create(EEGdir)}   # create a local directory to store EEG data
-PPdir <- 'local/Pupil/'
-if (!file.exists(PPdir)){dir.create(PPdir)}   # create a local directory to store pupil data
-Pydir <- 'local/Psychopy/'
-if (!file.exists(Pydir)){dir.create(Pydir)}   # create a local directory to store Psychopy output
-figdir <- 'local/Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/Data/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
 
-packagelist <- c('remotes','tictoc','utils')
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
[…]

### 2022-09-23 manuscript.Rmd
First fully working version of code for testing

@@
 title: "Different rules for binocular combination of luminance in cortical and subcortical pathways"
-author: "Federico G. Segala, Aurelio Bruno, Alex R. Wade &  Daniel H. Baker"
+author: "Federico G. Segala, Aurelio Bruno, Alex R. Wade &  Daniel H. Baker (+Myat? +Joel?)"
 date: "`r Sys.Date()`"
@@
 # 0 - do no processing, generate the pdf using existing versions of all figures
-# 1 - generate figures using the processed group data (requires XGB of storage)
+# 1 - generate figures using the processed group data
 # 2 - average data across participants, do bootstrapping and modelling
@@
 
-# reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot') # list of CRAN packages
+# check which packages are installed, install the missing ones, and activate
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
-matchdir <- 'local/Matching/'
-if (!file.exists(matchdir)){dir.create(matchdir)}   # create a local directory to store matching data
-TFdir <- 'local/TFdata/'
-if (!file.exists(TFdir)){dir.create(TFdir)}   # create a local directory to store  data from the temporal frequency experiment
-figdir <- 'local/Figures/'
+figdir <- 'Figures/'
 if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/Data/'
+datadir <- 'local/processeddata/'
 if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
@@
            # download it from OSF
-
+           if (!exists('osffiles')){
+           osfnode <- 'x8u4v'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('P',100+participant,'.tar'))
+          osf_download(osffiles[fid,],rawdir,progress=TRUE)
          }
@@
 
-hdata <- read.csv(paste0(EEGdir,'headerfile.csv'))
-
-d <- dir(datadir,pattern='*summaryC.RData',full.names=TRUE)
+for (participant in 1:30){
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',100+participant,'summary.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',100+participant,'summary.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
+
+          if (!file.exists(paste0(datadir,'headerfile.csv'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',100+participant,'headerfile.csv'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+          }
+
+  hdata <- read.csv(paste0(datadir,'headerfile.csv'))
+
+d <- dir(datadir,pattern='*summary.RData',full.names=TRUE)
 
@@
       i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmeansP[cond,level] <- mbs$meanamp
@@
       i <- which(D<SDthresh) 
-
-          mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+          mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmasksP[cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmeansEav[cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmasksEav[cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmeansE2av[cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmasksE2av[cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmeansE[ch,cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmasksE[ch,cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmeansE2[ch,cond,level] <- mbs$meanamp
@@
         i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=95,nresamples=nbootstraps)
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
     cleanmasksE2[ch,cond,level] <- mbs$meanamp
@@
 
-meanspectraP <- NULL
-meanspectraE <- NULL
+meanspectraP <- (1:300)*0
+meanspectraE <- (1:300)*0
 meanspectraPCI <- array(0,c(2,300))
@@
 
-for (f in 1:300){
-
-mbs <- amperrors(tempspectraP[,f],method='boot',quantiles=95,nresamples=nbootstraps)
+for (f in 2:300){
+
+        temp <- tempspectraP[,f]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
 meanspectraP[f] <- mbs$meanamp
@@
 meanspectraPCI[2,f] <- mbs$upperCI
-
-mbs <- amperrors(tempspectraE[,f],method='boot',quantiles=95,nresamples=nbootstraps)
+      }
+
+        temp <- tempspectraE[,f]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
 meanspectraE[f] <- mbs$meanamp
@@
 meanspectraECI[2,f] <- mbs$upperCI
-
-}
-
-meanwavesP <- apply(tempwavesP,2,mean)
-meanwavesE <- apply(tempwavesE,2,mean)
-meanwavesPCI <- array(0,dim=c(2,length(meanwavesP)))
-meanwavesECI <- array(0,dim=c(2,length(meanwavesE)))
+      }
+}
+
+meanwavesP <- NULL
+meanwavesE <- NULL
+meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
+meanwavesECI <- array(0,dim=c(2,dim(tempwavesE)[2]))
 nsubjs <- dim(tempwavesP)[1]
-for (t in 1:length(meanwavesP)){
+for (t in 1:dim(tempwavesP)[2]){
+  temp <- tempwavesP[,t]
+  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
+  meanwavesP[t] <- mean(temp[i])
   bspop <- NULL
-  for (s in 1:nbootstraps){bspop[s] <- mean(sample(tempwavesP[,t],nsubjs,replace=TRUE))}
-  meanwavesPCI[,t] <- quantile(bspop,c(0.025,0.975))
-}
-for (t in 1:length(meanwavesE)){
+  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
+  meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
+}
+
+for (t in 1:dim(tempwavesE)[2]){
+    temp <- tempwavesE[,t]
+  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
+  meanwavesE[t] <- mean(temp[i])
   bspop <- NULL
-  for (s in 1:nbootstraps){bspop[s] <- mean(sample(tempwavesE[,t],nsubjs,replace=TRUE))}
-  meanwavesECI[,t] <- quantile(bspop,c(0.025,0.975))
+  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
+  meanwavesECI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
 }
@@
 
+         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Averagedata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
 load(file=paste0(datadir,'Averagedata.RData'))
 
-plotlims <- c(12,40,0,0.03)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+plotlims <- c(15,40,0,0.03) 
 ticklocsx <- contrastsdB    # locations of tick marks on x axis
@@
 }  
-legend(19,0.03,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.028,'(c)',adj=0.5,cex=2.5)
+legend(22,0.03,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(c)',adj=0.5,cex=2.5)
 
@@
 }  
-legend(19,0.03,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.028,'(d)',adj=0.5,cex=2.5)
+legend(22,0.03,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(d)',adj=0.5,cex=2.5)
 
@@
 }
-legend(19,0.03,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.028,'(e)',adj=0.5,cex=2.5)
+legend(22,0.03,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(e)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(-1,13,-1,1) 
+plotlims <- c(-1,13,-1,0.5) 
 ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-1,1,1)    # locations of tick marks on y axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
 ticklabelsx <- ticklocsx        # set labels for x ticks
@@
 
-# polygon(frequencies[c(11:51,51:11)],c(meanspectraPCI[1,11:51],meanspectraPCI[2,51:11]),col=colpal[2],border=NA)
-
-lines(times, sinewave, col='black', lwd=3)
-
-text(-0.7,0.88,'(a)',adj=0.5,cex=2.5)
+filt <- butter(3,0.083)
+filtwaveP <- filter(filt, meanwavesP)
+filtU <- filter(filt,meanwavesPCI[1,])
+filtL <- filter(filt,meanwavesPCI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
+
+lines(times, filtwaveP, col=colpal[2], lwd=1.5)
+
+lines(times, (sinewave/10)-0.9, col='black', lwd=3)
+
+text(-0.7,0.4,'(a)',adj=0.5,cex=2.5)
 
@@
 
+      for (n in 1:length(p5@paths)){
+    temp <- class(p5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p5@paths[n]$path@rgb))<765){p5@paths[n]$path@rgb <- addalpha(p5@paths[n]$path@rgb,alpha=0.2)}}}
+
   pdf(paste0(figdir,"pupildata.pdf"), bg="transparent", height = 10, width = 15)
@@
 ```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation, with the driving signal plotted at the foot.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
 Panel (b) shows the average Fourier spectrum.
@@
 Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Shaded regions and error bars indicate bootstrapped 95 percent confidence intervals.", fig.align="center", echo=FALSE}
+Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", echo=FALSE}
 
@@
 
+hdata <- read.csv(paste0(datadir,'headerfile.csv'))
+
+         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Averagedata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
 load(file=paste0(datadir,'Averagedata.RData'))
@@
 
-plotlims <- c(12,40,0,0.8)  
+plotlims <- c(15,40,0,0.8)  
 ticklocsx <- contrastsdB    # locations of tick marks on x axis
@@
 }  
-legend(19,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.75,'(c)',adj=0.5,cex=2.5)
+legend(22,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(c)',adj=0.5,cex=2.5)
 
@@
 }  
-legend(19,0.8,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.75,'(d)',adj=0.5,cex=2.5)
+legend(22,0.8,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(d)',adj=0.5,cex=2.5)
 
@@
 }
-legend(19,0.8,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.75,'(e)',adj=0.5,cex=2.5)
+legend(22,0.8,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(e)',adj=0.5,cex=2.5)
 
@@
 }  
-legend(19,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.75,'(f)',adj=0.5,cex=2.5)
+legend(22,0.8,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(f)',adj=0.5,cex=2.5)
 
@@
 }  
-legend(19,0.8,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.75,'(g)',adj=0.5,cex=2.5)
+legend(22,0.8,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(g)',adj=0.5,cex=2.5)
 
@@
 }
-legend(19,0.8,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(14,0.75,'(h)',adj=0.5,cex=2.5)
+legend(22,0.8,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(h)',adj=0.5,cex=2.5)
 
@@
 
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
 axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
@@
 
-plotlims <- c(-1,13,-1,1) 
+plotlims <- c(-1,13,-10,20) 
 ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-1,1,1)    # locations of tick marks on y axis
+ticklocsy <- seq(-10,20,10)    # locations of tick marks on y axis
 ticklabelsx <- ticklocsx        # set labels for x ticks
@@
 
-# polygon(frequencies[c(11:51,51:11)],c(meanspectraPCI[1,11:51],meanspectraPCI[2,51:11]),col=colpal[2],border=NA)
-
-lines(times, sinewave, col='black', lwd=3)
-
-text(-0.7,0.88,'(a)',adj=0.5,cex=2.5)
+filt <- butter(3,0.083*0.12)
+filtwaveE <- filter(filt, meanwavesE)
+filtU <- filter(filt,meanwavesECI[1,])
+filtL <- filter(filt,meanwavesECI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
+
+lines(times, filtwaveE, col=colpal[2], lwd=1.5)
+
+lines(times, (sinewave*2.5)-7.5, col='black', lwd=3)
+
+text(-0.7,18,'(a)',adj=0.5,cex=2.5)
 
@@
 
+      for (n in 1:length(p5@paths)){
+    temp <- class(p5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p5@paths[n]$path@rgb))<765){p5@paths[n]$path@rgb <- addalpha(p5@paths[n]$path@rgb,alpha=0.2)}}}
+
   h1 <- readTIFF('head1.tiff')
@@
 ```{r EEGdata, fig.cap="Summary of EEG results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation, with the driving signal plotted at the foot.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
 Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
@@
 Panels (f-h) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped 95 percent confidence intervals.", fig.align="center", echo=FALSE}
+Shaded regions and error bars indicate bootstrapped standard errors.", fig.align="center", echo=FALSE}
 
@@
 
-Figure showing summary of data from the experiment with different temporal frequencies
+```{r include=FALSE, results='hide'}
+
+# (download and) analyse the raw data from the temporal frequency experiment
+
+if (processdata > 2){
+
+  legaltriggers <- 1
+
+  TFs <- c(2,4,8,16,30)
+  EEGtimes <- seq(1/1000,10,1/1000)
+  targetindices <- (TFs*10)+1
+
+  for (participant in 1:12){
+    print(participant)
+
+# download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',150+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',150+participant))){
+        dir.create(paste0(rawdir,'P',150+participant))}
+
+      d <- dir(paste0(rawdir,'P',150+participant))
+
+      if (length(d)==0){
+
+        # if the tar file of this participant's data doesn't exist
+        if (!file.exists(paste0(rawdir,'P',150+participant,'.tar'))){
+          # download it from OSF
+          if (!exists('tffiles')){
+            osfnode <- 'mvpyz'
+            osfproject <- osf_retrieve_node(osfnode)
+            tffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(tffiles$name==paste0('P',150+participant,'.tar'))
+          osf_download(tffiles[fid,],rawdir,progress=TRUE)
+        }
+
+        # then unzip the tar file
+        untar(paste0(rawdir,'P',150+participant,'.tar'),exdir=paste0(rawdir,'P',100+participant))
+
+        # and delete the tar file to save storage space
+        file.remove(paste0(rawdir,'P',150+participant,'.tar'))
+      }
+
+      d <- dir(paste0(rawdir,'P',150+participant),full.names=TRUE)
+
+      EEGtargets <- array(0,dim=c(5,64,20,5))
+      EEGspectra <- array(0,dim=c(5,64,20,500))
+
+      psychopyfiles <- dir(path=paste0(rawdir,'P',150+participant), pattern=paste0('P',150+participant,'_CRFstudy'), full.names = TRUE)
+
+      EEGfiles <- dir(path=paste0(rawdir,'P',150+participant), pattern='*_EEG.gz', full.names = TRUE)
+
+      for (block in 1:length(EEGfiles)){
+
+        psychoutput <- read.csv(psychopyfiles[block])
+
+        condorder <- psychoutput$condition
+
+        EEGdata <- read.csv(EEGfiles[block])
+        electrodes <- colnames(EEGdata)
+
+        triggertimes <- NULL
+        counter <- 0
+        lasttrigger <- -10000
+        for (n in 1:nrow(EEGdata)){
+          if(EEGdata$Trigger[n] %in% legaltriggers){
+            if(n>(lasttrigger+10000)){
+              counter <- counter + 1
+              triggertimes[counter] <- n
+              lasttrigger <- n
+            }}
+        }
+
+        for (cond in 1:counter){
+          for (ch in 1:64){
+            trial <- EEGdata[(triggertimes[cond]+(2001:12000)),ch+2]
+            fspec <- (fft(trial)/length(trial))
+            EEGtargets[block,ch,condorder[cond],] <- fspec[targetindices]
+            EEGspectra[block,ch,condorder[cond],1:500] <- fspec[1:500]
+          }}
+      }
+
+      electrodeindices <- match(targetelectrodes,electrodes)-2
+
+      cleanmeansE <- array(0,dim=c(2,5))
+      meanspec <- array(0,dim=c(2,5,500))
+
+      for (eye in 1:2){
+        for (cond in 1:5){
+          includedconds <- c(cond,cond+5) + (10*(eye-1))
+          temp <- as.vector(EEGtargets[,electrodeindices,includedconds,cond])
+          temp <- temp[which(!is.na(temp))]
+          temp <- temp[which(abs(temp)>0)]  
+          cartdata <- data.frame(Re(temp),Im(temp))
+          if (sum(cartdata)!=0){
+            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+            i <- which(D<SDthresh) 
+            cleanmeansE[eye,cond] <- mean(temp[i])}
+
+          for (f in 2:500){
+            temp <- as.vector(apply(EEGspectra[,electrodeindices,includedconds,f],c(1,3),mean))
+            temp <- temp[which(!is.na(temp))]
+            temp <- temp[which(abs(temp)>0)]  
+            cartdata <- data.frame(Re(temp),Im(temp))
+            if (sum(cartdata)!=0){
+              D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+              i <- which(D<SDthresh) 
+              meanspec[eye,cond,f] <- mean(temp[i])}   
+          }
+        }
+      }
+
+    }
+
+    save(file=paste0(datadir,'P',150+participant,'summary.RData'),list=c('cleanmeansE','meanspec'))
+
+  }
+
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# load in the processed data from the temporal frequency experiment and average
+
+if (processdata > 1){
+
+  allspec <- array(0,dim=c(12,2,5,500))
+  allmeans <- array(0,dim=c(12,2,5))
+  allratios <- matrix(0,nrow=12,ncol=5)
+
+  for (participant in 1:12){
+
+    for (participant in 1:30){
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',150+participant,'summary.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',100+participant,'summary.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+    }
+
+    load(paste0(datadir,'P',150+participant,'summary.RData'))
+
+    allmeans[participant,,] <- cleanmeansE
+    allspec[participant,,,] <- meanspec
+    allratios[participant,] <- 20*log10(abs(allmeans[participant,2,])/abs(allmeans[participant,1,]))
+  }
+
+meanratios <- NULL
+meanratiosCI <- matrix(0,nrow=2,ncol=5)
+cleanmeansTF <- matrix(0,nrow=2,ncol=5)
+cleanmeansTFCI <- array(0,dim=c(2,2,5))
+meanspectraTF <- array(0,dim=c(2,5,500))
+meanspectraTFCI <- array(0,dim=c(2,2,5,500))
+
+for (cond in 1:2){
+  for (level in 1:5){
+
+    temp <- allmeans[,cond,level]
+    cartdata <- data.frame(Re(temp),Im(temp))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+    cleanmeansTF[cond,level] <- mbs$meanamp
+    cleanmeansTFCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansTFCI[2,cond,level] <- mbs$upperCI
+    }
+
+    meanratios[level] <- mean(allratios[,level])
+    bspop <- NULL
+    for (n in 1:nbootstraps){
+      bspop[n] <- mean(sample(allratios[,level],nrow(allratios),replace=TRUE))
+    }
+    meanratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
+
+    for (f in 2:500){
+
+        temp <- allspec[,cond,level,f]
+      cartdata <- data.frame(Re(temp),Im(temp))
+      if (sum(cartdata)!=0){
+        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+        i <- which(D<SDthresh) 
+mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+meanspectraTF[cond,level,f] <- mbs$meanamp
+meanspectraTFCI[1,cond,level,f] <- mbs$lowerCI
+meanspectraTFCI[2,cond,level,f] <- mbs$upperCI
+      }
+    }
+  }
+}
+
+save(file=paste0(datadir,'AveragedataTF.RData'),list=c('cleanmeansTF','cleanmeansTFCI','meanspectraTF','meanspectraTFCI','meanratios','meanratiosCI'))
+
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# generate figure showing the TF data
+
+if (processdata > 0){
+
+         if (!file.exists(paste0(datadir,'AveragedataTF.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='AveragedataTF.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+  load(paste0(datadir,'AveragedataTF.RData'))
+
+  TFs <- c(2,4,8,16,30)
+  TFsdB <- 20*log10(TFs)
+
+  postscript("SpecTF.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 8, width = 5.5)
+
+frequencies <- (0:499)/10
+
+plotlims <- c(0,36,0,5) 
+ticklocsx <- seq(0,36,6)    # locations of tick marks on x axis
+ticklocsy <- seq(0,5,1)    # locations of tick marks on y axis
+ticklabelsx <- 2^(0:6)        # set labels for x ticks
+ticklabelsy <- c(0,1,'','','','')    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
+
+for (cond in 1:5){
+
+lines(c(0,36),c(cond,cond)-1)  
+polygon(20*log10(frequencies[c(11:490,490:11)]),(cond-1)+c(meanspectraTFCI[1,2,cond,11:490],meanspectraTFCI[2,2,cond,490:11]),col=colpal[cond],border=NA)
+
+lines(20*log10(frequencies[11:490]),(cond-1)+abs(meanspectraTF[2,cond,11:490]), col=colpal[cond], lwd=2, cex=0.5) 
+}
+
+text(33,0.25,'2Hz',adj=0.5,cex=1.5,col=colpal[1])
+text(33,1.25,'4Hz',adj=0.5,cex=1.5,col=colpal[2])
+text(33,2.25,'8Hz',adj=0.5,cex=1.5,col=colpal[3])
+text(33,3.25,'16Hz',adj=0.5,cex=1.5,col=colpal[4])
+text(33,4.25,'30Hz',adj=0.5,cex=1.5,col=colpal[5])
+
+text(1.5,4.8,'(a)',adj=0.5,cex=2.5)
+text(18,4.8,'Binocular',adj=0.5,cex=2)
+
+dev.off()
+
+plotlims <- c(6,30,0,1)  
+ticklocsx <- seq(6,30,6)    # locations of tick marks on x axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+ticklabelsx <- 2^(1:5)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("TF1.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:2){
+  lines(TFsdB,abs(cleanmeansTF[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(TFsdB,abs(cleanmeansTF[cond,]),TFsdB,cleanmeansTFCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(TFsdB,abs(cleanmeansTF[cond,]),TFsdB,cleanmeansTFCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(TFsdB,abs(cleanmeansTF[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(20,1,c('Monocular','Binocular'),pch=21:22,pt.bg=colpal[1:2],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(7.5,0.92,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+plotlims <- c(6,30,-3,12)  
+ticklocsy <- seq(-3,12,3)    # locations of tick marks on y axis
+ticklabelsy <- c(expression(1/sqrt(2)),'1',expression(sqrt(2)),'2',expression(2*sqrt(2)),'4')
+
+postscript("TF2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  lines(TFsdB,meanratios, col=colpal[3], lwd=3, cex=0.5)
+  arrows(TFsdB,meanratios,TFsdB,meanratiosCI[1,],lwd=3,col=colpal[3],length=0.05,angle=90)
+  arrows(TFsdB,meanratios,TFsdB,meanratiosCI[2,],lwd=3,col=colpal[3],length=0.05,angle=90)
+  points(TFsdB,meanratios, pch = 20+3, col='black', bg=colpal[3], cex=1.6, lwd=3)   
+ text(7.5,11,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+  PostScriptTrace('SpecTF.ps')
+  p1 <- readPicture('SpecTF.ps.xml')
+  PostScriptTrace('TF1.ps')
+  p2 <- readPicture('TF1.ps.xml')
+  PostScriptTrace('TF2.ps')
+  p3 <- readPicture('TF2.ps.xml')
+
+    for (n in 1:length(p1@paths)){
+    temp <- class(p1@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p1@paths[n]$path@rgb))<765){p1@paths[n]$path@rgb <- addalpha(p1@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf(paste0(figdir,"TFdata.pdf"), bg="transparent", height = 12, width = 15)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  grid.picture(p1,x=0.3,y=0.5,width=0.6,height=1)
+  grid.picture(p2,x=0.78,y=0.74,width=0.4,height=1)
+  grid.picture(p3,x=0.78,y=0.26,width=0.4,height=1)
+
+  dev.off()
+
+  file.remove(c('TF1.ps','TF2.ps','SpecTF.ps','TF1.ps.xml','TF2.ps.xml','SpecTF.ps.xml'))
+
+}
+
+```
+
+```{r TFdata, fig.cap="Binocular facilitation at different temporal frequencies.
+Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
+Panel (b) shows the response at each stimulation frequency for monocular (red) and binocular (blue) presentation.
+Panel (c) shows the ratio of binocular to monocular responses.
+Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('local/Figures/TFdata.pdf')
+
+```
 
@@
 
-Figure summarising the matching results (probably averaged across participants)
+```{r include=FALSE, results='hide'}
+
+# (download and) analyse individual participant data for the matching experiment
+
+if (processdata > 2){
+
+if (!file.exists(paste0(datadir,'matchingdata.csv'))){
+osfnode <- 'ey7rg'  
+osfproject <- osf_retrieve_node(osfnode)
+matchingfiles <- osf_ls_files(osfproject,n_max=300)
+fid <- which(matchingfiles$name=='matchingdata.csv')
+osf_download(matchingfiles[fid,],datadir,progress=TRUE)
+}
+
+matchingdata <- read.csv(paste0(datadir,'matchingdata.csv'))
+
+levels <- unique(matchingdata$allref)
+ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
+ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)
+subjects <- unique(matchingdata$Participant)
+
+allthresh <- array(0,dim=c(length(subjects),length(levels),length(ratiosL)))
+for (subj in 1:length(subjects)){
+  thissubj <- subset(matchingdata,Participant==subj)  
+  levels <- unique(thissubj$allref)
+for (cond in 1:length(levels)){
+  thiscond <- subset(thissubj,allref==levels[cond])
+  contrast <- levels[cond]
+  for (ll in 1:length(ratiosL)){
+    Lratio <- ratiosL[ll]
+    Rratio <- ratiosR[ll]
+    thisL <- subset(thiscond, allLratio==Lratio)
+    thisdata <- subset(thisL, allRratio==Rratio)
+
+Ncorrect <- NULL
+Ntrials <- NULL
+Clevs <- sort(unique(thisdata$allcontrast))
+for (lev in 1:length(Clevs)){
+  temp <- subset(thisdata,allcontrast==Clevs[lev])
+  Ncorrect[lev] <- sum(temp$correct)
+  Ntrials[lev] <- nrow(temp)
+}
+CdB <- 20*log10(Clevs)
+datatofit <- data.frame(CdB,Ncorrect,Ntrials)
+fit <- quickpsy::quickpsy(datatofit, x=CdB, k=Ncorrect, n=Ntrials, guess=0, xmin=0, xmax=40, B = 0, fun=cum_normal_fun)
+allthresh[subj,cond,ll] <- fit$thresholds$thre
+
+# plot(datatofit$CdB,datatofit$Ncorrect/datatofit$Ntrials)
+# points(datatofit$CdB,datatofit$Ncorrect/datatofit$Ntrials,pch=16)
+# lines(fit$curves$x,fit$curves$y)
+
+  }
+}
+}
+
+allthresh[1,2,] <- NA   # exclude outliers
+allthresh[2,2,2] <- NA  # exclude outliers
+meanthresh <- apply(allthresh,2:3,mean,na.rm=TRUE)
+SEthresh <- apply(allthresh,2:3,sd,na.rm=TRUE)/sqrt(apply(!is.na(allthresh),2:3,sum))
+
+pdf(paste0(figdir,"matchingdata.pdf"), bg="transparent", height = 5.5, width = 5.5)
+
+plotlims <- c(0,125,0,125)  
+ticklocs <- seq(0,125,25)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocs, side = 1, at=ticklocs)     # add the tick labels
+mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
+title(xlab="Right eye contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Left eye contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(0,24),c(24,24),lty=2)
+lines(c(0,48),c(48,48),lty=2)
+lines(c(24,24),c(0,24),lty=2)
+lines(c(48,48),c(0,48),lty=2)
+lines(c(0,96),c(96,0),lty=3)
+lines(c(0,48),c(48,0),lty=3)
+
+for (matchlev in 1:2){
+lines(ratiosR*10^(meanthresh[matchlev,]/20),ratiosL*10^(meanthresh[matchlev,]/20),pch=16,col=colpal[matchlev],lwd=3)}
+
+# # these lines of code plot the individual participants' data for checking
+# for (subj in 1:10){
+# for (matchlev in 1:2){
+#   lines(ratiosL*10^(allthresh[subj,matchlev,]/20),ratiosR*10^(allthresh[subj,matchlev,]/20),pch=16,col=colpal[matchlev],lwd=1)
+# for (cond in 1:9){
+#   points(ratiosL[cond]*10^(allthresh[subj,matchlev,cond]/20),ratiosR[cond]*10^(allthresh[subj,matchlev,cond]/20),pch=16,cex=1,col=colpal[matchlev])}}}
+
+for (matchlev in 1:2){
+for (cond in 1:9){
+  points(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),pch=16,cex=2,col=colpal[matchlev])
+
+  if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])<42){
+  arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
+  }
+
+  # plot as an arrow if exceeding the axis limits
+  if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])>42){
+  arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),125,ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.035, angle=45, lwd=2)
+  }
+
+  arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),ratiosL[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
+}
+}
+
+legend(75,95,c('48% match','24% match'),pch=16,col=colpal[2:1],pt.cex=2,box.lwd=2)
+
+legend(45.75,125,c('Winner-take-all','Linear summation'),lty=2:3,box.lwd=2)
+
+dev.off()
+
+}
+
+```
+
+```{r matchingdata, fig.cap="Contrast matching functions.
+Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('local/Figures/matchingdata.pdf')
+
+```
 
@@
 
-Figure showing model behaviour (four panels) and posterior weight distributions.
+```{r include=FALSE, results='hide'}
+
+# create text objects for Stan models
+
+CRFmodelstring = "
+  data {
+    int<lower=1> Nsubj ;
+    int<lower=1> Ntotal ;
+    real y[Ntotal] ;
+    real x[Ntotal] ;
+    real<lower=0> w[Ntotal] ;
+    int<lower=1> c[Ntotal] ;
+    int<lower=1> s[Ntotal] ;
+  }
+  parameters {
+    real<lower=1> Z[Nsubj] ;
+    real<lower=0> Rmax[Nsubj] ;
+    real<lower=0> wt[Nsubj] ;
+    real<lower=0> k[Nsubj] ;
+    real<lower=0> sigma ;
+    real<lower=1> Zmu ; 
+    real<lower=0> Rmaxmu ; 
+    real<lower=0> wtmu ; 
+    real<lower=0> kmu ; 
+    real<lower=0> Zsigma ;
+    real<lower=0> Rmaxsigma ;
+    real<lower=0> wtsigma ;
+    real<lower=0> ksigma ;
+    real<lower=0> nu ;
+  }
+  model {
+    Zmu ~ normal( 5 , 2 ) ;
+    Rmaxmu ~ normal( 1 , 0.5 ) ;
+    wtmu ~ normal( 1 , 0.5 ) ;
+    kmu ~ normal( 5 , 2 ) ;
+    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Rmaxsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wtsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    nu ~ exponential(1/30.0) ;
+    Z ~ normal( Zmu , Zsigma ) ; // vectorized
+    Rmax ~ normal( Rmaxmu , Rmaxsigma ) ; // vectorized
+    wt ~ normal( wtmu , wtsigma ) ; // vectorized
+    k ~ normal( kmu , ksigma ) ; // vectorized
+    for ( i in 1:Ntotal ) {
+
+    if (c[i]==1)  // monocular condition
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],2))/(Z[s[i]] + x[i])) ,
+                w[i]*sigma ) ;
+
+     else if (c[i]==2)  // binocular condition 
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*((pow(x[i],2))/(Z[s[i]] + x[i] + wt[s[i]]*x[i]) + (pow(x[i],2))/(Z[s[i]] + x[i] + wt[s[i]]*x[i]))),
+                w[i]*sigma ) ;
+
+     else if (c[i]==3)  // dichoptic condition
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*((pow(x[i],2))/(Z[s[i]] + x[i] + wt[s[i]]*48) + (pow(48,2))/(Z[s[i]] + 48 + wt[s[i]]*x[i]))),
+                w[i]*sigma ) ;
+
+     else if (c[i]==4)  // binocular cross condition 
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],2))/(Z[s[i]] + x[i] + wt[s[i]]*x[i])) ,
+                w[i]*sigma ) ;
+
+     else if (c[i]==5)  // dichoptic cross condition
+       y[i] ~ student_t( 
+                nu ,
+                k[s[i]] + (Rmax[s[i]]*(pow(x[i],2))/(Z[s[i]] + x[i] + wt[s[i]]*48)) ,
+                w[i]*sigma ) ;       
+    }
+  }
+
+  " # close quote for CRFmodelstring
+
+matchingmodelstring = "
+  data {
+    int<lower=1> Nsubj ;
+    int<lower=1> Ntotal ;
+    int correct[Ntotal] ;
+    real allcontrast[Ntotal] ;
+    real allref[Ntotal] ;
+    real allLratio[Ntotal] ;
+    real allRratio[Ntotal] ;    
+    int<lower=1> s[Ntotal] ;
+  }
+  parameters {
+    real<lower=0> Z[Nsubj] ;
+    real<lower=0> k[Nsubj] ;
+    real<lower=0> w[Nsubj] ;
+    real<lower=0> sigma ;
+    real<lower=0> Zmu ; 
+    real<lower=0> kmu ; 
+    real<lower=0> wmu ;     
+    real<lower=0> Zsigma ;
+    real<lower=0> ksigma ;
+    real<lower=0> wsigma ;
+    }
+  model {
+    Zmu ~ normal( 5 , 2 ) ;
+    wmu ~ normal( 1 , 0.5 ) ;
+    kmu ~ normal( 5 , 2 ) ;
+    sigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Zsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    ksigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    wsigma ~ uniform( 1.0E-3 , 1.0E+3 ) ;
+    Z ~ normal( Zmu , Zsigma ) ; // vectorized
+    k ~ normal( kmu , ksigma ) ; // vectorized
+    w ~ normal( wmu , wsigma ) ; // vectorized
+
+    for ( i in 1:Ntotal ) {
+
+      real standresp ;
+      real matchrespL ;
+      real matchrespR ;
+      real matchresp ;
+
+      standresp = 2 * pow(allref[i],2) / (Z[s[i]] + allref[i] + w[s[i]]*allref[i]);
+      matchrespL = pow(allLratio[i]*allcontrast[i],2) / (Z[s[i]] + allLratio[i]*allcontrast[i] + w[s[i]]*allRratio[i]*allcontrast[i]);
+      matchrespR = pow(allRratio[i]*allcontrast[i],2) / (Z[s[i]] + allRratio[i]*allcontrast[i] + w[s[i]]*allLratio[i]*allcontrast[i]);
+      matchresp = matchrespL + matchrespR;
+      correct[i] ~ bernoulli(((1 + erf((matchresp - standresp)/k[s[i]]))/2)*0.998 + 0.001) ;
+    }
+  }  
+  " # close quote for matchingmodelstring
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# do computational modelling
+
+if (processdata > 1){
+
+# settings for sampler 
+numSavedSteps <- 20000    # total number of MCMC steps
+adaptSteps = 1000  # Number of steps to "tune" the samplers
+burnInSteps = 2000 
+thinSteps <- 10
+nChains = 8
+ncores <- detectCores()/2  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
+options(mc.cores=ncores)
+
+if (!file.exists(paste0(datadir,'matchingdata.csv'))){
+osfnode <- 'ey7rg'  
+osfproject <- osf_retrieve_node(osfnode)
+matchingfiles <- osf_ls_files(osfproject,n_max=300)
+fid <- which(matchingfiles$name=='matchingdata.csv')
+osf_download(matchingfiles[fid,],datadir,progress=TRUE)
+}
+
+matchingdata <- read.csv(paste0(datadir,'matchingdata.csv'))
+
+matchingdatalist = list(correct = matchingdata$correct, allLratio = matchingdata$allLratio, allRratio = matchingdata$allRratio, allcontrast = matchingdata$allcontrast, allref = matchingdata$allref, s = matchingdata$Participant, Nsubj = max(matchingdata$Participant), Ntotal = nrow(matchingdata))
+
+for (participant in 1:30){
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',100+participant,'summary.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',100+participant,'summary.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
+
+d <- dir(datadir,pattern='*summary.RData',full.names=TRUE)
+
+tempmasksP <- array(0,dim=c(length(d),6,5))
+tempmeansP <- tempmasksP
+tempmasksE <- array(0,dim=c(length(d),64,6,5))
+tempmeansE <- tempmasksE
+tempmeansE2 <- tempmeansE
+tempmasksE2 <- tempmasksE
+
+  for (s in 1:length(d)){
+
+    load(d[s])
+
+  tempmasksP[s,,] <- cleanmasksP
+  tempmeansP[s,,] <- cleanmeansP
+  tempmeansE[s,,,] <- cleanmeansE
+  tempmasksE[s,,,] <- cleanmasksE
+  tempmeansE2[s,,,] <- cleanmeansE2
+  tempmasksE2[s,,,] <- cleanmasksE2
+
+  }
+  electrodeindices <- match(targetelectrodes,electrodes)-2
+
+  # THE DATA
+  condlist <- c(1,2,3,5,6)
+  contlist <- c(6,12,24,48,96)
+  y <- NULL
+  x <- NULL
+  c <- NULL
+  s <- NULL
+  w <- NULL
+  i <- 0
+  for (subj in 1:dim(tempmeansP)[1]){
+    for (cond in 1:length(condlist)){
+      for (cont in 1:length(contlist)){
+        dp <- abs(tempmeansP[subj,condlist[cond],cont])
+        if (is.na(dp)==0){
+          if (is.infinite(dp)==0){
+          i <- i + 1
+          x[i] <- contlist[cont]
+          y[i] <- dp
+          c[i] <- cond
+          s[i] <- subj
+          w[i] <- 1
+          }
+        }
+      }
+    }
+  }
+
+pupildatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
+
+  y <- NULL
+  x <- NULL
+  c <- NULL
+  s <- NULL
+  w <- NULL
+  i <- 0
+  for (subj in 1:dim(tempmeansE)[1]){
+    for (cond in 1:length(condlist)){
+      for (cont in 1:length(contlist)){
+        dp <- abs(mean(tempmeansE[subj,electrodeindices,condlist[cond],cont]))
+        if (is.na(dp)==0){
+          if (is.infinite(dp)==0){
+            i <- i + 1
+            x[i] <- contlist[cont]
+            y[i] <- dp
+            c[i] <- cond
+            s[i] <- subj
+            w[i] <- 1
+          }
+        }
+      }
+    }
+  }
+
+  EEG1Fdatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
+
+  y <- NULL
+  x <- NULL
+  c <- NULL
+  s <- NULL
+  w <- NULL
+  i <- 0
+  for (subj in 1:dim(tempmeansE)[1]){
+    for (cond in 1:length(condlist)){
+      for (cont in 1:length(contlist)){
+        dp <- abs(mean(tempmeansE2[subj,electrodeindices,condlist[cond],cont]))
+        if (is.na(dp)==0){
+          if (is.infinite(dp)==0){
+            i <- i + 1
+            x[i] <- contlist[cont]
+            y[i] <- dp
+            c[i] <- cond
+            s[i] <- subj
+            w[i] <- 1
+          }
+        }
+      }
+    }
+  }
+
+  EEG2Fdatalist = list(x = x, y = y, s = s, w = w, c = c, Nsubj = max(s), Ntotal = length(y))
+
+# Translate Stan models to C++ and compile to DSO:
+matchingmodel <- stan_model(model_code=matchingmodelstring)  
+CRFmodel <- stan_model(model_code=CRFmodelstring)
+
+# Get MC sample of posterior:
+pupilsamples <- sampling(object=CRFmodel, 
+                    data = pupildatalist, 
+                    chains = nChains,
+                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
+                    warmup = burnInSteps, 
+                    thin = thinSteps,
+                    cores = getOption("mc.cores", 1L))
+
+EEG1Fsamples <- sampling(object=CRFmodel, 
+                    data = EEG1Fdatalist, 
+                    chains = nChains,
+                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
+                    warmup = burnInSteps, 
+                    thin = thinSteps,
+                    cores = getOption("mc.cores", 1L))
+
+EEG2Fsamples <- sampling(object=CRFmodel, 
+                    data = EEG2Fdatalist, 
+                    chains = nChains,
+                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
+                    warmup = burnInSteps, 
+                    thin = thinSteps,
+                    cores = getOption("mc.cores", 1L))
+
+matchingsamples <- sampling(object=matchingmodel, 
+                    data = matchingdatalist, 
+                    chains = nChains,
+                    iter = (ceiling(numSavedSteps/nChains)*thinSteps+burnInSteps), 
+                    warmup = burnInSteps, 
+                    thin = thinSteps,
+                    cores = getOption("mc.cores", 1L))
+
+save(file=paste0(datadir,'modeloutput.RData'),list=c('pupilsamples','EEG1Fsamples','EEG2Fsamples','matchingsamples'))
+
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# create figure containing modelling results
+
+if (!file.exists(paste0(datadir,'modeloutput.RData'))){
+osfnode <- '2qu6y'  
+osfproject <- osf_retrieve_node(osfnode)
+osffilesP <- osf_ls_files(osfproject,n_max=300)
+fid <- which(osffilesP$name=='modeloutput.RData')
+osf_download(osffilesP[fid,],datadir,progress=TRUE)
+}
+
+  load(paste0(datadir,'modeloutput.RData'))
+
+  pupilweightpop <- pupilsamples@sim$samples[[1]]$wtmu
+  pupilW <- median(pupilsamples@sim$samples[[1]]$wtmu)
+  pupilZ <- median(pupilsamples@sim$samples[[1]]$Zmu)
+  pupilK <- median(pupilsamples@sim$samples[[1]]$kmu)
+  pupilRmax <- median(pupilsamples@sim$samples[[1]]$Rmaxmu)
+
+  EEGweightpop <- EEG1Fsamples@sim$samples[[1]]$wtmu
+  EEGW <- median(EEG1Fsamples@sim$samples[[1]]$wtmu)
+  EEGZ <- median(EEG1Fsamples@sim$samples[[1]]$Zmu)
+  EEGK <- median(EEG1Fsamples@sim$samples[[1]]$kmu)
+  EEGRmax <- median(EEG1Fsamples@sim$samples[[1]]$Rmaxmu)
+
+  EEG2weightpop <- EEG2Fsamples@sim$samples[[1]]$wtmu
+  EEG2W <- median(EEG2Fsamples@sim$samples[[1]]$wtmu)
+  EEG2Z <- median(EEG2Fsamples@sim$samples[[1]]$Zmu)
+  EEG2K <- median(EEG2Fsamples@sim$samples[[1]]$kmu)
+  EEG2Rmax <- median(EEG2Fsamples@sim$samples[[1]]$Rmaxmu)
+
+  matchingweightpop <- matchingsamples@sim$samples[[1]]$wmu
+  matchingW <- median(matchingsamples@sim$samples[[1]]$wmu)
+  matchingZ <- median(matchingsamples@sim$samples[[1]]$Zmu)
+  matchingK <- median(matchingsamples@sim$samples[[1]]$kmu)
+
+  if (processdata > 0){
+
+postscript('posteriors.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+plotlims <- c(-48,12,0,0.3) 
+ticklocsx <- seq(-48,12,12)    
+ticklocsy <- seq(0,0.3,0.1)    
+ticklabelsx <- c('1/256','1/64','1/16','1/4','1','4')        
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+
+title(xlab="w", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Probability", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+a <- density(20*log10(pupilweightpop),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=colpal[3],border=NA)
+
+a <- density(20*log10(EEGweightpop),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=colpal[4],border=NA)
+
+a <- density(20*log10(EEG2weightpop),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=colpal[5],border=NA)
+
+a <- density(20*log10(matchingweightpop),from=-48,to=12)   
+polygon(c(-48,a$x,12), c(0,a$y,0), col=colpal[6],border=NA)
+
+prior <- dnorm(10^((-48:12)/20),1,0.5)
+prior <- 0.3*prior/max(prior)
+lines(-48:12,prior)
+
+lines(20*log10(c(mean(pupilW),mean(pupilW))),c(0,0.3),lwd=3,col=colpal[3])
+lines(20*log10(c(mean(EEGW),mean(EEGW))),c(0,0.3),lwd=3,col=colpal[4])
+lines(20*log10(c(mean(EEG2W),mean(EEG2W))),c(0,0.3),lwd=3,col=colpal[5])
+lines(20*log10(c(mean(matchingW),mean(matchingW))),c(0,0.3),lwd=3,col=colpal[6])
+
+legend(-48,0.3,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')
+
+text(9,0.28,'(e)',cex=1.25,adj=0.5)
+
+dev.off()
+
+finex <- 10^(seq(20*log10(6),20*log10(96),length=100)/20)
+
+w <- pupilW
+Z <- pupilZ
+k <- pupilRmax
+n <- pupilK
+q <- 2
+modelA <- matrix(0,nrow=6,ncol=length(finex))
+modelB <- matrix(0,nrow=6,ncol=length(finex))
+# mon condition
+R <- 0
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[1,] <- k*(Lresp + Rresp) + n
+modelB[1,] <- n
+
+# bin condition
+R <- finex
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[2,] <- k*(Lresp + Rresp) + n
+modelB[2,] <- n
+
+# dich condition
+R <- 48
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[3,] <- k*(Lresp + Rresp) + n
+modelB[3,] <- n
+
+# mon X condition
+R <- 0
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[4,] <- n
+modelB[4,] <- k*(Lresp + Rresp) + n
+
+# bin X condition
+R <- finex
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[5,] <- k*(Lresp) + n 
+modelB[5,] <- k*(Rresp) + n
+
+# dich X condition
+L <- finex
+R <- 48
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[6,] <- k*(Lresp) + n 
+modelB[6,] <- k*(Rresp) + n
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+plotlims <- c(15,40,0,0.04)
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklocsy <- seq(0,0.04,0.01)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript(paste("CRF1p.ps",sep=''), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,2,3,6)
+for (cond in 1:4){lines(20*log10(finex),modelA[condlist[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)}
+
+legend(21,0.04,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.038,'(a)',adj=0.5,cex=2.5)
+
+dev.off()
+
+w <- EEGW
+Z <- EEGZ
+k <- EEGRmax
+n <- EEGK
+q <- 2
+modelA <- matrix(0,nrow=6,ncol=length(finex))
+modelB <- matrix(0,nrow=6,ncol=length(finex))
+# mon condition
+R <- 0
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[1,] <- k*(Lresp + Rresp) + n
+modelB[1,] <- n
+
+# bin condition
+R <- finex
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[2,] <- k*(Lresp + Rresp) + n
+modelB[2,] <- n
+
+# dich condition
+R <- 48
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[3,] <- k*(Lresp + Rresp) + n
+modelB[3,] <- n
+
+# mon X condition
+R <- 0
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[4,] <- n
+modelB[4,] <- k*(Lresp + Rresp) + n
+
+# bin X condition
+R <- finex
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[5,] <- k*(Lresp) + n 
+modelB[5,] <- k*(Rresp) + n
+
+# dich X condition
+L <- finex
+R <- 48
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[6,] <- k*(Lresp) + n 
+modelB[6,] <- k*(Rresp) + n
+
+plotlims <- c(15,40,0,0.8)  
+ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("CRF1e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 2Hz (µV) ", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,2,3,6)
+for (cond in 1:4){lines(20*log10(finex),modelA[condlist[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)}
+
+legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.75,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+w <- EEG2W
+Z <- EEG2Z
+k <- EEG2Rmax
+n <- EEG2K
+q <- 2
+modelA <- matrix(0,nrow=6,ncol=length(finex))
+modelB <- matrix(0,nrow=6,ncol=length(finex))
+# mon condition
+R <- 0
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[1,] <- k*(Lresp + Rresp) + n
+modelB[1,] <- n
+
+# bin condition
+R <- finex
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[2,] <- k*(Lresp + Rresp) + n
+modelB[2,] <- n
+
+# dich condition
+R <- 48
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[3,] <- k*(Lresp + Rresp) + n
+modelB[3,] <- n
+
+# mon X condition
+R <- 0
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[4,] <- n
+modelB[4,] <- k*(Lresp + Rresp) + n
+
+# bin X condition
+R <- finex
+L <- finex
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[5,] <- k*(Lresp) + n 
+modelB[5,] <- k*(Rresp) + n
+
+# dich X condition
+L <- finex
+R <- 48
+Lresp <- (L^q)/(Z + L + w*R)
+Rresp <- (R^q)/(Z + R + w*L)
+modelA[6,] <- k*(Lresp) + n 
+modelB[6,] <- k*(Rresp) + n
+
+plotlims <- c(15,40,0,0.8)  
+ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("CRF2e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)    
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 4Hz (µV) ", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,2,3,6)
+for (cond in 1:4){lines(20*log10(finex),modelA[condlist[cond],], col=colpal[condlist[cond]], lwd=3, cex=0.5)}
+
+legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.75,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+# very finely sampled ratios to produce smooth curves
+ratiosL <- seq(0,1,length=100)
+ratiosR <- rep(1,100)
+
+params <- c(2,matchingZ,matchingW)
+
+binmodel <- function(L,R,p){
+  # this is the two-stage model with a linear denominator and saturation constant
+  stage1L <- (L^p[1])/(p[2] + L + p[3]*R)
+  stage1R <- (R^p[1])/(p[2] + R + p[3]*L)
+  resp <- stage1L + stage1R
+
+  return(resp)}
+
+getmatch <- function(L,R,ratios,p){
+  standardresp <- binmodel(L,R,p)
+  contrast <- 0
+  matchresp <- 0
+  while (matchresp<standardresp){
+    contrast <- contrast + 0.1
+    matchresp <- binmodel(contrast*ratios[1],contrast*ratios[2],p)
+  }
+
+  return(contrast)}
+
+postscript("matchingmodel.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+plotlims <- c(0,125,0,125)  
+ticklocs <- seq(0,125,25)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocs, side = 1, at=ticklocs)     # add the tick labels
+mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
+title(xlab="Right eye contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Left eye contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+standardcontrast <- 48
+
+matchlist <- NULL
+for (n in 1:length(ratiosL)){
+  matchlist[n] <- getmatch(standardcontrast,standardcontrast,c(ratiosL[n],ratiosR[n]),params)
+}
+
+tempx <- c(matchlist*ratiosL, matchlist[100:1])
+tempy <- c(matchlist, matchlist[100:1]*ratiosL[100:1])
+
+lines(tempx,tempy,lwd=3,col=colpal[2])
+lines(c(0,standardcontrast),c(standardcontrast,standardcontrast),lty=2)
+lines(c(standardcontrast,standardcontrast),c(0,standardcontrast),lty=2)
+lines(c(0,2*standardcontrast),c(2*standardcontrast,0),lty=3)
+
+standardcontrast <- 24
+
+matchlist <- NULL
+for (n in 1:length(ratiosL)){
+  matchlist[n] <- getmatch(standardcontrast,standardcontrast,c(ratiosL[n],ratiosR[n]),params)
+}
+
+tempx <- c(matchlist*ratiosL, matchlist[100:1])
+tempy <- c(matchlist, matchlist[100:1]*ratiosL[100:1])
+lines(tempx,tempy,lwd=3,col=colpal[1])
+
+lines(c(0,standardcontrast),c(standardcontrast,standardcontrast),lty=2)
+lines(c(standardcontrast,standardcontrast),c(0,standardcontrast),lty=2)
+lines(c(0,2*standardcontrast),c(2*standardcontrast,0),lty=3)
+
+legend(62,95,c('48% match','24% match'),col=colpal[2:1],lwd=3,pt.cex=2,box.lwd=2)
+
+legend(45,125,c('Winner-take-all','Linear summation'),lty=2:3,box.lwd=2)
+
+text(10,117.5,'(d)',adj=0.5,cex=2.5)
+
+dev.off()
+
+  PostScriptTrace('CRF1p.ps')
+  p1 <- readPicture('CRF1p.ps.xml')
+  PostScriptTrace('CRF1e.ps')
+  p2 <- readPicture('CRF1e.ps.xml')
+  PostScriptTrace('CRF2e.ps')
+  p3 <- readPicture('CRF2e.ps.xml')
+  PostScriptTrace('matchingmodel.ps')
+  p4 <- readPicture('matchingmodel.ps.xml')
+  PostScriptTrace('posteriors.ps')
+  p5 <- readPicture('posteriors.ps.xml')
+
+    for (n in 1:length(p5@paths)){
+    temp <- class(p5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p5@paths[n]$path@rgb))<765){p5@paths[n]$path@rgb <- addalpha(p5@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 10, width = 20)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  grid.picture(p1,x=0.125,y=0.75,width=0.25,height=1)
+  grid.picture(p2,x=0.375,y=0.75,width=0.25,height=1)
+  grid.picture(p3,x=0.125,y=0.25,width=0.25,height=1)
+  grid.picture(p4,x=0.375,y=0.25,width=0.25,height=1)
+
+  grid.picture(p5,x=0.75,y=0.5,width=0.5,height=1)
+
+  dev.off()
+
+  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','posteriors.ps'))
+  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','posteriors.ps.xml'))
+
+}
+
+```
+
+```{r modelfigure, fig.cap="Summary of computational modelling.
+Panels (a-d) show model behaviour for our four main data set, pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d).
+Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
+The black curve shows the (scaled) prior distribution for the weight parameter.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('local/Figures/modelfigure.pdf')
+
+```
+
+```{r paramtable, echo=FALSE}
+
+exptnames <- c('Pupillometry','EEG 1F', 'EEG 2F', 'Matching')
+zlist <- c(pupilZ,EEGZ,EEG2Z,matchingZ)
+klist <- c(pupilK,EEGK,EEG2K,matchingK)
+wlist <- c(pupilW,EEGW,EEG2W,matchingW)
+Rlist <- c(round(c(pupilRmax,EEGRmax,EEG2Rmax),5),'-')
+tabledata <- data.frame(exptnames,round(zlist,digits=2),round(klist,digits=2),round(wlist,digits=2),Rlist)
+
+colnames(tabledata) <- c('Data set','Z','k','w','Rmax')
+kable(tabledata, align='lcccc',caption = 'Summary of median parameter values.')
+
+```
 

### 2022-09-23 manuscript.tex
First fully working version of code for testing

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Different rules for binocular combination of luminance in cortical and subcortical pathways},
  pdfauthor={Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Different rules for binocular combination of luminance in cortical and subcortical pathways}
\author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
\date{2022-09-22}

\begin{document}
\maketitle

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{apparatus-stimuli}{%
\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

Baker (2021)

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{experiment-1}{%
\subsection{Experiment 1}\label{experiment-1}}

\begin{figure}

{\centering \includegraphics{local/Figures/pupildata}

}

\caption{Summary of pupillometry results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Panel (b) shows the average Fourier spectrum. Panels (c,d) show contrast response functions at 2Hz for different conditions. Panel (e) shows contrast response functions at 1.6Hz for three conditions. Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
\end{figure}

\begin{figure}

{\centering \includegraphics{local/Figures/EEGdata}

}

\caption{Summary of EEG results for N=30 participants. Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot. Panel (b) shows the average Fourier spectrum, and inset scalp distributions. Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2. Panels (c,d) show contrast response functions at 2Hz for different conditions. Panel (e) shows contrast response functions at 1.6Hz for three conditions. Panels (f-h) are in the same format but for the second harmonic responses. Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
\end{figure}

\hypertarget{experiment-2}{%
\subsection{Experiment 2}\label{experiment-2}}

\begin{figure}

{\centering \includegraphics{local/Figures/TFdata}

}

\caption{Binocular facilitation at different temporal frequencies. Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity). Panel (b) shows the response at each stimulation frequency for monocular (red) and binocular (blue) presentation. Panel (c) shows the ratio of binocular to monocular responses. Error bars and shaded regions indicate bootstrapped standard errors.}\label{fig:TFdata}
\end{figure}

\hypertarget{experiment-3}{%
\subsection{Experiment 3}\label{experiment-3}}

\begin{figure}

{\centering \includegraphics{local/Figures/matchingdata}

}

\caption{Contrast matching functions. Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed). Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.}\label{fig:matchingdata}
\end{figure}

\hypertarget{computational-modelling}{%
\subsection{Computational modelling}\label{computational-modelling}}

\begin{figure}

{\centering \includegraphics{local/Figures/modelfigure}

}

\caption{Summary of computational modelling. Panels (a-d) show model behaviour for our four main data set, pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d). Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits. The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis). The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
\end{figure}

\begin{table}

\caption{\label{tab:paramtable}Summary of median parameter values.}
\centering
\begin{tabular}[t]{l|c|c|c|c}
\hline
Data set & Z & k & w & Rmax\\
\hline
Pupillometry & 2.73 & 0.01 & 0.60 & 0.00022\\
\hline
EEG 1F & 2.09 & 0.15 & 0.02 & 0.00336\\
\hline
EEG 2F & 3.39 & 0.07 & 0.02 & 0.00312\\
\hline
Matching & 0.22 & 5.06 & 0.09 & -\\
\hline
\end{tabular}
\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
Baker DH. 2021. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}

\end{CSLReferences}

\end{document}

### 2022-09-23 analysePP_EEG.R

@@ -1,891 +1,0 @@
-# WARNING: Each participant analysed will download around 1.3GB of data locally!
-# this script downloads and analyses pupillometry and EEG data 
-
-participant <- 'P310'
-outputplot <- 2    # 0 means plot to plot window, 1 means separate pdfs, 2 means combined pdf (via ps files)
-
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
-EEGdir <- 'local/EEG/'
-if (!file.exists(EEGdir)){dir.create(EEGdir)}   # create a local directory to store EEG data
-PPdir <- 'local/Pupil/'
-if (!file.exists(PPdir)){dir.create(PPdir)}   # create a local directory to store pupil data
-Pydir <- 'local/Psychopy/'
-if (!file.exists(Pydir)){dir.create(Pydir)}   # create a local directory to store Psychopy output
-figdir <- 'local/Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/Data/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
-
-packagelist <- c('signal','remotes','tictoc','grImport','tiff')
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
-if (packagelist[!'osfr' %in% installed.packages()[,1]]){remotes::install_github("centerforopenscience/osfr")}
-packagelist <- c(packagelist,'osfr')
-toinstall <- packagelist[which(!packagelist %in% (.packages()))]
-invisible(lapply(toinstall,library,character.only=TRUE))
-
-tic()
-
-if (!file.exists(paste(datadir,participant,'summary.RData',sep=''))){   # only download and process data if this has not been done already for this participant
-
[…]

### 2022-09-23 analysepilotdata.R

@@ -1,387 +1,0 @@
-library(signal)
-
-outputplot <- 0
-
-alltargets <- array(0,dim=c(2,2,60))
-allmasks <- alltargets
-allwaveforms <- array(0,dim=c(2,2,60,1200))
-allspectra <- allwaveforms
-timeseq <- seq(1/120,10,length.out=120*10)
-targetindex <- (2*10)+1
-maskindex <- (1.6*10)+1
-
-for (block in 1:2){
-infofile <- read.csv(paste('~/Google Drive/Current work/Research/Melatonin/DHBcrf/Block',block,'/info.csv',sep=''))
-pupilstarttime <- as.numeric(as.character(infofile[4,2]))
-localstarttime <- as.numeric(as.character(infofile[5,2]))
-
-if (block==1){psychoutput <- read.csv('~/Google Drive/Current work/Research/Melatonin/DHBcrf/Block1/DHB_CRFstudy_2019_Aug_23_1626.csv')}
-if (block==2){psychoutput <- read.csv('~/Google Drive/Current work/Research/Melatonin/DHBcrf/Block2/DHB_CRFstudy_2019_Aug_23_1643.csv')}
-
-trialtimes <- psychoutput$trialonset - pupilstarttime
-condorder <- psychoutput$condition
-
-pdata <- read.csv(paste('~/Google Drive/Current work/Research/Melatonin/DHBcrf/Block',block,'/pupil_positions.csv',sep=''))
-pdata2 <- pdata[,c(1,3,4,14)]
-pdata2[,1] <- pdata2[,1] - localstarttime
-pdata2 <- pdata2[which(pdata2[,3]>0.2),]
-
-for (eye in 1:2){
-eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]
-for (cond in 1:60){
-a <- which(eyedata[,1]>trialtimes[cond]+2)
-b <- which(eyedata[,1]<(trialtimes[cond]+12))
-i <- intersect(a,b)
-trial <- eyedata[i,]
-trial[,1] <- trial[,1] - trial[1,1]
-if (nrow(trial)>3){
-resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
-fspec <- (fft(resampled)/length(resampled))
-alltargets[block,eye,condorder[cond]] <- fspec[targetindex]
-allmasks[block,eye,condorder[cond]] <- fspec[maskindex]
-allwaveforms[block,eye,condorder[cond],] <- resampled - mean(resampled)
[…]

### 2022-09-23 averagesubjects.R

@@ -1,558 +1,0 @@
-
-
-outputplot <- 2    # 0 means plot to plot window, 1 means separate pdfs, 2 means combined pdf (via ps files)
-
-
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
-figdir <- 'local/Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/Data/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
-EEGdir <- 'local/EEG/'
-if (!file.exists(EEGdir)){dir.create(EEGdir)}   # create a local directory to store EEG data
-
-packagelist <- c('tictoc','grImport','tiff')
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
-toinstall <- packagelist[which(!packagelist %in% (.packages()))]
-invisible(lapply(toinstall,library,character.only=TRUE))
-
-tic()
-
-d <- dir(datadir,pattern='summary.RData')
-
-tempmasksP <- array(0,dim=c(length(d),6,5))
-tempmeansP <- tempmasksP
-tempmasksE <- array(0,dim=c(length(d),64,6,5))
-tempmeansE <- tempmasksE
-tempmeansE2 <- tempmeansE
-tempmasksE2 <- tempmasksE
-tempspectraP <- array(0,dim=c(length(d),60,300))
-tempspectraE <- array(0,dim=c(length(d),64,60,300))
-
-for (s in 1:length(d)){
-load(paste(datadir,d[s],sep=''))
-  
-  tempmasksP[s,,] <- cleanmasksP
-  tempmeansP[s,,] <- cleanmeansP
-  tempspectraP[s,,] <- meanspectraP
-  tempspectraE[s,,,] <- meanspectraE
-  tempmeansE[s,,,] <- cleanmeansE
-  tempmasksE[s,,,] <- cleanmasksE
-  tempmeansE2[s,,,] <- cleanmeansE2
-  tempmasksE2[s,,,] <- cleanmasksE2
-}
[…]

### 2022-09-23 infertriggers.R

@@ -1,190 +1,0 @@
-# script to reverse engineer trigger timing using coincidence of blinks between frontal electrodes and eye tracking data
-# DHB 12/10/19
-
-# first section is proof of concept on a participant without missing triggers
-# align eye tracking and EEG data based on blinks, then check if re-aligned triggers coincide
-
-participant <- 'P304'
-block <- 1
-
-packagelist <- c('signal','tictoc','R.utils')
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
-toinstall <- packagelist[which(!packagelist %in% (.packages()))]
-invisible(lapply(toinstall,library,character.only=TRUE))
-
-
-localdir <- 'local/'
-EEGdir <- '/local/EEG/'
-PPdir <- 'local/Pupil/'
-Pydir <- 'local/Psychopy/'
-figdir <- 'local/Figures/'
-datadir <- 'local/Data/'
-
-
-infofile <- read.csv(paste(PPdir,participant,'_S',block,'_info.csv',sep=''))
-pupilstarttime <- as.numeric(as.character(infofile[4,2]))
-localstarttime <- as.numeric(as.character(infofile[5,2]))
-
-psychopyfiles <- dir(path=Pydir,pattern=participant)
-psychoutput <- read.csv(paste(Pydir,psychopyfiles[block],sep=''))
-
-trialtimes <- psychoutput$trialonset - pupilstarttime
-condorder <- psychoutput$condition
-
-EEGdata <- read.csv(paste(EEGdir,participant,'_S',block,'_EEG.gz',sep=''))
-electrodes <- colnames(EEGdata)
-
-legaltriggers <- 1
-triggertimes <- NULL
-counter <- 0
-lasttrigger <- -10000
-for (n in 1:nrow(EEGdata)){
-  if(EEGdata$Trigger[n] %in% legaltriggers){
-    if(n>(lasttrigger+10000)){
-      counter <- counter + 1
-      triggertimes[counter] <- n
-      lasttrigger <- n
-    }}
-}
-
[…]

### 2022-09-23 renameandupload.R

@@ -1,4 +1,3 @@
-
 # packagelist <- c('remotes','tictoc','utils')
 # missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
 # if (length(missingpackages)>0){install.packages(missingpackages)}
@@ -7,20 +6,77 @@
 # toinstall <- packagelist[which(!packagelist %in% (.packages()))]
 # invisible(lapply(toinstall,library,character.only=TRUE))
 
-
-
-d <- dir('~/Desktop/P101/')
-p <- getwd()
-setwd('~/Desktop/P101/')
-tar(tarfile='P101.tar',files=d,compression='gzip')
-setwd(p)
+library(osfr)
 
 osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')
 osfproject <- osf_retrieve_node("x8u4v")
 componentlist <- osf_ls_nodes(osfproject)
-datafilesonOSF <- osf_ls_files(osfproject,n_max=300)
 
-if (!pmatch('P101.tar',datafilesonOSF$name,nomatch=0)){
-  osf_upload(osfproject,'~/Desktop/P101/P101.tar',progress=TRUE)
+p <- getwd()
+
+for (s in 16:30){
+  
+  subj <- paste0('P',s+100)
+  
+  subjdir <- paste0('/Users/danbaker/Desktop/Pupildata/',subj)
+  if (!file.exists(subjdir)){dir.create(subjdir)}
+  
+  eegfiles <- dir('/Volumes/DANLAB/Eyetracking/Federico/Exp1/EEG/Zipped',pattern=paste0(subj,'_*'),full.names=TRUE)
+  file.copy(eegfiles,subjdir)
+  
+  setwd(subjdir)
+  
+  d <- dir(subjdir)
+  for (n in 1:length(d)){file.rename(d[n],paste0(unlist(strsplit(d[n],'[.]'))[1],'.csv.gz'))}
+  
+  PPfiles <- dir('/Volumes/DANLAB/Eyetracking/Federico/Exp1/Psychopy/CSV/',pattern=paste0(subj,'_*'),full.names=TRUE)
+  file.copy(PPfiles,subjdir)
[…]

### 2022-09-23 renameanduploadpilot.R

@@ -1,127 +1,0 @@
-# script to collate the various files and upload to OSF
-# checks which files already exist and which need to be uploaded
-# important to run the matlab script to convert EEG data first
-
-participant <- 'P310'
-sourcedir <- '~/Desktop/Pupildata/'
-
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
-EEGdir <- 'local/EEG/'
-if (!file.exists(EEGdir)){dir.create(EEGdir)}   # create a local directory to store EEG data
-PPdir <- 'local/Pupil/'
-if (!file.exists(PPdir)){dir.create(PPdir)}   # create a local directory to store pupil data
-Pydir <- 'local/Psychopy/'
-if (!file.exists(Pydir)){dir.create(Pydir)}   # create a local directory to store Psychopy output
-figdir <- 'local/Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/Data/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
-
-packagelist <- c('remotes','tictoc','utils')
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
-if (packagelist[!'osfr' %in% installed.packages()[,1]]){remotes::install_github("centerforopenscience/osfr")}
-packagelist <- c(packagelist,'osfr')
-toinstall <- packagelist[which(!packagelist %in% (.packages()))]
-invisible(lapply(toinstall,library,character.only=TRUE))
-
-tic()
-
-my_wd <- getwd() # save your current working directory path
-
-# move EEG files to the correct place and rename
-d <- dir(paste(sourcedir,'EEG/',participant,sep=''),pattern='*.csv.gz')
-if (length(d)){
-for (n in 1:length(d)){
[…]

### 2022-09-24 manuscript.Rmd
Minor bug fixes

@@
 # 2 - average data across participants, do bootstrapping and modelling
-# 3 - download all raw data and analyse (requires XGB of storage)
+# 3 - download all raw data and analyse (requires 48GB of storage)
 
@@
 
+         if (!file.exists(paste0(datadir,'headerfile.csv'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'x8u4v'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='headerfile.csv')
+          osf_download(osffiles[fid,],datadir,progress=TRUE)
+          }
+
+  hdata <- read.csv(paste0(datadir,'headerfile.csv'))
+
 for (participant in 1:30){
-         # if the tar file of this participant's data doesn't exist
+         # if the summary file of this participant's data doesn't exist
          if (!file.exists(paste0(datadir,'P',100+participant,'summary.RData'))){
@@
 }
-
-          if (!file.exists(paste0(datadir,'headerfile.csv'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '2qu6y'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',100+participant,'headerfile.csv'))
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-          }
-
-  hdata <- read.csv(paste0(datadir,'headerfile.csv'))
 
@@
 filt <- butter(3,0.083)
-filtwaveP <- filter(filt, meanwavesP)
-filtU <- filter(filt,meanwavesPCI[1,])
-filtL <- filter(filt,meanwavesPCI[2,])
+filtwaveP <- signal::filter(filt, meanwavesP)
+filtU <- signal::filter(filt,meanwavesPCI[1,])
+filtL <- signal::filter(filt,meanwavesPCI[2,])
 polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
@@
 
+         if (!file.exists(paste0(datadir,'headerfile.csv'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'x8u4v'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='headerfile.csv')
+          osf_download(osffiles[fid,],datadir,progress=TRUE)
+          } 
 hdata <- read.csv(paste0(datadir,'headerfile.csv'))
@@
 filt <- butter(3,0.083*0.12)
-filtwaveE <- filter(filt, meanwavesE)
-filtU <- filter(filt,meanwavesECI[1,])
-filtL <- filter(filt,meanwavesECI[2,])
+filtwaveE <- signal::filter(filt, meanwavesE)
+filtU <- signal::filter(filt,meanwavesECI[1,])
+filtL <- signal::filter(filt,meanwavesECI[2,])
 polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
@@
         # then unzip the tar file
-        untar(paste0(rawdir,'P',150+participant,'.tar'),exdir=paste0(rawdir,'P',100+participant))
+        untar(paste0(rawdir,'P',150+participant,'.tar'),exdir=paste0(rawdir,'P',150+participant))
 
@@
       for (participant in 1:12){
-
-    for (participant in 1:30){
-         # if the tar file of this participant's data doesn't exist
+         # if the summary file of this participant's data doesn't exist
          if (!file.exists(paste0(datadir,'P',150+participant,'summary.RData'))){
@@
           osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name==paste0('P',100+participant,'summary.RData'))
+          fid <- which(osffilesP$name==paste0('P',150+participant,'summary.RData'))
           osf_download(osffilesP[fid,],datadir,progress=TRUE)
@@
       }
+
+  for (participant in 1:12){
 

### 2022-09-24 renameandupload.R

@@ -8,13 +8,13 @@
 
 library(osfr)
 
-osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')
+osf_auth(token = 'PRIVATETOKENGOESHERE')
 osfproject <- osf_retrieve_node("x8u4v")
 componentlist <- osf_ls_nodes(osfproject)
 
 p <- getwd()
 
-for (s in 16:30){
+for (s in 1:30){
   
   subj <- paste0('P',s+100)
   
@@ -57,7 +57,7 @@ componentlist <- osf_ls_nodes(osfproject)
 
 p <- getwd()
 
-for (s in 2:12){
+for (s in 1:12){
   
   subj <- paste0('P',s+150)
   

### 2022-09-25 manuscript.Rmd
Update manuscript.Rmd

@@
 
-knitr::include_graphics('local/Figures/pupildata.pdf')
+knitr::include_graphics(paste0(figdir,'pupildata.pdf'))
 
@@
 
-knitr::include_graphics('local/Figures/EEGdata.pdf')
+knitr::include_graphics(paste0(figdir,'EEGdata.pdf'))
 
@@
 
-knitr::include_graphics('local/Figures/TFdata.pdf')
+knitr::include_graphics(paste0(figdir,'TFdata.pdf'))
 
@@
 
+save(file=paste0(datadir,'meanmatching.RData'),list=c('meanthresh','SEthresh','allthresh'))
+
+}
+
+if (processdata > 0){
+
+load(paste0(datadir,'meanmatching.RData'))
+
 pdf(paste0(figdir,"matchingdata.pdf"), bg="transparent", height = 5.5, width = 5.5)
@@
 
-knitr::include_graphics('local/Figures/matchingdata.pdf')
+knitr::include_graphics(paste0(figdir,'matchingdata.pdf'))
 
@@
 # settings for sampler 
-numSavedSteps <- 20000    # total number of MCMC steps
-adaptSteps = 1000  # Number of steps to "tune" the samplers
-burnInSteps = 2000 
+numSavedSteps <- 100000    # total number of MCMC steps
+adaptSteps <- 1000  # Number of steps to "tune" the samplers
+burnInSteps <- 2000 
 thinSteps <- 10
-nChains = 8
+nChains <- 8
 ncores <- detectCores()/2  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
@@
 
-plotlims <- c(-48,12,0,0.3) 
+plotlims <- c(-48,12,0,0.5) 
 ticklocsx <- seq(-48,12,12)    
-ticklocsy <- seq(0,0.3,0.1)    
+ticklocsy <- seq(0,0.5,0.1)    
 ticklabelsx <- c('1/256','1/64','1/16','1/4','1','4')        
@@
 
-legend(-48,0.3,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')
-
-text(9,0.28,'(e)',cex=1.25,adj=0.5)
+legend(-48,0.5,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')
+
+text(9,0.48,'(i)',cex=1.25,adj=0.5)
 
@@
 par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
 axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)    
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
 title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
@@
 
-text(17,0.038,'(a)',adj=0.5,cex=2.5)
+text(17,0.038,'(e)',adj=0.5,cex=2.5)
 
@@
 
-legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.75,'(b)',adj=0.5,cex=2.5)
+# legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.75,'(f)',adj=0.5,cex=2.5)
 
@@
 
-legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.75,'(c)',adj=0.5,cex=2.5)
+# legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.75,'(g)',adj=0.5,cex=2.5)
 
@@
 
+text(10,117.5,'(h)',adj=0.5,cex=2.5)
+
+dev.off()
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Averagedata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(file=paste0(datadir,'Averagedata.RData'))
+
+plotlims <- c(15,40,0,0.03) 
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("pdata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+cond <- 6
+  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+
+legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(a)',adj=0.5,cex=2.5)
+
+dev.off()
+
+plotlims <- c(15,40,0,0.8)  
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("edata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+cond <- 6
+  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+
+# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("edata2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+cond <- 6
+  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+
+# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.75,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+         if (!file.exists(paste0(datadir,'meanmatching.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='meanmatching.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(paste0(datadir,'meanmatching.RData'))
+
+postscript("matchingdata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+plotlims <- c(0,125,0,125)  
+ticklocs <- seq(0,125,25)   
+ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
+ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocs, side = 1, at=ticklocs)     # add the tick labels
+mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
+title(xlab="Right eye contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Left eye contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(0,24),c(24,24),lty=2)
+lines(c(0,48),c(48,48),lty=2)
+lines(c(24,24),c(0,24),lty=2)
+lines(c(48,48),c(0,48),lty=2)
+lines(c(0,96),c(96,0),lty=3)
+lines(c(0,48),c(48,0),lty=3)
+
+for (matchlev in 1:2){
+lines(ratiosR*10^(meanthresh[matchlev,]/20),ratiosL*10^(meanthresh[matchlev,]/20),pch=16,col=colpal[matchlev],lwd=3)}
+
+for (matchlev in 1:2){
+for (cond in 1:9){
+  points(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),pch=16,cex=2,col=colpal[matchlev])
+
+  # if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])<42){
+  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
+  # }
+  # 
+  # # plot as an arrow if exceeding the axis limits
+  # if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])>42){
+  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),125,ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.035, angle=45, lwd=2)
+  # }
+
+  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),ratiosL[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
+}
+}
+
 text(10,117.5,'(d)',adj=0.5,cex=2.5)
+
+legend(75,95,c('48% match','24% match'),pch=16,col=colpal[2:1],pt.cex=2,box.lwd=2)
+
+legend(45.75,125,c('Winner-take-all','Linear summation'),lty=2:3,box.lwd=2)
 
@@
 
+  PostScriptTrace('pdata.ps')
+  p6 <- readPicture('pdata.ps.xml')
+  PostScriptTrace('edata.ps')
+  p7 <- readPicture('edata.ps.xml')
+  PostScriptTrace('edata2.ps')
+  p8 <- readPicture('edata2.ps.xml')
+  PostScriptTrace('matchingdata.ps')
+  p9 <- readPicture('matchingdata.ps.xml')
+
     for (n in 1:length(p5@paths)){
@@
 
-  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 10, width = 20)
+  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 10, width = 30)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-  grid.picture(p1,x=0.125,y=0.75,width=0.25,height=1)
-  grid.picture(p2,x=0.375,y=0.75,width=0.25,height=1)
-  grid.picture(p3,x=0.125,y=0.25,width=0.25,height=1)
-  grid.picture(p4,x=0.375,y=0.25,width=0.25,height=1)
-
-  grid.picture(p5,x=0.75,y=0.5,width=0.5,height=1)
-
-  dev.off()
-
-  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','posteriors.ps'))
-  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','posteriors.ps.xml'))
+  grid.picture(p1,x=1/12,y=0.25,width=1/6,height=1)
+  grid.picture(p2,x=3/12,y=0.25,width=1/6,height=1)
+  grid.picture(p3,x=5/12,y=0.25,width=1/6,height=1)
+  grid.picture(p4,x=7/12,y=0.25,width=1/6,height=1)
+
+  grid.picture(p5,x=5/6,y=0.5,width=1/3,height=1)
+
+  grid.picture(p6,x=1/12,y=0.75,width=1/6,height=1)
+  grid.picture(p7,x=3/12,y=0.75,width=1/6,height=1)
+  grid.picture(p8,x=5/12,y=0.75,width=1/6,height=1)
+  grid.picture(p9,x=7/12,y=0.75,width=1/6,height=1)
+
+  dev.off()
+
+  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','matchingdata.ps','pdata.ps','edata.ps','edata2.ps','posteriors.ps'))
+  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','matchingdata.ps.xml','pdata.ps.xml','edata.ps.xml','edata2.ps.xml','posteriors.ps.xml'))
 
@@
 
-knitr::include_graphics('local/Figures/modelfigure.pdf')
+knitr::include_graphics(paste0(figdir,'modelfigure.pdf'))
 

### 2022-09-25 manuscript.Rmd
Minor bug fix

@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
+ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
+ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)
+
 if (processdata > 2){
@@
 levels <- unique(matchingdata$allref)
-ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
-ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)
 subjects <- unique(matchingdata$Participant)
@@
 if (processdata > 0){
+
+           if (!file.exists(paste0(datadir,'meanmatching.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='meanmatching.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+           }
 

### 2022-09-26 manuscript.Rmd
Testing commit
Added introduction

--- 2022-09-25 manuscript.Rmd
@@
 output:
+  pdf_document:
+    toc: no
+  word_document: default
   bookdown::pdf_document2:
@@
     keep_tex: yes
-  word_document: default
-  pdf_document:
-    toc: no
   html_document: default
@@
 # Introduction
+BinocularBinocular combination provides a higher visual sensitivity than monocular viewing.
+This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around $\sqrt{2}$ ($\approx1.4$) for grating stimuli at detection threshold [@Campbell1965].
+In other words, a monocular stimulus can elicit the same response as a binocular stimulus if it has a contrast that is 1.4 times higher.
+This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination [@Legge1984]: monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = $\sqrt{R^2 + L^2}$, when R and L are equal to 1, the output is $\sqrt{2}$).
+However, subsequent research has shown that these explanations are not fully adequate to account for binocular summation.
+Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise [@Anderson1989].
+Moreover, more recent research has shown that the summation ratio can vary greatly between $\sqrt{2}$ and 2 depending on factors such as the spatial and temporal frequency of a stimulus or the sensitivity difference between the eyes [@Baker].
+These observations led to the development of multistage gain control models, which combine binocular summation and interocular suppression, and can account for contrast matching, detection and discrimination for spatial contrast [@Ding2006; @Meese2006].
+In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined [@Purves2008].
+However, there is an eye component that is often underestimated in its role to determine the quality of visual information: the pupil.
+The pupils are openings found in the centre of the eyes that appear to be black and allow light to enter the eyes.
+Their size determines how much light will reach the retina and it is usually determined by the ambient levels of light: in brightness the pupils will constrict and in darkness they will dilate.
+This is known as the pupillary light response (PLR).
+The anatomical pathways that regulate this response are well understood and are very clearly and extensively described in the literature [@Angée2021; @Mathôt2018; @McDougal2010; @Wang2015].
+However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
+Given this, not much is known about the computational processes behind the PLR except for some evidence of binocular interaction.
+The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) [@Wyatt1981] are evidence of this binocular interaction.
+With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
+The results should offer new insight about basic neural circuits and information on how they might be affected in clinical disorders of vision (e.g.
+amblyopia).
+Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
+To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
+Matching is a paradigm in which the perceived brightness of a standard stimulus is matched to that of a target stimulus.
+In the latter, the interocular ratios of luminance are varied to obtain an equibrightness curve.
+Previous literature has used this paradigm to investigate the binocular fusion of static stimuli and the temporal combination of spatial flickering of spatial increments (a bright target on a dark background) and decrements (a dark target on a bright background) [@Anstis1998; @Levelt1965].
+For spatial increments, it was found that binocular fusion seems to follow approximately linear combination rules.
+This means that, for a monocular stimulus to elicit the same response as a binocular stimulus, the former needs to have twice the signal of the latter.
+On the other hand, spatial decrements follow a winner-takes-all pattern.
+This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
+Our experiment used different stimuli than the ones used by Anstis and Ho: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
+In our experiment, in some conditions, the flicker was shown to only one eye.
+Moreover, they were looking at the temporal fusion of the flicker while we focussed on the binocular fusion of the flicker.
+Based on this and on the results from our first experiment, we expected to find a near linear summation of the responses.
 
@@
 
+Figure \@ref(fig:pupildata)a
+
 ```{r include=FALSE, results='hide'}

### 2022-09-26 manuscript.Rmd
Just small modifications

@@
 # Introduction
-BinocularBinocular combination provides a higher visual sensitivity than monocular viewing.
+Binocular combination provides a higher visual sensitivity than monocular viewing.
 This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around $\sqrt{2}$ ($\approx1.4$) for grating stimuli at detection threshold [@Campbell1965].
@@
 Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise [@Anderson1989].
-Moreover, more recent research has shown that the summation ratio can vary greatly between $\sqrt{2}$ and 2 depending on factors such as the spatial and temporal frequency of a stimulus or the sensitivity difference between the eyes [@Baker].
+Moreover, more recent research has shown that the summation ratio can vary greatly between $\sqrt{2}$ and 2 depending on factors such as the spatial and temporal frequency of a stimulus or the sensitivity difference between the eyes [@Baker2018].
 These observations led to the development of multistage gain control models, which combine binocular summation and interocular suppression, and can account for contrast matching, detection and discrimination for spatial contrast [@Ding2006; @Meese2006].
@@
 This is known as the pupillary light response (PLR).
-The anatomical pathways that regulate this response are well understood and are very clearly and extensively described in the literature [@Angée2021; @Mathôt2018; @McDougal2010; @Wang2015].
+The anatomical pathways that regulate this response are well understood and are very clearly and extensively described in the literature [@Angee2021; @Mathot2018; @McDougal2010; @Wang2015].
 However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
@@
 ## Data analysis
-
-@Baker2021
 

### 2022-09-27 manuscript.Rmd
Added methods

@@
 # Methods
-
 ## Participants
+Thirty, twelve and ten participants were recruited for experiment 1, 2 and 3 respectively.
+All participants had normal or corrected to normal binocular vision.
+All participants gave written informed consent.
 
 ## Apparatus & Stimuli
+The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background.
+The same stimuli were used for all three experiments.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc.
+Figure 1 shows an example of the of the unfused stimuli.
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc.
+The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+All stimuli were displayed at a mean luminance of 42 cd/m$^2$ on an Iiyama Vision Master™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 (Minolta Camera Co.
+Ltd., Japan).
+For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
+For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
+Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH).
 
 ## Procedure
+Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
+This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
+
+### Experiment 1
+The experiment was conducted in a windowless room, in which the only light source was the monitor.
+The participants sat at 99 cm from the monitor and their viewing distance through the stereoscope was 107 cm.
+The experiment was carried out in one session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants had no task and were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
+The discs flickered in counterphase at 2 Hz, but in some conditions (cross-frequency conditions) one of the two discs flickered at 1.6 Hz.
+They were set at five temporal contrast levels relative to the mean luminance: 6, 12, 24, 48 and 96 \%.
+As already stated, the mirror stereoscope allowed the use of three different ocular configurations.
+In the monocular configuration, one disc was set to flicker either at 2 Hz or 1.6 Hz for each contrast level, while the other disc remained stable at a constant mean luminance.
+In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz.
+Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 %.
+Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.
+
+### Experiment 2
+The conditions were similar to experiment 1 (windowless room and viewing distance of 107 cm).
+Like in experiment 1, participants had no specific task other than looking at the fixation crosses and minimising their blinking.
+Unlike the first experiment, only one contrast level was used (96 \%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
+The experiment was carried out in one session lasting 25 minutes in total, divided in five blocks of 5 minutes each.
+In each block, there were 20 trials in total lasting 15 seconds each (12s of stimulus presentation and 3s of interstimulus interval).
+
+### Experiment 3
+The experiment was conducted in a room with a blacked-out window.
+The sitting and viewing distances of the participants were similar to the two previous experiments.
+As this was a psychophysical task, no EEG or pupillometry data were collected for this experiment.
+A two-interval forced-choice staircase procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48 \%), which was selected by the experimenter at the beginning of each block.
+In a separate interval, a target fused disc flickering at varying contrast levels was displayed.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1.
+The standard and the target fused discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz.
+Due to its long duration (162 minutes in total), the participants completed the experiment across multiple sessions divided at their own discretion.
+The experiment was divided in 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each (depending on the response speed of the participant).
+In each block, there were a total of 50 trials.
+We pooled the data from all repetitions of a given condition and fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50 \% point.
 
 ## Data analysis
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
+The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted.
+Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each electrode.
+They were then averaged across the four occipital electrodes (POz, Oz, O1, O2), to obtain individual results.
+Finally, these were averaged across all participants to obtain the final results.
 
 # Results
-
 ## Experiment 1
-
+The results from the first experiment are shown in figures 2 and 3. Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
 ```{r include=FALSE, results='hide'}
@@
 
-Figure \@ref(fig:pupildata)a
+Figure @ref(fig:pupildata)a
 
@@
 ## Experiment 2
-
+The results from the second experiment are shown in figure 4.
+In figures 5A to 5C, the curves are showing the results for the monocular and the binocular configurations.
+In figure 5D, the curves are showing the results for the two harmonics.
 ```{r include=FALSE, results='hide'}

### 2022-09-27 manuscript.Rmd
Added experiment 3 results write up

@@
 output:
-  pdf_document:
-    toc: no
-  word_document: default
   bookdown::pdf_document2:
@@
     keep_tex: yes
+  word_document: default
+  pdf_document:
+    toc: no
   html_document: default
@@
 These observations led to the development of multistage gain control models, which combine binocular summation and interocular suppression, and can account for contrast matching, detection and discrimination for spatial contrast [@Ding2006; @Meese2006].
+
 In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined [@Purves2008].
@@
 The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) [@Wyatt1981] are evidence of this binocular interaction.
+
 With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
@@
 Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
+
 To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
@@
 This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
+
 Our experiment used different stimuli than the ones used by Anstis and Ho: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
@@
 The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+
 All stimuli were displayed at a mean luminance of 42 cd/m$^2$ on an Iiyama Vision Master™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 (Minolta Camera Co.
@@
 For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+
 EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
@@
 They were set at five temporal contrast levels relative to the mean luminance: 6, 12, 24, 48 and 96 \%.
+
 As already stated, the mirror stereoscope allowed the use of three different ocular configurations.
@@
 Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
+
 The experiment was carried out in one session lasting 25 minutes in total, divided in five blocks of 5 minutes each.
@@
 As this was a psychophysical task, no EEG or pupillometry data were collected for this experiment.
+
 A two-interval forced-choice staircase procedure was used to collect data.
@@
 The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz.
+
 Due to its long duration (162 minutes in total), the participants completed the experiment across multiple sessions divided at their own discretion.
@@
 ## Experiment 1
-The results from the first experiment are shown in figures 2 and 3. Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
+The results from the first experiment are shown in figure \@ref(fig:pupildata) and figure \@ref(fig:EEGdata).
+Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
 ```{r include=FALSE, results='hide'}
@@
 
-Figure @ref(fig:pupildata)a
-
 ```{r include=FALSE, results='hide'}
@@
 ## Experiment 2
-The results from the second experiment are shown in figure 4.
-In figures 5A to 5C, the curves are showing the results for the monocular and the binocular configurations.
-In figure 5D, the curves are showing the results for the two harmonics.
+The results from the second experiment are shown in figure \@ref(fig:TFdata). Figure \@ref(fig:TFdata)a is showing the fourier spectra 
 ```{r include=FALSE, results='hide'}
@@
 ## Experiment 3
+The results from the third experiment are shown in figure \@ref(fig:matchingdata). Each curve is showing the contrast level in each eye for the different interocular ratios.
+
+Looking at the results for the 48 % contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 % (red line).
+This is also observable for the 24 % contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 %.
+These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
+When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
+For the 48 % contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 %, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 %.
+For the 24 % contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 %, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 %.
+When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 % condition showing a very strong summation that seem to exceed this linear combination.
+Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
 
@@
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.", fig.align="center", echo=FALSE}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Interocular ratio distribution (from left to right of the figure): 1L0R, 1L0.25R, 1L0.5R, 1L0.75R, 1L1R, 0.75L1R, 0.5L1R, 0.25L1R, 0L1R.", fig.align="center", echo=FALSE}
 

### 2022-09-27 manuscript.tex
Minor bug fix
Testing commit
Added experiment 3 results write up

@@
 ]{article}
-\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Different rules for binocular combination of luminance in cortical and subcortical pathways},
+  pdfauthor={Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
+\usepackage{longtable,booktabs}
 % Correct order of tables after \paragraph or \subparagraph
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Different rules for binocular combination of luminance in cortical and subcortical pathways},
-  pdfauthor={Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 \author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
-\date{2022-09-22}
+\date{2022-09-27}
 
@@
 
+Binocular combination provides a higher visual sensitivity than monocular viewing.
+This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around \(\sqrt{2}\) (\(\approx1.4\)) for grating stimuli at detection threshold (Campbell and Green, 1965).
+In other words, a monocular stimulus can elicit the same response as a binocular stimulus if it has a contrast that is 1.4 times higher.
+This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination (Legge, 1984): monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = \(\sqrt{R^2 + L^2}\), when R and L are equal to 1, the output is \(\sqrt{2}\)).
+However, subsequent research has shown that these explanations are not fully adequate to account for binocular summation.
+Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise (Anderson and Movshon, 1989).
+Moreover, more recent research has shown that the summation ratio can vary greatly between \(\sqrt{2}\) and 2 depending on factors such as the spatial and temporal frequency of a stimulus or the sensitivity difference between the eyes (Baker et al., 2018).
+These observations led to the development of multistage gain control models, which combine binocular summation and interocular suppression, and can account for contrast matching, detection and discrimination for spatial contrast (Ding and Sperling, 2006; Meese et al., 2006).
+
+In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined (Purves et al., 2008).
+However, there is an eye component that is often underestimated in its role to determine the quality of visual information: the pupil.
+The pupils are openings found in the centre of the eyes that appear to be black and allow light to enter the eyes.
+Their size determines how much light will reach the retina and it is usually determined by the ambient levels of light: in brightness the pupils will constrict and in darkness they will dilate.
+This is known as the pupillary light response (PLR).
+The anatomical pathways that regulate this response are well understood and are very clearly and extensively described in the literature (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2010; Wang and Munoz, 2015).
+However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
+Given this, not much is known about the computational processes behind the PLR except for some evidence of binocular interaction.
+The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) (Wyatt and Musselman, 1981) are evidence of this binocular interaction.
+
+With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
+The results should offer new insight about basic neural circuits and information on how they might be affected in clinical disorders of vision (e.g.~amblyopia).
+Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
+
+To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
+Matching is a paradigm in which the perceived brightness of a standard stimulus is matched to that of a target stimulus.
+In the latter, the interocular ratios of luminance are varied to obtain an equibrightness curve.
+Previous literature has used this paradigm to investigate the binocular fusion of static stimuli and the temporal combination of spatial flickering of spatial increments (a bright target on a dark background) and decrements (a dark target on a bright background) (Anstis and Ho, 1998; Levelt, 1965).
+For spatial increments, it was found that binocular fusion seems to follow approximately linear combination rules.
+This means that, for a monocular stimulus to elicit the same response as a binocular stimulus, the former needs to have twice the signal of the latter.
+On the other hand, spatial decrements follow a winner-takes-all pattern.
+This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
+
+Our experiment used different stimuli than the ones used by Anstis and Ho: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
+In our experiment, in some conditions, the flicker was shown to only one eye.
+Moreover, they were looking at the temporal fusion of the flicker while we focussed on the binocular fusion of the flicker.
+Based on this and on the results from our first experiment, we expected to find a near linear summation of the responses.
+
 \hypertarget{methods}{%
@@
 
+Thirty, twelve and ten participants were recruited for experiment 1, 2 and 3 respectively.
+All participants had normal or corrected to normal binocular vision.
+All participants gave written informed consent.
+
 \hypertarget{apparatus-stimuli}{%
 \subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}}
+
+The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background.
+The same stimuli were used for all three experiments.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc.
+Figure 1 shows an example of the of the unfused stimuli.
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc.
+The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+
+All stimuli were displayed at a mean luminance of 42 cd/m\(^2\) on an Iiyama Vision Master™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 (Minolta Camera Co.~Ltd., Japan).
+For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
+For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+
+EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
+Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH).
 
@@
 
+Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
+This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
+
+\hypertarget{experiment-1}{%
+\subsubsection{Experiment 1}\label{experiment-1}}
+
+The experiment was conducted in a windowless room, in which the only light source was the monitor.
+The participants sat at 99 cm from the monitor and their viewing distance through the stereoscope was 107 cm.
+The experiment was carried out in one session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants had no task and were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
+The discs flickered in counterphase at 2 Hz, but in some conditions (cross-frequency conditions) one of the two discs flickered at 1.6 Hz.
+They were set at five temporal contrast levels relative to the mean luminance: 6, 12, 24, 48 and 96 \%.
+
+As already stated, the mirror stereoscope allowed the use of three different ocular configurations.
+In the monocular configuration, one disc was set to flicker either at 2 Hz or 1.6 Hz for each contrast level, while the other disc remained stable at a constant mean luminance.
+In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz.
+Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 \%.
+Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.
+
+\hypertarget{experiment-2}{%
+\subsubsection{Experiment 2}\label{experiment-2}}
+
+The conditions were similar to experiment 1 (windowless room and viewing distance of 107 cm).
+Like in experiment 1, participants had no specific task other than looking at the fixation crosses and minimising their blinking.
+Unlike the first experiment, only one contrast level was used (96 \%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
+
+The experiment was carried out in one session lasting 25 minutes in total, divided in five blocks of 5 minutes each.
+In each block, there were 20 trials in total lasting 15 seconds each (12s of stimulus presentation and 3s of interstimulus interval).
+
+\hypertarget{experiment-3}{%
+\subsubsection{Experiment 3}\label{experiment-3}}
+
+The experiment was conducted in a room with a blacked-out window.
+The sitting and viewing distances of the participants were similar to the two previous experiments.
+As this was a psychophysical task, no EEG or pupillometry data were collected for this experiment.
+
+A two-interval forced-choice staircase procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48 \%), which was selected by the experimenter at the beginning of each block.
+In a separate interval, a target fused disc flickering at varying contrast levels was displayed.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1.
+The standard and the target fused discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz.
+
+Due to its long duration (162 minutes in total), the participants completed the experiment across multiple sessions divided at their own discretion.
+The experiment was divided in 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each (depending on the response speed of the participant).
+In each block, there were a total of 50 trials.
+We pooled the data from all repetitions of a given condition and fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50 \% point.
+
 \hypertarget{data-analysis}{%
@@
 
-Baker (2021)
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
+The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted.
+Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each electrode.
+They were then averaged across the four occipital electrodes (POz, Oz, O1, O2), to obtain individual results.
+Finally, these were averaged across all participants to obtain the final results.
 
@@
 
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
+\hypertarget{experiment-1-1}{%
+\subsection{Experiment 1}\label{experiment-1-1}}
+
+The results from the first experiment are shown in figure \ref{fig:pupildata} and figure \ref{fig:EEGdata}.
+Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
 
@@
 
-{\centering \includegraphics{local/Figures/pupildata}
+{\centering \includegraphics{Figures/pupildata}
 
@@
 
-{\centering \includegraphics{local/Figures/EEGdata}
+{\centering \includegraphics{Figures/EEGdata}
 
@@
 
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
+\hypertarget{experiment-2-1}{%
+\subsection{Experiment 2}\label{experiment-2-1}}
+
+The results from the second experiment are shown in figure \ref{fig:TFdata}.
+In figures 5A to 5C, the curves are showing the results for the monocular and the binocular configurations.
+In figure 5D, the curves are showing the results for the two harmonics.
 
@@
 
-{\centering \includegraphics{local/Figures/TFdata}
+{\centering \includegraphics{Figures/TFdata}
 
@@
 Panel (c) shows the ratio of binocular to monocular responses.
-Error bars and shaded regions indicate bootstrapped standard errors.}\label{fig:TFdata}
+Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
 \end{figure}
 
-\hypertarget{experiment-3}{%
-\subsection{Experiment 3}\label{experiment-3}}
+\hypertarget{experiment-3-1}{%
+\subsection{Experiment 3}\label{experiment-3-1}}
 
@@
 
-{\centering \includegraphics{local/Figures/matchingdata}
+{\centering \includegraphics{Figures/matchingdata}
 
@@
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.}\label{fig:matchingdata}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Interocular ratio distribution (from left to right of the figure): 1L0R, 1L0.25R, 1L0.5R, 1L0.75R, 1L1R, 0.75L1R, 0.5L1R, 0.25L1R, 0L1R.}\label{fig:matchingdata}
 \end{figure}
+
+The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios.
+
+Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
+This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
+These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
+When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
+For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
+For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
+When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
+Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
 
@@
 
-{\centering \includegraphics{local/Figures/modelfigure}
+{\centering \includegraphics{Figures/modelfigure}
 
@@
 \hline
-Pupillometry & 2.73 & 0.01 & 0.60 & 0.00022\\
+Pupillometry & 2.45 & 0.01 & 0.67 & 0.00024\\
 \hline
-EEG 1F & 2.09 & 0.15 & 0.02 & 0.00336\\
+EEG 1F & 2.78 & 0.15 & 0.03 & 0.00262\\
 \hline
-EEG 2F & 3.39 & 0.07 & 0.02 & 0.00312\\
+EEG 2F & 2.31 & 0.06 & 0.01 & 0.00407\\
 \hline
-Matching & 0.22 & 5.06 & 0.09 & -\\
+Matching & 0.56 & 7.96 & 0.05 & -\\
 \hline
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
-Baker DH.
+\leavevmode\hypertarget{ref-Anderson1989}{}%
+Anderson PA, Movshon JA. 1989. Binocular combination of contrast signals. \emph{Vision Res} \textbf{29}:1115--32. doi:\href{https://doi.org/10.1016/0042-6989(89)90060-6}{10.1016/0042-6989(89)90060-6}
+
+\leavevmode\hypertarget{ref-Angee2021}{}%
+Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
 2021.
-Statistical analysis of periodic data in neuroscience.
-\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
-doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+Congenital microcoria: Clinical features and molecular genetics.
+\emph{Genes (Basel)} \textbf{12}.
+doi:\href{https://doi.org/10.3390/genes12050624}{10.3390/genes12050624}
 
-\end{CSLReferences}
+\leavevmode\hypertarget{ref-Anstis1998}{}%
+Anstis S, Ho A.
+1998.
+Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
+\emph{Vision Res} \textbf{38}:523--39.
+doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
+
+\leavevmode\hypertarget{ref-Baker2018}{}%
+Baker DH, Lygo FA, Meese TS, Georgeson MA.
+2018.
+Binocular summation revisited: Beyond \(\sqrt{2}\).
+\emph{Psychol Bull} \textbf{144}:1186--1199.
+doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
+
+\leavevmode\hypertarget{ref-Delorme2004}{}%
+Delorme A, Makeig S.
+2004.
+EEGLAB: An open source toolbox for analysis of single-trial eeg dynamics including independent component analysis.
+\emph{J Neurosci Methods} \textbf{134}:9--21.
+doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}
+
+\leavevmode\hypertarget{ref-Ding2006}{}%
+Ding J, Sperling G.
+2006.
+A gain-control theory of binocular combination.
+\emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6.
+doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}
+
+\leavevmode\hypertarget{ref-Legge1984}{}%
+Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+
+\leavevmode\hypertarget{ref-Levelt1965}{}%
+Levelt WJ.
+1965.
+BINOCULAR brightness averaging and contour information.
+\emph{Br J Psychol} \textbf{56}:1--13.
+doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}
+
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
+
+\leavevmode\hypertarget{ref-McDougal2010}{}%
+McDougal DH, Gamlin PD.
+2010.
+The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
+\emph{Vision Res} \textbf{50}:72--87.
+doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
+
+\leavevmode\hypertarget{ref-Meese2006}{}%
+Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
+
+\leavevmode\hypertarget{ref-Purves2008}{}%
+Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press, Incorporated.
+
+\leavevmode\hypertarget{ref-Wang2015}{}%
+Wang C-A, Munoz DP.
+2015.
+A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size.
+\emph{Curr Opin Neurobiol} \textbf{33}:134--40.
+doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}
+
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
+Wyatt HJ, Musselman JF.
+1981.
+Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res} \textbf{21}:513--25.
+doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
 

### 2022-09-28 manuscript.Rmd
Minor changes and added pupillometry analysis

@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc.
-Figure 1 shows an example of the of the unfused stimuli.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in figure \@ref(fig:pupildata)a for an example of the of the fused stimuli).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc.
@@
 EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
-Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH).
+Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, @Kassner2014) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH, @Kassner2014).
 
@@
 In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz.
-Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 %.
+Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 \%.
 Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.
@@
 They were then averaged across the four occipital electrodes (POz, Oz, O1, O2), to obtain individual results.
+Finally, these were averaged across all participants to obtain the final results.
+
+A similar process was adopted for the analysis of the pupillometry data.
+The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software [@Kassner2014].
+The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted.
+Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each eye.
+They were then averaged across the two eyes, to obtain individual results.
 Finally, these were averaged across all participants to obtain the final results.

### 2022-09-28 manuscript.tex
Minor changes and added pupillometry analysis

@@
 ]{article}
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
 % Correct order of tables after \paragraph or \subparagraph
@@
 \makesavenoteenv{longtable}
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \setcounter{secnumdepth}{5}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 
@@
 \author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
-\date{2022-09-27}
+\date{2022-09-28}
 
@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc.
-Figure 1 shows an example of the of the unfused stimuli.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in figure \ref{fig:pupildata}a for an example of the of the fused stimuli).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc.
@@
 EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
-Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH).
+Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Kassner et al.
+(2014)) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH, Kassner et al.
+(2014)).
 
@@
 
+A similar process was adopted for the analysis of the pupillometry data.
+The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software (Kassner et al., 2014).
+The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted.
+Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each eye.
+They were then averaged across the two eyes, to obtain individual results.
+Finally, these were averaged across all participants to obtain the final results.
+
 \hypertarget{results}{%
@@
 
-The results from the second experiment are shown in figure \ref{fig:TFdata}.
-In figures 5A to 5C, the curves are showing the results for the monocular and the binocular configurations.
-In figure 5D, the curves are showing the results for the two harmonics.
+The results from the second experiment are shown in figure \ref{fig:TFdata}. Figure \ref{fig:TFdata}a is showing the fourier spectra
 
@@
 
+The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios.
+
+Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
+This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
+These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
+When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
+For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
+For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
+When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
+Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
+
 \begin{figure}
@@
 \end{figure}
-
-The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios.
-
-Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
-This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
-These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
-When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
-For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
-For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
-When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
-Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Anderson1989}{}%
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Anderson1989}{}}%
 Anderson PA, Movshon JA. 1989. Binocular combination of contrast signals. \emph{Vision Res} \textbf{29}:1115--32. doi:\href{https://doi.org/10.1016/0042-6989(89)90060-6}{10.1016/0042-6989(89)90060-6}
 
-\leavevmode\hypertarget{ref-Angee2021}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Angee2021}{}}%
 Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
@@
 
-\leavevmode\hypertarget{ref-Anstis1998}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
 Anstis S, Ho A.
@@
 
-\leavevmode\hypertarget{ref-Baker2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
 Baker DH, Lygo FA, Meese TS, Georgeson MA.
@@
 
-\leavevmode\hypertarget{ref-Campbell1965}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
 Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
-\leavevmode\hypertarget{ref-Delorme2004}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
 Delorme A, Makeig S.
 2004.
-EEGLAB: An open source toolbox for analysis of single-trial eeg dynamics including independent component analysis.
+EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
 \emph{J Neurosci Methods} \textbf{134}:9--21.
@@
 
-\leavevmode\hypertarget{ref-Ding2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
 Ding J, Sperling G.
@@
 
-\leavevmode\hypertarget{ref-Legge1984}{}%
-Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+Kassner M, Patera W, Bulling A.
+2014.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interactionProceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
+UbiComp '14 Adjunct; {ACM}.
+pp.
+1151--1160.
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
 
-\leavevmode\hypertarget{ref-Levelt1965}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
+Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
 Levelt WJ.
 1965.
-BINOCULAR brightness averaging and contour information.
+BINOCULAR BRIGHTNESS AVERAGING AND CONTOUR INFORMATION.
 \emph{Br J Psychol} \textbf{56}:1--13.
@@
 
-\leavevmode\hypertarget{ref-Mathot2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
 Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
-\leavevmode\hypertarget{ref-McDougal2010}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
 McDougal DH, Gamlin PD.
@@
 
-\leavevmode\hypertarget{ref-Meese2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
 Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
-\leavevmode\hypertarget{ref-Purves2008}{}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press, Incorporated.
+\leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
+Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press, Incorporated.
 
-\leavevmode\hypertarget{ref-Wang2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
 Wang C-A, Munoz DP.
@@
 
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
 Wyatt HJ, Musselman JF.
@@
 
+\end{CSLReferences}
+
 \end{document}

### 2022-09-28 manuscript.Rmd
Added exeperiment 1 results write up

@@
 Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
+
+Figure \@ref(fig:pupildata) is showing the results for the pupillometry.
+Figure \@ref(fig:pupildata)a is showing the group average waveform for binocular presentation.
+Figure \@ref(fig:pupildata)b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli.
+Figures \@ref(fig:pupildata)c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz.
+In the same-frequency condition at 2 Hz (fig.
+\@ref(fig:pupildata)c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration.
+In the cross-frequency condtion at 2 Hz (fig.
+\@ref(fig:pupildata)d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition.
+Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.
+\@ref(fig:pupildata)e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels.
+This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils.
+Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.
+
+Figure \@ref(fig:EEGdata) shows the results for EEG.
+Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation.
+Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics.
+Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic.
+What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.
+\@ref(fig:EEGdata)c) and second (fig.
+\@ref(fig:EEGdata)f) harmonic are showing very high summation of binocular signals.
+The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses.
+This is especially clear at the highest contrasts.
+For the cross-frequency condition at 2 Hz and 4 Hz (fig.
+\@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals.
+This pattern is also observable in the cross-frequency condition at 1.6 (fig.
+\@ref(fig:EEGdata)e) and 3.2 Hz (fig.
+\@ref(fig:EEGdata)h).
+This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex.
+Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.
 ```{r include=FALSE, results='hide'}

### 2022-09-28 manuscript.tex
Added exeperiment 1 results write up

@@
 
+Figure \ref{fig:pupildata} is showing the results for the pupillometry.
+Figure \ref{fig:pupildata}a is showing the group average waveform for binocular presentation.
+Figure \ref{fig:pupildata}b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli.
+Figures \ref{fig:pupildata}c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz.
+In the same-frequency condition at 2 Hz (fig.~\ref{fig:pupildata}c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration.
+In the cross-frequency condtion at 2 Hz (fig.~\ref{fig:pupildata}d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition.
+Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.~\ref{fig:pupildata}e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels.
+This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils.
+Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.
+
+Figure \ref{fig:EEGdata} shows the results for EEG.
+Figure \ref{fig:EEGdata}a is showing the group average waveform for binocular presentation.
+Figure \ref{fig:EEGdata}b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics.
+Figures \ref{fig:EEGdata}c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \ref{fig:EEGdata}f-h show the CRFs at the second harmonic.
+What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonic are showing very high summation of binocular signals.
+The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses.
+This is especially clear at the highest contrasts.
+For the cross-frequency condition at 2 Hz and 4 Hz (fig.~\ref{fig:EEGdata}d and \ref{fig:EEGdata}g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals.
+This pattern is also observable in the cross-frequency condition at 1.6 (fig.~\ref{fig:EEGdata}e) and 3.2 Hz (fig.~\ref{fig:EEGdata}h).
+This pattern of results seems to suggest that processing of temporal luminance modulations happens in a linear way in the visual cortex.
+Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.
+
 \begin{figure}

### 2022-09-30 manuscript.Rmd
Small edits

@@
 
-Looking at the results for the 48 % contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 % (red line).
-This is also observable for the 24 % contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 %.
+Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
+This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
 These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
 When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
-For the 48 % contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 %, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 %.
-For the 24 % contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 %, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 %.
-When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 % condition showing a very strong summation that seem to exceed this linear combination.
+For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
+For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
+When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
 Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.

### 2022-10-04 manuscript.Rmd
Added experiment 2 results write up

@@
 A similar process was adopted for the analysis of the pupillometry data.
-The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software [@Kassner2014].
+The data were converted from the mp4 format to a  csv text file using the Pupil Player software [@Kassner2014].
 The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted.
@@
 \@ref(fig:pupildata)c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration.
+In general, we observe that the binocular to monocular ratio is roughly $\sqrt2$ at each contrast level (fig.
+).
 In the cross-frequency condtion at 2 Hz (fig.
@@
 \@ref(fig:pupildata)e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels.
+This facilitation is then lost at the highest contrast level, where the amplitude of the monocular signal is equal to the amplitude of the binocular signal.
 This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils.
@@
 \@ref(fig:EEGdata)c) and second (fig.
-\@ref(fig:EEGdata)f) harmonic are showing very high summation of binocular signals.
-The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses.
+\@ref(fig:EEGdata)f) harmonics are showing very high summation of binocular signals compared to the pupillometry.
+The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses.
 This is especially clear at the highest contrasts.
+This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry.
 For the cross-frequency condition at 2 Hz and 4 Hz (fig.
@@
 ## Experiment 2
-The results from the second experiment are shown in figure \@ref(fig:TFdata). Figure \@ref(fig:TFdata)a is showing the fourier spectra
+The results from the second experiment are shown in \@ref(fig:TFdata).
+Figure \@ref(fig:TFdata)a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz).
+We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics.
+However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded.
+This is also reflected in figure \@ref(fig:TFdata)b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz.
+The rest of figure \@ref(fig:TFdata)b is showing the response at each stimulation frequency.
+We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz.
+In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig.
+\@ref(fig:TFdata)c), suggesting that binocular facilitation is happening at higher frequencies.
+However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \@ref(fig:TFdata)c).
+The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
 ```{r include=FALSE, results='hide'}

### 2022-10-04 manuscript.tex
Added experiment 2 results write up

@@
 \author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
-\date{2022-09-28}
+\date{2022-10-04}
 
@@
 In the same-frequency condition at 2 Hz (fig.~\ref{fig:pupildata}c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration.
+In general, we observe that the binocular to monocular ratio is roughly \(\sqrt2\) at each contrast level (fig.~).
 In the cross-frequency condtion at 2 Hz (fig.~\ref{fig:pupildata}d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition.
 Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.~\ref{fig:pupildata}e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels.
+This facilitation is then lost at the highest contrast level, where the amplitude of the monocular signal is equal to the amplitude of the binocular signal.
 This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils.
@@
 Figures \ref{fig:EEGdata}c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \ref{fig:EEGdata}f-h show the CRFs at the second harmonic.
-What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonic are showing very high summation of binocular signals.
-The amplitudes of the binocular responses are twice, and even more than twice, the amplitude of the monocular responses.
+What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonics are showing very high summation of binocular signals compared to the pupillometry.
+The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses.
 This is especially clear at the highest contrasts.
+This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry.
 For the cross-frequency condition at 2 Hz and 4 Hz (fig.~\ref{fig:EEGdata}d and \ref{fig:EEGdata}g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals.
@@
 
-The results from the second experiment are shown in figure \ref{fig:TFdata}. Figure \ref{fig:TFdata}a is showing the fourier spectra
+The results from the second experiment are shown in \ref{fig:TFdata}.
+Figure \ref{fig:TFdata}a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz).
+We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics.
+However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded.
+This is also reflected in figure \ref{fig:TFdata}b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz.
+The rest of figure \ref{fig:TFdata}b is showing the response at each stimulation frequency.
+We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz.
+In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig.~\ref{fig:TFdata}c), suggesting that binocular facilitation is happening at higher frequencies.
+However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \ref{fig:TFdata}c).
+The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
 

### 2022-10-04 manuscript.Rmd
Rewrote experiment 3 results

@@
 ## Experiment 3
-The results from the third experiment are shown in figure \@ref(fig:matchingdata). Each curve is showing the contrast level in each eye for the different interocular ratios.
-
-Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
-This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
+The results from the third experiment are shown in figure \@ref(fig:matchingdata).
+Each curve is showing the contrast level in each eye for the different interocular ratios at the 24 \% (in red) and 48 \% (in blue) conditions.
+
+Looking at the results for the 48 \% contrast condition, we can observe that, when the match was presented binocularly (both eyes saw the same stimulus), the match appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
+This is also observable for the 24 \% contrast condition, where the match appeared to have the same flickering intensity as the standard when the contrast was selected to be around 25 \%.
 These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
-When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
-For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
-For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
-When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
-Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
-
+
+When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard.
+When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%.
+When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%.
+When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction.
+Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig.
+\@ref(fig:EEGdata)).
 ```{r include=FALSE, results='hide'}

### 2022-10-04 manuscript.tex
Rewrote experiment 3 results

@@
 A similar process was adopted for the analysis of the pupillometry data.
-The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software (Kassner et al., 2014).
+The data were converted from the mp4 format to a csv text file using the Pupil Player software (Kassner et al., 2014).
 The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted.
@@
 
-The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios.
+The results from the third experiment are shown in figure \ref{fig:matchingdata}.
+Each curve is showing the contrast level in each eye for the different interocular ratios at the 24 \% (in red) and 48 \% (in blue) conditions.
 
-Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
-This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
+Looking at the results for the 48 \% contrast condition, we can observe that, when the match was presented binocularly (both eyes saw the same stimulus), the match appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
+This is also observable for the 24 \% contrast condition, where the match appeared to have the same flickering intensity as the standard when the contrast was selected to be around 25 \%.
 These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
-When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
-For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
-For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
-When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
-Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
+
+When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard.
+When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%.
+When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%.
+When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction.
+Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig.~\ref{fig:EEGdata}).
 

### 2022-10-04 manuscript.Rmd
Added modelling write up and slightly modified caption of modelling figure

@@
 ## Computational modelling
+Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
+Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
+These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression
+
+The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other [@Ding2006].
+In the earlier stage, the right and left eye channels exert gain control on the other channel.
+Then, they exert gain control on the other channel’s gain control.
+Lastly, the outputs from each channel are summed binocularly to determine the binocular signal’s magnitude.
+
+The second model is similar as it also incorporates gain control mechanisms [@Meese2006].
+In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
+Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
+This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
+
+We therefore decided to use and readapt this second model to see if it could be used to explain our three different data sets from experiments 1 and 3.
+In the first stage, the responses from the right and the left eyes are computed separately, as shown by equation 1 and 2:
+
+_RespL_ = $\frac{(L^q)}{Z + R + w \times R}$ (1)
+
+_RespR_ = $\frac{(R^q)}{Z + R + w \times L}$ (2)
+
+where _L_ and _R_ are the signals from the left and right eyes, _Z_ is a saturation constant, _q_ is an exponent and _w_ is the suppression from the opponent weight.
+
+In the second stage, the responses from the two eyes are summed binocularly:
+
+_Resp(L,R)_ = k $\times$ (RespL + RespR) + n
+
+where _k_ is the noise parameter.
+
+For our analysis, we implemented the model using a Bayesian approach, using the Stan software in Rstudio, which allowed us to generate a posterior parameter distribution.
+Results for this are shown in figure \@ref(fig:modelfigure)i and the summary of the median parameter values are displayed in table \@ref(tab:paramtable).
+The key finding is that the pupillometry results display a much higher suppression from the opponent eye, shown by the _w_ parameter in table \@ref(tab:paramtable) and the green line in figure \@ref(fig:modelfigure)i, than the EEG results at the first harmonic (grey line in figure \@ref(fig:modelfigure)i), the EEG results at the second harmonic (purple line in figure \@ref(fig:modelfigure)i) and the matching results (yellow line in figure \@ref(fig:modelfigure)i).
+These results offer an explanation to the data from the previous experiments: the higher suppression displayed by the pupillometry explains the non-linearity observed in the first experiment, while the lower suppression by the EEG at both harmonics and the matching explains the strong linearity observed in experiments 1 and 3.
+
+Finally, figures \@ref(fig:modelfigure)a-d show the behavioural data for our four main data sets from experiments 1 and 3, and figures \@ref(fig:modelfigure)e-h show the outputs that the model produced based on the median parameter values that are presented in table \@ref(tab:paramtable).
+We can see that the data outputted by the model has a similar has a similar behaviour to the empirical data that we collected in our experiments.
+This would seem to suggest that the model can offer a good explanation of our data.
 
@@
 Panels (a-d) show model behaviour for our four main data set, pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d).
-Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
 The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).

### 2022-10-04 manuscript.tex
Added modelling write up and slightly modified caption of modelling figure

@@
 
+Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
+Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
+These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression
+
+The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other (Ding and Sperling, 2006).
+In the earlier stage, the right and left eye channels exert gain control on the other channel.
+Then, they exert gain control on the other channel's gain control.
+Lastly, the outputs from each channel are summed binocularly to determine the binocular signal's magnitude.
+
+The second model is similar as it also incorporates gain control mechanisms (Meese et al., 2006).
+In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
+Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
+This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
+
+We therefore decided to use and readapt this second model to see if it could be used to explain our three different data sets from experiments 1 and 3.
+In the first stage, the responses from the right and the left eyes are computed separately, as shown by equation 1 and 2:
+
+\emph{RespL} = \(\frac{(L^q)}{Z + R + w \times R}\) (1)
+
+\emph{RespR} = \(\frac{(R^q)}{Z + R + w \times L}\) (2)
+
+where \emph{L} and \emph{R} are the signals from the left and right eyes, \emph{Z} is a saturation constant, \emph{q} is an exponent and \emph{w} is the suppression from the opponent weight.
+
+In the second stage, the responses from the two eyes are summed binocularly:
+
+\emph{Resp(L,R)} = k \(\times\) (RespL + RespR) + n
+
+where \emph{k} is the noise parameter.
+
+For our analysis, we implemented the model using a Bayesian approach, using the Stan software in Rstudio, which allowed us to generate a posterior parameter distribution.
+Results for this are shown in figure \ref{fig:modelfigure}i and the summary of the median parameter values are displayed in table \ref{tab:paramtable}.
+The key finding is that the pupillometry results display a much higher suppression from the opponent eye, shown by the \emph{w} parameter in table \ref{tab:paramtable} and the green line in figure \ref{fig:modelfigure}i, than the EEG results at the first harmonic (grey line in figure \ref{fig:modelfigure}i), the EEG results at the second harmonic (purple line in figure \ref{fig:modelfigure}i) and the matching results (yellow line in figure \ref{fig:modelfigure}i).
+These results offer an explanation to the data from the previous experiments: the higher suppression displayed by the pupillometry explains the non-linearity observed in the first experiment, while the lower suppression by the EEG at both harmonics and the matching explains the strong linearity observed in experiments 1 and 3.
+
+Finally, figures \ref{fig:modelfigure}a-d show the behavioural data for our four main data sets from experiments 1 and 3, and figures \ref{fig:modelfigure}e-h show the outputs that the model produced based on the median parameter values that are presented in table \ref{tab:paramtable}.
+We can see that the data outputted by the model has a similar has a similar behaviour to the empirical data that we collected in our experiments.
+This would seem to suggest that the model can offer a good explanation of our data.
+
 \begin{figure}

### 2022-10-04 manuscript.Rmd
Code update with full OSF integration, added extra figure.

@@
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','osfr') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
 if (length(missingpackages)>0){install.packages(missingpackages)}
-if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
 if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
-packagelist <- c(packagelist,'osfr','FourierStats')
+packagelist <- c(packagelist,'FourierStats')
 toinstall <- packagelist[which(!packagelist %in% (.packages()))]
@@
 Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.
+
 ```{r include=FALSE, results='hide'}
@@
 
-tempmasksP <- array(0,dim=c(length(d),6,5))
-tempmeansP <- tempmasksP
-tempmasksE <- array(0,dim=c(length(d),64,6,5))
-tempmeansE <- tempmasksE
-tempmeansE2 <- tempmeansE
-tempmasksE2 <- tempmasksE
-tempspectraP <- array(0,dim=c(length(d),300))
-tempspectraE <- array(0,dim=c(length(d),300))
-tempwavesP <- array(0,dim=c(length(d),1680))
-tempwavesE <- array(0,dim=c(length(d),14000))
+allmasksP <- array(0,dim=c(length(d),6,5))
+allmeansP <- allmasksP
+allmasksE <- array(0,dim=c(length(d),64,6,5))
+allmeansE <- allmasksE
+allmeansE2 <- allmeansE
+allmasksE2 <- allmasksE
+allspectraP <- array(0,dim=c(length(d),300))
+allspectraE <- array(0,dim=c(length(d),300))
+allwavesP <- array(0,dim=c(length(d),1680))
+allwavesE <- array(0,dim=c(length(d),14000))
 
@@
 
-  tempmasksP[s,,] <- cleanmasksP
-  tempmeansP[s,,] <- cleanmeansP
-  tempspectraP[s,] <- meanspectraP
-  tempspectraE[s,] <- meanspectraE
-  tempwavesP[s,] <- meanwavesP
-  tempwavesE[s,] <- meanwavesE
-  tempmeansE[s,,,] <- cleanmeansE
-  tempmasksE[s,,,] <- cleanmasksE
-  tempmeansE2[s,,,] <- cleanmeansE2
-  tempmasksE2[s,,,] <- cleanmasksE2
+  allmasksP[s,,] <- cleanmasksP
+  allmeansP[s,,] <- cleanmeansP
+  allspectraP[s,] <- meanspectraP
+  allspectraE[s,] <- meanspectraE
+  allwavesP[s,] <- meanwavesP
+  allwavesE[s,] <- meanwavesE
+  allmeansE[s,,,] <- cleanmeansE
+  allmasksE[s,,,] <- cleanmasksE
+  allmeansE2[s,,,] <- cleanmeansE2
+  allmasksE2[s,,,] <- cleanmasksE2
 
@@
 
-tempspectraP <- tempspectraP[-c(2,4,13,20,26),]
+allspectraP <- allspectraP[-c(2,4,13,20,26),]
 
@@
 
-    temp <- tempmeansP[,cond,level]
+    temp <- allmeansP[,cond,level]
     cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-    temp <- tempmasksP[,cond,level]
+    temp <- allmasksP[,cond,level]
     cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-      temp <- apply(tempmeansE[,electrodeindices,cond,level],1,mean)
+      temp <- apply(allmeansE[,electrodeindices,cond,level],1,mean)
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-temp <- apply(tempmasksE[,electrodeindices,cond,level],1,mean)
+temp <- apply(allmasksE[,electrodeindices,cond,level],1,mean)
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-temp <- apply(tempmeansE2[,electrodeindices,cond,level],1,mean)
+temp <- apply(allmeansE2[,electrodeindices,cond,level],1,mean)
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-      temp <- apply(tempmasksE2[,electrodeindices,cond,level],1,mean)
+      temp <- apply(allmasksE2[,electrodeindices,cond,level],1,mean)
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-      temp <- tempmeansE[,ch,cond,level]
+      temp <- allmeansE[,ch,cond,level]
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-      temp <- tempmasksE[,ch,cond,level]
+      temp <- allmasksE[,ch,cond,level]
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-      temp <- tempmeansE2[,ch,cond,level]
+      temp <- allmeansE2[,ch,cond,level]
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-      temp <- tempmasksE2[,ch,cond,level]
+      temp <- allmasksE2[,ch,cond,level]
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-        temp <- tempspectraP[,f]
+        temp <- allspectraP[,f]
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 
-        temp <- tempspectraE[,f]
+        temp <- allspectraE[,f]
       cartdata <- data.frame(Re(temp),Im(temp))
@@
 meanwavesE <- NULL
-meanwavesPCI <- array(0,dim=c(2,dim(tempwavesP)[2]))
-meanwavesECI <- array(0,dim=c(2,dim(tempwavesE)[2]))
-nsubjs <- dim(tempwavesP)[1]
-for (t in 1:dim(tempwavesP)[2]){
-  temp <- tempwavesP[,t]
+meanwavesPCI <- array(0,dim=c(2,dim(allwavesP)[2]))
+meanwavesECI <- array(0,dim=c(2,dim(allwavesE)[2]))
+nsubjs <- dim(allwavesP)[1]
+for (t in 1:dim(allwavesP)[2]){
+  temp <- allwavesP[,t]
   i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
@@
 
-for (t in 1:dim(tempwavesE)[2]){
-    temp <- tempwavesE[,t]
+for (t in 1:dim(allwavesE)[2]){
+    temp <- allwavesE[,t]
   i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
@@
 
-save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes'))
+save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2'))
 
@@
 
+```{r include=FALSE, results='hide'}
+
+# generate plot showing the bin:mon ratio for three data sets
+
+if (processdata > 0){
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Averagedata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(file=paste0(datadir,'Averagedata.RData'))
+
+allPratios <- 20*log10(abs(allmeansP[,2,])/abs(allmeansP[,1,]))
+allEratios <- 20*log10(abs(apply(allmeansE[,electrodeindices,2,],c(1,3),mean))/abs(apply(allmeansE[,electrodeindices,1,],c(1,3),mean)))
+allE2ratios <- 20*log10(abs(apply(allmeansE2[,electrodeindices,2,],c(1,3),mean))/abs(apply(allmeansE2[,electrodeindices,1,],c(1,3),mean)))
+
+PratiosCI <- matrix(0,nrow=2,ncol=5)
+EratiosCI <- matrix(0,nrow=2,ncol=5)
+E2ratiosCI <- matrix(0,nrow=2,ncol=5)
+for (level in 1:5){
+    bspop <- NULL
+    for (n in 1:nbootstraps){
+      bspop[n] <- mean(sample(allPratios[,level],nrow(allPratios),replace=TRUE))
+    }
+    PratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
+     bspop <- NULL
+    for (n in 1:nbootstraps){
+      bspop[n] <- mean(sample(allEratios[,level],nrow(allEratios),replace=TRUE))
+    }
+    EratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
+    bspop <- NULL
+    for (n in 1:nbootstraps){
+      bspop[n] <- mean(sample(allE2ratios[,level],nrow(allE2ratios),replace=TRUE))
+    }
+    E2ratiosCI[,level] <- quantile(bspop,c((1-0.68)/2,1-((1-0.68)/2)))
+}
+
+plotlims <- c(15,40,-3,12)  
+ticklocsx <- contrastsdB
+ticklabelsx <-c(6,12,24,48,96) 
+ticklocsy <- seq(-3,12,3)    # locations of tick marks on y axis
+ticklabelsy <- c(expression(1/sqrt(2)),'1',expression(sqrt(2)),'2',expression(2*sqrt(2)),'4')
+
+pdf("Figures/BSratios.pdf", onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Bin:Mon ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+arrows(contrastsdB,colMeans(allPratios),contrastsdB,PratiosCI[1,],lwd=3,col=colpal[3],length=0.05,angle=90)
+arrows(contrastsdB,colMeans(allPratios),contrastsdB,PratiosCI[2,],lwd=3,col=colpal[3],length=0.05,angle=90)
+arrows(contrastsdB,colMeans(allEratios),contrastsdB,EratiosCI[1,],lwd=3,col=colpal[4],length=0.05,angle=90)
+arrows(contrastsdB,colMeans(allEratios),contrastsdB,EratiosCI[2,],lwd=3,col=colpal[4],length=0.05,angle=90)
+arrows(contrastsdB,colMeans(allE2ratios),contrastsdB,E2ratiosCI[1,],lwd=3,col=colpal[5],length=0.05,angle=90)
+arrows(contrastsdB,colMeans(allE2ratios),contrastsdB,E2ratiosCI[2,],lwd=3,col=colpal[5],length=0.05,angle=90)
+
+lines(contrastsdB,colMeans(allPratios), col=colpal[3], lwd=3, cex=0.5)
+lines(contrastsdB,colMeans(allEratios), col=colpal[4], lwd=3, cex=0.5)
+lines(contrastsdB,colMeans(allE2ratios), col=colpal[5], lwd=3, cex=0.5)
+
+points(contrastsdB,colMeans(allPratios), pch = 21, col='black', bg=colpal[3], cex=1.6, lwd=3) 
+points(contrastsdB,colMeans(allEratios), pch = 22, col='black', bg=colpal[4], cex=1.6, lwd=3)
+points(contrastsdB,colMeans(allE2ratios), pch = 23, col='black', bg=colpal[5], cex=1.6, lwd=3)
+
+legend(15,12,c('Pupillometry','EEG 1F', 'EEG 2F'), pch=21:23, pt.bg=colpal[3:5],box.lwd=2,pt.cex=1.6,pt.lwd=3)
+
+dev.off()
+
+}
+
+```
+
+```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'BSratios.pdf'))
+
+```
+
 ## Experiment 2
@@
 The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
+
 ```{r include=FALSE, results='hide'}
@@
 \@ref(fig:EEGdata)).
+
 ```{r include=FALSE, results='hide'}
@@
 
-tempmasksP <- array(0,dim=c(length(d),6,5))
-tempmeansP <- tempmasksP
-tempmasksE <- array(0,dim=c(length(d),64,6,5))
-tempmeansE <- tempmasksE
-tempmeansE2 <- tempmeansE
-tempmasksE2 <- tempmasksE
+allmasksP <- array(0,dim=c(length(d),6,5))
+allmeansP <- allmasksP
+allmasksE <- array(0,dim=c(length(d),64,6,5))
+allmeansE <- allmasksE
+allmeansE2 <- allmeansE
+allmasksE2 <- allmasksE
 
@@
 
-  tempmasksP[s,,] <- cleanmasksP
-  tempmeansP[s,,] <- cleanmeansP
-  tempmeansE[s,,,] <- cleanmeansE
-  tempmasksE[s,,,] <- cleanmasksE
-  tempmeansE2[s,,,] <- cleanmeansE2
-  tempmasksE2[s,,,] <- cleanmasksE2
+  allmasksP[s,,] <- cleanmasksP
+  allmeansP[s,,] <- cleanmeansP
+  allmeansE[s,,,] <- cleanmeansE
+  allmasksE[s,,,] <- cleanmasksE
+  allmeansE2[s,,,] <- cleanmeansE2
+  allmasksE2[s,,,] <- cleanmasksE2
 
@@
   i <- 0
-  for (subj in 1:dim(tempmeansP)[1]){
+  for (subj in 1:dim(allmeansP)[1]){
     for (cond in 1:length(condlist)){
       for (cont in 1:length(contlist)){
-        dp <- abs(tempmeansP[subj,condlist[cond],cont])
+        dp <- abs(allmeansP[subj,condlist[cond],cont])
         if (is.na(dp)==0){
@@
   i <- 0
-  for (subj in 1:dim(tempmeansE)[1]){
+  for (subj in 1:dim(allmeansE)[1]){
     for (cond in 1:length(condlist)){
       for (cont in 1:length(contlist)){
-        dp <- abs(mean(tempmeansE[subj,electrodeindices,condlist[cond],cont]))
+        dp <- abs(mean(allmeansE[subj,electrodeindices,condlist[cond],cont]))
         if (is.na(dp)==0){
@@
   i <- 0
-  for (subj in 1:dim(tempmeansE)[1]){
+  for (subj in 1:dim(allmeansE)[1]){
     for (cond in 1:length(condlist)){
       for (cont in 1:length(contlist)){
-        dp <- abs(mean(tempmeansE2[subj,electrodeindices,condlist[cond],cont]))
+        dp <- abs(mean(allmeansE2[subj,electrodeindices,condlist[cond],cont]))
         if (is.na(dp)==0){
@@
 
-  pupilweightpop <- pupilsamples@sim$samples[[1]]$wtmu
-  pupilW <- median(pupilsamples@sim$samples[[1]]$wtmu)
-  pupilZ <- median(pupilsamples@sim$samples[[1]]$Zmu)
-  pupilK <- median(pupilsamples@sim$samples[[1]]$kmu)
-  pupilRmax <- median(pupilsamples@sim$samples[[1]]$Rmaxmu)
-
-  EEGweightpop <- EEG1Fsamples@sim$samples[[1]]$wtmu
-  EEGW <- median(EEG1Fsamples@sim$samples[[1]]$wtmu)
-  EEGZ <- median(EEG1Fsamples@sim$samples[[1]]$Zmu)
-  EEGK <- median(EEG1Fsamples@sim$samples[[1]]$kmu)
-  EEGRmax <- median(EEG1Fsamples@sim$samples[[1]]$Rmaxmu)
-
-  EEG2weightpop <- EEG2Fsamples@sim$samples[[1]]$wtmu
-  EEG2W <- median(EEG2Fsamples@sim$samples[[1]]$wtmu)
-  EEG2Z <- median(EEG2Fsamples@sim$samples[[1]]$Zmu)
-  EEG2K <- median(EEG2Fsamples@sim$samples[[1]]$kmu)
-  EEG2Rmax <- median(EEG2Fsamples@sim$samples[[1]]$Rmaxmu)
-
-  matchingweightpop <- matchingsamples@sim$samples[[1]]$wmu
-  matchingW <- median(matchingsamples@sim$samples[[1]]$wmu)
-  matchingZ <- median(matchingsamples@sim$samples[[1]]$Zmu)
-  matchingK <- median(matchingsamples@sim$samples[[1]]$kmu)
+  nchains <- dim(pupilsamples)[2]
+  pupilweightpop <- NULL
+  pupilZpop <- NULL
+  pupilKpop <- NULL
+  pupilRpop <- NULL
+  for (n in 1:nchains){
+  pupilweightpop <- c(pupilweightpop,pupilsamples@sim$samples[[n]]$wtmu)
+  pupilZpop <- c(pupilZpop,pupilsamples@sim$samples[[n]]$Zmu)
+  pupilKpop <- c(pupilKpop,pupilsamples@sim$samples[[n]]$kmu)
+  pupilRpop <- c(pupilRpop,pupilsamples@sim$samples[[n]]$Rmaxmu)
+  }
+  pupilW <- median(pupilweightpop)
+  pupilZ <- median(pupilZpop)
+  pupilK <- median(pupilKpop)
+  pupilRmax <- median(pupilRpop)
+
+  nchains <- dim(EEG1Fsamples)[2]
+  EEGweightpop <- NULL
+  EEGZpop <- NULL
+  EEGKpop <- NULL
+  EEGRpop <- NULL
+  for (n in 1:nchains){
+  EEGweightpop <- c(EEGweightpop,EEG1Fsamples@sim$samples[[n]]$wtmu)
+  EEGZpop <- c(EEGZpop,EEG1Fsamples@sim$samples[[n]]$Zmu)
+  EEGKpop <- c(EEGKpop,EEG1Fsamples@sim$samples[[n]]$kmu)
+  EEGRpop <- c(EEGRpop,EEG1Fsamples@sim$samples[[n]]$Rmaxmu)
+  }
+  EEGW <- median(EEGweightpop)
+  EEGZ <- median(EEGZpop)
+  EEGK <- median(EEGKpop)
+  EEGRmax <- median(EEGRpop)
+
+  nchains <- dim(EEG2Fsamples)[2]
+  EEG2weightpop <- NULL
+  EEG2Zpop <- NULL
+  EEG2Kpop <- NULL
+  EEG2Rpop <- NULL
+  for (n in 1:nchains){
+  EEG2weightpop <- c(EEG2weightpop,EEG2Fsamples@sim$samples[[n]]$wtmu)
+  EEG2Zpop <- c(EEG2Zpop,EEG2Fsamples@sim$samples[[n]]$Zmu)
+  EEG2Kpop <- c(EEG2Kpop,EEG2Fsamples@sim$samples[[n]]$kmu)
+  EEG2Rpop <- c(EEG2Rpop,EEG2Fsamples@sim$samples[[n]]$Rmaxmu)
+  }
+  EEG2W <- median(EEG2weightpop)
+  EEG2Z <- median(EEG2Zpop)
+  EEG2K <- median(EEG2Kpop)
+  EEG2Rmax <- median(EEG2Rpop)
+
+  nchains <- dim(matchingsamples)[2]
+  matchingweightpop <- NULL
+  matchingZpop <- NULL
+  matchingKpop <- NULL
+  for (n in 1:nchains){
+  matchingweightpop <- c(matchingweightpop,matchingsamples@sim$samples[[n]]$wmu)
+  matchingZpop <- c(matchingZpop,matchingsamples@sim$samples[[n]]$Zmu)
+  matchingKpop <- c(matchingKpop,matchingsamples@sim$samples[[n]]$kmu)
+  }
+  matchingW <- median(matchingweightpop)
+  matchingZ <- median(matchingZpop)
+  matchingK <- median(matchingKpop)
 
@@
 
-plotlims <- c(-48,12,0,0.5) 
+plotlims <- c(-48,12,0,0.6) 
 ticklocsx <- seq(-48,12,12)    
-ticklocsy <- seq(0,0.5,0.1)    
+ticklocsy <- seq(0,0.6,0.1)    
 ticklabelsx <- c('1/256','1/64','1/16','1/4','1','4')        
@@
 
-lines(20*log10(c(mean(pupilW),mean(pupilW))),c(0,0.3),lwd=3,col=colpal[3])
-lines(20*log10(c(mean(EEGW),mean(EEGW))),c(0,0.3),lwd=3,col=colpal[4])
-lines(20*log10(c(mean(EEG2W),mean(EEG2W))),c(0,0.3),lwd=3,col=colpal[5])
-lines(20*log10(c(mean(matchingW),mean(matchingW))),c(0,0.3),lwd=3,col=colpal[6])
-
-legend(-48,0.5,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')
-
-text(9,0.48,'(i)',cex=1.25,adj=0.5)
+lines(20*log10(c(mean(pupilW),mean(pupilW))),c(0,0.6),lwd=3,col=colpal[3])
+lines(20*log10(c(mean(EEGW),mean(EEGW))),c(0,0.6),lwd=3,col=colpal[4])
+lines(20*log10(c(mean(EEG2W),mean(EEG2W))),c(0,0.6),lwd=3,col=colpal[5])
+lines(20*log10(c(mean(matchingW),mean(matchingW))),c(0,0.6),lwd=3,col=colpal[6])
+
+legend(-48,0.6,c('Prior','Pupillometry','EEG 1F','EEG 2F','Matching'),col=c('black',colpal[3:6]),lwd=c(1,3,3,3,3),lty=1, box.lwd=2, bg='white')
+
+text(9,0.58,'(i)',cex=1.25,adj=0.5)
 

### 2022-10-16 manuscript.Rmd
Updates to manuscript

@@
 ---
-title: "Different rules for binocular combination of luminance in cortical and subcortical pathways"
-author: "Federico G. Segala, Aurelio Bruno, Alex R. Wade &  Daniel H. Baker (+Myat? +Joel?)"
+title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
+author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
 date: "`r Sys.Date()`"
@@
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','osfr') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','osfr') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
+anovacirc2way <- function(data, groupA=NULL, groupB=NULL, participant=NULL){
+
+  grouplabelsA <- groupA
+  grouplabelsB <- groupB
+  participantlabels <- participant
+  datavals <- data
+
+  grouplabelsA <- as.factor(grouplabelsA)
+  factorlistA <- levels(grouplabelsA)
+  grouplabelsB <- as.factor(grouplabelsB)
+  factorlistB <- levels(grouplabelsB)
+  participantlabels <- as.factor(participantlabels)
+  participantlist <- levels(participantlabels)
+
+  grandmean <- mean(datavals)
+  grandvar <- sum(abs(datavals - grandmean)^2)/(length(datavals)-1)
+
+    SST <- grandvar*(length(datavals) - 1)
+
+    SSW <- 0
+    for (n in 1:nlevels(participantlabels)){SSW <- SSW + sum(abs(datavals[which(participantlabels==participantlist[n])] - mean(datavals[which(participantlabels==participantlist[n])]))^2)}
+    dfW <- 2*(nlevels(participantlabels)*(nlevels(grouplabelsA)*nlevels(grouplabelsB)-1))
+
+    SSBet <- SST - SSW  # between subjects SS - not actually used
+    SSM <- 0
+    for (a in 1:nlevels(grouplabelsA)){
+      for (b in 1:nlevels(grouplabelsB)){
+        i <- as.numeric(((grouplabelsA==grouplabelsA[a])))
+        j <- as.numeric(((grouplabelsB==grouplabelsB[b])))
+        indices <- which((i*j)>0)
+        SSM <- SSM + (nlevels(participantlabels)*sum(abs(datavals[indices] - grandmean)^2))
+      }
+    }
+    dfM <- 2*((nlevels(grouplabelsA)*nlevels(grouplabelsB))-1)
+
+    SSR <- 0
+    for (a in 1:nlevels(grouplabelsA)){
+      for (b in 1:nlevels(grouplabelsB)){
+        i <- as.numeric(((grouplabelsA==grouplabelsA[a])))
+        j <- as.numeric(((grouplabelsB==grouplabelsB[b])))
+        indices <- which((i*j)>0)
+        condvar <- sum(abs(datavals[indices] - mean(datavals[indices]))^2)/(length(indices)-1)
+        SSR <- SSR + (nlevels(participantlabels)-1)*condvar
+      }
+    }    
+    dfR <- 2*(nlevels(participantlabels)-1)*(nlevels(grouplabelsA)*nlevels(grouplabelsB))
+
+    groupmeansA <- NULL
+    for (n in 1:nlevels(grouplabelsA)){groupmeansA[n] <- mean(datavals[which(grouplabelsA==factorlistA[n])])}
+    SSA <- 0
+    for (n in 1:nlevels(grouplabelsA)){SSA <- SSA + length(which(grouplabelsA==factorlistA[n]))*abs(groupmeansA[n]-grandmean)^2}
+    dfA <- 2*(nlevels(grouplabelsA)-1)
+
+    groupmeansB <- NULL
+    for (n in 1:nlevels(grouplabelsB)){groupmeansB[n] <- mean(datavals[which(grouplabelsB==factorlistB[n])])}
+    SSB <- 0
+    for (n in 1:nlevels(grouplabelsB)){SSB <- SSB + length(which(grouplabelsB==factorlistB[n]))*abs(groupmeansB[n]-grandmean)^2}
+    dfB <- 2*(nlevels(grouplabelsB)-1)
+
+    SSAB <- SSW - (SSA + SSB)
+    dfAB <- 2 * (nlevels(grouplabelsA)-1) * (nlevels(grouplabelsB)-1)
+
+    MSA <- SSA/dfA
+    MSB <- SSB/dfB
+    MSAB <- SSAB/dfAB
+    MSR <- SSR/dfR
+
+    FratioA <- MSA/MSR
+    pvalA <- pf(FratioA,df1=dfA,df2=dfR,lower.tail=FALSE)
+    FratioB <- MSB/MSR
+    pvalB <- pf(FratioB,df1=dfB,df2=dfR,lower.tail=FALSE)
+    FratioAB <- MSAB/MSR
+    pvalAB <- pf(FratioAB,df1=dfAB,df2=dfR,lower.tail=FALSE)
+
+    method <- 'Factorial repeated measures ANOVA^2-circ'
+    output <- data.frame(FratioA,pvalA,FratioB,pvalB,FratioAB,pvalAB,dfA,dfB,dfAB,dfR,method)
+
+  return(output)
+}
+
 colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
@@
 # Introduction
+
+---------------------------------
+OK, some pointers for the introduction:
+
+I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
+Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
+I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
+
+The key points should be:
+
+1. For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
+
+2. Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
+
+3.
+We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
+
+4. Actually there's not much work on temporal binocular combination even in the primary visual pathway.
+
+5. We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
+
+I wouldn't say too much about models, or about the matching experiment, at this stage.
+---------------------------------
+
 Binocular combination provides a higher visual sensitivity than monocular viewing.
@@
 
+Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
+Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
+These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other [@Ding2006].
+In the earlier stage, the right and left eye channels exert gain control on the other channel.
+Then, they exert gain control on the other channel’s gain control.
+Lastly, the outputs from each channel are summed binocularly to determine the binocular signal’s magnitude.
+The second model is similar as it also incorporates gain control mechanisms [@Meese2006].
+In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
+Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
+This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
+
 To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
@@
 
-Our experiment used different stimuli than the ones used by Anstis and Ho: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
+Our experiment used different stimuli than the ones used by @Anstis1998: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
 In our experiment, in some conditions, the flicker was shown to only one eye.
@@
 # Methods
+
 ## Participants
-Thirty, twelve and ten participants were recruited for experiment 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision.
-All participants gave written informed consent.
-
-## Apparatus & Stimuli
+
+Thirty, twelve and ten participants were recruited for Experiments 1, 2 and 3 respectively. All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+
+## Apparatus & stimuli
+
 The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background.
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in figure \@ref(fig:pupildata)a for an example of the of the fused stimuli).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc.
-The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \@ref(fig:pupildata)b for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
 
@@
 
-EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
-Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, @Kassner2014) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH, @Kassner2014).
+EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
 ## Procedure
+
 Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
@@
 
-### Experiment 1
+### Experiment 1: simultaneous EEG and pupillometry
+
 The experiment was conducted in a windowless room, in which the only light source was the monitor.
-The participants sat at 99 cm from the monitor and their viewing distance through the stereoscope was 107 cm.
+The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
 The experiment was carried out in one session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
 In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants had no task and were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
-The discs flickered in counterphase at 2 Hz, but in some conditions (cross-frequency conditions) one of the two discs flickered at 1.6 Hz.
-They were set at five temporal contrast levels relative to the mean luminance: 6, 12, 24, 48 and 96 \%.
-
-As already stated, the mirror stereoscope allowed the use of three different ocular configurations.
-In the monocular configuration, one disc was set to flicker either at 2 Hz or 1.6 Hz for each contrast level, while the other disc remained stable at a constant mean luminance.
-In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz.
-Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 \%.
-Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.
-
-### Experiment 2
-The conditions were similar to experiment 1 (windowless room and viewing distance of 107 cm).
-Like in experiment 1, participants had no specific task other than looking at the fixation crosses and minimising their blinking.
-Unlike the first experiment, only one contrast level was used (96 \%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+The participants were given no specific task instructions, but were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
+We included six distinct ocular conditions, each at five temporal target contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a fixed luminance contrast of 48\%.
+In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
+We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
+The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
+The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
+the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
+We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+### Experiment 2: EEG responses across temporal frequency
+
+This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
+Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
 Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
-
-The experiment was carried out in one session lasting 25 minutes in total, divided in five blocks of 5 minutes each.
-In each block, there were 20 trials in total lasting 15 seconds each (12s of stimulus presentation and 3s of interstimulus interval).
-
-### Experiment 3
-The experiment was conducted in a room with a blacked-out window.
-The sitting and viewing distances of the participants were similar to the two previous experiments.
-As this was a psychophysical task, no EEG or pupillometry data were collected for this experiment.
-
-A two-interval forced-choice staircase procedure was used to collect data.
-In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48 \%), which was selected by the experimenter at the beginning of each block.
-In a separate interval, a target fused disc flickering at varying contrast levels was displayed.
+The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
+In each block, there were 20 trials in total with the same timing as for Experiment 1.
+
+### Experiment 3: temporal contrast matching
+
+The experiment was conducted in a darkened room with a blacked-out window.
+The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
+A two-interval contrast matching procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
+In the other interval, a target disc flickering at varying contrast levels was displayed.
 The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
-The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1.
-The standard and the target fused discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
+The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
 After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
-The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz.
-
-Due to its long duration (162 minutes in total), the participants completed the experiment across multiple sessions divided at their own discretion.
-The experiment was divided in 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each (depending on the response speed of the participant).
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
+
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
 In each block, there were a total of 50 trials.
-We pooled the data from all repetitions of a given condition and fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50 \% point.
+No auditory feedback was given for this subjective task.
 
 ## Data analysis
+
 EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
-The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted.
-Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The fast Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
 All repetitions of each condition were then averaged for each electrode.
-They were then averaged across the four occipital electrodes (POz, Oz, O1, O2), to obtain individual results.
-Finally, these were averaged across all participants to obtain the final results.
-
-A similar process was adopted for the analysis of the pupillometry data.
-The data were converted from the mp4 format to a  csv text file using the Pupil Player software [@Kassner2014].
-The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted.
-Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
-All repetitions of each condition were then averaged for each eye.
-They were then averaged across the two eyes, to obtain individual results.
-Finally, these were averaged across all participants to obtain the final results.
+They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
+Finally, these were averaged across participants to obtain the group results.
+All averaging retained the phase information (i.e.
+coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
+For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.
+
+A similar analysis pipeline was adopted for the pupillometry data.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The fast Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
+Note that previous pupillometry studies using luminance flicker have tended to fit sine-waves to the data, rather than using Fourier analysis [e.g.
+@Spitschan2014].
+Our novel approach is more robust to noise at other frequencies, and makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
+@Figueira2022]
+
+To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
+We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
+Thresholds were averaged across participants in logarithmic (dB) units.
+For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
+
+## Computational model and parameter estimation
+
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by @Meese2006.
+The second gain control stage was omitted [consistent with @Baker2017] to simplify the model and reduce the number of free parameters.
+The response of the left eye's channel is given by:
+
+\begin{equation}
+\label{eq:respL}
+Resp_L = \frac{L^2}{Z + L + wR},
+\end{equation}
+
+with an equivalent expression for the right eye:
+
+\begin{equation}
+\label{eq:respR}
+Resp_R = \frac{R^2}{Z + R + wL}.
+\end{equation}
+
+In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+Resp_B = R_{max}(Resp_L + Resp_R) + n,
+\end{equation}
+
+where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
+The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it had no effect in this paradigm.
+
+Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
+@Ding2006; @Legge1984; @Schrodinger1926].
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
+Our key parameter of interest is the weight of interocular suppression.
+Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
+Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
+
+We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$.
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+The models were fit using the individual data across all participants, independently for each data set.
+Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+However it is clear that the character of the model in all cases gives a good representation of the data.
+We sampled over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+
+## Preregistration, data and code availability
+
+We initially preregistered our main hypotheses and analysis intentions for the first experiment.
+We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then ran the main experiment, followed by two additional experiments that were not preregistered.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://osf.io/tbema/.
 
 # Results
+
 ## Experiment 1
-The results from the first experiment are shown in figure \@ref(fig:pupildata) and figure \@ref(fig:EEGdata).
-Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
-
-Figure \@ref(fig:pupildata) is showing the results for the pupillometry.
-Figure \@ref(fig:pupildata)a is showing the group average waveform for binocular presentation.
-Figure \@ref(fig:pupildata)b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli.
-Figures \@ref(fig:pupildata)c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz.
-In the same-frequency condition at 2 Hz (fig.
-\@ref(fig:pupildata)c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration.
-In general, we observe that the binocular to monocular ratio is roughly $\sqrt2$ at each contrast level (fig.
-).
-In the cross-frequency condtion at 2 Hz (fig.
-\@ref(fig:pupildata)d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition.
-Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.
-\@ref(fig:pupildata)e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels.
-This facilitation is then lost at the highest contrast level, where the amplitude of the monocular signal is equal to the amplitude of the binocular signal.
-This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils.
-Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.
-
-Figure \@ref(fig:EEGdata) shows the results for EEG.
-Figure \@ref(fig:EEGdata)a is showing the group average waveform for binocular presentation.
-Figure \@ref(fig:EEGdata)b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics.
-Figures \@ref(fig:EEGdata)c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \@ref(fig:EEGdata)f-h show the CRFs at the second harmonic.
-What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.
-\@ref(fig:EEGdata)c) and second (fig.
-\@ref(fig:EEGdata)f) harmonics are showing very high summation of binocular signals compared to the pupillometry.
-The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses.
-This is especially clear at the highest contrasts.
-This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry.
-For the cross-frequency condition at 2 Hz and 4 Hz (fig.
-\@ref(fig:EEGdata)d and \@ref(fig:EEGdata)g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals.
-This pattern is also observable in the cross-frequency condition at 1.6 (fig.
-\@ref(fig:EEGdata)e) and 3.2 Hz (fig.
-\@ref(fig:EEGdata)h).
-This pattern of results seems to suggest that processing of temporal luminance modulations happens in a  linear way in the visual cortex.
-Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.
 
@@
 
-if (processdata > 0){
-
-contrastsdB <- 20*log10(c(6,12,24,48,96))
-
          if (!file.exists(paste0(datadir,'Averagedata.RData'))){
@@
 
+if (processdata > 0){
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
 plotlims <- c(15,40,0,0.03) 
@@
 dev.off()
+
+         if (!file.exists(paste0(localdir,'StimulusExample.png'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'tbema'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='StimulusExample.png')
+          osf_download(osffiles[fid,],localdir,progress=TRUE)
+         }
+
+stim <- readPNG('local/StimulusExample.png')
 
@@
 
+  aspratio <- 10/15  # this is the aspect ratio of the output pdf
+  imwidth <- 0.2
+  xstart <- 0.85
+  ystart <- 0.72
+  rasterImage(stim,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
   grid.picture(p1,x=0.17,y=0.25,width=0.32,height=1)
@@
 
+```{r include=FALSE, results='hide'}
+
+# do statistics on the pupillometry data
+
+alldata <- NULL
+groupID <- NULL
+allP <- NULL
+counter <- 0
+for (cont in 1:dim(allmeansP)[3]){
+  for (p in 1:dim(allmeansP)[1]){
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,3,cont]
+    groupID[counter] <- cont
+    allP[counter] <- p
+  }
+}
+dichA2c <- anovacirc.test(alldata,group=groupID,participant=allP)
+# groupID <- as.factor(groupID)
+# participantID <- as.factor(participantID)
+# adata <- data.frame(dichdata,groupID,participantID)
+# dichA2c <- ezANOVA(data = adata, dv = dichdata, within=groupID, wid=participantID)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    for (cond in 1:2){
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,cond,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- cond
+    allP[counter] <- p
+    }
+  }
+}
+monbinPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# monbinPstats <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,1,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,3,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+mondichPstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# mondichPstats <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,1,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,5,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+
+monbinPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# monbinPstatsX <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,1,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- allmeansP[p,6,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+
+mondichPstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# mondichPstatsX <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+```
+
+The pupillometry results are summarised in Figure \@ref(fig:pupildata).
+The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildata)a.
+There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
+The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a substantial spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
+
 ```{r pupildata, fig.cap="Summary of pupillometry results for N=30 participants.
 Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum.
+Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
 Panels (c,d) show contrast response functions at 2Hz for different conditions.
@@
 
+Figure \@ref(fig:pupildata)c shows contrast response functions in response to stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
+The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
+A $2\times5$ repeated measures $ANOVA^2_{circ}$ [@Baker2021] comparing these conditions revealed a significant main effect of target contrast (F(`r monbinPstats$dfA`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioA,digits=2)`, $p$ < 0.001), a significant effect of condition (F(`r monbinPstats$dfB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioB,digits=2)`, $p$ < 0.001), and a significant interaction (F(`r monbinPstats$dfAB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioAB,digits=2)`, $p$ < 0.001).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(`r dichA2c$dfM`,`r dichA2c$dfR`) = `r round(dichA2c$Fratio,digits=2)`, $p$ < `r round(dichA2c$pval,digits=3)`).
+
+In Figure \@ref(fig:pupildata)d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildata)c for comparison).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(`r monbinPstatsX$dfAB`,`r monbinPstatsX$dfR`) = `r round(monbinPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
+When the 1.6Hz component had a fixed contrast of 48% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(`r mondichPstatsX$dfAB`,`r mondichPstatsX$dfR`) = `r round(mondichPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
+
+Figure \@ref(fig:pupildata)e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Surprisingly there appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
+The dichoptic cross condition does not show clear modulation with target contrast.
+
+Figure \@ref(fig:EEGdata) shows equivalent results, measured contemporaneously using EEG.
+Figure \@ref(fig:EEGdata)a shows the group average waveform for binocular presentation, and Figure \@ref(fig:EEGdata)b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (_Oz_, _POz_, _O1_ and _O2_, marked on the inset scalp plots).
+Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
+We therefore calculated contrast response functions at both first and second harmonic frequencies.
+
 ```{r include=FALSE, results='hide'}
@@
 # generate plot showing the group EEG data
-
-if (processdata > 0){
 
@@
 electrodeindices <- match(targetelectrodes,electrodes)-2
+
+if (processdata > 0){
 
@@
 
+```{r include=FALSE, results='hide'}
+
+# do statistics on the EEG data
+
+alldata <- NULL
+groupID <- NULL
+allP <- NULL
+counter <- 0
+for (cont in 1:dim(allmeansP)[3]){
+  for (p in 1:dim(allmeansP)[1]){
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,3,cont])
+    groupID[counter] <- cont
+    allP[counter] <- p
+  }
+}
+dichE2c <- anovacirc.test(alldata,group=groupID,participant=allP)
+# groupID <- as.factor(groupID)
+# participantID <- as.factor(participantID)
+# adata <- data.frame(dichdata,groupID,participantID)
+# dichE2c <- ezANOVA(data = adata, dv = dichdata, within=groupID, wid=participantID)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    for (cond in 1:2){
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,cond,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- cond
+    allP[counter] <- p
+    }
+  }
+}
+monbinEstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# monbinEstats <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,1,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,3,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+mondichEstats <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# mondichEstats <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,1,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,5,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+
+monbinEstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# monbinEstatsX <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,1,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- mean(allmeansE[p,electrodeindices,6,lev])
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+
+mondichEstatsX <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+# allgroupA <- as.factor(allgroupA)
+# allgroupB <- as.factor(allgroupB)
+# allP <- as.factor(allP)
+# alldata <- abs(alldata)
+# adata <- data.frame(alldata,allgroupA,allgroupB,allP)
+# mondichEstatsX <- ezANOVA(data = adata, dv = alldata, within=c(allgroupA,allgroupB), wid=allP)
+
+```
+
 ```{r EEGdata, fig.cap="Summary of EEG results for N=30 participants.
@@
 
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \@ref(fig:EEGdata)c) and second (Figure \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`).
+For the cross-frequency conditions (Figure \@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \@ref(fig:EEGdata)e) and 3.2Hz (Figure \@ref(fig:EEGdata)h).
+This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
+
 ```{r include=FALSE, results='hide'}
@@
 # generate plot showing the bin:mon ratio for three data sets
-
-if (processdata > 0){
-
-contrastsdB <- 20*log10(c(6,12,24,48,96))
-electrodeindices <- match(targetelectrodes,electrodes)-2
 
@@
 
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
 allPratios <- 20*log10(abs(allmeansP[,2,])/abs(allmeansP[,1,]))
@@
 allE2ratios <- 20*log10(abs(apply(allmeansE2[,electrodeindices,2,],c(1,3),mean))/abs(apply(allmeansE2[,electrodeindices,1,],c(1,3),mean)))
+
+allratios <- NULL
+allconds <- NULL
+allconts <- NULL
+allparticipants <- NULL
+counter <- 0
+for (cont in 1:length(contrastsdB)){
+  for (s in 1:nrow(allPratios)){
+    counter <- counter + 1
+    allratios[counter] <- allPratios[s,cont]
+    allconds[counter] <- 1
+    allparticipants[counter] <- s
+    allconts[counter] <- cont
+
+    counter <- counter + 1
+    allratios[counter] <- allEratios[s,cont]
+    allconds[counter] <- 2
+    allparticipants[counter] <- s
+    allconts[counter] <- cont
+
+    counter <- counter + 1
+    allratios[counter] <- allE2ratios[s,cont]
+    allconds[counter] <- 3
+    allparticipants[counter] <- s
+    allconts[counter] <- cont
+
+  }
+}
+allparticipants <- as.factor(allparticipants)
+allconds <- as.factor(allconds)
+allconts <- as.factor(allconts)
+aovdata <- data.frame(allparticipants,allconds,allconts,allratios)
+ratioaov <- ezANOVA(aovdata,dv=allratios,within=c(allconds,allconts),wid=allparticipants)
+gg <- ratioaov$`Sphericity Corrections`$GGe
+
+if (processdata > 0){
 
@@
 
-```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types.", fig.align="center", echo=FALSE}
+Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
+Figure \@ref(fig:BSratios) shows that these ratios are approximately $\sqrt2$ across the low-to-intermediate contrast range for all three data types.
+At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \@ref(fig:pupildata) and \@ref(fig:EEGdata).
+A $3 \times 5$ repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(`r round(ratioaov$ANOVA$DFn[2]*gg[2],digits=2)`,`r round(ratioaov$ANOVA$DFd[2]*gg[2],digits=2)`) = `r round(ratioaov$ANOVA$F[2],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[2],digits=3)`), no effect of data modality (F(`r ratioaov$ANOVA$DFn[1]`,`r ratioaov$ANOVA$DFd[1]`) = `r round(ratioaov$ANOVA$F[1],digits=2)`, \emph{p} = `r round(ratioaov$ANOVA$p[1],digits=2)`), but a highly significant interaction (F(`r round(ratioaov$ANOVA$DFn[3]*gg[3],digits=2)`,`r round(ratioaov$ANOVA$DFd[3]*gg[3],digits=2)`) = `r round(ratioaov$ANOVA$F[3],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[3],digits=4)`).
+
+```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types.
+Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
 
@@
 ## Experiment 2
-The results from the second experiment are shown in \@ref(fig:TFdata).
-Figure \@ref(fig:TFdata)a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz).
-We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics.
-However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded.
-This is also reflected in figure \@ref(fig:TFdata)b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz.
-The rest of figure \@ref(fig:TFdata)b is showing the response at each stimulation frequency.
-We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz.
-In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig.
-\@ref(fig:TFdata)c), suggesting that binocular facilitation is happening at higher frequencies.
-However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \@ref(fig:TFdata)c).
-The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
+
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli [@Baker2017].
+One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
+We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz [@Spitschan2014].
 
@@
 
+Results from the temporal frequency experiment are shown in \@ref(fig:TFdata).
+Figure \@ref(fig:TFdata)a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
+However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
+Figure \@ref(fig:TFdata)b compares the monocular and binocular responses at each stimulation frequency.
+Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
+\@ref(fig:TFdata)c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
+
 ```{r TFdata, fig.cap="Binocular facilitation at different temporal frequencies.
 Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
-Panel (b) shows the response at each stimulation frequency for monocular (red) and binocular (blue) presentation.
+Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
 Panel (c) shows the ratio of binocular to monocular responses.
@@
 ## Experiment 3
-The results from the third experiment are shown in figure \@ref(fig:matchingdata).
-Each curve is showing the contrast level in each eye for the different interocular ratios at the 24 \% (in red) and 48 \% (in blue) conditions.
-
-Looking at the results for the 48 \% contrast condition, we can observe that, when the match was presented binocularly (both eyes saw the same stimulus), the match appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
-This is also observable for the 24 \% contrast condition, where the match appeared to have the same flickering intensity as the standard when the contrast was selected to be around 25 \%.
-These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
-
-When the match was presented monocularly (only one eye was presented with a flickering stimulus), we observe that, for the match to appear to flicker similarly to the standard, the contrast in that eye was set to be around double the contrast of the standard.
-When the flicker was presented only to the left eye, for the 48 \% contrast, the contrast of the match was around 90 \%, and, for the 24 \% contrast, the contrast of the match was around 57 \%.
-When the flicker was presented only to the right eye, for the 48 \% contrast, the contrast in the right eye was around 96 \%, and, for the 24 \% contrast, the contrast was around 50 \%.
-When looking at the intermediate condition, we can see that the points, for both contrast conditions, seem to fall along the main diagonal representing the linear summation prediction, with the results for the 24 \% condition showing a very strong summation that seem to exceed this prediction.
-Overall, these results seem to suggest that the way we perceive temporal luminance modulations follows near linear combination rules, which is in line with the processes observed in the visual cortex in experiment 1 (fig.
-\@ref(fig:EEGdata)).
+
+In Experiment 1 we found evidence of much stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+Since perception is dependent on cortical responses, these results provide a clear prediction for percieved contrast judgements indexed by psychophysical contrast matching paradigms [e.g.
+@Anstis1998; @Levelt1965; @Quaia2018].
+We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
+One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
+The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
+We tested 9 ratios of contrast between the left and right eyes.
+
+The results from the matching experiment are shown in Figure \@ref(fig:matchingdata).
+Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
+For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
+The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \@ref(fig:EEGdata)c,f).
 
@@
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Interocular ratio distribution (from left to right of the figure): 1L0R, 1L0.25R, 1L0.5R, 1L0.75R, 1L1R, 0.75L1R, 0.5L1R, 0.25L1R, 0L1R.", fig.align="center", echo=FALSE}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.", out.width = '50%', fig.align="center", echo=FALSE}
 
@@
 ## Computational modelling
-Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
-Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
-These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression
-
-The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other [@Ding2006].
-In the earlier stage, the right and left eye channels exert gain control on the other channel.
-Then, they exert gain control on the other channel’s gain control.
-Lastly, the outputs from each channel are summed binocularly to determine the binocular signal’s magnitude.
-
-The second model is similar as it also incorporates gain control mechanisms [@Meese2006].
-In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
-Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
-This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
-
-We therefore decided to use and readapt this second model to see if it could be used to explain our three different data sets from experiments 1 and 3.
-In the first stage, the responses from the right and the left eyes are computed separately, as shown by equation 1 and 2:
-
-_RespL_ = $\frac{(L^q)}{Z + R + w \times R}$ (1)
-
-_RespR_ = $\frac{(R^q)}{Z + R + w \times L}$ (2)
-
-where _L_ and _R_ are the signals from the left and right eyes, _Z_ is a saturation constant, _q_ is an exponent and _w_ is the suppression from the opponent weight.
-
-In the second stage, the responses from the two eyes are summed binocularly:
-
-_Resp(L,R)_ = k $\times$ (RespL + RespR) + n
-
-where _k_ is the noise parameter.
-
-For our analysis, we implemented the model using a Bayesian approach, using the Stan software in Rstudio, which allowed us to generate a posterior parameter distribution.
-Results for this are shown in figure \@ref(fig:modelfigure)i and the summary of the median parameter values are displayed in table \@ref(tab:paramtable).
-The key finding is that the pupillometry results display a much higher suppression from the opponent eye, shown by the _w_ parameter in table \@ref(tab:paramtable) and the green line in figure \@ref(fig:modelfigure)i, than the EEG results at the first harmonic (grey line in figure \@ref(fig:modelfigure)i), the EEG results at the second harmonic (purple line in figure \@ref(fig:modelfigure)i) and the matching results (yellow line in figure \@ref(fig:modelfigure)i).
-These results offer an explanation to the data from the previous experiments: the higher suppression displayed by the pupillometry explains the non-linearity observed in the first experiment, while the lower suppression by the EEG at both harmonics and the matching explains the strong linearity observed in experiments 1 and 3.
-
-Finally, figures \@ref(fig:modelfigure)a-d show the behavioural data for our four main data sets from experiments 1 and 3, and figures \@ref(fig:modelfigure)e-h show the outputs that the model produced based on the median parameter values that are presented in table \@ref(tab:paramtable).
-We can see that the data outputted by the model has a similar has a similar behaviour to the empirical data that we collected in our experiments.
-This would seem to suggest that the model can offer a good explanation of our data.
+
+We fitted a computational model to the data from Experiments 1 & 3 using a hierarchical Bayesian approach.
+The model behaviour is displayed in Figure \@ref(fig:modelfigure)e-h, with empirical data replotted in Figure \@ref(fig:modelfigure)a-d for comparison.
+In general, the model captures the key characteristics of the empirical data.
+Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
+In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \@ref(tab:paramtable)).
+This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
+This explains the amplitude differences between model and data, particularly at low target contrast levels, but are of no consequence for the pattern of relative responses across conditions.
+
+We were particularly interested in comparing the weight of interocular suppression across data sets.
+We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \@ref(fig:modelfigure)i).
+The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
+There is no overlap between the pupillometry distribution and any of the other three.
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict [@Meese2006; @Baker2017].
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absence of dichoptic masking.
 
@@
 prior <- dnorm(10^((-48:12)/20),1,0.5)
-prior <- 0.3*prior/max(prior)
+prior <- 0.5*prior/max(prior)
 lines(-48:12,prior)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
 title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
 title(ylab="Amplitude at 2Hz (µV) ", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
@@
 mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Target contrast (dB)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
 title(ylab="Amplitude at 4Hz (µV) ", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
@@
 ```{r modelfigure, fig.cap="Summary of computational modelling.
-Panels (a-d) show model behaviour for our four main data set, pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d).
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
+Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
 Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.

### 2022-10-16 manuscript.tex
Code update with full OSF integration, added extra figure.
Updates to manuscript

--- 2022-10-04 manuscript.tex
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Different rules for binocular combination of luminance in cortical and subcortical pathways},
-  pdfauthor={Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
+  pdfauthor={Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
-\title{Different rules for binocular combination of luminance in cortical and subcortical pathways}
-\author{Federico G. Segala, Aurelio Bruno, Alex R. Wade \& Daniel H. Baker (+Myat? +Joel?)}
-\date{2022-10-04}
+\title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
+\author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
+\date{2022-10-16}
 
@@
 \section{Introduction}\label{introduction}}
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+OK, some pointers for the introduction:
+
+I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
+Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
+I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
+
+The key points should be:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\item
+  For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
+\item
+  Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
+\item
+  We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
+\item
+  Actually there's not much work on temporal binocular combination even in the primary visual pathway.
+\item
+  We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
+\end{enumerate}
+
+I wouldn't say too much about models, or about the matching experiment, at this stage.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 
+Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
+Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
+These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other (Ding and Sperling, 2006).
+In the earlier stage, the right and left eye channels exert gain control on the other channel.
+Then, they exert gain control on the other channel's gain control.
+Lastly, the outputs from each channel are summed binocularly to determine the binocular signal's magnitude.
+The second model is similar as it also incorporates gain control mechanisms (Meese et al., 2006).
+In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
+Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
+This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
+
 To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
@@
 
-Our experiment used different stimuli than the ones used by Anstis and Ho: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
+Our experiment used different stimuli than the ones used by Anstis and Ho (1998): in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
 In our experiment, in some conditions, the flicker was shown to only one eye.
@@
 
-Thirty, twelve and ten participants were recruited for experiment 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision.
-All participants gave written informed consent.
+Thirty, twelve and ten participants were recruited for Experiments 1, 2 and 3 respectively. All participants had normal or corrected to normal binocular vision, and gave written informed consent.
 
 \hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& Stimuli}\label{apparatus-stimuli}}
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
 
@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in figure \ref{fig:pupildata}a for an example of the of the fused stimuli).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors and so did not suffer from internal reflections, and allowed participants to see only one fused disc.
-The use of a stereoscope allowed us to display the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \ref{fig:pupildata}b for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
 
@@
 
-EEG data were collected for experiments 1 and 2 sampled at 1 kHz using a 64-electrode ANT WaveGuard cap and the signals were recorded using the ASA software (ANT Neuro, Hengelo, NL, United States).
-Pupillometry data were collected only for experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Kassner et al.
-(2014)) running at 120 Hz and the signals were recorded with the Pupil Capture software (Pupil Labs GmbH, Kassner et al.
-(2014)).
+EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; Kassner et al.
+(2014)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-\hypertarget{experiment-1}{%
-\subsubsection{Experiment 1}\label{experiment-1}}
+\hypertarget{experiment-1-simultaneous-eeg-and-pupillometry}{%
+\subsubsection{Experiment 1: simultaneous EEG and pupillometry}\label{experiment-1-simultaneous-eeg-and-pupillometry}}
 
 The experiment was conducted in a windowless room, in which the only light source was the monitor.
-The participants sat at 99 cm from the monitor and their viewing distance through the stereoscope was 107 cm.
+The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
 The experiment was carried out in one session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
 In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants had no task and were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
-The discs flickered in counterphase at 2 Hz, but in some conditions (cross-frequency conditions) one of the two discs flickered at 1.6 Hz.
-They were set at five temporal contrast levels relative to the mean luminance: 6, 12, 24, 48 and 96 \%.
+The participants were given no specific task instructions, but were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
+We included six distinct ocular conditions, each at five temporal target contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a fixed luminance contrast of 48\%.
+In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
+We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
+The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
+The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.~the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
+We counterbalanced presentation of the target stimulus across the left and right eyes.
 
-As already stated, the mirror stereoscope allowed the use of three different ocular configurations.
-In the monocular configuration, one disc was set to flicker either at 2 Hz or 1.6 Hz for each contrast level, while the other disc remained stable at a constant mean luminance.
-In the binocular configuration, both discs flickered at the same contrast level with both discs flickering at 2 Hz in the same-frequency condition, while, in the cross-frequency condition, one disc flickered at 2 Hz and the other at 1.6 Hz.
-Finally, in the dichoptic configuration, one disc flickered across all contrast levels and the other flickered at a fixed contrast level that was set at 48 \%.
-Similar to the binocular configuration, the dichoptic configuration was divided in same-frequency and cross-frequency conditions.
+\hypertarget{experiment-2-eeg-responses-across-temporal-frequency}{%
+\subsubsection{Experiment 2: EEG responses across temporal frequency}\label{experiment-2-eeg-responses-across-temporal-frequency}}
 
-\hypertarget{experiment-2}{%
-\subsubsection{Experiment 2}\label{experiment-2}}
+This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
+Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
+The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
+In each block, there were 20 trials in total with the same timing as for Experiment 1.
 
-The conditions were similar to experiment 1 (windowless room and viewing distance of 107 cm).
-Like in experiment 1, participants had no specific task other than looking at the fixation crosses and minimising their blinking.
-Unlike the first experiment, only one contrast level was used (96 \%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
-Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
+\hypertarget{experiment-3-temporal-contrast-matching}{%
+\subsubsection{Experiment 3: temporal contrast matching}\label{experiment-3-temporal-contrast-matching}}
 
-The experiment was carried out in one session lasting 25 minutes in total, divided in five blocks of 5 minutes each.
-In each block, there were 20 trials in total lasting 15 seconds each (12s of stimulus presentation and 3s of interstimulus interval).
+The experiment was conducted in a darkened room with a blacked-out window.
+The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
+A two-interval contrast matching procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
+In the other interval, a target disc flickering at varying contrast levels was displayed.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
+The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
 
-\hypertarget{experiment-3}{%
-\subsubsection{Experiment 3}\label{experiment-3}}
-
-The experiment was conducted in a room with a blacked-out window.
-The sitting and viewing distances of the participants were similar to the two previous experiments.
-As this was a psychophysical task, no EEG or pupillometry data were collected for this experiment.
-
-A two-interval forced-choice staircase procedure was used to collect data.
-In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48 \%), which was selected by the experimenter at the beginning of each block.
-In a separate interval, a target fused disc flickering at varying contrast levels was displayed.
-The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
-The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1.
-The standard and the target fused discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
-The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz.
-
-Due to its long duration (162 minutes in total), the participants completed the experiment across multiple sessions divided at their own discretion.
-The experiment was divided in 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each (depending on the response speed of the participant).
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience The experiment was divided into 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
 In each block, there were a total of 50 trials.
-We pooled the data from all repetitions of a given condition and fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50 \% point.
+No auditory feedback was given for this subjective task.
 
@@
 EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
-The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted.
-Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The fast Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
 All repetitions of each condition were then averaged for each electrode.
-They were then averaged across the four occipital electrodes (POz, Oz, O1, O2), to obtain individual results.
-Finally, these were averaged across all participants to obtain the final results.
+They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
+Finally, these were averaged across participants to obtain the group results.
+All averaging retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (2021).
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (1991) that can compare more than two conditions.
 
-A similar process was adopted for the analysis of the pupillometry data.
-The data were converted from the mp4 format to a compressed csv text file using the Pupil Player software (Kassner et al., 2014).
-The individual data were then loaded into R for analysis where a twelve-second waveform for each trial in each eye was extracted.
-Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
-All repetitions of each condition were then averaged for each eye.
-They were then averaged across the two eyes, to obtain individual results.
-Finally, these were averaged across all participants to obtain the final results.
+A similar analysis pipeline was adopted for the pupillometry data.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., 2014), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The fast Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
+Note that previous pupillometry studies using luminance flicker have tended to fit sine-waves to the data, rather than using Fourier analysis (e.g.
+Spitschan et al., 2014).
+Our novel approach is more robust to noise at other frequencies, and makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
+Figueira et al., 2022)
+
+To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
+We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
+Thresholds were averaged across participants in logarithmic (dB) units.
+For all experiments, we used a bootstrapping procedure with 1000 iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
+
+\hypertarget{computational-model-and-parameter-estimation}{%
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
+(2006).
+The second gain control stage was omitted (consistent with Baker and Wade, 2017) to simplify the model and reduce the number of free parameters.
+The response of the left eye's channel is given by:
+
+\begin{equation}
+\label{eq:respL}
+Resp_L = \frac{L^2}{Z + L + wR},
+\end{equation}
+
+with an equivalent expression for the right eye:
+
+\begin{equation}
+\label{eq:respR}
+Resp_R = \frac{R^2}{Z + R + wL}.
+\end{equation}
+
+In both equations, \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \emph{w} is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+Resp_B = R_{max}(Resp_L + Resp_R) + n,
+\end{equation}
+
+where \emph{n} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
+The \(R_{max}\) parameter was omitted when modelling the contrast matching data, as it had no effect in this paradigm.
+
+Despite being derived from the model proposed by Meese et al.
+(2006), the simplifications applied to this architecture make it very similar to other models (e.g.
+Ding and Sperling, 2006; Legge, 1984; Schrödinger, 1926).
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
+Our key parameter of interest is the weight of interocular suppression.
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, 2017).
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., 2020).
+
+We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., 2017).
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\).
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+The models were fit using the individual data across all participants, independently for each data set.
+Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+However it is clear that the character of the model in all cases gives a good representation of the data.
+We sampled over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+
+\hypertarget{preregistration-data-and-code-availability}{%
+\subsection{Preregistration, data and code availability}\label{preregistration-data-and-code-availability}}
+
+We initially preregistered our main hypotheses and analysis intentions for the first experiment.
+We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then ran the main experiment, followed by two additional experiments that were not preregistered.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: \url{https://osf.io/tbema/}.
 
@@
 
-\hypertarget{experiment-1-1}{%
-\subsection{Experiment 1}\label{experiment-1-1}}
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
 
-The results from the first experiment are shown in figure \ref{fig:pupildata} and figure \ref{fig:EEGdata}.
-Each curve is showing the amplitude of the signal for the three different configurations (monocular, binocular and dichoptic).
-
-Figure \ref{fig:pupildata} is showing the results for the pupillometry.
-Figure \ref{fig:pupildata}a is showing the group average waveform for binocular presentation.
-Figure \ref{fig:pupildata}b is showing the average Fourier spectrum, where we can observe a spike at 2 Hz, which shows a very clear, non-noisy response to the flickering stimuli.
-Figures \ref{fig:pupildata}c-e show the contrast response functions (CRFs) at 2 and 1.6 Hz.
-In the same-frequency condition at 2 Hz (fig.~\ref{fig:pupildata}c), the amplitude of the binocular configuration is bigger than the amplitude of the monocular configuration.
-In general, we observe that the binocular to monocular ratio is roughly \(\sqrt2\) at each contrast level (fig.~).
-In the cross-frequency condtion at 2 Hz (fig.~\ref{fig:pupildata}d), no summation is observed since the amplitudes of the binocular and dichoptic conditions are smaller than the amplitude of the monocular condition.
-Interestingly, we observe a relatively small cross-frequency facilitation at 1.6 Hz (fig.~\ref{fig:pupildata}e), with the binocular amplitude being bigger than the monocular amplitude, especially at the lower contrast levels.
-This facilitation is then lost at the highest contrast level, where the amplitude of the monocular signal is equal to the amplitude of the binocular signal.
-This pattern of results in the cross-frequency conditions suggests the presence of interocular suppression at the level of the pupils.
-Moreover, the low summation observed in the same-frequency condition suggests that theprocessing of temporal luminance modulations happens in a non-linear way at the level of the pupils.
-
-Figure \ref{fig:EEGdata} shows the results for EEG.
-Figure \ref{fig:EEGdata}a is showing the group average waveform for binocular presentation.
-Figure \ref{fig:EEGdata}b is showing the average Fourier spectrum, where we can observe two spikes at 2 and 4 Hz, which show a very clear, non-noisy response to the flickering stimuli at the first and second harmonics.
-Figures \ref{fig:EEGdata}c-e show the CRFs at 2 and 1.6 Hz at the first harmonic, and figures \ref{fig:EEGdata}f-h show the CRFs at the second harmonic.
-What is immediately apparent is that, in the same-frequency condition, the binocular responses at the first (fig.~\ref{fig:EEGdata}c) and second (fig.~\ref{fig:EEGdata}f) harmonics are showing very high summation of binocular signals compared to the pupillometry.
-The amplitudes of the binocular responses are twice, and even more than twice, the amplitudes of the monocular responses.
-This is especially clear at the highest contrasts.
-This is clearly displayed in figure, which is showing the binocular to monocular ratios for the EEG at both harmonics and the pupillometry.
-For the cross-frequency condition at 2 Hz and 4 Hz (fig.~\ref{fig:EEGdata}d and \ref{fig:EEGdata}g), there is almost no summation, with the amplitudes of the binocular and dichoptic configurations being equal, and even smaller, than the amplitudes of the monocular signals.
-This pattern is also observable in the cross-frequency condition at 1.6 (fig.~\ref{fig:EEGdata}e) and 3.2 Hz (fig.~\ref{fig:EEGdata}h).
-This pattern of results seems to suggest that processing of temporal luminance modulations happens in a linear way in the visual cortex.
-Moreover, the lower amplitudes for the binocular and the dichoptic configurations in the cross-frequency conditions seem to indicate the presence of interocular suppression in the visual cortex.
+The pupillometry results are summarised in Figure \ref{fig:pupildata}.
+The group average waveform for binocular presentation is shown in Figure \ref{fig:pupildata}a.
+There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
+The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a substantial spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
 
@@
 Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum.
+Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
 Panels (c,d) show contrast response functions at 2Hz for different conditions.
@@
 \end{figure}
+
+Figure \ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
+The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, 2021) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
+
+In Figure \ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \ref{fig:pupildata}c for comparison).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
+When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless{} 0.001).
+
+Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Surprisingly there appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
+The dichoptic cross condition does not show clear modulation with target contrast.
+
+Figure \ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
+Figure \ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Figure \ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
+Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
+We therefore calculated contrast response functions at both first and second harmonic frequencies.
 
@@
 
-\hypertarget{experiment-2-1}{%
-\subsection{Experiment 2}\label{experiment-2-1}}
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13).
+For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \ref{fig:EEGdata}e) and 3.2Hz (Figure \ref{fig:EEGdata}h).
+This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
 
-The results from the second experiment are shown in \ref{fig:TFdata}.
-Figure \ref{fig:TFdata}a is showing the Fourier spectra for responses to binocular flicker at the 5 different frequencies (2, 4, 8, 16, 30 Hz).
-We can observe that from 2 to 16 Hz, we recorded very clear and significant signals, as we can observe spikes at the respective frequencies and their subsequent harmonics.
-However, at 30 Hz, the responses recorded were mainly noise, with no clear data recorded.
-This is also reflected in figure \ref{fig:TFdata}b, where we observe almost no amplitude recorded for monocular and binocular responses at 30 Hz.
-The rest of figure \ref{fig:TFdata}b is showing the response at each stimulation frequency.
-We can see that there is an increase in the amplitudes from 2 Hz to 8 Hz and a decrease at 16 Hz.
-In general, we observe that the binocular response is twice, and more than twice, the monocular response from 2 to 16 Hz (fig.~\ref{fig:TFdata}c), suggesting that binocular facilitation is happening at higher frequencies.
-However, at 30 Hz, this facilitation is lost (the binocular and monocular responses are the same, as demonstrated by the binocular to monocular ratio being 1in figure \ref{fig:TFdata}c).
-The fact that the signal recorded at the highest frequency is mainly noise would seem to suggest that the visual cortex cannot process temporal luminance modulations anymore.
+Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
+Figure \ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
+At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/BSratios}
+
+}
+
+\caption{Ratio of binocular to monocular response for three data types.
+Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
+\end{figure}
+
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
+
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, 2017).
+One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
+We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014).
+
+Results from the temporal frequency experiment are shown in \ref{fig:TFdata}.
+Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
+However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
+Figure \ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
+Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
+\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
 
@@
 Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
-Panel (b) shows the response at each stimulation frequency for monocular (red) and binocular (blue) presentation.
+Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
 Panel (c) shows the ratio of binocular to monocular responses.
@@
 
-\hypertarget{experiment-3-1}{%
-\subsection{Experiment 3}\label{experiment-3-1}}
+\hypertarget{experiment-3}{%
+\subsection{Experiment 3}\label{experiment-3}}
 
-The results from the third experiment are shown in figure \ref{fig:matchingdata}. Each curve is showing the contrast level in each eye for the different interocular ratios.
+In Experiment 1 we found evidence of much stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+Since perception is dependent on cortical responses, these results provide a clear prediction for percieved contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
+Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
+We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
+One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
+The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
+We tested 9 ratios of contrast between the left and right eyes.
 
-Looking at the results for the 48 \% contrast condition, we can observe that, when the ratio in both eyes was set to be one, the target appeared to have the same flickering intensity as the standard when the contrast in both eyes was selected to be, on average, 50 \% (red line).
-This is also observable for the 24 \% contrast condition, where the target appeared to have the same flickering intensity when the contrast was selected to be around 25 \%.
-These two results show that the paradigm was working correctly and that the participants could see the flicker properly.
-When the ratio was set to be 0 in one of the two eyes, we observe that, for the target to appear to flicker similarly to the standard, the contrast in the other eye was set to be around double the contrast of the standard.
-For the 48 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 90 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 96 \%.
-For the 24 \% contrast, when the ratio in the right eye was 0, the contrast in the left eye was around 57 \%, while, when the ratio in the left eye was 0, contrast in the right eye was around 50 \%.
-When looking at the rest of the data, we can see that the points, for both contrast conditions, seem to fall along the line representing a linear combination model, with the results for the 24 \% condition showing a very strong summation that seem to exceed this linear combination.
-Overall, these results seem to suggest that the processing of temporal luminance modulations seems to follow near linear combination rules, which is in line with our results from experiment 1.
+The results from the matching experiment are shown in Figure \ref{fig:matchingdata}.
+Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
+For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
+The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \ref{fig:EEGdata}c,f).
 
@@
 
-{\centering \includegraphics{Figures/matchingdata}
+{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
 
@@
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Interocular ratio distribution (from left to right of the figure): 1L0R, 1L0.25R, 1L0.5R, 1L0.75R, 1L1R, 0.75L1R, 0.5L1R, 0.25L1R, 0L1R.}\label{fig:matchingdata}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.}\label{fig:matchingdata}
 \end{figure}
@@
 \subsection{Computational modelling}\label{computational-modelling}}
+
+We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
+The model behaviour is displayed in Figure \ref{fig:modelfigure}e-h, with empirical data replotted in Figure \ref{fig:modelfigure}a-d for comparison.
+In general, the model captures the key characteristics of the empirical data.
+Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
+In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \ref{tab:paramtable}).
+This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
+This explains the amplitude differences between model and data, particularly at low target contrast levels, but are of no consequence for the pattern of relative responses across conditions.
+
+We were particularly interested in comparing the weight of interocular suppression across data sets.
+We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}i).
+The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
+There is no overlap between the pupillometry distribution and any of the other three.
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006).
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absence of dichoptic masking.
 
@@
 \caption{Summary of computational modelling.
-Panels (a-d) show model behaviour for our four main data set, pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d).
-Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
+Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
+Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
 The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
@@
 \hline
-Pupillometry & 2.45 & 0.01 & 0.67 & 0.00024\\
+Pupillometry & 2.37 & 0.01 & 0.67 & 0.00023\\
 \hline
-EEG 1F & 2.78 & 0.15 & 0.03 & 0.00262\\
+EEG 1F & 2.59 & 0.15 & 0.02 & 0.0026\\
 \hline
-EEG 2F & 2.31 & 0.06 & 0.01 & 0.00407\\
+EEG 2F & 2.21 & 0.06 & 0.01 & 0.00404\\
 \hline
-Matching & 0.56 & 7.96 & 0.05 & -\\
+Matching & 0.30 & 5.07 & 0.09 & -\\
 \hline
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
+Baker DH.
+2021.
+Statistical analysis of periodic data in neuroscience.
+\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
+doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+2020.
+Binaural summation of amplitude modulation involves weak interaural suppression.
+\emph{Sci Rep} \textbf{10}:3560.
+doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+Baker DH, Wade AR.
+2017.
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+\emph{Cereb Cortex} \textbf{27}:254--264.
+doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2012}{}}%
+Baker DH, Wallis SA, Georgeson MA, Meese TS.
+2012.
+Nonlinearities in the binocular combination of luminance and contrast.
+\emph{Vision Res} \textbf{56}:1--9.
+doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
 Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A.
+2017.
+Stan: A probabilistic programming language.
+\emph{Journal of Statistical Software, Articles} \textbf{76}:1--32.
+doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
 
@@
 2004.
-EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
+{EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis.
 \emph{J Neurosci Methods} \textbf{134}:9--21.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Figueira2022}{}}%
+Figueira JSB, Kutlu E, Scott LS, Keil A.
+2022.
+The FreqTag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
+\emph{Dev Cogn Neurosci} \textbf{54}:101066.
+doi:\href{https://doi.org/10.1016/j.dcn.2022.101066}{10.1016/j.dcn.2022.101066}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+Kingdom FAA, Libenson L.
+2015.
+Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+\emph{J Vis} \textbf{15(5)}:2.
+doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
@@
 1965.
-BINOCULAR BRIGHTNESS AVERAGING AND CONTOUR INFORMATION.
+Binocular brightness averaging and contour information.
 \emph{Br J Psychol} \textbf{56}:1--13.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Quaia2018}{}}%
+Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Schrodinger1926}{}}%
+Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+Spitschan M, Jain S, Brainard DH, Aguirre GK.
+2014.
+Opponent melanopsin and s-cone signals in the human pupillary light response.
+\emph{Proc Natl Acad Sci U S A} \textbf{111}:15568--72.
+doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Victor1991}{}}%
+Victor JD, Mast J.
+1991.
+A new statistic for steady-state evoked potentials.
+\emph{Electroencephalogr Clin Neurophysiol} \textbf{78}:378--88.
+doi:\href{https://doi.org/10.1016/0013-4694(91)90099-p}{10.1016/0013-4694(91)90099-p}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%

### 2022-12-15 manuscript.Rmd
Added discussion, began writing abstract and conclusion.

@@
 
+We investigated the rules of binocular combination of temporal flickering stimuli.
+Using EEG and pupillometry simultaneously, we investigated the combination of light discs at five temporal contrast levels flickering at 2 Hz in the cortical and subcortical pathways.
+Results showed a strong binocular facilitation in the visual cortex and a non-linear combination process with evidence of suppression in the subcortical pathways.
+Following these findings, we performed a matching experiment using the same type of stimuli and found equivalent linear summation effects.
+Using a Bayesian approach, all our data were fitted to a computational model that showed a stronger interocular suppression for the pupillometry data compared with the EEG and matching data.
+
+---
+OK, some pointers for the introduction: I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
+Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
+I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I’ve tried to do this elsewhere in the paper).
+The key points should be:
+1. For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
+2. Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
+3.
+We don’t know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
+4. Actually there’s not much work on temporal binocular combination even in the primary visual
+pathway.
+5. We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
+I wouldn’t say too much about models, or about the matching experiment, at this stage.
+
 # Introduction
 
----------------------------------
-OK, some pointers for the introduction:
-
-I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
-Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
-I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
-
-The key points should be:
-
-1. For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
-
-2. Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
-
-3.
-We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
-
-4. Actually there's not much work on temporal binocular combination even in the primary visual pathway.
-
-5. We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
-
-I wouldn't say too much about models, or about the matching experiment, at this stage.
----------------------------------
-
 Binocular combination provides a higher visual sensitivity than monocular viewing.
-This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around $\sqrt{2}$ ($\approx1.4$) for grating stimuli at detection threshold [@Campbell1965].
-In other words, a monocular stimulus can elicit the same response as a binocular stimulus if it has a contrast that is 1.4 times higher.
-This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination [@Legge1984]: monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = $\sqrt{R^2 + L^2}$, when R and L are equal to 1, the output is $\sqrt{2}$).
-However, subsequent research has shown that these explanations are not fully adequate to account for binocular summation.
+At threshold, this superiority is known as binocular summation, while, above threshold, we refer to this as binocular facilitation.
+Binocular summation is defined by the binocular summation ratio (BSR).
+This was originally believed to be around $\sqrt{2}$ ($\approx1.4$) for grating stimuli at detection threshold [@Campbell1965].
+In other words, a monocular grating can elicit the same response as a binocular grating if it has a contrast that is 1.4 times higher.
+This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination for grating stimuli [@Legge1984]: monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = $\sqrt{R^2 + L^2}$, when R and L are equal to 1, the output is $\sqrt{2}$).
+However, subsequent research has shown that these explanations are not fully adequate to account for binocular facilitation above threshold, as this summation effects are lost for gratings at high contrast.
 Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise [@Anderson1989].
@@
 
-In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined [@Purves2008].
+In general, it seems that the mechanisms behind spatial binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined [@Purves2008].
 However, there is an eye component that is often underestimated in its role to determine the quality of visual information: the pupil.
@@
 However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
-Given this, not much is known about the computational processes behind the PLR except for some evidence of binocular interaction.
-The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) [@Wyatt1981] are evidence of this binocular interaction.
-
-With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
+Given this, not much is known about the computational processes behind the PLR although there is some evidence of binocular interaction and binocular combination happening at the level of the pupil pathways.
+Evidence of binocular interaction is provided by the presence of a consensual response in the pupils: when only one pupil is stimulated, an equivalent response will be recorded in the unstimulated pupil [@Wyatt1981].
+Evidence of binocular combination is provided by the binocular facilitation observed for the ocular following eye movements in response to fast moving stimuli: when comparing the amplitude of the responses to monocular and binocular stimuli, the binocular response will be more than twice the monocular response [@Quaia2018].
+
+With this in mind, we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses using changes in the temporal contrast of a flickering light.
+This is a novel paradigm that we developed that allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously for flickering light.
 The results should offer new insight about basic neural circuits and information on how they might be affected in clinical disorders of vision (e.g.
 amblyopia).
-Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
-
-Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
-Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
-These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other [@Ding2006].
-In the earlier stage, the right and left eye channels exert gain control on the other channel.
-Then, they exert gain control on the other channel’s gain control.
-Lastly, the outputs from each channel are summed binocularly to determine the binocular signal’s magnitude.
-The second model is similar as it also incorporates gain control mechanisms [@Meese2006].
-In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
-Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
-This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
-
-To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
-Matching is a paradigm in which the perceived brightness of a standard stimulus is matched to that of a target stimulus.
-In the latter, the interocular ratios of luminance are varied to obtain an equibrightness curve.
-Previous literature has used this paradigm to investigate the binocular fusion of static stimuli and the temporal combination of spatial flickering of spatial increments (a bright target on a dark background) and decrements (a dark target on a bright background) [@Anstis1998; @Levelt1965].
-For spatial increments, it was found that binocular fusion seems to follow approximately linear combination rules.
-This means that, for a monocular stimulus to elicit the same response as a binocular stimulus, the former needs to have twice the signal of the latter.
-On the other hand, spatial decrements follow a winner-takes-all pattern.
-This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
-
-Our experiment used different stimuli than the ones used by @Anstis1998: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
-In our experiment, in some conditions, the flicker was shown to only one eye.
-Moreover, they were looking at the temporal fusion of the flicker while we focussed on the binocular fusion of the flicker.
-Based on this and on the results from our first experiment, we expected to find a near linear summation of the responses.
+Based on previous literature, we expected to find a non-linear combination of the responses in the visual cortex, as described by the gain control mechanisms used to describe spatial contrast combination, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
+Additionally, we decided to follow up on our results from this first experiments to test whether perception of flickering light is consistent with the results that we observed in the cortical pathways (visual cortex).
+We therefore conducted a contrast matching experiment using the same type of flickering stimuli used in our first experiment.
 
@@
 @Spitschan2014].
-Our novel approach is more robust to noise at other frequencies, and makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
+The Fourier approach is more robust to noise at other frequencies and has already been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
 @Figueira2022]
@@
 Thresholds were averaged across participants in logarithmic (dB) units.
+
 For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
@@
 
-Results from the temporal frequency experiment are shown in \@ref(fig:TFdata).
+Results from the temporal frequency experiment are shown in figure \@ref(fig:TFdata).
 Figure \@ref(fig:TFdata)a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
@@
 
+Using a novel paradigm that combines elctrophysiological and pupillometic measures, we found surprising results for binocular combination of flickering light: in the visual cortex, the processing of temporal luminance modulations seems to happen linearly, with no evidence of interocular suppression, while, in the subcortical pathways, this seems to happen non-linearly with evidence of interocular suppression.
+This pattern of results was also supported by the computational model that we fitted our data to, which showed a much greater suppression weight of the pupillometry data compared with the EEG data.
+Additionally, we also found that perception of flickering light is consistent with cortical responses, with our matching results also showing linear summation effects.
+
+The results from our first experiment were unexpected for both the pupillometry and the EEG.
+Previous studies investigating binocular combination of grating stimuli using steady-state EEG showed that combination for this type of stimuli seems to happen in a non-linear way [@Baker2017].
+However, we found that there seems to be a strong binocular facilitation for flickering stimuli.
+While this could have been due to the lower frequency used in our experiment, our second experiment showed that this was not the case.
+A reason for this apparent facilitation could be due to the different nature of our stimuli: @Baker2017 used static gratings, while here we used flickering stimuli.
+@Quaia2018 observed a strong binocular facilitation in eye movement response to moving stimuli.
+Here, obviously, we were not investigating eye movements, but our stimuli included a movement component due to their flickering nature.
+This induced movement of the stimuli could be the reason why we observed this strong facilitation in the visual cortex.
+As for our pupillometry results, we observed less binocular facilitation than what we hypothesised at beginning of testing.
+As mentioned in the introduction, the presence of a consensual response in the pupils [@Wyatt1981] is evidence of binocular interaction.
+@Wyatt1981 measured an inequality of the responses between the two eyes during this consensual response, which could actually be explained by the presence of interocular suppression between the two pupils.
+
+On the other hand, the results of our matching experiment were not completely unexpected.
+Previous literature has used the matching paradigm to investigate the binocular fusion of static stimuli for spatial increments, which consists of a bright target on a dark background, and spatial decrements, which consist of a dark target on a bright background [@Anstis1998; @Levelt1965].
+For the former, it was found that binocular fusion seems to follow approximately linear combination rules, while, for the latter, it was found that binocular fusion seems to follow a winner-take-all pattern, where the observer is seeing what the eye that is receiving the strongest signal is seeing.
+Our flickering stimuli were a combination of both increments and decrements presented on a dark background, but presented a stronger similarity in presentation to the increments than the decrements.
+This would explain why our results showed a strong facilitation.
+
+As mentioned before, the main frequency for the three experiments was 2 Hz.
+The reason behind this was that we wanted to be able to measure both EEG and pupillary responses simultaneously.
+However, these two methods have different temporal properties: pupillometry is most responsive to slow flicker frequencies of less than 1 Hz [@Spitschan2014], while steady-state EEG generates stronger responses to faster frequencies of more than 3 Hz [@Norcia2015].
+This means that stronger responses for pupillometry should be obtained at a lower frequency than the one we used in the main experiment, and for EEG at a higher frequency, meaning that our interpretation of the results might have been limited by the frequency that we selected.
+However, previous studies have shown that significant pupil responses can be obtained at higher frequencies, with the pupils showing a similar pattern of responses as at 1 Hz or lower, although at a reduced amplitude [@Barrionuevo2014; @Barrionuevo2016].
+Additionally, our second experiment shows that the strong binocular facilitation observed in the cortical areas for flickering stimuli at 2 Hz is also observable at higher frequencies.
+Therefore, this would seem to indicate that 2 Hz was a good compromise to obtain significant responses from both pupillometry and EEG.
+
+# Conclusions
+
+With these three experiments, we have demonstrated that binocular combination for temporal flickering stimuli seems to happen in different manners in cortical and subcortical pathways.
+
 # References

### 2022-12-15 manuscript.tex
Added discussion, began writing abstract and conclusion.

@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
+  pdfauthor={Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
+\usepackage{longtable,booktabs}
 % Correct order of tables after \paragraph or \subparagraph
@@
 \setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
-  pdfauthor={Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 \author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{2022-10-16}
+\date{2022-12-15}
 
@@
 
+We investigated the rules of binocular combination of temporal flickering stimuli.
+Using EEG and pupillometry simultaneously, we investigated the combination of light discs at five temporal contrast levels flickering at 2 Hz in the cortical and subcortical pathways.
+Results showed a strong binocular facilitation in the visual cortex and a non-linear combination process with evidence of suppression in the subcortical pathways.
+Following these findings, we performed a matching experiment using the same type of stimuli and found equivalent linear summation effects.
+Using a Bayesian approach, all our data were fitted to a computational model that showed a stronger interocular suppression for the pupillometry data compared with the EEG and matching data.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+OK, some pointers for the introduction: I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
+Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
+I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
+The key points should be:
+1. For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
+2. Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
+3.
+We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
+4. Actually there's not much work on temporal binocular combination even in the primary visual
+pathway.
+5. We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
+I wouldn't say too much about models, or about the matching experiment, at this stage.
+
 \hypertarget{introduction}{%
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-OK, some pointers for the introduction:
-
-I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
-Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
-I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
-
-The key points should be:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
-\item
-  Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
-\item
-  We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
-\item
-  Actually there's not much work on temporal binocular combination even in the primary visual pathway.
-\item
-  We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
-\end{enumerate}
-
-I wouldn't say too much about models, or about the matching experiment, at this stage.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
 Binocular combination provides a higher visual sensitivity than monocular viewing.
-This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around \(\sqrt{2}\) (\(\approx1.4\)) for grating stimuli at detection threshold (Campbell and Green, 1965).
-In other words, a monocular stimulus can elicit the same response as a binocular stimulus if it has a contrast that is 1.4 times higher.
-This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination (Legge, 1984): monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = \(\sqrt{R^2 + L^2}\), when R and L are equal to 1, the output is \(\sqrt{2}\)).
-However, subsequent research has shown that these explanations are not fully adequate to account for binocular summation.
+At threshold, this superiority is known as binocular summation, while, above threshold, we refer to this as binocular facilitation.
+Binocular summation is defined by the binocular summation ratio (BSR).
+This was originally believed to be around \(\sqrt{2}\) (\(\approx1.4\)) for grating stimuli at detection threshold (Campbell and Green, 1965).
+In other words, a monocular grating can elicit the same response as a binocular grating if it has a contrast that is 1.4 times higher.
+This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination for grating stimuli (Legge, 1984): monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = \(\sqrt{R^2 + L^2}\), when R and L are equal to 1, the output is \(\sqrt{2}\)).
+However, subsequent research has shown that these explanations are not fully adequate to account for binocular facilitation above threshold, as this summation effects are lost for gratings at high contrast.
 Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise (Anderson and Movshon, 1989).
@@
 
-In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined (Purves et al., 2008).
+In general, it seems that the mechanisms behind spatial binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined (Purves et al., 2008).
 However, there is an eye component that is often underestimated in its role to determine the quality of visual information: the pupil.
@@
 However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
-Given this, not much is known about the computational processes behind the PLR except for some evidence of binocular interaction.
-The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) (Wyatt and Musselman, 1981) are evidence of this binocular interaction.
+Given this, not much is known about the computational processes behind the PLR although there is some evidence of binocular interaction and binocular combination happening at the level of the pupil pathways.
+Evidence of binocular interaction is provided by the presence of a consensual response in the pupils: when only one pupil is stimulated, an equivalent response will be recorded in the unstimulated pupil (Wyatt and Musselman, 1981).
+Evidence of binocular combination is provided by the binocular facilitation observed for the ocular following eye movements in response to fast moving stimuli: when comparing the amplitude of the responses to monocular and binocular stimuli, the binocular response will be more than twice the monocular response (Quaia et al., 2018).
 
-With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
+With this in mind, we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses using changes in the temporal contrast of a flickering light.
+This is a novel paradigm that we developed that allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously for flickering light.
 The results should offer new insight about basic neural circuits and information on how they might be affected in clinical disorders of vision (e.g.~amblyopia).
-Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
-
-Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
-Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
-These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other (Ding and Sperling, 2006).
-In the earlier stage, the right and left eye channels exert gain control on the other channel.
-Then, they exert gain control on the other channel's gain control.
-Lastly, the outputs from each channel are summed binocularly to determine the binocular signal's magnitude.
-The second model is similar as it also incorporates gain control mechanisms (Meese et al., 2006).
-In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
-Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
-This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
-
-To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
-Matching is a paradigm in which the perceived brightness of a standard stimulus is matched to that of a target stimulus.
-In the latter, the interocular ratios of luminance are varied to obtain an equibrightness curve.
-Previous literature has used this paradigm to investigate the binocular fusion of static stimuli and the temporal combination of spatial flickering of spatial increments (a bright target on a dark background) and decrements (a dark target on a bright background) (Anstis and Ho, 1998; Levelt, 1965).
-For spatial increments, it was found that binocular fusion seems to follow approximately linear combination rules.
-This means that, for a monocular stimulus to elicit the same response as a binocular stimulus, the former needs to have twice the signal of the latter.
-On the other hand, spatial decrements follow a winner-takes-all pattern.
-This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
-
-Our experiment used different stimuli than the ones used by Anstis and Ho (1998): in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
-In our experiment, in some conditions, the flicker was shown to only one eye.
-Moreover, they were looking at the temporal fusion of the flicker while we focussed on the binocular fusion of the flicker.
-Based on this and on the results from our first experiment, we expected to find a near linear summation of the responses.
+Based on previous literature, we expected to find a non-linear combination of the responses in the visual cortex, as described by the gain control mechanisms used to describe spatial contrast combination, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
+Additionally, we decided to follow up on our results from this first experiments to test whether perception of flickering light is consistent with the results that we observed in the cortical pathways (visual cortex).
+We therefore conducted a contrast matching experiment using the same type of flickering stimuli used in our first experiment.
 
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit sine-waves to the data, rather than using Fourier analysis (e.g.
-Spitschan et al., 2014).
-Our novel approach is more robust to noise at other frequencies, and makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
-Figueira et al., 2022)
+Note that previous pupillometry studies using luminance flicker have tended to fit sine-waves to the data, rather than using Fourier analysis (e.g.~Spitschan et al., 2014).
+The Fourier approach is more robust to noise at other frequencies and has already been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., 2022)
 
@@
 Thresholds were averaged across participants in logarithmic (dB) units.
+
 For all experiments, we used a bootstrapping procedure with 1000 iterations to estimate standard errors across participants.
@@
 Despite being derived from the model proposed by Meese et al.
-(2006), the simplifications applied to this architecture make it very similar to other models (e.g.
-Ding and Sperling, 2006; Legge, 1984; Schrödinger, 1926).
+(2006), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, 2006; Legge, 1984; Schrödinger, 1926).
 In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
@@
 
-Results from the temporal frequency experiment are shown in \ref{fig:TFdata}.
+Results from the temporal frequency experiment are shown in figure \ref{fig:TFdata}.
 Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
@@
 In Experiment 1 we found evidence of much stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for percieved contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
-Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
+Since perception is dependent on cortical responses, these results provide a clear prediction for percieved contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 
+Using a novel paradigm that combines elctrophysiological and pupillometic measures, we found surprising results for binocular combination of flickering light: in the visual cortex, the processing of temporal luminance modulations seems to happen linearly, with no evidence of interocular suppression, while, in the subcortical pathways, this seems to happen non-linearly with evidence of interocular suppression.
+This pattern of results was also supported by the computational model that we fitted our data to, which showed a much greater suppression weight of the pupillometry data compared with the EEG data.
+Additionally, we also found that perception of flickering light is consistent with cortical responses, with our matching results also showing linear summation effects.
+
+The results from our first experiment were unexpected for both the pupillometry and the EEG.
+Previous studies investigating binocular combination of grating stimuli using steady-state EEG showed that combination for this type of stimuli seems to happen in a non-linear way (Baker and Wade, 2017).
+However, we found that there seems to be a strong binocular facilitation for flickering stimuli.
+While this could have been due to the lower frequency used in our experiment, our second experiment showed that this was not the case.
+A reason for this apparent facilitation could be due to the different nature of our stimuli: Baker and Wade (2017) used static gratings, while here we used flickering stimuli.
+Quaia et al.
+(2018) observed a strong binocular facilitation in eye movement response to moving stimuli.
+Here, obviously, we were not investigating eye movements, but our stimuli included a movement component due to their flickering nature.
+This induced movement of the stimuli could be the reason why we observed this strong facilitation in the visual cortex.
+As for our pupillometry results, we observed less binocular facilitation than what we hypothesised at beginning of testing.
+As mentioned in the introduction, the presence of a consensual response in the pupils (Wyatt and Musselman, 1981) is evidence of binocular interaction.
+Wyatt and Musselman (1981) measured an inequality of the responses between the two eyes during this consensual response, which could actually be explained by the presence of interocular suppression between the two pupils.
+
+On the other hand, the results of our matching experiment were not completely unexpected.
+Previous literature has used the matching paradigm to investigate the binocular fusion of static stimuli for spatial increments, which consists of a bright target on a dark background, and spatial decrements, which consist of a dark target on a bright background (Anstis and Ho, 1998; Levelt, 1965).
+For the former, it was found that binocular fusion seems to follow approximately linear combination rules, while, for the latter, it was found that binocular fusion seems to follow a winner-take-all pattern, where the observer is seeing what the eye that is receiving the strongest signal is seeing.
+Our flickering stimuli were a combination of both increments and decrements presented on a dark background, but presented a stronger similarity in presentation to the increments than the decrements.
+This would explain why our results showed a strong facilitation.
+
+As mentioned before, the main frequency for the three experiments was 2 Hz.
+The reason behind this was that we wanted to be able to measure both EEG and pupillary responses simultaneously.
+However, these two methods have different temporal properties: pupillometry is most responsive to slow flicker frequencies of less than 1 Hz (Spitschan et al., 2014), while steady-state EEG generates stronger responses to faster frequencies of more than 3 Hz (Norcia et al., 2015).
+This means that stronger responses for pupillometry should be obtained at a lower frequency than the one we used in the main experiment, and for EEG at a higher frequency, meaning that our interpretation of the results might have been limited by the frequency that we selected.
+However, previous studies have shown that significant pupil responses can be obtained at higher frequencies, with the pupils showing a similar pattern of responses as at 1 Hz or lower, although at a reduced amplitude (Barrionuevo and Cao, 2016; Barrionuevo et al., 2014).
+Additionally, our second experiment shows that the strong binocular facilitation observed in the cortical areas for flickering stimuli at 2 Hz is also observable at higher frequencies.
+Therefore, this would seem to indicate that 2 Hz was a good compromise to obtain significant responses from both pupillometry and EEG.
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+With these three experiments, we have demonstrated that binocular combination for temporal flickering stimuli seems to happen in different manners in cortical and subcortical pathways.
+
 \hypertarget{references}{%
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson1989}{}}%
+\leavevmode\hypertarget{ref-Anderson1989}{}%
 Anderson PA, Movshon JA. 1989. Binocular combination of contrast signals. \emph{Vision Res} \textbf{29}:1115--32. doi:\href{https://doi.org/10.1016/0042-6989(89)90060-6}{10.1016/0042-6989(89)90060-6}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Angee2021}{}}%
+\leavevmode\hypertarget{ref-Angee2021}{}%
 Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
+\leavevmode\hypertarget{ref-Anstis1998}{}%
 Anstis S, Ho A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
+\leavevmode\hypertarget{ref-Baker2021}{}%
 Baker DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+\leavevmode\hypertarget{ref-Baker2018}{}%
 Baker DH, Lygo FA, Meese TS, Georgeson MA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
+\leavevmode\hypertarget{ref-Baker2020}{}%
 Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+\leavevmode\hypertarget{ref-Baker2017}{}%
 Baker DH, Wade AR.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2012}{}}%
+\leavevmode\hypertarget{ref-Baker2012}{}%
 Baker DH, Wallis SA, Georgeson MA, Meese TS.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+Barrionuevo PA, Cao D.
+2016.
+Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+\emph{J Vis} \textbf{16}:29.
+doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
+
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
+Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
+2014.
+Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
+\emph{Invest Ophthalmol Vis Sci} \textbf{55}:719--27.
+doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
 Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
 Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
+\leavevmode\hypertarget{ref-Delorme2004}{}%
 Delorme A, Makeig S.
 2004.
-{EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis.
+EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
 \emph{J Neurosci Methods} \textbf{134}:9--21.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
+\leavevmode\hypertarget{ref-Ding2006}{}%
 Ding J, Sperling G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Figueira2022}{}}%
+\leavevmode\hypertarget{ref-Figueira2022}{}%
 Figueira JSB, Kutlu E, Scott LS, Keil A.
 2022.
-The FreqTag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
+The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
 \emph{Dev Cogn Neurosci} \textbf{54}:101066.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+\leavevmode\hypertarget{ref-Kassner2014}{}%
 Kassner M, Patera W, Bulling A.
 2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interactionProceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-UbiComp '14 Adjunct; {ACM}.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interactionProceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
+UbiComp '14 Adjunct; ACM.
 pp.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
 Kingdom FAA, Libenson L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
-Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+\leavevmode\hypertarget{ref-Legge1984}{}%
+Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
+\leavevmode\hypertarget{ref-Levelt1965}{}%
 Levelt WJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
+\leavevmode\hypertarget{ref-Mathot2018}{}%
 Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
+\leavevmode\hypertarget{ref-McDougal2010}{}%
 McDougal DH, Gamlin PD.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\leavevmode\hypertarget{ref-Meese2006}{}%
 Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press, Incorporated.
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+2015.
+The steady-state visual evoked potential in vision research: A review.
+\emph{J Vis} \textbf{15}:4.
+doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Quaia2018}{}}%
+\leavevmode\hypertarget{ref-Purves2008}{}%
+Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press, Incorporated.
+
+\leavevmode\hypertarget{ref-Quaia2018}{}%
 Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schrodinger1926}{}}%
+\leavevmode\hypertarget{ref-Schrodinger1926}{}%
 Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
 Spitschan M, Jain S, Brainard DH, Aguirre GK.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Victor1991}{}}%
+\leavevmode\hypertarget{ref-Victor1991}{}%
 Victor JD, Mast J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
+\leavevmode\hypertarget{ref-Wang2015}{}%
 Wang C-A, Munoz DP.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
 Wyatt HJ, Musselman JF.
@@
 
-\end{CSLReferences}
-
 \end{document}

### 2022-12-21 manuscript.Rmd
Edits to abstract, introduction and discussion

--- 2022-10-16 manuscript.Rmd
@@
 
+How does the brain combine information across the eyes?
+In primary visual cortex, spatial patterns are subject to 'ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
+Here we find a very different pattern of activity in response to luminance flicker, both in the cortex and also in the subcortical pathway that determines pupil diameter, by simultaneously collecting steady-state EEG and pupillometry data.
+We find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas pupil diameters showed weaker facilitation and stronger suppression.
+We confirm that this is not a consequence of the temporal parameters chosen, as pronounced binocular facilitation was also observed at faster flicker rates.
+Near-linear binocular combination was also found for the same stimuli using a matching task.
+A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data, compared with the pupillometry results.
+These findings illustrate that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+
 # Introduction
 
----------------------------------
-OK, some pointers for the introduction:
-
-I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
-Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
-I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
-
-The key points should be:
-
-1. For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
-
-2. Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
-
-3.
-We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
-
-4. Actually there's not much work on temporal binocular combination even in the primary visual pathway.
-
-5. We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
-
-I wouldn't say too much about models, or about the matching experiment, at this stage.
----------------------------------
-
-Binocular combination provides a higher visual sensitivity than monocular viewing.
-This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around $\sqrt{2}$ ($\approx1.4$) for grating stimuli at detection threshold [@Campbell1965].
-In other words, a monocular stimulus can elicit the same response as a binocular stimulus if it has a contrast that is 1.4 times higher.
-This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination [@Legge1984]: monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = $\sqrt{R^2 + L^2}$, when R and L are equal to 1, the output is $\sqrt{2}$).
-However, subsequent research has shown that these explanations are not fully adequate to account for binocular summation.
-Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise [@Anderson1989].
-Moreover, more recent research has shown that the summation ratio can vary greatly between $\sqrt{2}$ and 2 depending on factors such as the spatial and temporal frequency of a stimulus or the sensitivity difference between the eyes [@Baker2018].
-These observations led to the development of multistage gain control models, which combine binocular summation and interocular suppression, and can account for contrast matching, detection and discrimination for spatial contrast [@Ding2006; @Meese2006].
-
-In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined [@Purves2008].
-However, there is an eye component that is often underestimated in its role to determine the quality of visual information: the pupil.
-The pupils are openings found in the centre of the eyes that appear to be black and allow light to enter the eyes.
-Their size determines how much light will reach the retina and it is usually determined by the ambient levels of light: in brightness the pupils will constrict and in darkness they will dilate.
-This is known as the pupillary light response (PLR).
-The anatomical pathways that regulate this response are well understood and are very clearly and extensively described in the literature [@Angee2021; @Mathot2018; @McDougal2010; @Wang2015].
-However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
-Given this, not much is known about the computational processes behind the PLR except for some evidence of binocular interaction.
-The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) [@Wyatt1981] are evidence of this binocular interaction.
-
-With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
-The results should offer new insight about basic neural circuits and information on how they might be affected in clinical disorders of vision (e.g.
-amblyopia).
-Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
-
-Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
-Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
-These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other [@Ding2006].
-In the earlier stage, the right and left eye channels exert gain control on the other channel.
-Then, they exert gain control on the other channel’s gain control.
-Lastly, the outputs from each channel are summed binocularly to determine the binocular signal’s magnitude.
-The second model is similar as it also incorporates gain control mechanisms [@Meese2006].
-In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
-Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
-This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
-
-To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
-Matching is a paradigm in which the perceived brightness of a standard stimulus is matched to that of a target stimulus.
-In the latter, the interocular ratios of luminance are varied to obtain an equibrightness curve.
-Previous literature has used this paradigm to investigate the binocular fusion of static stimuli and the temporal combination of spatial flickering of spatial increments (a bright target on a dark background) and decrements (a dark target on a bright background) [@Anstis1998; @Levelt1965].
-For spatial increments, it was found that binocular fusion seems to follow approximately linear combination rules.
-This means that, for a monocular stimulus to elicit the same response as a binocular stimulus, the former needs to have twice the signal of the latter.
-On the other hand, spatial decrements follow a winner-takes-all pattern.
-This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
-
-Our experiment used different stimuli than the ones used by @Anstis1998: in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
-In our experiment, in some conditions, the flicker was shown to only one eye.
-Moreover, they were looking at the temporal fusion of the flicker while we focussed on the binocular fusion of the flicker.
-Based on this and on the results from our first experiment, we expected to find a near linear summation of the responses.
+The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
+This involves a process of signal combination both within [@Baker2017] and between [@Ernst2002] the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established [@Hubel1962].
+Yet much of our knowledge about binocular combination focuses on the 'canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) [@Purves2008].
+Signals are also combined across the eyes in a network of subcortical nuclei that govern pupil diameter in response to incoming light levels [@McDougal2008].
+Our primary purpose here is to investigate whether signal combination involves the same or different operations across these two anatomically distinct pathways.
+
+For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between $\sqrt{2}$ and 2 [@Campbell1965; @Baker2018].
+But this advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) [@Legge1984; @Meese2006] and neural activity [@Moradi2009; @Baker2017] are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision [@Ding2006; @Meese2006] advocate a process of interocular suppression that, at high contrasts, normalizes the two eyes inputs and negates the binocular advantage.
+This is consistent with our everyday experience of 'ocularity invariance' [@Baker2007]: perceived contrast does not change when one eye is opened and closed.
+
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink [@McDougal2008].
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; @Wyatt1981).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus [@Angee2021; @Mathot2018; @McDougal2008; @Wang2015].
+To account for the consensual response, these brain regions must necessarily combine information from the left and right eyes [@Doesschate1967], yet the precise algorithm by which this is achieved is currently unclear.
+
+To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
+This novel paradigm allows us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
+Using periodic flicker entrains both neural [@Norcia2015] and pupil [@Spitschan2014] responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+We follow up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.
+temporal contrast).
+The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways involve stronger interocular suppression than the canonical cortical pathway.
 
@@
 
-Thirty, twelve and ten participants were recruited for Experiments 1, 2 and 3 respectively. All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+Thirty, twelve and ten adult participants were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
 
@@
 
-All stimuli were displayed at a mean luminance of 42 cd/m$^2$ on an Iiyama Vision Master™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 (Minolta Camera Co.
+All stimuli had a mean luminance of 42 cd/m$^2$ on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
 Ltd., Japan).
@@
 In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no specific task instructions, but were asked to look at the fixation crosses in the middle of the two discs while trying to minimise their blinking during the presentation period.
+The participants were given no specific task instructions, but were asked to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+
 We included six distinct ocular conditions, each at five temporal target contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast is defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
 In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a fixed luminance contrast of 48\%.
+In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
 In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
@@
 Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
-Only two ocular configurations, monocular and binocular, were used, with the latter having both discs flickering at the same frequency.
+Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
 The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
@@
 The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
 The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
 
-Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
+The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
 In each block, there were a total of 50 trials.
@@
 EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
-The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
 The fast Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
@@
 @Spitschan2014].
-Our novel approach is more robust to noise at other frequencies, and makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
-@Figueira2022]
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
+@Figueira2022].
 
@@
 where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
-The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it had no effect in this paradigm.
+The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
 
 Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
-@Ding2006; @Legge1984; @Schrodinger1926].
+@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
 In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
@@
 However it is clear that the character of the model in all cases gives a good representation of the data.
-We sampled over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
 
@@
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a substantial spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 Figure \@ref(fig:pupildata)e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Surprisingly there appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
+Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
 The dichoptic cross condition does not show clear modulation with target contrast.
@@
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz [@Spitschan2014].
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz [@Spitschan2014]; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 
-Results from the temporal frequency experiment are shown in \@ref(fig:TFdata).
+Results from the temporal frequency experiment are shown in Figure \@ref(fig:TFdata).
 Figure \@ref(fig:TFdata)a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
@@
 
-In Experiment 1 we found evidence of much stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for percieved contrast judgements indexed by psychophysical contrast matching paradigms [e.g.
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms [e.g.
 @Anstis1998; @Levelt1965; @Quaia2018].
@@
 
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular combination of flickering light.
+In the visual cortex, the processing of temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
+This pattern of results was also supported by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
+
+The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
+Previous studies investigating binocular combination of spatial patterns (i.e.
+sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation [@Baker2017; @Moradi2009; @Meese2006].
+Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
+However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
+For example, @Quaia2018 observed a strong binocular facilitation (or 'supersummation') in the reflexive eye movement response to rapidly moving stimuli, and @Spitschan2019 report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm [@Baker2020].
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments [@Levelt1965; @Anstis1998; @Baker2012], though not for luminance decrements [@Anstis1998].
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+
+Given the above, where does this leave our understanding of the overarching purpose of signal combination?
+@Baker2017 point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs [see also @Ernst2002].
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction [@Li1994; @May2022].
+One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
+Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
+
+Pupil size determines the total amount of light falling on the retina.
+It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
+We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2% of overall diameter [e.g.
+@Spitschan2014].
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms [e.g.
+@Bradley2008].
+We think it unlikely that these temporally coarse processes would have a differential effect on e.g.
+monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+
+# Conclusions
+
+We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulation in visual cortex.
+Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
+We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
+
 # References

### 2022-12-21 manuscript.tex
Edits to abstract, introduction and discussion

--- 2022-10-16 manuscript.tex
@@
 \author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{2022-10-16}
+\date{2022-12-21}
 
@@
 
+How does the brain combine information across the eyes?
+In primary visual cortex, spatial patterns are subject to `ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
+Here we find a very different pattern of activity in response to luminance flicker, both in the cortex and also in the subcortical pathway that determines pupil diameter, by simultaneously collecting steady-state EEG and pupillometry data.
+We find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas pupil diameters showed weaker facilitation and stronger suppression.
+We confirm that this is not a consequence of the temporal parameters chosen, as pronounced binocular facilitation was also observed at faster flicker rates.
+Near-linear binocular combination was also found for the same stimuli using a matching task.
+A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data, compared with the pupillometry results.
+These findings illustrate that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+
 \hypertarget{introduction}{%
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
+This involves a process of signal combination both within (Baker and Wade, 2017) and between (Ernst and Banks, 2002) the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, 1962).
+Yet much of our knowledge about binocular combination focuses on the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
+Signals are also combined across the eyes in a network of subcortical nuclei that govern pupil diameter in response to incoming light levels (McDougal and Gamlin, 2008).
+Our primary purpose here is to investigate whether signal combination involves the same or different operations across these two anatomically distinct pathways.
 
-OK, some pointers for the introduction:
+For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., 2018; Campbell and Green, 1965).
+But this advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that, at high contrasts, normalizes the two eyes inputs and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance' (Baker et al., 2007): perceived contrast does not change when one eye is opened and closed.
 
-I think we need to draw a distinction between binocular summation at threshold (on which there is a big literature) and binocular facilitation above threshold.
-Much of the introduction is focussed on threshold measures, but actually I think our focus here is more about suprathreshold conditions where we usually see little facilitation.
-I think it will help the reader if we use the term summation only to refer to threshold phenomena, and facilitation in the more general case (I've tried to do this elsewhere in the paper).
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, 2008).
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (1981)).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2008; Wang and Munoz, 2015).
+To account for the consensual response, these brain regions must necessarily combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the precise algorithm by which this is achieved is currently unclear.
 
-The key points should be:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\item
-  For grating stimuli, there are summation effects at threshold, but these are lost at high contrasts.
-\item
-  Binocular combination happens in multiple pathways, including the pupil pathway. (This is a good place to mention the Quaia paper).
-\item
-  We don't know much about the pupil response, though it is clearly binocular because of the consensual response (convergence and divergence seem to be other ways of saying the same thing, so not sure they are worth mentioning).
-\item
-  Actually there's not much work on temporal binocular combination even in the primary visual pathway.
-\item
-  We have developed a novel paradigm that allows us to probe both cortical and subcortical pathways simultaneously for flickering light.
-\end{enumerate}
-
-I wouldn't say too much about models, or about the matching experiment, at this stage.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-Binocular combination provides a higher visual sensitivity than monocular viewing.
-This superiority is known as binocular summation and is defined by the binocular summation ratio (BSR), which was originally believed to be around \(\sqrt{2}\) (\(\approx1.4\)) for grating stimuli at detection threshold (Campbell and Green, 1965).
-In other words, a monocular stimulus can elicit the same response as a binocular stimulus if it has a contrast that is 1.4 times higher.
-This led Legge to develop a widely accepted explanation that used quadratic summation to describe binocular combination (Legge, 1984): monocular signals from the right (R) and the left (L) eyes are squared before being summed together and the binocular response (B) is given by the square root of the output (B = \(\sqrt{R^2 + L^2}\), when R and L are equal to 1, the output is \(\sqrt{2}\)).
-However, subsequent research has shown that these explanations are not fully adequate to account for binocular summation.
-Both of these accounts constitute single channel models, and this type of model has been shown to not being able to account for contrast detection in the presence of noise (Anderson and Movshon, 1989).
-Moreover, more recent research has shown that the summation ratio can vary greatly between \(\sqrt{2}\) and 2 depending on factors such as the spatial and temporal frequency of a stimulus or the sensitivity difference between the eyes (Baker et al., 2018).
-These observations led to the development of multistage gain control models, which combine binocular summation and interocular suppression, and can account for contrast matching, detection and discrimination for spatial contrast (Ding and Sperling, 2006; Meese et al., 2006).
-
-In general, it seems that the mechanisms behind binocular combination have been thoroughly studied, as have been the anatomical pathways behind it: light enters the eye though the pupil and signals are sent from the left and right retinae to the primary visual cortex, remaining anatomically isolated while passing through the lateral geniculate nucleus (LGN) until they reach V1, where they are binocularly combined (Purves et al., 2008).
-However, there is an eye component that is often underestimated in its role to determine the quality of visual information: the pupil.
-The pupils are openings found in the centre of the eyes that appear to be black and allow light to enter the eyes.
-Their size determines how much light will reach the retina and it is usually determined by the ambient levels of light: in brightness the pupils will constrict and in darkness they will dilate.
-This is known as the pupillary light response (PLR).
-The anatomical pathways that regulate this response are well understood and are very clearly and extensively described in the literature (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2010; Wang and Munoz, 2015).
-However, they are anatomically distinct from the LGN-V1 pathway meaning that binocular combination occurs separately in anatomically distinct pathways.
-Given this, not much is known about the computational processes behind the PLR except for some evidence of binocular interaction.
-The presence of a consensual response in one eye when the other is being stimulated, and the presence of convergence (one pupil responds to illumination in either retina) and divergence (both pupils respond to illumination of one retina) (Wyatt and Musselman, 1981) are evidence of this binocular interaction.
-
-With this in mind we designed an experiment that simultaneously recorded electrophysiological and pupillometric responses to investigate the combination of flickering light signals in both the visual cortex and the pupils.
-The results should offer new insight about basic neural circuits and information on how they might be affected in clinical disorders of vision (e.g.~amblyopia).
-Based on previous literature, we expected to find a non-linear combination of the responses in visual cortex, as described by the gain control mechanisms, and a more linear combination of the responses and a greater binocular response at the level of the pupils.
-
-Several models have been developed and proposed to describe binocular combination and contrast matching results for spatial contrast.
-Among these, the models proposed by Ding and Sperling (2006) and Meese and colleagues (2006) are widely accepted.
-These models incorporate a dynamic contrast gain control, which allows to develop a model that combines binocular summation and interocular suppression The first model is a multistage model that consists of two pairs of gain control mechanisms that inhibit each other (Ding and Sperling, 2006).
-In the earlier stage, the right and left eye channels exert gain control on the other channel.
-Then, they exert gain control on the other channel's gain control.
-Lastly, the outputs from each channel are summed binocularly to determine the binocular signal's magnitude.
-The second model is similar as it also incorporates gain control mechanisms (Meese et al., 2006).
-In the first stage, it is applied to the left and right eye channels with suppression from the other eye.
-Then the signal from the two eyes is summed binocularly and gain control is applied a second time.
-This second model in particular is interesting and relevant as it was designed to also explain data from matching experiments.
-
-To follow up on the results that we obtained, we decided to perform a contrast matching experiment to investigate whether perception of flickering light is consistent with the results observed in the cortical pathways (visual cortex) or the subcortical pathways (pupils).
-Matching is a paradigm in which the perceived brightness of a standard stimulus is matched to that of a target stimulus.
-In the latter, the interocular ratios of luminance are varied to obtain an equibrightness curve.
-Previous literature has used this paradigm to investigate the binocular fusion of static stimuli and the temporal combination of spatial flickering of spatial increments (a bright target on a dark background) and decrements (a dark target on a bright background) (Anstis and Ho, 1998; Levelt, 1965).
-For spatial increments, it was found that binocular fusion seems to follow approximately linear combination rules.
-This means that, for a monocular stimulus to elicit the same response as a binocular stimulus, the former needs to have twice the signal of the latter.
-On the other hand, spatial decrements follow a winner-takes-all pattern.
-This means that the observer is seeing what the eye that is receiving the strongest signal is seeing.
-
-Our experiment used different stimuli than the ones used by Anstis and Ho (1998): in the binocular fusion experiment, their stimuli were not flickering and, in the flicker experiment, they were always shown in both eyes.
-In our experiment, in some conditions, the flicker was shown to only one eye.
-Moreover, they were looking at the temporal fusion of the flicker while we focussed on the binocular fusion of the flicker.
-Based on this and on the results from our first experiment, we expected to find a near linear summation of the responses.
+To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
+This novel paradigm allows us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
+Using periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+We follow up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
+The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways involve stronger interocular suppression than the canonical cortical pathway.
 
@@
 
-All stimuli were displayed at a mean luminance of 42 cd/m\(^2\) on an Iiyama Vision Master™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 (Minolta Camera Co.~Ltd., Japan).
+All stimuli had a mean luminance of 42 cd/m\(^2\) on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
 For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
@@
 The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After the discs appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
 The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
 
-Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience The experiment was divided into 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
+The experiment was divided into 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
 In each block, there were a total of 50 trials.
@@
 EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
-The data for each participant were then loaded into R for analysis where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
 The fast Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
@@
 Spitschan et al., 2014).
-Our novel approach is more robust to noise at other frequencies, and makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
-Figueira et al., 2022)
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
+Figueira et al., 2022).
 
@@
 where \emph{n} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
-The \(R_{max}\) parameter was omitted when modelling the contrast matching data, as it had no effect in this paradigm.
+The \(R_{max}\) parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
 
@@
 (2006), the simplifications applied to this architecture make it very similar to other models (e.g.
-Ding and Sperling, 2006; Legge, 1984; Schrödinger, 1926).
+Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
 In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
@@
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a substantial spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Surprisingly there appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
+Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
 The dichoptic cross condition does not show clear modulation with target contrast.
@@
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014).
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
-Results from the temporal frequency experiment are shown in \ref{fig:TFdata}.
+Results from the temporal frequency experiment are shown in Figure \ref{fig:TFdata}.
 Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
@@
 
-In Experiment 1 we found evidence of much stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for percieved contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
 Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
@@
 
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular combination of flickering light.
+In the visual cortex, the processing of temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
+This pattern of results was also supported by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
+
+The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
+Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
+However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
+For example, Quaia et al.
+(2018) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (2019) report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., 2020).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, 1998; Baker et al., 2012; Levelt, 1965), though not for luminance decrements (Anstis and Ho, 1998).
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+
+Given the above, where does this leave our understanding of the overarching purpose of signal combination?
+Baker and Wade (2017) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, 2002).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, 1994; May and Zhaoping, 2022).
+One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
+Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
+
+Pupil size determines the total amount of light falling on the retina.
+It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
+We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.
+Spitschan et al., 2014).
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.
+Bradley et al., 2008).
+We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulation in visual cortex.
+Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
+We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
+
 \hypertarget{references}{%
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Anderson1989}{}}%
-Anderson PA, Movshon JA. 1989. Binocular combination of contrast signals. \emph{Vision Res} \textbf{29}:1115--32. doi:\href{https://doi.org/10.1016/0042-6989(89)90060-6}{10.1016/0042-6989(89)90060-6}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Angee2021}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+Baker DH, Meese TS, Georgeson MA.
+2007.
+Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
+\emph{Spat Vis} \textbf{20}:397--413.
+doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
@@
 doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
+Barrionuevo PA, Cao D.
+2016.
+Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+\emph{J Vis} \textbf{16}:29.
+doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
+Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
+2014.
+Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
+\emph{Invest Ophthalmol Vis Sci} \textbf{55}:719--27.
+doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Bradley2008}{}}%
+Bradley MM, Miccoli L, Escrig MA, Lang PJ.
+2008.
+The pupil as a measure of emotional arousal and autonomic activation.
+\emph{Psychophysiology} \textbf{45}:602--7.
+doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Doesschate1967}{}}%
+Doesschate J ten, Alpern M.
+1967.
+Effect of photoexcitation of the two retinas on pupil size.
+\emph{J Neurophysiol} \textbf{30}:562--76.
+doi:\href{https://doi.org/10.1152/jn.1967.30.3.562}{10.1152/jn.1967.30.3.562}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Ernst2002}{}}%
+Ernst MO, Banks MS.
+2002.
+Humans integrate visual and haptic information in a statistically optimal fashion.
+\emph{Nature} \textbf{415}:429--33.
+doi:\href{https://doi.org/10.1038/415429a}{10.1038/415429a}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Figueira2022}{}}%
@@
 doi:\href{https://doi.org/10.1016/j.dcn.2022.101066}{10.1016/j.dcn.2022.101066}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
+Hubel DH, Wiesel TN.
+1962.
+Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
+\emph{J Physiol} \textbf{160}:106--54.
+doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Li1994}{}}%
+Li Z, Atick JJ.
+1994.
+Efficient stereo coding in the multiscale representation.
+\emph{Network: Computation in Neural Systems} \textbf{5}:157--174.
+doi:\href{https://doi.org/10.1088/0954-898X_5_2_003}{10.1088/0954-898X\_5\_2\_003}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2010}{}}%
-McDougal DH, Gamlin PD.
-2010.
-The influence of intrinsically-photosensitive retinal ganglion cells on the spectral sensitivity and response dynamics of the human pupillary light reflex.
-\emph{Vision Res} \textbf{50}:72--87.
-doi:\href{https://doi.org/10.1016/j.visres.2009.10.012}{10.1016/j.visres.2009.10.012}
+\leavevmode\vadjust pre{\hypertarget{ref-May2022}{}}%
+May K, Zhaoping L.
+2022.
+Li and {Atick's} theory of efficient binocular coding: A tutorial and mini-review.
+\emph{Vision Res} \textbf{201}:107950.
+doi:\href{https://doi.org/10.1016/j.visres.2021.08.005}{10.1016/j.visres.2021.08.005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
+McDougal DH, Gamlin PD. 2008. Pupillary control pathwaysThe Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+2015.
+The steady-state visual evoked potential in vision research: A review.
+\emph{J Vis} \textbf{15}:4.
+doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press, Incorporated.
+Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press.
 
@@
 Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
+Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 

### 2023-01-05 manuscript.Rmd
Integrated comments from ARW

@@
 output:
+  word_document: default
   bookdown::pdf_document2:
@@
     keep_tex: yes
-  word_document: default
   pdf_document:
@@
 In primary visual cortex, spatial patterns are subject to 'ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
-Here we find a very different pattern of activity in response to luminance flicker, both in the cortex and also in the subcortical pathway that determines pupil diameter, by simultaneously collecting steady-state EEG and pupillometry data.
-We find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas pupil diameters showed weaker facilitation and stronger suppression.
-We confirm that this is not a consequence of the temporal parameters chosen, as pronounced binocular facilitation was also observed at faster flicker rates.
-Near-linear binocular combination was also found for the same stimuli using a matching task.
-A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data, compared with the pupillometry results.
-These findings illustrate that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+Here we asked whether this invariance holds for pure changes in luminance.
+We collected steady-state EEG and pupillometry data simultaneously, and find strong deviations from ocularity invariance both in the cortex and also in the subcortical pathway that determines pupil diameter.
+In cortex, we find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas measurements of pupil diameter showed weaker facilitation and stronger suppression.
+This was not purely a consequence of the temporal stimulus parameters; pronounced binocular facilitation was also observed at faster flicker rates.
+Near-linear binocular combination was also found for the same stimuli using a perceptual matching task.
+A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data compared with the pupillometry results.
+These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
 
@@
 Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established [@Hubel1962].
-Yet much of our knowledge about binocular combination focuses on the 'canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) [@Purves2008].
-Signals are also combined across the eyes in a network of subcortical nuclei that govern pupil diameter in response to incoming light levels [@McDougal2008].
-Our primary purpose here is to investigate whether signal combination involves the same or different operations across these two anatomically distinct pathways.
+Much of our knowledge about binocular combination derives from studies on the contrast response of the 'canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) [@Purves2008].
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels [@McDougal2008] and much less is known about the computations that operate in these subcortical pathways.
+In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
@@
 This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between $\sqrt{2}$ and 2 [@Campbell1965; @Baker2018].
-But this advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) [@Legge1984; @Meese2006] and neural activity [@Moradi2009; @Baker2017] are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision [@Ding2006; @Meese2006] advocate a process of interocular suppression that, at high contrasts, normalizes the two eyes inputs and negates the binocular advantage.
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) [@Legge1984; @Meese2006] and neural activity [@Moradi2009; @Baker2017] are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision [@Ding2006; @Meese2006] advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
 This is consistent with our everyday experience of 'ocularity invariance' [@Baker2007]: perceived contrast does not change when one eye is opened and closed.
@@
 Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus [@Angee2021; @Mathot2018; @McDougal2008; @Wang2015].
-To account for the consensual response, these brain regions must necessarily combine information from the left and right eyes [@Doesschate1967], yet the precise algorithm by which this is achieved is currently unclear.
+To account for the consensual response, these brain regions must  combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is achieved is unclear.
 
 To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
-This novel paradigm allows us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Using periodic flicker entrains both neural [@Norcia2015] and pupil [@Spitschan2014] responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
-We follow up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.
+This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
+Periodic flicker entrains both neural [@Norcia2015] and pupil [@Spitschan2014] responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.
 temporal contrast).
-The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways involve stronger interocular suppression than the canonical cortical pathway.
+The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways implement stronger interocular suppression than the canonical cortical pathway.
 
@@
 
-The stimuli were two discs of flickering light with a diameter of 3.74 degrees, presented on a black background.
+The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
 The same stimuli were used for all three experiments.
@@
 The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in one session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
-In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no specific task instructions, but were asked to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
-
-We included six distinct ocular conditions, each at five temporal target contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
-Contrast is defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
+The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+
+We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
 In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
@@
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
-The fast Fourier transform was calculated for each waveform, and the spectrum stored in a matrix.
+The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
 All repetitions of each condition were then averaged for each electrode.
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging retained the phase information (i.e.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.
 coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
@@
 We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The fast Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
 Finally, data were averaged across all participants to obtain the group results.
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit sine-waves to the data, rather than using Fourier analysis [e.g.
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis [e.g.
 @Spitschan2014].
@@
 Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular combination of flickering light.
-In the visual cortex, the processing of temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
 In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
-This pattern of results was also supported by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
 Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.

### 2023-01-07 manuscript.Rmd
Added paragraph to discussion on blobs

@@
 output:
-  word_document: default
   bookdown::pdf_document2:
@@
     toc: no
+  word_document: default
   html_document: default
@@
 This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
-This explains the amplitude differences between model and data, particularly at low target contrast levels, but are of no consequence for the pattern of relative responses across conditions.
+This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
 
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict [@Meese2006; @Baker2017].
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict [@Meese2006; @Baker2017], and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
-The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absence of dichoptic masking.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
 
@@
 
-Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular combination of flickering light.
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
 In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
@@
 Previous studies investigating binocular combination of spatial patterns (i.e.
-sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation [@Baker2017; @Moradi2009; @Meese2006].
+sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts [@Baker2017; @Moradi2009; @Meese2006].
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
@@
 
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase 'blobs' [@Horton1981; @Livingstone1984] are biased towards low spatial frequencies [@Tootell1988; @Edwards1995], and relatively insensitive to stimulus orientation [@Horton1981; @Livingstone1984; though see @Economides2011].
+As the blob regions are embedded within ocular dominance columns [@Horton1981], they are also largely monocular [@Livingstone1984; @Tychsen2004].
+More recent work has reported psychophysical evidence for unoriented chromatic [@Gheiratmand2013] and achromatic [@Meese2011] mechanisms, that also appear to be monocular.
+Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.
+Figures \@ref(fig:BSratios) & \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
+However our matching data (Figure \@ref(fig:matchingdata)), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+
 # Conclusions
@@
 We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
-Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulation in visual cortex.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
 Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
@@
 
+# Acknowledgements
+
+Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+
 # References

### 2023-01-07 manuscript.tex
Added paragraph to discussion on blobs

@@
 \author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{2022-12-21}
+\date{2023-01-07}
 
@@
 In primary visual cortex, spatial patterns are subject to `ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
-Here we find a very different pattern of activity in response to luminance flicker, both in the cortex and also in the subcortical pathway that determines pupil diameter, by simultaneously collecting steady-state EEG and pupillometry data.
-We find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas pupil diameters showed weaker facilitation and stronger suppression.
-We confirm that this is not a consequence of the temporal parameters chosen, as pronounced binocular facilitation was also observed at faster flicker rates.
-Near-linear binocular combination was also found for the same stimuli using a matching task.
-A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data, compared with the pupillometry results.
-These findings illustrate that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+Here we asked whether this invariance holds for pure changes in luminance.
+We collected steady-state EEG and pupillometry data simultaneously, and find strong deviations from ocularity invariance both in the cortex and also in the subcortical pathway that determines pupil diameter.
+In cortex, we find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas measurements of pupil diameter showed weaker facilitation and stronger suppression.
+This was not purely a consequence of the temporal stimulus parameters; pronounced binocular facilitation was also observed at faster flicker rates.
+Near-linear binocular combination was also found for the same stimuli using a perceptual matching task.
+A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data compared with the pupillometry results.
+These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
 
@@
 Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, 1962).
-Yet much of our knowledge about binocular combination focuses on the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
-Signals are also combined across the eyes in a network of subcortical nuclei that govern pupil diameter in response to incoming light levels (McDougal and Gamlin, 2008).
-Our primary purpose here is to investigate whether signal combination involves the same or different operations across these two anatomically distinct pathways.
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, 2008) and much less is known about the computations that operate in these subcortical pathways.
+In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
@@
 This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., 2018; Campbell and Green, 1965).
-But this advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that, at high contrasts, normalizes the two eyes inputs and negates the binocular advantage.
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
 This is consistent with our everyday experience of `ocularity invariance' (Baker et al., 2007): perceived contrast does not change when one eye is opened and closed.
@@
 Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2008; Wang and Munoz, 2015).
-To account for the consensual response, these brain regions must necessarily combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the precise algorithm by which this is achieved is currently unclear.
+To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the computation that achieves this is achieved is unclear.
 
 To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
-This novel paradigm allows us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Using periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
-We follow up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
-The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways involve stronger interocular suppression than the canonical cortical pathway.
+This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
+Periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
+The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways implement stronger interocular suppression than the canonical cortical pathway.
 
@@
 The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in one session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
-In each block, there were 60 trials in total lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no specific task instructions, but were asked to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
 
-We included six distinct ocular conditions, each at five temporal target contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
-Contrast is defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
+We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
 In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
 For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (2021).
@@
 We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The fast Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
 Finally, data were averaged across all participants to obtain the group results.
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit sine-waves to the data, rather than using Fourier analysis (e.g.
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.
 Spitschan et al., 2014).
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006).
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006), and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
-The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absence of dichoptic masking.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
 
@@
 
-Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular combination of flickering light.
-In the visual cortex, the processing of temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
+In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
 In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
-This pattern of results was also supported by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
 Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
@@
 
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, 1981; Livingstone and Hubel, 1984) are biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988), and relatively insensitive to stimulus orientation (Horton and Hubel, 1981; Livingstone and Hubel, 1984; though see Economides et al., 2011).
+As the blob regions are embedded within ocular dominance columns (Horton and Hubel, 1981), they are also largely monocular (Livingstone and Hubel, 1984; Tychsen et al., 2004).
+More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., 2013) and achromatic (Meese and Baker, 2011) mechanisms, that also appear to be monocular.
+Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
+However our matching data (Figure \ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+
 \hypertarget{conclusions}{%
@@
 We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
-Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulation in visual cortex.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
 Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
 We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
+
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
+
+Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
 
@@
 Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
-\emph{J Vis} \textbf{16}:29.
+\emph{J Vis} \textbf{16(11)}:29.
 doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
@@
 Stan: A probabilistic programming language.
-\emph{Journal of Statistical Software, Articles} \textbf{76}:1--32.
+\emph{Journal of Statistical Software} \textbf{76}:1--32.
 doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Economides2011}{}}%
+Economides JR, Sincich LC, Adams DL, Horton JC.
+2011.
+Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
+\emph{Nat Neurosci} \textbf{14}:1574--80.
+doi:\href{https://doi.org/10.1038/nn.2958}{10.1038/nn.2958}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
+Edwards DP, Purpura KP, Kaplan E.
+1995.
+Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
+\emph{Vision Res} \textbf{35}:1501--23.
+doi:\href{https://doi.org/10.1016/0042-6989(94)00253-i}{10.1016/0042-6989(94)00253-i}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Ernst2002}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Gheiratmand2013}{}}%
+Gheiratmand M, Meese TS, Mullen KT.
+2013.
+Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
+\emph{Journal of Vision} \textbf{13(1)}:2.
+doi:\href{https://doi.org/10.1167/13.1.2}{10.1167/13.1.2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Horton1981}{}}%
+Horton JC, Hubel DH.
+1981.
+Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
+\emph{Nature} \textbf{292}:762--4.
+doi:\href{https://doi.org/10.1038/292762a0}{10.1038/292762a0}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
@@
 2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interactionProceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
 UbiComp '14 Adjunct; {ACM}.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Livingstone1984}{}}%
+Livingstone MS, Hubel DH.
+1984.
+Anatomy and physiology of a color system in the primate visual cortex.
+\emph{J Neurosci} \textbf{4}:309--56.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{10.1523/JNEUROSCI.04-01-00309.1984}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
@@
 \leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
-McDougal DH, Gamlin PD. 2008. Pupillary control pathwaysThe Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
+McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2011}{}}%
+Meese TS, Baker DH.
+2011.
+A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
+\emph{{iPerception}} \textbf{2}:159--82.
+doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
-Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9}:13.1--22. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
+Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}:13. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
@@
 The steady-state visual evoked potential in vision research: A review.
-\emph{J Vis} \textbf{15}:4.
+\emph{J Vis} \textbf{15(6)}:4.
 doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Quaia2018}{}}%
-Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
+Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
 
@@
 doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tootell1988}{}}%
+Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
+1988.
+Functional anatomy of macaque striate cortex.
+V.
+Spatial frequency.
+\emph{J Neurosci} \textbf{8}:1610--24.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{10.1523/JNEUROSCI.08-05-01610.1988}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tychsen2004}{}}%
+Tychsen L, Wong AM-F, Burkhalter A.
+2004.
+Paucity of horizontal connections for binocular vision in V1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
+\emph{The Journal of Comparative Neurology} \textbf{474}:261--275.
+doi:\href{https://doi.org/10.1002/cne.20113}{10.1002/cne.20113}
 

### 2023-01-10 manuscript.Rmd
Small edits for Aurelio's comments. Somehow I broke everything after the matching figure caption...

@@
 
-Thirty, twelve and ten adult participants were recruited for Experiments 1, 2 and 3 respectively.
+Thirty, twelve and ten adult participants, whose age ranged from 18 to 40, were recruited for Experiments 1, 2 and 3 respectively.
 All participants had normal or corrected to normal binocular vision, and gave written informed consent.
@@
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$.
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data.
+However it is clear that the character of the model in all cases gives a good representation of the data, as it can be seen in figures \@ref(fig:modelfigure)a-h.
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \@ref(fig:EEGdata)c) and second (Figure \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`).
+Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of statistical results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.", out.width = '50%', fig.align="center", echo=FALSE}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Note that, for the 48% match, the data point on the x axis falls higher than 100% contrast.
+This is because some individual results were interpolated above 100%, therefore skewing the results slighlty above that value.
+The effects are negligible.", out.width = '50%', fig.align="center", echo=FALSE}
 

### 2023-01-10 manuscript.tex
Small edits for Aurelio's comments. Somehow I broke everything after the matching figure caption...

@@
 \author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{2023-01-07}
+\date{2023-01-10}
 
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.
-Spitschan et al., 2014).
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.~Spitschan et al., 2014).
 The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
-Figueira et al., 2022).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., 2022).
 
@@
 Despite being derived from the model proposed by Meese et al.
-(2006), the simplifications applied to this architecture make it very similar to other models (e.g.
-Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
+(2006), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
 In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
@@
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., 2012; Meese et al., 2006).
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data.
+However it is clear that the character of the model in all cases gives a good representation of the data, as it can be seen in figures \ref{fig:modelfigure}a-h.
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13).
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of statistical results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
-Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 
-\begin{figure}
+\textbackslash begin\{figure\}
 
-{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
+\{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
 
-}
+\}
 
-\caption{Contrast matching functions.
+\textbackslash caption\{Contrast matching functions.
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.}\label{fig:matchingdata}
-\end{figure}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Note that, for the 48\% match, the data point on the x axis falls higher than 100\% contrast.
+This is because some individual results were interpolated above 100\%, therefore skewing the results slighlty above that value.
+The effects are negligible.\}\label{fig:matchingdata}
+\textbackslash end\{figure\}
 
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.
-Spitschan et al., 2014).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.
-Bradley et al., 2008).
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.~Spitschan et al., 2014).
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.~Bradley et al., 2008).
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Angee2021}{}}%
+\leavevmode\hypertarget{ref-Angee2021}{}%
 Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+\leavevmode\hypertarget{ref-Baker2007}{}%
 Baker DH, Meese TS, Georgeson MA.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
 Barrionuevo PA, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
 Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Bradley2008}{}}%
+\leavevmode\hypertarget{ref-Bradley2008}{}%
 Bradley MM, Miccoli L, Escrig MA, Lang PJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\leavevmode\hypertarget{ref-Campbell1965}{}%
 Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
 Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Doesschate1967}{}}%
+\leavevmode\hypertarget{ref-Doesschate1967}{}%
 Doesschate J ten, Alpern M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Economides2011}{}}%
+\leavevmode\hypertarget{ref-Economides2011}{}%
 Economides JR, Sincich LC, Adams DL, Horton JC.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
+\leavevmode\hypertarget{ref-Edwards1995}{}%
 Edwards DP, Purpura KP, Kaplan E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Ernst2002}{}}%
+\leavevmode\hypertarget{ref-Ernst2002}{}%
 Ernst MO, Banks MS.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Gheiratmand2013}{}}%
+\leavevmode\hypertarget{ref-Gheiratmand2013}{}%
 Gheiratmand M, Meese TS, Mullen KT.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Horton1981}{}}%
+\leavevmode\hypertarget{ref-Horton1981}{}%
 Horton JC, Hubel DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
+\leavevmode\hypertarget{ref-Hubel1962}{}%
 Hubel DH, Wiesel TN.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+\leavevmode\hypertarget{ref-Kassner2014}{}%
 Kassner M, Patera W, Bulling A.
 2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 {ACM} International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-UbiComp '14 Adjunct; {ACM}.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
+UbiComp '14 Adjunct; ACM.
 pp.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Li1994}{}}%
+\leavevmode\hypertarget{ref-Li1994}{}%
 Li Z, Atick JJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Livingstone1984}{}}%
+\leavevmode\hypertarget{ref-Livingstone1984}{}%
 Livingstone MS, Hubel DH.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
+\leavevmode\hypertarget{ref-Mathot2018}{}%
 Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
-\leavevmode\vadjust pre{\hypertarget{ref-May2022}{}}%
+\leavevmode\hypertarget{ref-May2022}{}%
 May K, Zhaoping L.
 2022.
-Li and {Atick's} theory of efficient binocular coding: A tutorial and mini-review.
+Li and Atick's theory of efficient binocular coding: A tutorial and mini-review.
 \emph{Vision Res} \textbf{201}:107950.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
+\leavevmode\hypertarget{ref-McDougal2008}{}%
 McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2011}{}}%
+\leavevmode\hypertarget{ref-Meese2011}{}%
 Meese TS, Baker DH.
@@
 A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-\emph{{iPerception}} \textbf{2}:159--82.
+\emph{iPerception} \textbf{2}:159--82.
 doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\leavevmode\hypertarget{ref-Meese2006}{}%
 Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\leavevmode\hypertarget{ref-Moradi2009}{}%
 Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}:13. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+\leavevmode\hypertarget{ref-Norcia2015}{}%
 Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press.
+\leavevmode\hypertarget{ref-Purves2008}{}%
+Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Quaia2018}{}}%
+\leavevmode\hypertarget{ref-Quaia2018}{}%
 Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schrodinger1926}{}}%
+\leavevmode\hypertarget{ref-Schrodinger1926}{}%
 Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
 Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
 Spitschan M, Jain S, Brainard DH, Aguirre GK.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tootell1988}{}}%
+\leavevmode\hypertarget{ref-Tootell1988}{}%
 Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tychsen2004}{}}%
+\leavevmode\hypertarget{ref-Tychsen2004}{}%
 Tychsen L, Wong AM-F, Burkhalter A.
 2004.
-Paucity of horizontal connections for binocular vision in V1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
+Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
 \emph{The Journal of Comparative Neurology} \textbf{474}:261--275.

### 2023-01-10 manuscript.Rmd
Minor fixes

@@
 
-Thirty, twelve and ten adult participants, whose age ranged from 18 to 40, were recruited for Experiments 1, 2 and 3 respectively.
+Thirty, twelve and ten adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
 All participants had normal or corrected to normal binocular vision, and gave written informed consent.
@@
 Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as it can be seen in figures \@ref(fig:modelfigure)a-h.
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \@ref(fig:modelfigure).
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \@ref(fig:EEGdata)c) and second (Figure \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of statistical results obtained at the second harmonic.
+Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Note that, for the 48% match, the data point on the x axis falls higher than 100% contrast.
-This is because some individual results were interpolated above 100%, therefore skewing the results slighlty above that value.
-The effects are negligible.", out.width = '50%', fig.align="center", echo=FALSE}
+Note that, for the {48\\%} match, the data point on the x axis falls higher than {100\\%} contrast.
+This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\\%}, shifting the mean slightly above that value.", out.width = '50%', fig.align="center", echo=FALSE}
 

### 2023-01-10 manuscript.tex
Minor fixes

--- 2023-01-07 manuscript.tex
@@
 
-Thirty, twelve and ten adult participants were recruited for Experiments 1, 2 and 3 respectively.
+Thirty, twelve and ten adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
 All participants had normal or corrected to normal binocular vision, and gave written informed consent.
@@
 Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data.
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \ref{fig:modelfigure}.
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13).
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.}\label{fig:matchingdata}
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
+This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
 \end{figure}

### 2023-01-10 manuscript.Rmd
Added author contributions section

@@
 author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
-date: "`r Sys.Date()`"
+date: "Department of Psychology, University of York, UK"
 output:
@@
 We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://osf.io/tbema/.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
 
@@
 
+# Author contributions
+
+**Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
+**Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
+**Myat Aung**: Software, resources, writing - review & editing.
+**Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
+**Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
+
 # References

### 2023-01-10 manuscript.tex
Added author contributions section

@@
 \author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{2023-01-10}
+\date{Department of Psychology, University of York, UK}
 
@@
 We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: \url{https://osf.io/tbema/}.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
@@
 Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
+
+\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
+\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Myat Aung}: Software, resources, writing - review \& editing.
+\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
 

### 2023-01-12 manuscript.Rmd
Added declaration of interest and gender distribution for 3 experiments.

@@
 
-Thirty, twelve and ten adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
 All participants had normal or corrected to normal binocular vision, and gave written informed consent.
@@
 
+# Declaration of interests
+
+The authors declare no competing interests.
+
 # References

### 2023-01-12 manuscript.tex
Added declaration of interest and gender distribution for 3 experiments.

--- 2023-01-10 manuscript.tex
@@
 
-Thirty, twelve and ten adult participants, whose age ranged from 18 to 40, were recruited for Experiments 1, 2 and 3 respectively.
+Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
 All participants had normal or corrected to normal binocular vision, and gave written informed consent.
@@
 Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as it can be seen in figures \ref{fig:modelfigure}a-h.
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \ref{fig:modelfigure}.
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of statistical results obtained at the second harmonic.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 
-\textbackslash begin\{figure\}
+\begin{figure}
 
-\{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
+{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
 
-\}
+}
 
-\textbackslash caption\{Contrast matching functions.
+\caption{Contrast matching functions.
 Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
 Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Note that, for the 48\% match, the data point on the x axis falls higher than 100\% contrast.
-This is because some individual results were interpolated above 100\%, therefore skewing the results slighlty above that value.
-The effects are negligible.\}\label{fig:matchingdata}
-\textbackslash end\{figure\}
+Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
+This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
+\end{figure}
 
@@
 Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
+
+\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
+\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Myat Aung}: Software, resources, writing - review \& editing.
+\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
+
+\hypertarget{declaration-of-interests}{%
+\section{Declaration of interests}\label{declaration-of-interests}}
+
+The authors declare no competing interests.
 

### 2023-01-20 manuscriptNature.Rmd
Created rmd file specific for Nature and added Nature referencing style.

--- 2023-01-10 manuscript.Rmd
@@
 bibliography: references.bib
-csl: elife.csl
+csl: nature-neuroscience.csl
 ---
@@
 
-# Methods
-
-## Participants
-
-Thirty, twelve and ten adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
-
-## Apparatus & stimuli
-
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
-The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \@ref(fig:pupildata)b for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
-The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
-Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
-
-All stimuli had a mean luminance of 42 cd/m$^2$ on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
-Ltd., Japan).
-For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
-For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
-
-EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-## Procedure
-
-Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
-This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
-
-### Experiment 1: simultaneous EEG and pupillometry
-
-The experiment was conducted in a windowless room, in which the only light source was the monitor.
-The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
-In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
-
-We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
-Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
-In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
-In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
-We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
-The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
-The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
-the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
-We counterbalanced presentation of the target stimulus across the left and right eyes.
-
-### Experiment 2: EEG responses across temporal frequency
-
-This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
-Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
-Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
-The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
-In each block, there were 20 trials in total with the same timing as for Experiment 1.
-
-### Experiment 3: temporal contrast matching
-
-The experiment was conducted in a darkened room with a blacked-out window.
-The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
-A two-interval contrast matching procedure was used to collect data.
-In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
-In the other interval, a target disc flickering at varying contrast levels was displayed.
-The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
-The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
-The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
-The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
-
-Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
-The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
-In each block, there were a total of 50 trials.
-No auditory feedback was given for this subjective task.
-
-## Data analysis
-
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
-The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
-The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
-All repetitions of each condition were then averaged for each electrode.
-They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
-Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.
-coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
-For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021.
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.
-
-A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-Finally, data were averaged across all participants to obtain the group results.
-Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis [e.g.
-@Spitschan2014].
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
-@Figueira2022].
-
-To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
-We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
-Thresholds were averaged across participants in logarithmic (dB) units.
-
-For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
-
-## Computational model and parameter estimation
-
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by @Meese2006.
-The second gain control stage was omitted [consistent with @Baker2017] to simplify the model and reduce the number of free parameters.
-The response of the left eye's channel is given by:
-
-\begin{equation}
-\label{eq:respL}
-Resp_L = \frac{L^2}{Z + L + wR},
-\end{equation}
-
-with an equivalent expression for the right eye:
-
-\begin{equation}
-\label{eq:respR}
-Resp_R = \frac{R^2}{Z + R + wL}.
-\end{equation}
-
-In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respB}
-Resp_B = R_{max}(Resp_L + Resp_R) + n,
-\end{equation}
-
-where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
-The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
-
-Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
-@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
-Our key parameter of interest is the weight of interocular suppression.
-Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
-Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
-
-We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
-This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
-We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
-The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \@ref(fig:modelfigure).
-We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
-
-## Preregistration, data and code availability
-
-We initially preregistered our main hypotheses and analysis intentions for the first experiment.
-We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
-We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://osf.io/tbema/.
-
 # Results
@@
 
-The pupillometry results are summarised in Figure \@ref(fig:pupildata).
-The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildata)a.
+The pupillometry results are summarised in Fig.
+\@ref(fig:pupildata).
+The group average waveform for binocular presentation is shown in Fig.
+\@ref(fig:pupildata)a.
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Fig.
+\@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 
-Figure \@ref(fig:pupildata)c shows contrast response functions in response to stimuli flickering only at 2Hz.
+Fig.
+\@ref(fig:pupildata)c shows contrast response functions in response to stimuli flickering only at 2Hz.
 Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
@@
 
-In Figure \@ref(fig:pupildata)d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildata)c for comparison).
+In Fig.
+\@ref(fig:pupildata)d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Fig.
+\@ref(fig:pupildata)c for comparison).
 When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(`r monbinPstatsX$dfAB`,`r monbinPstatsX$dfR`) = `r round(monbinPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
@@
 
-Figure \@ref(fig:pupildata)e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Fig.
+\@ref(fig:pupildata)e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
 Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
@@
 
-Figure \@ref(fig:EEGdata) shows equivalent results, measured contemporaneously using EEG.
-Figure \@ref(fig:EEGdata)a shows the group average waveform for binocular presentation, and Figure \@ref(fig:EEGdata)b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (_Oz_, _POz_, _O1_ and _O2_, marked on the inset scalp plots).
+Fig.
+\@ref(fig:EEGdata) shows equivalent results, measured contemporaneously using EEG.
+Fig.
+\@ref(fig:EEGdata)a shows the group average waveform for binocular presentation, and Fig.
+\@ref(fig:EEGdata)b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (_Oz_, _POz_, _O1_ and _O2_, marked on the inset scalp plots).
 Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
@@
 
-When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \@ref(fig:EEGdata)c) and second (Figure \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Fig.
+\@ref(fig:EEGdata)c) and second (Fig.
+\@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
 Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
-For the cross-frequency conditions (Figure \@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
-Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \@ref(fig:EEGdata)e) and 3.2Hz (Figure \@ref(fig:EEGdata)h).
+For the cross-frequency conditions (Fig.
+\@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Fig.
+\@ref(fig:EEGdata)e) and 3.2Hz (Fig.
+\@ref(fig:EEGdata)h).
 This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
@@
 Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
-Figure \@ref(fig:BSratios) shows that these ratios are approximately $\sqrt2$ across the low-to-intermediate contrast range for all three data types.
+Fig.
+\@ref(fig:BSratios) shows that these ratios are approximately $\sqrt2$ across the low-to-intermediate contrast range for all three data types.
 At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
-Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \@ref(fig:pupildata) and \@ref(fig:EEGdata).
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Fig.
+\@ref(fig:pupildata) and \@ref(fig:EEGdata).
 A $3 \times 5$ repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(`r round(ratioaov$ANOVA$DFn[2]*gg[2],digits=2)`,`r round(ratioaov$ANOVA$DFd[2]*gg[2],digits=2)`) = `r round(ratioaov$ANOVA$F[2],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[2],digits=3)`), no effect of data modality (F(`r ratioaov$ANOVA$DFn[1]`,`r ratioaov$ANOVA$DFd[1]`) = `r round(ratioaov$ANOVA$F[1],digits=2)`, \emph{p} = `r round(ratioaov$ANOVA$p[1],digits=2)`), but a highly significant interaction (F(`r round(ratioaov$ANOVA$DFn[3]*gg[3],digits=2)`,`r round(ratioaov$ANOVA$DFd[3]*gg[3],digits=2)`) = `r round(ratioaov$ANOVA$F[3],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[3],digits=4)`).
@@
 
-Results from the temporal frequency experiment are shown in Figure \@ref(fig:TFdata).
-Figure \@ref(fig:TFdata)a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+Results from the temporal frequency experiment are shown in Fig.
+\@ref(fig:TFdata).
+Fig.
+\@ref(fig:TFdata)a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
 From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
 However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
-Figure \@ref(fig:TFdata)b compares the monocular and binocular responses at each stimulation frequency.
+Fig.
+\@ref(fig:TFdata)b compares the monocular and binocular responses at each stimulation frequency.
 Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
@@
 
-The results from the matching experiment are shown in Figure \@ref(fig:matchingdata).
+The results from the matching experiment are shown in Fig.
+\@ref(fig:matchingdata).
 Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
@@
 The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
-Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \@ref(fig:EEGdata)c,f).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Fig.
+\@ref(fig:EEGdata)c,f).
 
@@
 We fitted a computational model to the data from Experiments 1 & 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \@ref(fig:modelfigure)e-h, with empirical data replotted in Figure \@ref(fig:modelfigure)a-d for comparison.
+The model behaviour is displayed in Fig.
+\@ref(fig:modelfigure)e-h, with empirical data replotted in Fig.
+\@ref(fig:modelfigure)a-d for comparison.
 In general, the model captures the key characteristics of the empirical data.
@@
 We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \@ref(fig:modelfigure)i).
+We therefore plot the posterior distributions for this parameter for all four data sets (see Fig.
+\@ref(fig:modelfigure)i).
 The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
@@
 Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.
-Figures \@ref(fig:BSratios) & \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
-However our matching data (Figure \@ref(fig:matchingdata)), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+Fig.
+\@ref(fig:BSratios) & \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
+However our matching data (Fig.
+\@ref(fig:matchingdata)), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
 
@@
 
-# Acknowledgements
-
-Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+# Methods
+
+## Participants
+
+Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected to normal binocular vision, and gave written informed consent in accordance to the Declaration of Helsinki.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
+
+## Apparatus & stimuli
+
+The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The same stimuli were used for all three experiments.
+Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Fig.
+\@ref(fig:pupildata)b for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
+
+All stimuli had a mean luminance of 42 cd/m$^2$ on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
+Ltd., Japan).
+For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
+For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+
+EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+## Procedure
+
+Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
+This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
+
+### Experiment 1: simultaneous EEG and pupillometry
+
+The experiment was conducted in a windowless room, in which the only light source was the monitor.
+The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
+The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+
+We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
+In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
+We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
+The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
+The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
+the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
+We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+### Experiment 2: EEG responses across temporal frequency
+
+This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
+Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
+The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
+In each block, there were 20 trials in total with the same timing as for Experiment 1.
+
+### Experiment 3: temporal contrast matching
+
+The experiment was conducted in a darkened room with a blacked-out window.
+The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
+A two-interval contrast matching procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
+In the other interval, a target disc flickering at varying contrast levels was displayed.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
+The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
+
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
+The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
+In each block, there were a total of 50 trials.
+No auditory feedback was given for this subjective task.
+
+## Data analysis
+
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each electrode.
+They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
+Finally, these were averaged across participants to obtain the group results.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.
+coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
+For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.
+
+A similar analysis pipeline was adopted for the pupillometry data.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis [e.g.
+@Spitschan2014].
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
+@Figueira2022].
+
+To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
+We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
+Thresholds were averaged across participants in logarithmic (dB) units.
+
+For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
+
+## Computational model and parameter estimation
+
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by @Meese2006.
+The second gain control stage was omitted [consistent with @Baker2017] to simplify the model and reduce the number of free parameters.
+The response of the left eye's channel is given by:
+
+\begin{equation}
+\label{eq:respL}
+Resp_L = \frac{L^2}{Z + L + wR},
+\end{equation}
+
+with an equivalent expression for the right eye:
+
+\begin{equation}
+\label{eq:respR}
+Resp_R = \frac{R^2}{Z + R + wL}.
+\end{equation}
+
+In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+Resp_B = R_{max}(Resp_L + Resp_R) + n,
+\end{equation}
+
+where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
+The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
+
+Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
+@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
+Our key parameter of interest is the weight of interocular suppression.
+Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
+Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
+
+We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+The models were fit using the individual data across all participants, independently for each data set.
+Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
+\@ref(fig:modelfigure).
+We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+
+## Preregistration
+
+We initially preregistered our main hypotheses and analysis intentions for the first experiment.
+We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then ran the main experiment, followed by two additional experiments that were not preregistered.
+The preregistration document is available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+
+# Data availability
+
+Raw data files are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+
+# Code availability
+
+Experimental and analysis codes are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+
+# Funding
+
+Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+
+# Author information
+
+## Authors and Affiliations
+
+**Department of Psychology, University of York, York, UK**
+
+Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker
+
+## Contributions
+
+**F.G.S.**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
+**A.B.**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
+**M.A.**: Software, resources, writing - review & editing.
+**A.R.W.**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
+**D.H.B.**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
+
+## Corresponding Author
+
+Correspondance to Federico G. Segala.
+
+# Ethics declarations
+
+## Competing interests
+
+The authors declare no competing interests.
 

### 2023-01-20 manuscriptNature.tex
Created rmd file specific for Nature and added Nature referencing style.

--- 2023-01-12 manuscript.tex
@@
 The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
-This involves a process of signal combination both within (Baker and Wade, 2017) and between (Ernst and Banks, 2002) the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, 1962).
-Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
-However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, 2008) and much less is known about the computations that operate in these subcortical pathways.
+This involves a process of signal combination both within\textsuperscript{1} and between\textsuperscript{2} the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established.\textsuperscript{3} Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN).\textsuperscript{4} However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels\textsuperscript{5} and much less is known about the computations that operate in these subcortical pathways.
 In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
@@
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., 2018; Campbell and Green, 1965).
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance' (Baker et al., 2007): perceived contrast does not change when one eye is opened and closed.
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2.\textsuperscript{6,7} This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds)\textsuperscript{8,9} and neural activity\textsuperscript{1,10} are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision\textsuperscript{9,11} advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance':\textsuperscript{12} perceived contrast does not change when one eye is opened and closed.
 
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, 2008).
-There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (1981)).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2008; Wang and Munoz, 2015).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the computation that achieves this is achieved is unclear.
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink.\textsuperscript{5} There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; 13).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus.\textsuperscript{5,14--16} To account for the consensual response, these brain regions must combine information from the left and right eyes,\textsuperscript{17} yet the computation that achieves this is achieved is unclear.
 
@@
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Periodic flicker entrains both neural\textsuperscript{18} and pupil\textsuperscript{19} responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
 The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways implement stronger interocular suppression than the canonical cortical pathway.
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
+
+The pupillometry results are summarised in Fig.
+\ref{fig:pupildata}.
+The group average waveform for binocular presentation is shown in Fig.
+\ref{fig:pupildata}a.
+There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
+The average Fourier spectrum is displayed in Fig.
+\ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/pupildata}
+
+}
+
+\caption{Summary of pupillometry results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
+\end{figure}
+
+Fig.
+\ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
+The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\)\textsuperscript{20} comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
+
+In Fig.
+\ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Fig.
+\ref{fig:pupildata}c for comparison).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
+When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless{} 0.001).
+
+Fig.
+\ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
+The dichoptic cross condition does not show clear modulation with target contrast.
+
+Fig.
+\ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
+Fig.
+\ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Fig.
+\ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
+Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
+We therefore calculated contrast response functions at both first and second harmonic frequencies.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/EEGdata}
+
+}
+
+\caption{Summary of EEG results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
+Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Panels (f-h) are in the same format but for the second harmonic responses.
+Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
+\end{figure}
+
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Fig.
+\ref{fig:EEGdata}c) and second (Fig.
+\ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
+For the cross-frequency conditions (Fig.
+\ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Fig.
+\ref{fig:EEGdata}e) and 3.2Hz (Fig.
+\ref{fig:EEGdata}h).
+This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
+
+Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
+Fig.
+\ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
+At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Fig.
+\ref{fig:pupildata} and \ref{fig:EEGdata}.
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/BSratios}
+
+}
+
+\caption{Ratio of binocular to monocular response for three data types.
+Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
+\end{figure}
+
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
+
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli.\textsuperscript{1} One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
+We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz;\textsuperscript{19} note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+
+Results from the temporal frequency experiment are shown in Fig.
+\ref{fig:TFdata}.
+Fig.
+\ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
+However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
+Fig.
+\ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
+Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
+\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/TFdata}
+
+}
+
+\caption{Binocular facilitation at different temporal frequencies.
+Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
+Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
+Panel (c) shows the ratio of binocular to monocular responses.
+Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
+\end{figure}
+
+\hypertarget{experiment-3}{%
+\subsection{Experiment 3}\label{experiment-3}}
+
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms.\textsuperscript{21--23} We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
+One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
+The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
+We tested 9 ratios of contrast between the left and right eyes.
+
+The results from the matching experiment are shown in Fig.
+\ref{fig:matchingdata}.
+Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
+For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
+The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Fig.
+\ref{fig:EEGdata}c,f).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
+
+}
+
+\caption{Contrast matching functions.
+Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
+This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
+\end{figure}
+
+\hypertarget{computational-modelling}{%
+\subsection{Computational modelling}\label{computational-modelling}}
+
+We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
+The model behaviour is displayed in Fig.
+\ref{fig:modelfigure}e-h, with empirical data replotted in Fig.
+\ref{fig:modelfigure}a-d for comparison.
+In general, the model captures the key characteristics of the empirical data.
+Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
+In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \ref{tab:paramtable}).
+This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
+This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
+
+We were particularly interested in comparing the weight of interocular suppression across data sets.
+We therefore plot the posterior distributions for this parameter for all four data sets (see Fig.
+\ref{fig:modelfigure}i).
+The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
+There is no overlap between the pupillometry distribution and any of the other three.
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict,\textsuperscript{1,9} and the peak location of our prior distribution (black curve).
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/modelfigure}
+
+}
+
+\caption{Summary of computational modelling.
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
+Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
+Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
+The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:paramtable}Summary of median parameter values.}
+\centering
+\begin{tabular}[t]{l|c|c|c|c}
+\hline
+Data set & Z & k & w & Rmax\\
+\hline
+Pupillometry & 2.37 & 0.01 & 0.67 & 0.00023\\
+\hline
+EEG 1F & 2.59 & 0.15 & 0.02 & 0.0026\\
+\hline
+EEG 2F & 2.21 & 0.06 & 0.01 & 0.00404\\
+\hline
+Matching & 0.30 & 5.07 & 0.09 & -\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
+In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
+This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
+
+The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts.\textsuperscript{1,9,10} Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
+However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
+For example, 23 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and 24 report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm.\textsuperscript{25} Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments,\textsuperscript{21,22,26} though not for luminance decrements.\textsuperscript{21} Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+
+Given the above, where does this leave our understanding of the overarching purpose of signal combination?
+1 point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs.\textsuperscript{2} This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction.\textsuperscript{27,28} One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
+Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
+
+Pupil size determines the total amount of light falling on the retina.
+It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
+We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter.\textsuperscript{19} It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms.\textsuperscript{29} We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs'\textsuperscript{30,31} are biased towards low spatial frequencies,\textsuperscript{32,33} and relatively insensitive to stimulus orientation.\textsuperscript{30,31,34} As the blob regions are embedded within ocular dominance columns,\textsuperscript{30} they are also largely monocular.\textsuperscript{31,35} More recent work has reported psychophysical evidence for unoriented chromatic\textsuperscript{36} and achromatic\textsuperscript{37} mechanisms, that also appear to be monocular.
+Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Fig.
+\ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
+However our matching data (Fig.
+\ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
+Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
+We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
 
@@
 Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+All participants had normal or corrected to normal binocular vision, and gave written informed consent in accordance to the Declaration of Helsinki.
 Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \ref{fig:pupildata}b for an example of the fused stimulus).
+Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Fig.
+\ref{fig:pupildata}b for an example of the fused stimulus).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
@@
 EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; Kassner et al.
-(2014)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; 38) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
-The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox.\textsuperscript{39} The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
 The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (2021).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (1991) that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean.\textsuperscript{20} For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by 20.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of 40 that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., 2014), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software,\textsuperscript{38} which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.~Spitschan et al., 2014).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., 2022).
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis.\textsuperscript{19} The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies.\textsuperscript{41,42} Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis.\textsuperscript{43}
 
@@
 
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
-(2006).
-The second gain control stage was omitted (consistent with Baker and Wade, 2017) to simplify the model and reduce the number of free parameters.
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by 9.
+The second gain control stage was omitted\textsuperscript{1} to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 
-Despite being derived from the model proposed by Meese et al.
-(2006), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
-Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, 2017).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., 2020).
+Despite being derived from the model proposed by 9, the simplifications applied to this architecture make it very similar to other models.\textsuperscript{8,11,17,44} In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression.\textsuperscript{26,45} Our key parameter of interest is the weight of interocular suppression.
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli.\textsuperscript{1} Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation.\textsuperscript{25}
 
-We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., 2017).
-This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., 2012; Meese et al., 2006).
-We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+We implemented the model within a Bayesian framework using the Stan software.\textsuperscript{46} This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature.\textsuperscript{9,26} We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
 The models were fit using the individual data across all participants, independently for each data set.
 Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \ref{fig:modelfigure}.
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
+\ref{fig:modelfigure}.
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
 
-\hypertarget{preregistration-data-and-code-availability}{%
-\subsection{Preregistration, data and code availability}\label{preregistration-data-and-code-availability}}
+\hypertarget{preregistration}{%
+\subsection{Preregistration}\label{preregistration}}
 
@@
 We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
+The preregistration document is available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{data-availability}{%
+\section{Data availability}\label{data-availability}}
 
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
+Raw data files are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
-The pupillometry results are summarised in Figure \ref{fig:pupildata}.
-The group average waveform for binocular presentation is shown in Figure \ref{fig:pupildata}a.
-There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
-These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
+\hypertarget{code-availability}{%
+\section{Code availability}\label{code-availability}}
 
-\begin{figure}
+Experimental and analysis codes are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
-{\centering \includegraphics{Figures/pupildata}
+\hypertarget{funding}{%
+\section{Funding}\label{funding}}
 
-}
+Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
 
-\caption{Summary of pupillometry results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
-Panels (c,d) show contrast response functions at 2Hz for different conditions.
-Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
-\end{figure}
+\hypertarget{author-information}{%
+\section{Author information}\label{author-information}}
 
-Figure \ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
-Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
-The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, 2021) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
-The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
+\hypertarget{authors-and-affiliations}{%
+\subsection{Authors and Affiliations}\label{authors-and-affiliations}}
 
-In Figure \ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \ref{fig:pupildata}c for comparison).
-When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
-When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless{} 0.001).
+\textbf{Department of Psychology, University of York, York, UK}
 
-Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
-The dichoptic cross condition does not show clear modulation with target contrast.
+Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker
 
-Figure \ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
-Figure \ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Figure \ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
-Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
-We therefore calculated contrast response functions at both first and second harmonic frequencies.
+\hypertarget{contributions}{%
+\subsection{Contributions}\label{contributions}}
 
-\begin{figure}
+\textbf{F.G.S.}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
+\textbf{A.B.}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{M.A.}: Software, resources, writing - review \& editing.
+\textbf{A.R.W.}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{D.H.B.}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
 
-{\centering \includegraphics{Figures/EEGdata}
+\hypertarget{corresponding-author}{%
+\subsection{Corresponding Author}\label{corresponding-author}}
 
-}
+Correspondance to Federico G. Segala.
 
-\caption{Summary of EEG results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
-Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
-Panels (c,d) show contrast response functions at 2Hz for different conditions.
-Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Panels (f-h) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
-\end{figure}
+\hypertarget{ethics-declarations}{%
+\section{Ethics declarations}\label{ethics-declarations}}
 
-When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
-For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
-Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \ref{fig:EEGdata}e) and 3.2Hz (Figure \ref{fig:EEGdata}h).
-This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
-
-Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
-Figure \ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
-At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
-Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
-A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/BSratios}
-
-}
-
-\caption{Ratio of binocular to monocular response for three data types.
-Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
-\end{figure}
-
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
-
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, 2017).
-One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
-We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
-
-Results from the temporal frequency experiment are shown in Figure \ref{fig:TFdata}.
-Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
-From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
-However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
-Figure \ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
-Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
-\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/TFdata}
-
-}
-
-\caption{Binocular facilitation at different temporal frequencies.
-Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
-Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
-Panel (c) shows the ratio of binocular to monocular responses.
-Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
-\end{figure}
-
-\hypertarget{experiment-3}{%
-\subsection{Experiment 3}\label{experiment-3}}
-
-In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
-We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
-One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
-The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
-We tested 9 ratios of contrast between the left and right eyes.
-
-The results from the matching experiment are shown in Figure \ref{fig:matchingdata}.
-Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
-At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
-For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
-The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
-Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \ref{fig:EEGdata}c,f).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
-
-}
-
-\caption{Contrast matching functions.
-Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
-This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
-\end{figure}
-
-\hypertarget{computational-modelling}{%
-\subsection{Computational modelling}\label{computational-modelling}}
-
-We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \ref{fig:modelfigure}e-h, with empirical data replotted in Figure \ref{fig:modelfigure}a-d for comparison.
-In general, the model captures the key characteristics of the empirical data.
-Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
-In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \ref{tab:paramtable}).
-This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
-This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
-
-We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}i).
-The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
-There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006), and the peak location of our prior distribution (black curve).
-These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
-The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/modelfigure}
-
-}
-
-\caption{Summary of computational modelling.
-Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
-Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
-Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
-The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
-The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
-\end{figure}
-
-\begin{table}
-
-\caption{\label{tab:paramtable}Summary of median parameter values.}
-\centering
-\begin{tabular}[t]{l|c|c|c|c}
-\hline
-Data set & Z & k & w & Rmax\\
-\hline
-Pupillometry & 2.37 & 0.01 & 0.67 & 0.00023\\
-\hline
-EEG 1F & 2.59 & 0.15 & 0.02 & 0.0026\\
-\hline
-EEG 2F & 2.21 & 0.06 & 0.01 & 0.00404\\
-\hline
-Matching & 0.30 & 5.07 & 0.09 & -\\
-\hline
-\end{tabular}
-\end{table}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
-In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
-In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
-This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
-Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
-
-The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
-Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
-However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, Quaia et al.
-(2018) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (2019) report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., 2020).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, 1998; Baker et al., 2012; Levelt, 1965), though not for luminance decrements (Anstis and Ho, 1998).
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
-
-Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-Baker and Wade (2017) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, 2002).
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, 1994; May and Zhaoping, 2022).
-One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
-Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
-Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
-
-Pupil size determines the total amount of light falling on the retina.
-It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
-We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.~Spitschan et al., 2014).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.~Bradley et al., 2008).
-We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
-
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, 1981; Livingstone and Hubel, 1984) are biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988), and relatively insensitive to stimulus orientation (Horton and Hubel, 1981; Livingstone and Hubel, 1984; though see Economides et al., 2011).
-As the blob regions are embedded within ocular dominance columns (Horton and Hubel, 1981), they are also largely monocular (Livingstone and Hubel, 1984; Tychsen et al., 2004).
-More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., 2013) and achromatic (Meese and Baker, 2011) mechanisms, that also appear to be monocular.
-Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
-Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
-However our matching data (Figure \ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
-Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
-Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
-We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
-
-\hypertarget{author-contributions}{%
-\section{Author contributions}\label{author-contributions}}
-
-\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
-\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Myat Aung}: Software, resources, writing - review \& editing.
-\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
-
-\hypertarget{declaration-of-interests}{%
-\section{Declaration of interests}\label{declaration-of-interests}}
+\hypertarget{competing-interests}{%
+\subsection{Competing interests}\label{competing-interests}}
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Baker2017}{}%
+1. Baker, D. H. \& Wade, A. R. Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
+
+\leavevmode\hypertarget{ref-Ernst2002}{}%
+2. Ernst, M. O. \& Banks, M. S. Humans integrate visual and haptic information in a statistically optimal fashion. \emph{Nature} \textbf{415}, 429--33 (2002).
+
+\leavevmode\hypertarget{ref-Hubel1962}{}%
+3. Hubel, D. H. \& Wiesel, T. N. Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
+
+\leavevmode\hypertarget{ref-Purves2008}{}%
+4. Purves, D. \emph{et al.} \emph{Principles of Cognitive Neuroscience}. (Oxford University Press, 2008).
+
+\leavevmode\hypertarget{ref-McDougal2008}{}%
+5. McDougal, D. H. \& Gamlin, P. D. Pupillary control pathways. in \emph{The senses: A comprehensive reference} 521--536 (Elsevier, 2008).
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+6. Campbell, F. W. \& Green, D. G. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
+
+\leavevmode\hypertarget{ref-Baker2018}{}%
+7. Baker, D. H., Lygo, F. A., Meese, T. S. \& Georgeson, M. A. Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
+
+\leavevmode\hypertarget{ref-Legge1984}{}%
+8. Legge, G. E. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
+
+\leavevmode\hypertarget{ref-Meese2006}{}%
+9. Meese, T. S., Georgeson, M. A. \& Baker, D. H. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}, 1224--43 (2006).
+
+\leavevmode\hypertarget{ref-Moradi2009}{}%
+10. Moradi, F. \& Heeger, D. J. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}, 13 (2009).
+
+\leavevmode\hypertarget{ref-Ding2006}{}%
+11. Ding, J. \& Sperling, G. A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
+
+\leavevmode\hypertarget{ref-Baker2007}{}%
+12. Baker, D. H., Meese, T. S. \& Georgeson, M. A. Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
+
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
+13.
+Wyatt, H.
+J.
+\& Musselman, J.
+F.
+Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res} \textbf{21}, 513--25 (1981).
+
 \leavevmode\hypertarget{ref-Angee2021}{}%
-Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
-2021.
-Congenital microcoria: Clinical features and molecular genetics.
-\emph{Genes (Basel)} \textbf{12}.
-doi:\href{https://doi.org/10.3390/genes12050624}{10.3390/genes12050624}
+14. Angée, C., Nedelec, B., Erjavec, E., Rozet, J.-M. \& Fares Taie, L. Congenital microcoria: Clinical features and molecular genetics. \emph{Genes (Basel)} \textbf{12}, (2021).
+
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+15. Mathôt, S. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
+
+\leavevmode\hypertarget{ref-Wang2015}{}%
+16. Wang, C.-A. \& Munoz, D. P. A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+
+\leavevmode\hypertarget{ref-Doesschate1967}{}%
+17. Doesschate, J. ten \& Alpern, M. Effect of photoexcitation of the two retinas on pupil size. \emph{J Neurophysiol} \textbf{30}, 562--76 (1967).
+
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+18. Norcia, A. M., Appelbaum, L. G., Ales, J. M., Cottereau, B. R. \& Rossion, B. The steady-state visual evoked potential in vision research: A review. \emph{J Vis} \textbf{15(6)}, 4 (2015).
+
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
+19.
+Spitschan, M., Jain, S., Brainard, D.
+H.
+\& Aguirre, G.
+K.
+Opponent melanopsin and s-cone signals in the human pupillary light response.
+\emph{Proc Natl Acad Sci U S A} \textbf{111}, 15568--72 (2014).
+
+\leavevmode\hypertarget{ref-Baker2021}{}%
+20. Baker, D. H. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}, (2021).
 
 \leavevmode\hypertarget{ref-Anstis1998}{}%
-Anstis S, Ho A.
-1998.
-Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
-\emph{Vision Res} \textbf{38}:523--39.
-doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
+21. Anstis, S. \& Ho, A. Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}, 523--39 (1998).
 
-\leavevmode\hypertarget{ref-Baker2021}{}%
-Baker DH.
-2021.
-Statistical analysis of periodic data in neuroscience.
-\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
-doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+\leavevmode\hypertarget{ref-Levelt1965}{}%
+22. Levelt, W. J. Binocular brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).
 
-\leavevmode\hypertarget{ref-Baker2018}{}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA.
-2018.
-Binocular summation revisited: Beyond \(\sqrt{2}\).
-\emph{Psychol Bull} \textbf{144}:1186--1199.
-doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
+\leavevmode\hypertarget{ref-Quaia2018}{}%
+23. Quaia, C., Optican, L. M. \& Cumming, B. G. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}, 7 (2018).
 
-\leavevmode\hypertarget{ref-Baker2007}{}%
-Baker DH, Meese TS, Georgeson MA.
-2007.
-Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
-\emph{Spat Vis} \textbf{20}:397--413.
-doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+24. Spitschan, M. \& Cajochen, C. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
 
 \leavevmode\hypertarget{ref-Baker2020}{}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
-2020.
-Binaural summation of amplitude modulation involves weak interaural suppression.
-\emph{Sci Rep} \textbf{10}:3560.
-doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
-
-\leavevmode\hypertarget{ref-Baker2017}{}%
-Baker DH, Wade AR.
-2017.
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-\emph{Cereb Cortex} \textbf{27}:254--264.
-doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
+25. Baker, D. H. \emph{et al.} Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
 
 \leavevmode\hypertarget{ref-Baker2012}{}%
-Baker DH, Wallis SA, Georgeson MA, Meese TS.
-2012.
-Nonlinearities in the binocular combination of luminance and contrast.
-\emph{Vision Res} \textbf{56}:1--9.
-doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
+26. Baker, D. H., Wallis, S. A., Georgeson, M. A. \& Meese, T. S. Nonlinearities in the binocular combination of luminance and contrast. \emph{Vision Res} \textbf{56}, 1--9 (2012).
 
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-Barrionuevo PA, Cao D.
-2016.
-Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
-\emph{J Vis} \textbf{16(11)}:29.
-doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
+\leavevmode\hypertarget{ref-Li1994}{}%
+27. Li, Z. \& Atick, J. J. Efficient stereo coding in the multiscale representation. \emph{Network: Computation in Neural Systems} \textbf{5}, 157--174 (1994).
 
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
-2014.
-Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
-\emph{Invest Ophthalmol Vis Sci} \textbf{55}:719--27.
-doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}
+\leavevmode\hypertarget{ref-May2022}{}%
+28. May, K. \& Zhaoping, L. Li and Atick's theory of efficient binocular coding: A tutorial and mini-review. \emph{Vision Res} \textbf{201}, 107950 (2022).
 
 \leavevmode\hypertarget{ref-Bradley2008}{}%
-Bradley MM, Miccoli L, Escrig MA, Lang PJ.
-2008.
-The pupil as a measure of emotional arousal and autonomic activation.
-\emph{Psychophysiology} \textbf{45}:602--7.
-doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
-
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
-
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A.
-2017.
-Stan: A probabilistic programming language.
-\emph{Journal of Statistical Software} \textbf{76}:1--32.
-doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
-
-\leavevmode\hypertarget{ref-Delorme2004}{}%
-Delorme A, Makeig S.
-2004.
-EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
-\emph{J Neurosci Methods} \textbf{134}:9--21.
-doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}
-
-\leavevmode\hypertarget{ref-Ding2006}{}%
-Ding J, Sperling G.
-2006.
-A gain-control theory of binocular combination.
-\emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6.
-doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}
-
-\leavevmode\hypertarget{ref-Doesschate1967}{}%
-Doesschate J ten, Alpern M.
-1967.
-Effect of photoexcitation of the two retinas on pupil size.
-\emph{J Neurophysiol} \textbf{30}:562--76.
-doi:\href{https://doi.org/10.1152/jn.1967.30.3.562}{10.1152/jn.1967.30.3.562}
-
-\leavevmode\hypertarget{ref-Economides2011}{}%
-Economides JR, Sincich LC, Adams DL, Horton JC.
-2011.
-Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
-\emph{Nat Neurosci} \textbf{14}:1574--80.
-doi:\href{https://doi.org/10.1038/nn.2958}{10.1038/nn.2958}
-
-\leavevmode\hypertarget{ref-Edwards1995}{}%
-Edwards DP, Purpura KP, Kaplan E.
-1995.
-Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
-\emph{Vision Res} \textbf{35}:1501--23.
-doi:\href{https://doi.org/10.1016/0042-6989(94)00253-i}{10.1016/0042-6989(94)00253-i}
-
-\leavevmode\hypertarget{ref-Ernst2002}{}%
-Ernst MO, Banks MS.
-2002.
-Humans integrate visual and haptic information in a statistically optimal fashion.
-\emph{Nature} \textbf{415}:429--33.
-doi:\href{https://doi.org/10.1038/415429a}{10.1038/415429a}
-
-\leavevmode\hypertarget{ref-Figueira2022}{}%
-Figueira JSB, Kutlu E, Scott LS, Keil A.
-2022.
-The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
-\emph{Dev Cogn Neurosci} \textbf{54}:101066.
-doi:\href{https://doi.org/10.1016/j.dcn.2022.101066}{10.1016/j.dcn.2022.101066}
-
-\leavevmode\hypertarget{ref-Gheiratmand2013}{}%
-Gheiratmand M, Meese TS, Mullen KT.
-2013.
-Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
-\emph{Journal of Vision} \textbf{13(1)}:2.
-doi:\href{https://doi.org/10.1167/13.1.2}{10.1167/13.1.2}
+29. Bradley, M. M., Miccoli, L., Escrig, M. A. \& Lang, P. J. The pupil as a measure of emotional arousal and autonomic activation. \emph{Psychophysiology} \textbf{45}, 602--7 (2008).
 
 \leavevmode\hypertarget{ref-Horton1981}{}%
-Horton JC, Hubel DH.
-1981.
-Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
-\emph{Nature} \textbf{292}:762--4.
-doi:\href{https://doi.org/10.1038/292762a0}{10.1038/292762a0}
-
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-Hubel DH, Wiesel TN.
-1962.
-Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
-\emph{J Physiol} \textbf{160}:106--54.
-doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-Kassner M, Patera W, Bulling A.
-2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-UbiComp '14 Adjunct; ACM.
-pp.
-1151--1160.
-doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-Kingdom FAA, Libenson L.
-2015.
-Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
-\emph{J Vis} \textbf{15(5)}:2.
-doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
-
-\leavevmode\hypertarget{ref-Legge1984}{}%
-Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
-
-\leavevmode\hypertarget{ref-Levelt1965}{}%
-Levelt WJ.
-1965.
-Binocular brightness averaging and contour information.
-\emph{Br J Psychol} \textbf{56}:1--13.
-doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}
-
-\leavevmode\hypertarget{ref-Li1994}{}%
-Li Z, Atick JJ.
-1994.
-Efficient stereo coding in the multiscale representation.
-\emph{Network: Computation in Neural Systems} \textbf{5}:157--174.
-doi:\href{https://doi.org/10.1088/0954-898X_5_2_003}{10.1088/0954-898X\_5\_2\_003}
+30. Horton, J. C. \& Hubel, D. H. Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey. \emph{Nature} \textbf{292}, 762--4 (1981).
 
 \leavevmode\hypertarget{ref-Livingstone1984}{}%
-Livingstone MS, Hubel DH.
-1984.
-Anatomy and physiology of a color system in the primate visual cortex.
-\emph{J Neurosci} \textbf{4}:309--56.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{10.1523/JNEUROSCI.04-01-00309.1984}
-
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
-
-\leavevmode\hypertarget{ref-May2022}{}%
-May K, Zhaoping L.
-2022.
-Li and Atick's theory of efficient binocular coding: A tutorial and mini-review.
-\emph{Vision Res} \textbf{201}:107950.
-doi:\href{https://doi.org/10.1016/j.visres.2021.08.005}{10.1016/j.visres.2021.08.005}
-
-\leavevmode\hypertarget{ref-McDougal2008}{}%
-McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
-
-\leavevmode\hypertarget{ref-Meese2011}{}%
-Meese TS, Baker DH.
-2011.
-A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-\emph{iPerception} \textbf{2}:159--82.
-doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
-
-\leavevmode\hypertarget{ref-Meese2006}{}%
-Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
-
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}:13. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
-2015.
-The steady-state visual evoked potential in vision research: A review.
-\emph{J Vis} \textbf{15(6)}:4.
-doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
-
-\leavevmode\hypertarget{ref-Purves2008}{}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press.
-
-\leavevmode\hypertarget{ref-Quaia2018}{}%
-Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
-
-\leavevmode\hypertarget{ref-Schrodinger1926}{}%
-Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
-
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-Spitschan M, Jain S, Brainard DH, Aguirre GK.
-2014.
-Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proc Natl Acad Sci U S A} \textbf{111}:15568--72.
-doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
+31. Livingstone, M. S. \& Hubel, D. H. Anatomy and physiology of a color system in the primate visual cortex. \emph{J Neurosci} \textbf{4}, 309--56 (1984).
 
 \leavevmode\hypertarget{ref-Tootell1988}{}%
-Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
-1988.
+32.
+Tootell, R.
+B., Silverman, M.
+S., Hamilton, S.
+L., Switkes, E.
+\& De Valois, R.
+L.
 Functional anatomy of macaque striate cortex.
@@
 Spatial frequency.
-\emph{J Neurosci} \textbf{8}:1610--24.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{10.1523/JNEUROSCI.08-05-01610.1988}
+\emph{J Neurosci} \textbf{8}, 1610--24 (1988).
+
+\leavevmode\hypertarget{ref-Edwards1995}{}%
+33.
+Edwards, D.
+P., Purpura, K.
+P.
+\& Kaplan, E.
+Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
+\emph{Vision Res} \textbf{35}, 1501--23 (1995).
+
+\leavevmode\hypertarget{ref-Economides2011}{}%
+34.
+Economides, J.
+R., Sincich, L.
+C., Adams, D.
+L.
+\& Horton, J.
+C.
+Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
+\emph{Nat Neurosci} \textbf{14}, 1574--80 (2011).
 
 \leavevmode\hypertarget{ref-Tychsen2004}{}%
-Tychsen L, Wong AM-F, Burkhalter A.
-2004.
+35.
+Tychsen, L., Wong, A.
+M.-F.
+\& Burkhalter, A.
 Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
-\emph{The Journal of Comparative Neurology} \textbf{474}:261--275.
-doi:\href{https://doi.org/10.1002/cne.20113}{10.1002/cne.20113}
+\emph{The Journal of Comparative Neurology} \textbf{474}, 261--275 (2004).
+
+\leavevmode\hypertarget{ref-Gheiratmand2013}{}%
+36.
+Gheiratmand, M., Meese, T.
+S.
+\& Mullen, K.
+T.
+Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
+\emph{Journal of Vision} \textbf{13(1)}, 2 (2013).
+
+\leavevmode\hypertarget{ref-Meese2011}{}%
+37.
+Meese, T.
+S.
+\& Baker, D.
+H.
+A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
+\emph{iPerception} \textbf{2}, 159--82 (2011).
+
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+38.
+Kassner, M., Patera, W.
+\& Bulling, A.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+in \emph{Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication} 1151--1160 (UbiComp '14 Adjunct; ACM, 2014).
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.
+
+\leavevmode\hypertarget{ref-Delorme2004}{}%
+39. Delorme, A. \& Makeig, S. EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).
 
 \leavevmode\hypertarget{ref-Victor1991}{}%
-Victor JD, Mast J.
-1991.
-A new statistic for steady-state evoked potentials.
-\emph{Electroencephalogr Clin Neurophysiol} \textbf{78}:378--88.
-doi:\href{https://doi.org/10.1016/0013-4694(91)90099-p}{10.1016/0013-4694(91)90099-p}
+40. Victor, J. D. \& Mast, J. A new statistic for steady-state evoked potentials. \emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).
 
-\leavevmode\hypertarget{ref-Wang2015}{}%
-Wang C-A, Munoz DP.
-2015.
-A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size.
-\emph{Curr Opin Neurobiol} \textbf{33}:134--40.
-doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
+41. Barrionuevo, P. A. \emph{et al.} Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).
 
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-Wyatt HJ, Musselman JF.
-1981.
-Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}:513--25.
-doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+42. Barrionuevo, P. A. \& Cao, D. Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{J Vis} \textbf{16(11)}, 29 (2016).
+
+\leavevmode\hypertarget{ref-Figueira2022}{}%
+43.
+Figueira, J.
+S.
+B., Kutlu, E., Scott, L.
+S.
+\& Keil, A.
+The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
+\emph{Dev Cogn Neurosci} \textbf{54}, 101066 (2022).
+
+\leavevmode\hypertarget{ref-Schrodinger1926}{}%
+44. Schrödinger, E. Die gesichtsempfindungen. in \emph{Mueller-pouillets lehrbuch der physik (11th ed.)} vol. Book 2 456--560 (Vieweg: Braunschweig, 1926).
+
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+45. Kingdom, F. A. A. \& Libenson, L. Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15(5)}, 2 (2015).
+
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+46. Carpenter, B. \emph{et al.} Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).
 

### 2023-01-22 manuscriptNature.Rmd
Minor edits

@@
 
-How does the brain combine information across the eyes?
-In primary visual cortex, spatial patterns are subject to 'ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
-Here we asked whether this invariance holds for pure changes in luminance.
-We collected steady-state EEG and pupillometry data simultaneously, and find strong deviations from ocularity invariance both in the cortex and also in the subcortical pathway that determines pupil diameter.
-In cortex, we find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas measurements of pupil diameter showed weaker facilitation and stronger suppression.
-This was not purely a consequence of the temporal stimulus parameters; pronounced binocular facilitation was also observed at faster flicker rates.
-Near-linear binocular combination was also found for the same stimuli using a perceptual matching task.
-A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data compared with the pupillometry results.
-These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+How does the human brain combine information across the eyes?
+It has been known for many years that cortical normalisation mechanisms implement ‘ocularity invariance’: equalising neural responses to spatial patterns presented either monocularly or binocularly.
+Here we used a novel combination of electrophysiology, psychophysics, pupillometry and computational modelling to ask whether this invariance also holds for flickering luminance stimuli with no spatial contrast.
+We find dramatic violations of ocularity invariance for these stimuli, both in cortex and also in the subcortical pathways that govern pupil diameter.
+Specifically, we find substantial binocular facilitation in both pathways with the effect being strongest in cortex.
+Near-linear binocular additivity (instead of ocularity invariance) was also found using a perceptual luminance matching task.
+Ocularity invariance is therefore not a ubiquitous feature of visual processing, and the brain appears to repurpose a generic normalisation algorithm for different visual functions by adjusting the amount of interocular suppression.
 
@@
 However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels [@McDougal2008] and much less is known about the computations that operate in these subcortical pathways.
-In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
+Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between $\sqrt{2}$ and 2 [@Campbell1965; @Baker2018].
+This is known as binocular summation[@Campbell1965; @Baker2018], with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between $\sqrt{2}$ and 2.
 This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) [@Legge1984; @Meese2006] and neural activity [@Moradi2009; @Baker2017] are approximately equal for monocular and binocular presentation.
@@
 Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus [@Angee2021; @Mathot2018; @McDougal2008; @Wang2015].
-To account for the consensual response, these brain regions must  combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is achieved is unclear.
+To account for the consensual response, these brain regions must  combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is unclear.
 
@@
 
-The pupillometry results are summarised in Fig.
+The pupillometry results for our first experiment are summarised in Fig.
 \@ref(fig:pupildata).
@@
 Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
-We therefore calculated contrast response functions at both first and second harmonic frequencies.
+We therefore derived contrast response functions at both first and second harmonic frequencies.
 
@@
 \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
+Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic (note that the absence of a main effect of condition is expected, given that there should be negligible differences between conditions at low contrasts, and any differences are therefore captured by the interaction term).
 For the cross-frequency conditions (Fig.
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms [e.g.
-@Anstis1998; @Levelt1965; @Quaia2018].
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms [@Anstis1998; @Levelt1965; @Quaia2018].
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict [@Meese2006; @Baker2017], and the peak location of our prior distribution (black curve).
-These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and significant dichoptic masking observed using that method.
 The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
@@
 Previous studies investigating binocular combination of spatial patterns (i.e.
-sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts [@Baker2017; @Moradi2009; @Meese2006].
+sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts [@Baker2017; @Moradi2009; @Meese2006].
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
 However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, @Quaia2018 observed a strong binocular facilitation (or 'supersummation') in the reflexive eye movement response to rapidly moving stimuli, and @Spitschan2019 report a similar result in archival data on melatonin suppression due to light exposure.
+For example, Quaia et al.@Quaia2018 observed a strong binocular facilitation (or 'supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen@Spitschan2019 report a similar result in archival data on melatonin suppression due to light exposure.
 In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm [@Baker2020].
 Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments [@Levelt1965; @Anstis1998; @Baker2012], though not for luminance decrements [@Anstis1998].
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination.
 
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-@Baker2017 point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs [see also @Ernst2002].
+We previously@Baker2017 pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also [@Ernst2002]).
 This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction [@Li1994; @May2022].
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or are otherwise phylogenetically older than binocular pattern vision.
 Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2% of overall diameter [e.g.
-@Spitschan2014].
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms [e.g.
-@Bradley2008].
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2% of overall diameter [@Spitschan2014].
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms [@Bradley2008].
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.
 monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
-
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase 'blobs' [@Horton1981; @Livingstone1984] are biased towards low spatial frequencies [@Tootell1988; @Edwards1995], and relatively insensitive to stimulus orientation [@Horton1981; @Livingstone1984; though see @Economides2011].
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but intend to investigate this directly in future neuroimaging work.
+
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase 'blobs' [@Horton1981; @Livingstone1984] are biased towards low spatial frequencies [@Tootell1988; @Edwards1995], and relatively insensitive to stimulus orientation [@Horton1981; @Livingstone1984] (though see @Economides2011).
 As the blob regions are embedded within ocular dominance columns [@Horton1981], they are also largely monocular [@Livingstone1984; @Tychsen2004].
@@
 
-Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision, and gave written informed consent in accordance to the Declaration of Helsinki.
+Thirty (20 F, 10 M), twelve (7 F, 5 M) and ten (3 F, 7 M) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected-to-normal binocular vision, and gave written informed consent in accordance with the Declaration of Helsinki.
 Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
@@
 
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The stimuli were two monocularly presented discs of achromatic flickering light with a diameter of 3.74 degrees, displayed against a black background.
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Fig.
+Four dark red lines were added around each monocular disc to help with their fusion into a single binocular disc (see insert in Fig.
 \@ref(fig:pupildata)b for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants perceived a single fused disc.
 The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
@@
 
-All stimuli had a mean luminance of 42 cd/m$^2$ on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
+All stimuli had a mean luminance of 42 cd/m$^2$, and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
 Ltd., Japan).
-For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
-For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
-
-EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+All stimuli were presented using Psychopy [@Peirce2019] (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
+
+EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
-In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
+In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 2Hz, and the other eye's disc flickered at 1.6Hz.
 We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
-The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
+The rationale for flickering both eyes at 2Hz is that we can measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
 The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
@@
 All averaging was performed in the complex domain and therefore retained the phase information (i.e.
-coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
-For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021.
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.
+coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [@Baker2021].
+For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described previously @Baker2021.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic @Victor1991 that can compare more than two conditions.
 
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis [e.g.
-@Spitschan2014].
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
-@Figueira2022].
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis @Spitschan2014.
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [@Barrionuevo2014; @Barrionuevo2016].
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [@Figueira2022].
 
@@
 
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by @Meese2006.
-The second gain control stage was omitted [consistent with @Baker2017] to simplify the model and reduce the number of free parameters.
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
+[@Meese2006].
+The second gain control stage was omitted, consistent with previous work [@Baker2017], to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 
-Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
-@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
+Despite being derived from the model proposed by Meese et al.
+[@Meese2006], the simplifications applied to this architecture make it very similar to other models [@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [@Baker2012; @Kingdom2015].
 Our key parameter of interest is the weight of interocular suppression.
@@
 The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+Because we used coherent averaging across participants for our steady-state data, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
 However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
@@
 We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document is available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+The preregistration document is available at the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
 
@@
 
-Raw data files are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+Raw data files are available at the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
 
@@
 
-Experimental and analysis codes are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+Experimental and analysis code is available at the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
 

### 2023-01-22 manuscriptNature.tex
Minor edits

@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
-  pdfauthor={Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs}
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
 % Correct order of tables after \paragraph or \subparagraph
@@
 \setcounter{secnumdepth}{5}
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
+  pdfauthor={Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
 
@@
 
-How does the brain combine information across the eyes?
-In primary visual cortex, spatial patterns are subject to `ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
-Here we asked whether this invariance holds for pure changes in luminance.
-We collected steady-state EEG and pupillometry data simultaneously, and find strong deviations from ocularity invariance both in the cortex and also in the subcortical pathway that determines pupil diameter.
-In cortex, we find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas measurements of pupil diameter showed weaker facilitation and stronger suppression.
-This was not purely a consequence of the temporal stimulus parameters; pronounced binocular facilitation was also observed at faster flicker rates.
-Near-linear binocular combination was also found for the same stimuli using a perceptual matching task.
-A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data compared with the pupillometry results.
-These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+How does the human brain combine information across the eyes?
+It has been known for many years that cortical normalisation mechanisms implement `ocularity invariance': equalising neural responses to spatial patterns presented either monocularly or binocularly.
+Here we used a novel combination of electrophysiology, psychophysics, pupillometry and computational modelling to ask whether this invariance also holds for flickering luminance stimuli with no spatial contrast.
+We find dramatic violations of ocularity invariance for these stimuli, both in cortex and also in the subcortical pathways that govern pupil diameter.
+Specifically, we find substantial binocular facilitation in both pathways with the effect being strongest in cortex.
+Near-linear binocular additivity (instead of ocularity invariance) was also found using a perceptual luminance matching task.
+Ocularity invariance is therefore not a ubiquitous feature of visual processing, and the brain appears to repurpose a generic normalisation algorithm for different visual functions by adjusting the amount of interocular suppression.
 
@@
 This involves a process of signal combination both within\textsuperscript{1} and between\textsuperscript{2} the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established.\textsuperscript{3} Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN).\textsuperscript{4} However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels\textsuperscript{5} and much less is known about the computations that operate in these subcortical pathways.
-In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established\textsuperscript{3}.
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN)\textsuperscript{4}.
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels\textsuperscript{5} and much less is known about the computations that operate in these subcortical pathways.
+Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2.\textsuperscript{6,7} This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds)\textsuperscript{8,9} and neural activity\textsuperscript{1,10} are approximately equal for monocular and binocular presentation.
+This is known as binocular summation\textsuperscript{6,7}, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2.
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds)\textsuperscript{8,9} and neural activity\textsuperscript{1,10} are approximately equal for monocular and binocular presentation.
 Contemporary models of binocular vision\textsuperscript{9,11} advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance':\textsuperscript{12} perceived contrast does not change when one eye is opened and closed.
+This is consistent with our everyday experience of `ocularity invariance'\textsuperscript{12}: perceived contrast does not change when one eye is opened and closed.
 
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink.\textsuperscript{5} There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; 13).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus.\textsuperscript{5,14--16} To account for the consensual response, these brain regions must combine information from the left and right eyes,\textsuperscript{17} yet the computation that achieves this is achieved is unclear.
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink\textsuperscript{5}.
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response;\textsuperscript{13}).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus\textsuperscript{5,14--16}.
+To account for the consensual response, these brain regions must combine information from the left and right eyes\textsuperscript{17}, yet the computation that achieves this is unclear.
 
@@
 
-The pupillometry results are summarised in Fig.
+The pupillometry results for our first experiment are summarised in Fig.
 \ref{fig:pupildata}.
@@
 \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic (note that the absence of a main effect of condition is expected, given that there should be negligible differences between conditions at low contrasts, and any differences are therefore captured by the interaction term).
 For the cross-frequency conditions (Fig.
@@
 
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli.\textsuperscript{1} One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli\textsuperscript{1}.
+One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz;\textsuperscript{19} note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz\textsuperscript{19}; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms.\textsuperscript{21--23} We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms\textsuperscript{21--23}.
+We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
 One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict,\textsuperscript{1,9} and the peak location of our prior distribution (black curve).
-These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict\textsuperscript{1,9}, and the peak location of our prior distribution (black curve).
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and significant dichoptic masking observed using that method.
 The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts.\textsuperscript{1,9,10} Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts\textsuperscript{1,9,10}.
+Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
 However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, 23 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and 24 report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm.\textsuperscript{25} Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments,\textsuperscript{21,22,26} though not for luminance decrements.\textsuperscript{21} Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+For example, Quaia et al.@Quaia2018 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and \href{mailto:Cajochen@Spitschan2019}{\nolinkurl{Cajochen@Spitschan2019}} report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm\textsuperscript{24}.
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments\textsuperscript{21,22,25}, though not for luminance decrements\textsuperscript{21}.
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination.
 
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-1 point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs.\textsuperscript{2} This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction.\textsuperscript{27,28} One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+We \href{mailto:previously@Baker2017}{\nolinkurl{previously@Baker2017}} pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also\textsuperscript{2}).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction\textsuperscript{26,27}.
+One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or are otherwise phylogenetically older than binocular pattern vision.
 Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter.\textsuperscript{19} It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms.\textsuperscript{29} We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter\textsuperscript{19}.
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms\textsuperscript{28}.
+We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but intend to investigate this directly in future neuroimaging work.
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs'\textsuperscript{30,31} are biased towards low spatial frequencies,\textsuperscript{32,33} and relatively insensitive to stimulus orientation.\textsuperscript{30,31,34} As the blob regions are embedded within ocular dominance columns,\textsuperscript{30} they are also largely monocular.\textsuperscript{31,35} More recent work has reported psychophysical evidence for unoriented chromatic\textsuperscript{36} and achromatic\textsuperscript{37} mechanisms, that also appear to be monocular.
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs'\textsuperscript{29,30} are biased towards low spatial frequencies\textsuperscript{31,32}, and relatively insensitive to stimulus orientation\textsuperscript{29,30} (though see\textsuperscript{33}).
+As the blob regions are embedded within ocular dominance columns\textsuperscript{29}, they are also largely monocular\textsuperscript{30,34}.
+More recent work has reported psychophysical evidence for unoriented chromatic\textsuperscript{35} and achromatic\textsuperscript{36} mechanisms, that also appear to be monocular.
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
@@
 
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The stimuli were two monocularly presented discs of achromatic flickering light with a diameter of 3.74 degrees, displayed against a black background.
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Fig.
+Four dark red lines were added around each monocular disc to help with their fusion into a single binocular disc (see insert in Fig.
 \ref{fig:pupildata}b for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants perceived a single fused disc.
 The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
@@
 
-All stimuli had a mean luminance of 42 cd/m\(^2\) on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
-For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
-For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+All stimuli had a mean luminance of 42 cd/m\(^2\), and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
+All stimuli were presented using Psychopy\textsuperscript{37} (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
 
-EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; 38) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany\textsuperscript{38}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
-In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
+In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 2Hz, and the other eye's disc flickered at 1.6Hz.
 We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
-The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
+The rationale for flickering both eyes at 2Hz is that we can measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
 The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.~the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox.\textsuperscript{39} The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox\textsuperscript{39}.
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
 The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean.\textsuperscript{20} For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by 20.
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of 40 that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean\textsuperscript{20}.
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described previously\textsuperscript{20}.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic\textsuperscript{40} that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software,\textsuperscript{38} which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software\textsuperscript{38}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis.\textsuperscript{19} The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies.\textsuperscript{41,42} Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis.\textsuperscript{43}
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis\textsuperscript{19}.
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies\textsuperscript{41,42}.
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis\textsuperscript{43}.
 
@@
 
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by 9.
-The second gain control stage was omitted\textsuperscript{1} to simplify the model and reduce the number of free parameters.
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.\textsuperscript{9}.
+The second gain control stage was omitted, consistent with previous work\textsuperscript{1}, to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 
-Despite being derived from the model proposed by 9, the simplifications applied to this architecture make it very similar to other models.\textsuperscript{8,11,17,44} In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression.\textsuperscript{26,45} Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli.\textsuperscript{1} Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation.\textsuperscript{25}
+Despite being derived from the model proposed by Meese et al.\textsuperscript{9}, the simplifications applied to this architecture make it very similar to other models\textsuperscript{8,11,17,44}.
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression\textsuperscript{25,45}.
+Our key parameter of interest is the weight of interocular suppression.
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli\textsuperscript{1}.
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation\textsuperscript{24}.
 
-We implemented the model within a Bayesian framework using the Stan software.\textsuperscript{46} This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature.\textsuperscript{9,26} We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+We implemented the model within a Bayesian framework using the Stan software\textsuperscript{46}.
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature\textsuperscript{9,25}.
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
 The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+Because we used coherent averaging across participants for our steady-state data, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
 However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
@@
 We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document is available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
+The preregistration document is available at the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
@@
 
-Raw data files are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
+Raw data files are available at the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
@@
 
-Experimental and analysis codes are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
+Experimental and analysis code is available at the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Baker2017}{}%
-1. Baker, D. H. \& Wade, A. R. Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2017}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Baker, D.
+H.
+\& Wade, A.
+R.
+\href{https://doi.org/10.1093/cercor/bhw395}{Evidence for an optimal algorithm underlying signal combination in human visual cortex}.
+\emph{Cereb Cortex} \textbf{27}, 254--264 (2017).}
 
-\leavevmode\hypertarget{ref-Ernst2002}{}%
-2. Ernst, M. O. \& Banks, M. S. Humans integrate visual and haptic information in a statistically optimal fashion. \emph{Nature} \textbf{415}, 429--33 (2002).
+\leavevmode\vadjust pre{\hypertarget{ref-Ernst2002}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Ernst, M.
+O.
+\& Banks, M.
+S.
+\href{https://doi.org/10.1038/415429a}{Humans integrate visual and haptic information in a statistically optimal fashion}.
+\emph{Nature} \textbf{415}, 429--33 (2002).}
 
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-3. Hubel, D. H. \& Wiesel, T. N. Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
+\leavevmode\vadjust pre{\hypertarget{ref-Hubel1962}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{Hubel, D.
+H.
+\& Wiesel, T.
+N.
+\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{Receptive fields, binocular interaction and functional architecture in the cat's visual cortex}.
+\emph{J Physiol} \textbf{160}, 106--54 (1962).}
 
-\leavevmode\hypertarget{ref-Purves2008}{}%
-4. Purves, D. \emph{et al.} \emph{Principles of Cognitive Neuroscience}. (Oxford University Press, 2008).
+\leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Purves, D. \emph{et al.} \emph{Principles of {Cognitive} {Neuroscience}}. (Oxford University Press, 2008).}
 
-\leavevmode\hypertarget{ref-McDougal2008}{}%
-5. McDougal, D. H. \& Gamlin, P. D. Pupillary control pathways. in \emph{The senses: A comprehensive reference} 521--536 (Elsevier, 2008).
+\leavevmode\vadjust pre{\hypertarget{ref-McDougal2008}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{McDougal, D. H. \& Gamlin, P. D. Pupillary control pathways. in \emph{The senses: A comprehensive reference} 521--536 (Elsevier, 2008).}
 
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-6. Campbell, F. W. \& Green, D. G. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
+\leavevmode\vadjust pre{\hypertarget{ref-Campbell1965}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Campbell, F. W. \& Green, D. G. \href{https://doi.org/10.1038/208191a0}{Monocular versus binocular visual acuity}. \emph{Nature} \textbf{208}, 191--2 (1965).}
 
-\leavevmode\hypertarget{ref-Baker2018}{}%
-7. Baker, D. H., Lygo, F. A., Meese, T. S. \& Georgeson, M. A. Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2018}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Baker, D.
+H., Lygo, F.
+A., Meese, T.
+S.
+\& Georgeson, M.
+A.
+\href{https://doi.org/10.1037/bul0000163}{Binocular summation revisited: Beyond \(\sqrt{2}\)}.
+\emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).}
 
-\leavevmode\hypertarget{ref-Legge1984}{}%
-8. Legge, G. E. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
+\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Legge, G. E. \href{https://doi.org/10.1016/0042-6989(84)90064-6}{Binocular contrast summation--II. Quadratic summation}. \emph{Vision Res} \textbf{24}, 385--94 (1984).}
 
-\leavevmode\hypertarget{ref-Meese2006}{}%
-9. Meese, T. S., Georgeson, M. A. \& Baker, D. H. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}, 1224--43 (2006).
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Meese, T. S., Georgeson, M. A. \& Baker, D. H. \href{https://doi.org/10.1167/6.11.7}{Binocular contrast vision at and above threshold}. \emph{J Vis} \textbf{6}, 1224--43 (2006).}
 
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-10. Moradi, F. \& Heeger, D. J. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}, 13 (2009).
+\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Moradi, F. \& Heeger, D. J. \href{https://doi.org/10.1167/9.3.13}{Inter-ocular contrast normalization in human visual cortex}. \emph{J Vis} \textbf{9(3)}, 13 (2009).}
 
-\leavevmode\hypertarget{ref-Ding2006}{}%
-11. Ding, J. \& Sperling, G. A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
+\leavevmode\vadjust pre{\hypertarget{ref-Ding2006}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Ding, J. \& Sperling, G. \href{https://doi.org/10.1073/pnas.0509629103}{A gain-control theory of binocular combination}. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).}
 
-\leavevmode\hypertarget{ref-Baker2007}{}%
-12. Baker, D. H., Meese, T. S. \& Georgeson, M. A. Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Baker, D.
+H., Meese, T.
+S.
+\& Georgeson, M.
+A.
+\href{https://doi.org/10.1163/156856807781503622}{Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model}.
+\emph{Spat Vis} \textbf{20}, 397--413 (2007).}
 
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-13.
-Wyatt, H.
+\leavevmode\vadjust pre{\hypertarget{ref-Wyatt1981}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Wyatt, H.
 J.
@@
 F.
-Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}, 513--25 (1981).
+\href{https://doi.org/10.1016/0042-6989(81)90097-3}{Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem}.
+\emph{Vision Res} \textbf{21}, 513--25 (1981).}
 
-\leavevmode\hypertarget{ref-Angee2021}{}%
-14. Angée, C., Nedelec, B., Erjavec, E., Rozet, J.-M. \& Fares Taie, L. Congenital microcoria: Clinical features and molecular genetics. \emph{Genes (Basel)} \textbf{12}, (2021).
+\leavevmode\vadjust pre{\hypertarget{ref-Angee2021}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{Angée, C., Nedelec, B., Erjavec, E., Rozet, J.-M.
+\& Fares Taie, L.
+\href{https://doi.org/10.3390/genes12050624}{Congenital microcoria: Clinical features and molecular genetics}.
+\emph{Genes (Basel)} \textbf{12}, (2021).}
 
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-15. Mathôt, S. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
+\leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Mathôt, S. \href{https://doi.org/10.5334/joc.18}{Pupillometry: Psychology, physiology, and function}. \emph{J Cogn} \textbf{1}, 16 (2018).}
 
-\leavevmode\hypertarget{ref-Wang2015}{}%
-16. Wang, C.-A. \& Munoz, D. P. A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Wang, C.-A.
+\& Munoz, D.
+P.
+\href{https://doi.org/10.1016/j.conb.2015.03.018}{A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size}.
+\emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).}
 
-\leavevmode\hypertarget{ref-Doesschate1967}{}%
-17. Doesschate, J. ten \& Alpern, M. Effect of photoexcitation of the two retinas on pupil size. \emph{J Neurophysiol} \textbf{30}, 562--76 (1967).
+\leavevmode\vadjust pre{\hypertarget{ref-Doesschate1967}{}}%
+\CSLLeftMargin{17. }%
+\CSLRightInline{Doesschate, J.
+ten \& Alpern, M.
+\href{https://doi.org/10.1152/jn.1967.30.3.562}{Effect of photoexcitation of the two retinas on pupil size}.
+\emph{J Neurophysiol} \textbf{30}, 562--76 (1967).}
 
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-18. Norcia, A. M., Appelbaum, L. G., Ales, J. M., Cottereau, B. R. \& Rossion, B. The steady-state visual evoked potential in vision research: A review. \emph{J Vis} \textbf{15(6)}, 4 (2015).
+\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+\CSLLeftMargin{18. }%
+\CSLRightInline{Norcia, A.
+M., Appelbaum, L.
+G., Ales, J.
+M., Cottereau, B.
+R.
+\& Rossion, B.
+\href{https://doi.org/10.1167/15.6.4}{The steady-state visual evoked potential in vision research: A review}.
+\emph{J Vis} \textbf{15(6)}, 4 (2015).}
 
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-19.
-Spitschan, M., Jain, S., Brainard, D.
+\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\CSLLeftMargin{19. }%
+\CSLRightInline{Spitschan, M., Jain, S., Brainard, D.
 H.
@@
 K.
-Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proc Natl Acad Sci U S A} \textbf{111}, 15568--72 (2014).
+\href{https://doi.org/10.1073/pnas.1400942111}{Opponent melanopsin and s-cone signals in the human pupillary light response}.
+\emph{Proc Natl Acad Sci U S A} \textbf{111}, 15568--72 (2014).}
 
-\leavevmode\hypertarget{ref-Baker2021}{}%
-20. Baker, D. H. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}, (2021).
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Baker, D. H. \href{https://doi.org/10.51628/001c.27680}{Statistical analysis of periodic data in neuroscience}. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}, (2021).}
 
-\leavevmode\hypertarget{ref-Anstis1998}{}%
-21. Anstis, S. \& Ho, A. Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}, 523--39 (1998).
+\leavevmode\vadjust pre{\hypertarget{ref-Anstis1998}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{Anstis, S.
+\& Ho, A.
+\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion}.
+\emph{Vision Res} \textbf{38}, 523--39 (1998).}
 
-\leavevmode\hypertarget{ref-Levelt1965}{}%
-22. Levelt, W. J. Binocular brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).
+\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
+\CSLLeftMargin{22. }%
+\CSLRightInline{Levelt, W. J. \href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{Binocular brightness averaging and contour information}. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).}
 
-\leavevmode\hypertarget{ref-Quaia2018}{}%
-23. Quaia, C., Optican, L. M. \& Cumming, B. G. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}, 7 (2018).
+\leavevmode\vadjust pre{\hypertarget{ref-Quaia2018}{}}%
+\CSLLeftMargin{23. }%
+\CSLRightInline{Quaia, C., Optican, L. M. \& Cumming, B. G. \href{https://doi.org/10.1167/18.4.7}{Binocular summation for reflexive eye movements}. \emph{J Vis} \textbf{18(4)}, 7 (2018).}
 
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-24. Spitschan, M. \& Cajochen, C. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2020}{}}%
+\CSLLeftMargin{24. }%
+\CSLRightInline{Baker, D.
+H.
+\emph{et al.} \href{https://doi.org/10.1038/s41598-020-60602-5}{Binaural summation of amplitude modulation involves weak interaural suppression}.
+\emph{Sci Rep} \textbf{10}, 3560 (2020).}
 
-\leavevmode\hypertarget{ref-Baker2020}{}%
-25. Baker, D. H. \emph{et al.} Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
+\leavevmode\vadjust pre{\hypertarget{ref-Baker2012}{}}%
+\CSLLeftMargin{25. }%
+\CSLRightInline{Baker, D.
+H., Wallis, S.
+A., Georgeson, M.
+A.
+\& Meese, T.
+S.
+\href{https://doi.org/10.1016/j.visres.2012.01.008}{Nonlinearities in the binocular combination of luminance and contrast}.
+\emph{Vision Res} \textbf{56}, 1--9 (2012).}
 
-\leavevmode\hypertarget{ref-Baker2012}{}%
-26. Baker, D. H., Wallis, S. A., Georgeson, M. A. \& Meese, T. S. Nonlinearities in the binocular combination of luminance and contrast. \emph{Vision Res} \textbf{56}, 1--9 (2012).
+\leavevmode\vadjust pre{\hypertarget{ref-Li1994}{}}%
+\CSLLeftMargin{26. }%
+\CSLRightInline{Li, Z.
+\& Atick, J.
+J.
+\href{https://doi.org/10.1088/0954-898X_5_2_003}{Efficient stereo coding in the multiscale representation}.
+\emph{Network: Computation in Neural Systems} \textbf{5}, 157--174 (1994).}
 
-\leavevmode\hypertarget{ref-Li1994}{}%
-27. Li, Z. \& Atick, J. J. Efficient stereo coding in the multiscale representation. \emph{Network: Computation in Neural Systems} \textbf{5}, 157--174 (1994).
+\leavevmode\vadjust pre{\hypertarget{ref-May2022}{}}%
+\CSLLeftMargin{27. }%
+\CSLRightInline{May, K.
+\& Zhaoping, L.
+\href{https://doi.org/10.1016/j.visres.2021.08.005}{Li and {Atick's} theory of efficient binocular coding: A tutorial and mini-review}.
+\emph{Vision Res} \textbf{201}, 107950 (2022).}
 
-\leavevmode\hypertarget{ref-May2022}{}%
-28. May, K. \& Zhaoping, L. Li and Atick's theory of efficient binocular coding: A tutorial and mini-review. \emph{Vision Res} \textbf{201}, 107950 (2022).
+\leavevmode\vadjust pre{\hypertarget{ref-Bradley2008}{}}%
+\CSLLeftMargin{28. }%
+\CSLRightInline{Bradley, M.
+M., Miccoli, L., Escrig, M.
+A.
+\& Lang, P.
+J.
+\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{The pupil as a measure of emotional arousal and autonomic activation}.
+\emph{Psychophysiology} \textbf{45}, 602--7 (2008).}
 
-\leavevmode\hypertarget{ref-Bradley2008}{}%
-29. Bradley, M. M., Miccoli, L., Escrig, M. A. \& Lang, P. J. The pupil as a measure of emotional arousal and autonomic activation. \emph{Psychophysiology} \textbf{45}, 602--7 (2008).
+\leavevmode\vadjust pre{\hypertarget{ref-Horton1981}{}}%
+\CSLLeftMargin{29. }%
+\CSLRightInline{Horton, J.
+C.
+\& Hubel, D.
+H.
+\href{https://doi.org/10.1038/292762a0}{Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey}.
+\emph{Nature} \textbf{292}, 762--4 (1981).}
 
-\leavevmode\hypertarget{ref-Horton1981}{}%
-30. Horton, J. C. \& Hubel, D. H. Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey. \emph{Nature} \textbf{292}, 762--4 (1981).
+\leavevmode\vadjust pre{\hypertarget{ref-Livingstone1984}{}}%
+\CSLLeftMargin{30. }%
+\CSLRightInline{Livingstone, M.
+S.
+\& Hubel, D.
+H.
+\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{Anatomy and physiology of a color system in the primate visual cortex}.
+\emph{J Neurosci} \textbf{4}, 309--56 (1984).}
 
-\leavevmode\hypertarget{ref-Livingstone1984}{}%
-31. Livingstone, M. S. \& Hubel, D. H. Anatomy and physiology of a color system in the primate visual cortex. \emph{J Neurosci} \textbf{4}, 309--56 (1984).
-
-\leavevmode\hypertarget{ref-Tootell1988}{}%
-32.
-Tootell, R.
+\leavevmode\vadjust pre{\hypertarget{ref-Tootell1988}{}}%
+\CSLLeftMargin{31. }%
+\CSLRightInline{Tootell, R.
 B., Silverman, M.
@@
 L.
-Functional anatomy of macaque striate cortex.
+\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{Functional anatomy of macaque striate cortex.
 V.
-Spatial frequency.
-\emph{J Neurosci} \textbf{8}, 1610--24 (1988).
+Spatial frequency}.
+\emph{J Neurosci} \textbf{8}, 1610--24 (1988).}
 
-\leavevmode\hypertarget{ref-Edwards1995}{}%
-33.
-Edwards, D.
+\leavevmode\vadjust pre{\hypertarget{ref-Edwards1995}{}}%
+\CSLLeftMargin{32. }%
+\CSLRightInline{Edwards, D.
 P., Purpura, K.
@@
 \& Kaplan, E.
-Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
-\emph{Vision Res} \textbf{35}, 1501--23 (1995).
+\href{https://doi.org/10.1016/0042-6989(94)00253-i}{Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs}.
+\emph{Vision Res} \textbf{35}, 1501--23 (1995).}
 
-\leavevmode\hypertarget{ref-Economides2011}{}%
-34.
-Economides, J.
+\leavevmode\vadjust pre{\hypertarget{ref-Economides2011}{}}%
+\CSLLeftMargin{33. }%
+\CSLRightInline{Economides, J.
 R., Sincich, L.
@@
 C.
-Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
-\emph{Nat Neurosci} \textbf{14}, 1574--80 (2011).
+\href{https://doi.org/10.1038/nn.2958}{Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex}.
+\emph{Nat Neurosci} \textbf{14}, 1574--80 (2011).}
 
-\leavevmode\hypertarget{ref-Tychsen2004}{}%
-35.
-Tychsen, L., Wong, A.
+\leavevmode\vadjust pre{\hypertarget{ref-Tychsen2004}{}}%
+\CSLLeftMargin{34. }%
+\CSLRightInline{Tychsen, L., Wong, A.
 M.-F.
 \& Burkhalter, A.
-Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
-\emph{The Journal of Comparative Neurology} \textbf{474}, 261--275 (2004).
+\href{https://doi.org/10.1002/cne.20113}{Paucity of horizontal connections for binocular vision in V1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity}.
+\emph{The Journal of Comparative Neurology} \textbf{474}, 261--275 (2004).}
 
-\leavevmode\hypertarget{ref-Gheiratmand2013}{}%
-36.
-Gheiratmand, M., Meese, T.
+\leavevmode\vadjust pre{\hypertarget{ref-Gheiratmand2013}{}}%
+\CSLLeftMargin{35. }%
+\CSLRightInline{Gheiratmand, M., Meese, T.
 S.
@@
 T.
-Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
-\emph{Journal of Vision} \textbf{13(1)}, 2 (2013).
+\href{https://doi.org/10.1167/13.1.2}{Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision}.
+\emph{Journal of Vision} \textbf{13(1)}, 2 (2013).}
 
-\leavevmode\hypertarget{ref-Meese2011}{}%
-37.
-Meese, T.
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2011}{}}%
+\CSLLeftMargin{36. }%
+\CSLRightInline{Meese, T.
 S.
@@
 H.
-A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-\emph{iPerception} \textbf{2}, 159--82 (2011).
+\href{https://doi.org/10.1068/i0416}{A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds}.
+\emph{{iPerception}} \textbf{2}, 159--82 (2011).}
 
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-38.
-Kassner, M., Patera, W.
+\leavevmode\vadjust pre{\hypertarget{ref-Peirce2019}{}}%
+\CSLLeftMargin{37. }%
+\CSLRightInline{Peirce, J. \emph{et al.} \href{https://doi.org/10.3758/s13428-018-01193-y}{PsychoPy2: Experiments in behavior made easy}. \emph{Behav Res Methods} \textbf{51}, 195--203 (2019).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Kassner2014}{}}%
+\CSLLeftMargin{38. }%
+\CSLRightInline{Kassner, M., Patera, W.
 \& Bulling, A.
 Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-in \emph{Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication} 1151--1160 (UbiComp '14 Adjunct; ACM, 2014).
-doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.
+in \emph{Proceedings of the 2014 {ACM} international joint conference on pervasive and ubiquitous computing: Adjunct publication} 1151--1160 (UbiComp '14 Adjunct; {ACM}, 2014).
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}.}
 
-\leavevmode\hypertarget{ref-Delorme2004}{}%
-39. Delorme, A. \& Makeig, S. EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).
+\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
+\CSLLeftMargin{39. }%
+\CSLRightInline{Delorme, A.
+\& Makeig, S.
+\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{{EEGLAB}: An open source toolbox for analysis of single-trial {EEG} dynamics including independent component analysis}.
+\emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).}
 
-\leavevmode\hypertarget{ref-Victor1991}{}%
-40. Victor, J. D. \& Mast, J. A new statistic for steady-state evoked potentials. \emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).
+\leavevmode\vadjust pre{\hypertarget{ref-Victor1991}{}}%
+\CSLLeftMargin{40. }%
+\CSLRightInline{Victor, J.
+D.
+\& Mast, J.
+\href{https://doi.org/10.1016/0013-4694(91)90099-p}{A new statistic for steady-state evoked potentials}.
+\emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).}
 
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-41. Barrionuevo, P. A. \emph{et al.} Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2014}{}}%
+\CSLLeftMargin{41. }%
+\CSLRightInline{Barrionuevo, P.
+A.
+\emph{et al.} \href{https://doi.org/10.1167/iovs.13-13252}{Assessing rod, cone, and melanopsin contributions to human pupil flicker responses}.
+\emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).}
 
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-42. Barrionuevo, P. A. \& Cao, D. Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{J Vis} \textbf{16(11)}, 29 (2016).
+\leavevmode\vadjust pre{\hypertarget{ref-Barrionuevo2016}{}}%
+\CSLLeftMargin{42. }%
+\CSLRightInline{Barrionuevo, P.
+A.
+\& Cao, D.
+\href{https://doi.org/10.1167/16.11.29}{Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response}.
+\emph{J Vis} \textbf{16(11)}, 29 (2016).}
 
-\leavevmode\hypertarget{ref-Figueira2022}{}%
-43.
-Figueira, J.
+\leavevmode\vadjust pre{\hypertarget{ref-Figueira2022}{}}%
+\CSLLeftMargin{43. }%
+\CSLRightInline{Figueira, J.
 S.
@@
 \& Keil, A.
-The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
-\emph{Dev Cogn Neurosci} \textbf{54}, 101066 (2022).
+\href{https://doi.org/10.1016/j.dcn.2022.101066}{The FreqTag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms}.
+\emph{Dev Cogn Neurosci} \textbf{54}, 101066 (2022).}
 
-\leavevmode\hypertarget{ref-Schrodinger1926}{}%
-44. Schrödinger, E. Die gesichtsempfindungen. in \emph{Mueller-pouillets lehrbuch der physik (11th ed.)} vol. Book 2 456--560 (Vieweg: Braunschweig, 1926).
+\leavevmode\vadjust pre{\hypertarget{ref-Schrodinger1926}{}}%
+\CSLLeftMargin{44. }%
+\CSLRightInline{Schrödinger, E. Die gesichtsempfindungen. in \emph{Mueller-pouillets lehrbuch der physik (11th ed.)} vols Book 2 456--560 (Vieweg: Braunschweig, 1926).}
 
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-45. Kingdom, F. A. A. \& Libenson, L. Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15(5)}, 2 (2015).
+\leavevmode\vadjust pre{\hypertarget{ref-Kingdom2015}{}}%
+\CSLLeftMargin{45. }%
+\CSLRightInline{Kingdom, F.
+A.
+A.
+\& Libenson, L.
+\href{https://doi.org/10.1167/15.5.2}{Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging}.
+\emph{J Vis} \textbf{15(5)}, 2 (2015).}
 
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-46. Carpenter, B. \emph{et al.} Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).
+\leavevmode\vadjust pre{\hypertarget{ref-Carpenter2017}{}}%
+\CSLLeftMargin{46. }%
+\CSLRightInline{Carpenter, B. \emph{et al.} \href{https://doi.org/10.18637/jss.v076.i01}{Stan: A probabilistic programming language}. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).}
+
+\end{CSLReferences}
 

### 2023-02-02 manuscriptPNAS.Rmd
Reformatted for PNAS.

--- 2023-01-12 manuscript.Rmd
@@
 date: "Department of Psychology, University of York, UK"
+
 output:
@@
 bibliography: references.bib
-csl: elife.csl
+csl: pnas.csl
 ---
@@
 ```
+Federico G. Segala
+**Email**: fgs502@york.ac.uk
+
+**Author contributions: Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
+**Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
+**Myat Aung**: Software, resources, writing - review & editing.
+**Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
+**Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
+
+**Competing interest declaration:** The authors declare no competing interests.
+
+**Classification:** Biological Sciences - Neuroscience/Psychological and Cognitive Sciences
+
+**Keywords:** Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
 
@@
 These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+
+# Significance Statement
+Please note that it should not exceed 120 words, but should be at least 50 words in length.
 
@@
 
-# Author contributions
-
-**Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
-**Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
-**Myat Aung**: Software, resources, writing - review & editing.
-**Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
-**Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
-
-# Declaration of interests
-
-The authors declare no competing interests.
-
 # References

### 2023-02-02 manuscriptPNAS.tex
Reformatted for PNAS.

--- 2023-01-12 manuscript.tex
@@
 
+Federico G. Segala
+\textbf{Email}: \href{mailto:fgs502@york.ac.uk}{\nolinkurl{fgs502@york.ac.uk}}
+
+\textbf{Author contributions: Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
+\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Myat Aung}: Software, resources, writing - review \& editing.
+\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
+
+\textbf{Competing interest declaration:} The authors declare no competing interests.
+
+\textbf{Classification:}
+
+\textbf{Keywords:} Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
+
 \hypertarget{abstract}{%
@@
 The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
-This involves a process of signal combination both within (Baker and Wade, 2017) and between (Ernst and Banks, 2002) the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, 1962).
-Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
-However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, 2008) and much less is known about the computations that operate in these subcortical pathways.
+This involves a process of signal combination both within (1) and between (2) the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (3).
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (4).
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (5) and much less is known about the computations that operate in these subcortical pathways.
 In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
@@
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., 2018; Campbell and Green, 1965).
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance' (Baker et al., 2007): perceived contrast does not change when one eye is opened and closed.
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (6, 7).
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (8, 9) and neural activity (1, 10) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (9, 11) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance' (12): perceived contrast does not change when one eye is opened and closed.
 
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, 2008).
-There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (1981)).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2008; Wang and Munoz, 2015).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the computation that achieves this is achieved is unclear.
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (5).
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; (13)).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (5, 14--16).
+To account for the consensual response, these brain regions must combine information from the left and right eyes (17), yet the computation that achieves this is achieved is unclear.
 
@@
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Periodic flicker entrains both neural (18) and pupil (19) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
@@
 EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; Kassner et al.
-(2014)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; (20)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (21).
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (2021).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (1991) that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (22).
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by (22).
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of (23) that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., 2014), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (20), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.~Spitschan et al., 2014).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., 2022).
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (19).
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (24, 25).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (26).
 
@@
 
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
-(2006).
-The second gain control stage was omitted (consistent with Baker and Wade, 2017) to simplify the model and reduce the number of free parameters.
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by (9).
+The second gain control stage was omitted (1) to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 
-Despite being derived from the model proposed by Meese et al.
-(2006), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
+Despite being derived from the model proposed by (9), the simplifications applied to this architecture make it very similar to other models (8, 11, 17, 27).
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (28, 29).
 Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, 2017).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., 2020).
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (1).
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (30).
 
-We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., 2017).
+We implemented the model within a Bayesian framework using the Stan software (31).
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., 2012; Meese et al., 2006).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (9, 28).
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, 2021) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (22) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
 The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
@@
 
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, 2017).
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (1).
 One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (19); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (32--34).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006), and the peak location of our prior distribution (black curve).
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (1, 9), and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (1, 9, 10).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
 However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, Quaia et al.
-(2018) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (2019) report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., 2020).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, 1998; Baker et al., 2012; Levelt, 1965), though not for luminance decrements (Anstis and Ho, 1998).
+For example, (34) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and (35) report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (30).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (28, 32, 33), though not for luminance decrements (32).
 Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
@@
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-Baker and Wade (2017) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, 2002).
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, 1994; May and Zhaoping, 2022).
+(1) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (2).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (36, 37).
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.~Spitschan et al., 2014).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.~Bradley et al., 2008).
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (19).
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (38).
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
@@
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, 1981; Livingstone and Hubel, 1984) are biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988), and relatively insensitive to stimulus orientation (Horton and Hubel, 1981; Livingstone and Hubel, 1984; though see Economides et al., 2011).
-As the blob regions are embedded within ocular dominance columns (Horton and Hubel, 1981), they are also largely monocular (Livingstone and Hubel, 1984; Tychsen et al., 2004).
-More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., 2013) and achromatic (Meese and Baker, 2011) mechanisms, that also appear to be monocular.
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (39, 40) are biased towards low spatial frequencies (41, 42), and relatively insensitive to stimulus orientation (39, 40, 43).
+As the blob regions are embedded within ocular dominance columns (39), they are also largely monocular (40, 44).
+More recent work has reported psychophysical evidence for unoriented chromatic (45) and achromatic (46) mechanisms, that also appear to be monocular.
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
@@
 
-\hypertarget{author-contributions}{%
-\section{Author contributions}\label{author-contributions}}
-
-\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
-\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Myat Aung}: Software, resources, writing - review \& editing.
-\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
-
-\hypertarget{declaration-of-interests}{%
-\section{Declaration of interests}\label{declaration-of-interests}}
-
-The authors declare no competing interests.
-
 \hypertarget{references}{%
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-Baker2017}{}%
+1. D. H. Baker, A. R. Wade, Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
+
+\leavevmode\hypertarget{ref-Ernst2002}{}%
+2. M. O. Ernst, M. S. Banks, Humans integrate visual and haptic information in a statistically optimal fashion. \emph{Nature} \textbf{415}, 429--33 (2002).
+
+\leavevmode\hypertarget{ref-Hubel1962}{}%
+3. D. H. Hubel, T. N. Wiesel, Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
+
+\leavevmode\hypertarget{ref-Purves2008}{}%
+4. D. Purves\emph{et al.}, \emph{Principles of Cognitive Neuroscience} (Oxford University Press, 2008).
+
+\leavevmode\hypertarget{ref-McDougal2008}{}%
+5. D. H. McDougal, P. D. Gamlin, ``Pupillary control pathways.'' in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.
+
+\leavevmode\hypertarget{ref-Campbell1965}{}%
+6. F. W. Campbell, D. G. Green, Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
+
+\leavevmode\hypertarget{ref-Baker2018}{}%
+7. D. H. Baker, F. A. Lygo, T. S. Meese, M. A. Georgeson, Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
+
+\leavevmode\hypertarget{ref-Legge1984}{}%
+8. G. E. Legge, Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
+
+\leavevmode\hypertarget{ref-Meese2006}{}%
+9. T. S. Meese, M. A. Georgeson, D. H. Baker, Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}, 1224--43 (2006).
+
+\leavevmode\hypertarget{ref-Moradi2009}{}%
+10. F. Moradi, D. J. Heeger, Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}, 13 (2009).
+
+\leavevmode\hypertarget{ref-Ding2006}{}%
+11. J. Ding, G. Sperling, A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
+
+\leavevmode\hypertarget{ref-Baker2007}{}%
+12. D. H. Baker, T. S. Meese, M. A. Georgeson, Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
+
+\leavevmode\hypertarget{ref-Wyatt1981}{}%
+13.
+H.
+J.
+Wyatt, J.
+F.
+Musselman, Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+\emph{Vision Res} \textbf{21}, 513--25 (1981).
+
 \leavevmode\hypertarget{ref-Angee2021}{}%
-Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
-2021.
-Congenital microcoria: Clinical features and molecular genetics.
-\emph{Genes (Basel)} \textbf{12}.
-doi:\href{https://doi.org/10.3390/genes12050624}{10.3390/genes12050624}
+14. C. Angée, B. Nedelec, E. Erjavec, J.-M. Rozet, L. Fares Taie, Congenital microcoria: Clinical features and molecular genetics. \emph{Genes (Basel)} \textbf{12} (2021).
+
+\leavevmode\hypertarget{ref-Mathot2018}{}%
+15. S. Mathôt, Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
+
+\leavevmode\hypertarget{ref-Wang2015}{}%
+16. C.-A. Wang, D. P. Munoz, A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+
+\leavevmode\hypertarget{ref-Doesschate1967}{}%
+17. J. ten Doesschate, M. Alpern, Effect of photoexcitation of the two retinas on pupil size. \emph{J Neurophysiol} \textbf{30}, 562--76 (1967).
+
+\leavevmode\hypertarget{ref-Norcia2015}{}%
+18. A. M. Norcia, L. G. Appelbaum, J. M. Ales, B. R. Cottereau, B. Rossion, The steady-state visual evoked potential in vision research: A review. \emph{J Vis} \textbf{15(6)}, 4 (2015).
+
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
+19. M. Spitschan, S. Jain, D. H. Brainard, G. K. Aguirre, Opponent melanopsin and s-cone signals in the human pupillary light response. \emph{Proc Natl Acad Sci U S A} \textbf{111}, 15568--72 (2014).
+
+\leavevmode\hypertarget{ref-Kassner2014}{}%
+20.
+M.
+Kassner, W.
+Patera, A.
+Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+in \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, (UbiComp '14 Adjunct; ACM, 2014), pp.
+1151--1160.
+
+\leavevmode\hypertarget{ref-Delorme2004}{}%
+21. A. Delorme, S. Makeig, EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).
+
+\leavevmode\hypertarget{ref-Baker2021}{}%
+22. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
+
+\leavevmode\hypertarget{ref-Victor1991}{}%
+23. J. D. Victor, J. Mast, A new statistic for steady-state evoked potentials. \emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).
+
+\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
+24. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).
+
+\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
+25. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{J Vis} \textbf{16(11)}, 29 (2016).
+
+\leavevmode\hypertarget{ref-Figueira2022}{}%
+26.
+J.
+S.
+B.
+Figueira, E.
+Kutlu, L.
+S.
+Scott, A.
+Keil, The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
+\emph{Dev Cogn Neurosci} \textbf{54}, 101066 (2022).
+
+\leavevmode\hypertarget{ref-Schrodinger1926}{}%
+27. E. Schrödinger, ``Die gesichtsempfindungen.'' in \emph{Mueller-Pouillets Lehrbuch Der Physik (11th Ed.)}, (Vieweg: Braunschweig, 1926), pp. 456--560.
+
+\leavevmode\hypertarget{ref-Baker2012}{}%
+28. D. H. Baker, S. A. Wallis, M. A. Georgeson, T. S. Meese, Nonlinearities in the binocular combination of luminance and contrast. \emph{Vision Res} \textbf{56}, 1--9 (2012).
+
+\leavevmode\hypertarget{ref-Kingdom2015}{}%
+29. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15(5)}, 2 (2015).
+
+\leavevmode\hypertarget{ref-Baker2020}{}%
+30. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
+
+\leavevmode\hypertarget{ref-Carpenter2017}{}%
+31. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).
 
 \leavevmode\hypertarget{ref-Anstis1998}{}%
-Anstis S, Ho A.
-1998.
-Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
-\emph{Vision Res} \textbf{38}:523--39.
-doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
+32. S. Anstis, A. Ho, Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}, 523--39 (1998).
 
-\leavevmode\hypertarget{ref-Baker2021}{}%
-Baker DH.
-2021.
-Statistical analysis of periodic data in neuroscience.
-\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
-doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+\leavevmode\hypertarget{ref-Levelt1965}{}%
+33. W. J. Levelt, Binocular brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).
 
-\leavevmode\hypertarget{ref-Baker2018}{}%
-Baker DH, Lygo FA, Meese TS, Georgeson MA.
-2018.
-Binocular summation revisited: Beyond \(\sqrt{2}\).
-\emph{Psychol Bull} \textbf{144}:1186--1199.
-doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
+\leavevmode\hypertarget{ref-Quaia2018}{}%
+34. C. Quaia, L. M. Optican, B. G. Cumming, Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}, 7 (2018).
 
-\leavevmode\hypertarget{ref-Baker2007}{}%
-Baker DH, Meese TS, Georgeson MA.
-2007.
-Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
-\emph{Spat Vis} \textbf{20}:397--413.
-doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
+35. M. Spitschan, C. Cajochen, Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
 
-\leavevmode\hypertarget{ref-Baker2020}{}%
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
-2020.
-Binaural summation of amplitude modulation involves weak interaural suppression.
-\emph{Sci Rep} \textbf{10}:3560.
-doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
+\leavevmode\hypertarget{ref-Li1994}{}%
+36. Z. Li, J. J. Atick, Efficient stereo coding in the multiscale representation. \emph{Network: Computation in Neural Systems} \textbf{5}, 157--174 (1994).
 
-\leavevmode\hypertarget{ref-Baker2017}{}%
-Baker DH, Wade AR.
-2017.
-Evidence for an optimal algorithm underlying signal combination in human visual cortex.
-\emph{Cereb Cortex} \textbf{27}:254--264.
-doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
-
-\leavevmode\hypertarget{ref-Baker2012}{}%
-Baker DH, Wallis SA, Georgeson MA, Meese TS.
-2012.
-Nonlinearities in the binocular combination of luminance and contrast.
-\emph{Vision Res} \textbf{56}:1--9.
-doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
-
-\leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-Barrionuevo PA, Cao D.
-2016.
-Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
-\emph{J Vis} \textbf{16(11)}:29.
-doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
-
-\leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
-2014.
-Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
-\emph{Invest Ophthalmol Vis Sci} \textbf{55}:719--27.
-doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}
+\leavevmode\hypertarget{ref-May2022}{}%
+37. K. May, L. Zhaoping, Li and Atick's theory of efficient binocular coding: A tutorial and mini-review. \emph{Vision Res} \textbf{201}, 107950 (2022).
 
 \leavevmode\hypertarget{ref-Bradley2008}{}%
-Bradley MM, Miccoli L, Escrig MA, Lang PJ.
-2008.
-The pupil as a measure of emotional arousal and autonomic activation.
-\emph{Psychophysiology} \textbf{45}:602--7.
-doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
+38. M. M. Bradley, L. Miccoli, M. A. Escrig, P. J. Lang, The pupil as a measure of emotional arousal and autonomic activation. \emph{Psychophysiology} \textbf{45}, 602--7 (2008).
 
-\leavevmode\hypertarget{ref-Campbell1965}{}%
-Campbell FW, Green DG. 1965. Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}:191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
+\leavevmode\hypertarget{ref-Horton1981}{}%
+39. J. C. Horton, D. H. Hubel, Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey. \emph{Nature} \textbf{292}, 762--4 (1981).
 
-\leavevmode\hypertarget{ref-Carpenter2017}{}%
-Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, Brubaker M, Guo J, Li P, Riddell A.
-2017.
-Stan: A probabilistic programming language.
-\emph{Journal of Statistical Software} \textbf{76}:1--32.
-doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
+\leavevmode\hypertarget{ref-Livingstone1984}{}%
+40. M. S. Livingstone, D. H. Hubel, Anatomy and physiology of a color system in the primate visual cortex. \emph{J Neurosci} \textbf{4}, 309--56 (1984).
 
-\leavevmode\hypertarget{ref-Delorme2004}{}%
-Delorme A, Makeig S.
-2004.
-EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
-\emph{J Neurosci Methods} \textbf{134}:9--21.
-doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}
+\leavevmode\hypertarget{ref-Tootell1988}{}%
+41. R. B. Tootell, M. S. Silverman, S. L. Hamilton, E. Switkes, R. L. De Valois, Functional anatomy of macaque striate cortex. V. Spatial frequency. \emph{J Neurosci} \textbf{8}, 1610--24 (1988).
 
-\leavevmode\hypertarget{ref-Ding2006}{}%
-Ding J, Sperling G.
-2006.
-A gain-control theory of binocular combination.
-\emph{Proc Natl Acad Sci U S A} \textbf{103}:1141--6.
-doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}
-
-\leavevmode\hypertarget{ref-Doesschate1967}{}%
-Doesschate J ten, Alpern M.
-1967.
-Effect of photoexcitation of the two retinas on pupil size.
-\emph{J Neurophysiol} \textbf{30}:562--76.
-doi:\href{https://doi.org/10.1152/jn.1967.30.3.562}{10.1152/jn.1967.30.3.562}
+\leavevmode\hypertarget{ref-Edwards1995}{}%
+42.
+D.
+P.
+Edwards, K.
+P.
+Purpura, E.
+Kaplan, Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
+\emph{Vision Res} \textbf{35}, 1501--23 (1995).
 
 \leavevmode\hypertarget{ref-Economides2011}{}%
-Economides JR, Sincich LC, Adams DL, Horton JC.
-2011.
-Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
-\emph{Nat Neurosci} \textbf{14}:1574--80.
-doi:\href{https://doi.org/10.1038/nn.2958}{10.1038/nn.2958}
+43. J. R. Economides, L. C. Sincich, D. L. Adams, J. C. Horton, Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex. \emph{Nat Neurosci} \textbf{14}, 1574--80 (2011).
 
-\leavevmode\hypertarget{ref-Edwards1995}{}%
-Edwards DP, Purpura KP, Kaplan E.
-1995.
-Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
-\emph{Vision Res} \textbf{35}:1501--23.
-doi:\href{https://doi.org/10.1016/0042-6989(94)00253-i}{10.1016/0042-6989(94)00253-i}
-
-\leavevmode\hypertarget{ref-Ernst2002}{}%
-Ernst MO, Banks MS.
-2002.
-Humans integrate visual and haptic information in a statistically optimal fashion.
-\emph{Nature} \textbf{415}:429--33.
-doi:\href{https://doi.org/10.1038/415429a}{10.1038/415429a}
-
-\leavevmode\hypertarget{ref-Figueira2022}{}%
-Figueira JSB, Kutlu E, Scott LS, Keil A.
-2022.
-The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
-\emph{Dev Cogn Neurosci} \textbf{54}:101066.
-doi:\href{https://doi.org/10.1016/j.dcn.2022.101066}{10.1016/j.dcn.2022.101066}
+\leavevmode\hypertarget{ref-Tychsen2004}{}%
+44.
+L.
+Tychsen, A.
+M.-F.
+Wong, A.
+Burkhalter, Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
+\emph{The Journal of Comparative Neurology} \textbf{474}, 261--275 (2004).
 
 \leavevmode\hypertarget{ref-Gheiratmand2013}{}%
-Gheiratmand M, Meese TS, Mullen KT.
-2013.
-Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
-\emph{Journal of Vision} \textbf{13(1)}:2.
-doi:\href{https://doi.org/10.1167/13.1.2}{10.1167/13.1.2}
-
-\leavevmode\hypertarget{ref-Horton1981}{}%
-Horton JC, Hubel DH.
-1981.
-Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
-\emph{Nature} \textbf{292}:762--4.
-doi:\href{https://doi.org/10.1038/292762a0}{10.1038/292762a0}
-
-\leavevmode\hypertarget{ref-Hubel1962}{}%
-Hubel DH, Wiesel TN.
-1962.
-Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
-\emph{J Physiol} \textbf{160}:106--54.
-doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
-
-\leavevmode\hypertarget{ref-Kassner2014}{}%
-Kassner M, Patera W, Bulling A.
-2014.
-Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication.
-UbiComp '14 Adjunct; ACM.
-pp.
-1151--1160.
-doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
-
-\leavevmode\hypertarget{ref-Kingdom2015}{}%
-Kingdom FAA, Libenson L.
-2015.
-Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
-\emph{J Vis} \textbf{15(5)}:2.
-doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
-
-\leavevmode\hypertarget{ref-Legge1984}{}%
-Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
-
-\leavevmode\hypertarget{ref-Levelt1965}{}%
-Levelt WJ.
-1965.
-Binocular brightness averaging and contour information.
-\emph{Br J Psychol} \textbf{56}:1--13.
-doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}
-
-\leavevmode\hypertarget{ref-Li1994}{}%
-Li Z, Atick JJ.
-1994.
-Efficient stereo coding in the multiscale representation.
-\emph{Network: Computation in Neural Systems} \textbf{5}:157--174.
-doi:\href{https://doi.org/10.1088/0954-898X_5_2_003}{10.1088/0954-898X\_5\_2\_003}
-
-\leavevmode\hypertarget{ref-Livingstone1984}{}%
-Livingstone MS, Hubel DH.
-1984.
-Anatomy and physiology of a color system in the primate visual cortex.
-\emph{J Neurosci} \textbf{4}:309--56.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{10.1523/JNEUROSCI.04-01-00309.1984}
-
-\leavevmode\hypertarget{ref-Mathot2018}{}%
-Mathôt S. 2018. Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}:16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
-
-\leavevmode\hypertarget{ref-May2022}{}%
-May K, Zhaoping L.
-2022.
-Li and Atick's theory of efficient binocular coding: A tutorial and mini-review.
-\emph{Vision Res} \textbf{201}:107950.
-doi:\href{https://doi.org/10.1016/j.visres.2021.08.005}{10.1016/j.visres.2021.08.005}
-
-\leavevmode\hypertarget{ref-McDougal2008}{}%
-McDougal DH, Gamlin PD. 2008. Pupillary control pathways.The Senses: A Comprehensive Reference. Elsevier. pp. 521--536.
+45.
+M.
+Gheiratmand, T.
+S.
+Meese, K.
+T.
+Mullen, Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
+\emph{Journal of Vision} \textbf{13(1)}, 2 (2013).
 
 \leavevmode\hypertarget{ref-Meese2011}{}%
-Meese TS, Baker DH.
-2011.
-A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-\emph{iPerception} \textbf{2}:159--82.
-doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
-
-\leavevmode\hypertarget{ref-Meese2006}{}%
-Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
-
-\leavevmode\hypertarget{ref-Moradi2009}{}%
-Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}:13. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
-
-\leavevmode\hypertarget{ref-Norcia2015}{}%
-Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
-2015.
-The steady-state visual evoked potential in vision research: A review.
-\emph{J Vis} \textbf{15(6)}:4.
-doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
-
-\leavevmode\hypertarget{ref-Purves2008}{}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press.
-
-\leavevmode\hypertarget{ref-Quaia2018}{}%
-Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
-
-\leavevmode\hypertarget{ref-Schrodinger1926}{}%
-Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
-
-\leavevmode\hypertarget{ref-Spitschan2014}{}%
-Spitschan M, Jain S, Brainard DH, Aguirre GK.
-2014.
-Opponent melanopsin and s-cone signals in the human pupillary light response.
-\emph{Proc Natl Acad Sci U S A} \textbf{111}:15568--72.
-doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
-
-\leavevmode\hypertarget{ref-Tootell1988}{}%
-Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
-1988.
-Functional anatomy of macaque striate cortex.
-V.
-Spatial frequency.
-\emph{J Neurosci} \textbf{8}:1610--24.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{10.1523/JNEUROSCI.08-05-01610.1988}
-
-\leavevmode\hypertarget{ref-Tychsen2004}{}%
-Tychsen L, Wong AM-F, Burkhalter A.
-2004.
-Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
-\emph{The Journal of Comparative Neurology} \textbf{474}:261--275.
-doi:\href{https://doi.org/10.1002/cne.20113}{10.1002/cne.20113}
-
-\leavevmode\hypertarget{ref-Victor1991}{}%
-Victor JD, Mast J.
-1991.
-A new statistic for steady-state evoked potentials.
-\emph{Electroencephalogr Clin Neurophysiol} \textbf{78}:378--88.
-doi:\href{https://doi.org/10.1016/0013-4694(91)90099-p}{10.1016/0013-4694(91)90099-p}
-
-\leavevmode\hypertarget{ref-Wang2015}{}%
-Wang C-A, Munoz DP.
-2015.
-A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size.
-\emph{Curr Opin Neurobiol} \textbf{33}:134--40.
-doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}
-
-\leavevmode\hypertarget{ref-Wyatt1981}{}%
-Wyatt HJ, Musselman JF.
-1981.
-Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}:513--25.
-doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
+46.
+T.
+S.
+Meese, D.
+H.
+Baker, A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
+\emph{iPerception} \textbf{2}, 159--82 (2011).
 

### 2023-02-02 manuscriptPNAS.Rmd
Other edits

@@
 date: "Department of Psychology, University of York, UK"
-
 output:
@@
 ```
-Federico G. Segala
-**Email**: fgs502@york.ac.uk
+Federico G. Segala, email: fgs502@york.ac.uk
 
@@
 
-**Classification:** Biological Sciences - Neuroscience/Psychological and Cognitive Sciences
+**Classification:** Biological Sciences - Neuroscience
 
@@
 
+**This PDF includes**:
+
+  Main Text (Abstract, Significance Statement, Introduction, Methods, Results, Discussion, Conclusions, Acknowledgments)
+
+  Figures 1 to 6
+
+  Table 1
+
 # Abstract
 
-How does the brain combine information across the eyes?
-In primary visual cortex, spatial patterns are subject to 'ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
-Here we asked whether this invariance holds for pure changes in luminance.
-We collected steady-state EEG and pupillometry data simultaneously, and find strong deviations from ocularity invariance both in the cortex and also in the subcortical pathway that determines pupil diameter.
-In cortex, we find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas measurements of pupil diameter showed weaker facilitation and stronger suppression.
-This was not purely a consequence of the temporal stimulus parameters; pronounced binocular facilitation was also observed at faster flicker rates.
-Near-linear binocular combination was also found for the same stimuli using a perceptual matching task.
-A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data compared with the pupillometry results.
-These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+How does the human brain combine information across the eyes?
+It has been known for many years that cortical normalisation mechanisms implement ‘ocularity invariance’: equalising neural responses to spatial patterns presented either monocularly or binocularly.
+Here we used a novel combination of electrophysiology, psychophysics, pupillometry and computational modelling to ask whether this invariance also holds for flickering luminance stimuli with no spatial contrast.
+We find dramatic violations of ocularity invariance for these stimuli, both in cortex and also in the subcortical pathways that govern pupil diameter.
+Specifically, we find substantial binocular facilitation in both pathways with the effect being strongest in cortex.
+Near-linear binocular additivity (instead of ocularity invariance) was also found using a perceptual luminance matching task.
+Ocularity invariance is therefore not a ubiquitous feature of visual processing, and the brain appears to repurpose a generic normalisation algorithm for different visual functions by adjusting the amount of interocular suppression.
 
@@
 
-Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+Thirty (20 F, 10 M), twelve (7 F, 5 M) and ten (3 F, 7 M) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected-to-normal binocular vision, and gave written informed consent in accordance with the Declaration of Helsinki.
 Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
@@
 
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The stimuli were two monocularly presented discs of achromatic flickering light with a diameter of 3.74 degrees, displayed against a black background.
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \@ref(fig:pupildata)b for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+Four dark red lines were added around each monocular disc to help with their fusion into a single binocular disc (see insert in Fig.
+\@ref(fig:pupildata)b for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants perceived a single fused disc.
 The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
@@
 The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \@ref(fig:modelfigure).
+Because we used coherent averaging across participants for our steady-state data, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
+\@ref(fig:modelfigure).
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 
-The pupillometry results are summarised in Figure \@ref(fig:pupildata).
-The group average waveform for binocular presentation is shown in Figure \@ref(fig:pupildata)a.
+The pupillometry results for our first experiment are summarised in Fig.
+\@ref(fig:pupildata).
+The group average waveform for binocular presentation is shown in Fig.
+\@ref(fig:pupildata)a.
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Fig.
+\@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 
-Figure \@ref(fig:EEGdata) shows equivalent results, measured contemporaneously using EEG.
-Figure \@ref(fig:EEGdata)a shows the group average waveform for binocular presentation, and Figure \@ref(fig:EEGdata)b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (_Oz_, _POz_, _O1_ and _O2_, marked on the inset scalp plots).
+Fig.
+\@ref(fig:EEGdata) shows equivalent results, measured contemporaneously using EEG.
+Fig.
+\@ref(fig:EEGdata)a shows the group average waveform for binocular presentation, and Fig.
+\@ref(fig:EEGdata)b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (_Oz_, _POz_, _O1_ and _O2_, marked on the inset scalp plots).
 Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
-We therefore calculated contrast response functions at both first and second harmonic frequencies.
+We therefore derived contrast response functions at both first and second harmonic frequencies.
 
@@
 
-When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \@ref(fig:EEGdata)c) and second (Figure \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
-For the cross-frequency conditions (Figure \@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
-Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \@ref(fig:EEGdata)e) and 3.2Hz (Figure \@ref(fig:EEGdata)h).
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Fig.
+\@ref(fig:EEGdata)c) and second (Fig.
+\@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic (note that the absence of a main effect of condition is expected, given that there should be negligible differences between conditions at low contrasts, and any differences are therefore captured by the interaction term).
+For the cross-frequency conditions (Fig.
+\@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Fig.
+\@ref(fig:EEGdata)e) and 3.2Hz (Fig.
+\@ref(fig:EEGdata)h).
 This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
@@
 
-Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
 

### 2023-02-02 manuscriptPNAS.tex
Other edits

@@
 
-Federico G. Segala
-\textbf{Email}: \href{mailto:fgs502@york.ac.uk}{\nolinkurl{fgs502@york.ac.uk}}
+Federico G. Segala, email: \href{mailto:fgs502@york.ac.uk}{\nolinkurl{fgs502@york.ac.uk}}
 
@@
 
-\textbf{Classification:}
+\textbf{Classification:} Biological Sciences - Neuroscience
 
 \textbf{Keywords:} Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
+
+\textbf{This PDF includes}:
+
+Main Text (Abstract, Significance Statement, Introduction, Methods, Results, Discussion, Conclusions, Acknowledgments)
+
+Figures 1 to 6
+
+Table 1
 
@@
 
-How does the brain combine information across the eyes?
-In primary visual cortex, spatial patterns are subject to `ocularity invariance', where monocular and binocular responses are rendered equal by mutual suppression between the eyes.
-Here we asked whether this invariance holds for pure changes in luminance.
-We collected steady-state EEG and pupillometry data simultaneously, and find strong deviations from ocularity invariance both in the cortex and also in the subcortical pathway that determines pupil diameter.
-In cortex, we find strong binocular facilitation, and negligible interocular suppression from cortical sources, whereas measurements of pupil diameter showed weaker facilitation and stronger suppression.
-This was not purely a consequence of the temporal stimulus parameters; pronounced binocular facilitation was also observed at faster flicker rates.
-Near-linear binocular combination was also found for the same stimuli using a perceptual matching task.
-A hierarchical Bayesian implementation of a standard binocular combination model confirms that interocular suppression was substantially weaker for our EEG and matching data compared with the pupillometry results.
-These findings illustrate that ocularity invariance is not a ubiquitous feature of visual processing, and that the brain can repurpose a generic algorithm for different functions by adjusting parameters such as the weight of suppression between pathways.
+How does the human brain combine information across the eyes?
+It has been known for many years that cortical normalisation mechanisms implement `ocularity invariance': equalising neural responses to spatial patterns presented either monocularly or binocularly.
+Here we used a novel combination of electrophysiology, psychophysics, pupillometry and computational modelling to ask whether this invariance also holds for flickering luminance stimuli with no spatial contrast.
+We find dramatic violations of ocularity invariance for these stimuli, both in cortex and also in the subcortical pathways that govern pupil diameter.
+Specifically, we find substantial binocular facilitation in both pathways with the effect being strongest in cortex.
+Near-linear binocular additivity (instead of ocularity invariance) was also found using a perceptual luminance matching task.
+Ocularity invariance is therefore not a ubiquitous feature of visual processing, and the brain appears to repurpose a generic normalisation algorithm for different visual functions by adjusting the amount of interocular suppression.
+
+\hypertarget{significance-statement}{%
+\section{Significance Statement}\label{significance-statement}}
+
+Please note that it should not exceed 120 words, but should be at least 50 words in length.
 
@@
 However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (5) and much less is known about the computations that operate in these subcortical pathways.
-In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
+Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (6, 7).
+This is known as binocular summation(6, 7), with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2.
 This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (8, 9) and neural activity (1, 10) are approximately equal for monocular and binocular presentation.
@@
 Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (5, 14--16).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (17), yet the computation that achieves this is achieved is unclear.
+To account for the consensual response, these brain regions must combine information from the left and right eyes (17), yet the computation that achieves this is unclear.
 
@@
 
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The stimuli were two monocularly presented discs of achromatic flickering light with a diameter of 3.74 degrees, displayed against a black background.
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \ref{fig:pupildata}b for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+Four dark red lines were added around each monocular disc to help with their fusion into a single binocular disc (see insert in Fig.
+\ref{fig:pupildata}b for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants perceived a single fused disc.
 The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
@@
 
-All stimuli had a mean luminance of 42 cd/m\(^2\) on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
-For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
-For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+All stimuli had a mean luminance of 42 cd/m\(^2\), and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
+All stimuli were presented using Psychopy (20) (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
 
-EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; (20)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany (21)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (21).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (22).
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (22).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by (22).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of (23) that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (23).
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described previously (23).
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic (24) that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (20), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (21), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (19).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (24, 25).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (26).
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (25, 26).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (27).
 
@@
 
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by (9).
-The second gain control stage was omitted (1) to simplify the model and reduce the number of free parameters.
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.~(9).
+The second gain control stage was omitted, consistent with previous work (1), to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 
-Despite being derived from the model proposed by (9), the simplifications applied to this architecture make it very similar to other models (8, 11, 17, 27).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (28, 29).
+Despite being derived from the model proposed by Meese et al.~(9), the simplifications applied to this architecture make it very similar to other models (8, 11, 17, 28).
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (29, 30).
 Our key parameter of interest is the weight of interocular suppression.
 Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (1).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (30).
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (31).
 
-We implemented the model within a Bayesian framework using the Stan software (31).
+We implemented the model within a Bayesian framework using the Stan software (32).
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (9, 28).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (9, 29).
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
 The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \ref{fig:modelfigure}.
+Because we used coherent averaging across participants for our steady-state data, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
+\ref{fig:modelfigure}.
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 
-The pupillometry results are summarised in Figure \ref{fig:pupildata}.
-The group average waveform for binocular presentation is shown in Figure \ref{fig:pupildata}a.
+The pupillometry results for our first experiment are summarised in Fig.
+\ref{fig:pupildata}.
+The group average waveform for binocular presentation is shown in Fig.
+\ref{fig:pupildata}a.
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Fig.
+\ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 
-Figure \ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
+Fig.
+\ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
 Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (22) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (23) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
 The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
 
-In Figure \ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \ref{fig:pupildata}c for comparison).
+In Fig.
+\ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Fig.
+\ref{fig:pupildata}c for comparison).
 When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
@@
 
-Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Fig.
+\ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
 Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
@@
 
-Figure \ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
-Figure \ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Figure \ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
+Fig.
+\ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
+Fig.
+\ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Fig.
+\ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
 Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
-We therefore calculated contrast response functions at both first and second harmonic frequencies.
+We therefore derived contrast response functions at both first and second harmonic frequencies.
 
@@
 
-When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
-For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
-Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \ref{fig:EEGdata}e) and 3.2Hz (Figure \ref{fig:EEGdata}h).
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Fig.
+\ref{fig:EEGdata}c) and second (Fig.
+\ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic (note that the absence of a main effect of condition is expected, given that there should be negligible differences between conditions at low contrasts, and any differences are therefore captured by the interaction term).
+For the cross-frequency conditions (Fig.
+\ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Fig.
+\ref{fig:EEGdata}e) and 3.2Hz (Fig.
+\ref{fig:EEGdata}h).
 This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
@@
 Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
-Figure \ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
+Fig.
+\ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
 At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
-Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Fig.
+\ref{fig:pupildata} and \ref{fig:EEGdata}.
 A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
@@
 
-Results from the temporal frequency experiment are shown in Figure \ref{fig:TFdata}.
-Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+Results from the temporal frequency experiment are shown in Fig.
+\ref{fig:TFdata}.
+Fig.
+\ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
 From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
 However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
-Figure \ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
+Fig.
+\ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
 Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (32--34).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (33--35).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 
-The results from the matching experiment are shown in Figure \ref{fig:matchingdata}.
+The results from the matching experiment are shown in Fig.
+\ref{fig:matchingdata}.
 Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
@@
 The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
-Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \ref{fig:EEGdata}c,f).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Fig.
+\ref{fig:EEGdata}c,f).
 
@@
 We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \ref{fig:modelfigure}e-h, with empirical data replotted in Figure \ref{fig:modelfigure}a-d for comparison.
+The model behaviour is displayed in Fig.
+\ref{fig:modelfigure}e-h, with empirical data replotted in Fig.
+\ref{fig:modelfigure}a-d for comparison.
 In general, the model captures the key characteristics of the empirical data.
@@
 We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}i).
+We therefore plot the posterior distributions for this parameter for all four data sets (see Fig.
+\ref{fig:modelfigure}i).
 The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
@@
 All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (1, 9), and the peak location of our prior distribution (black curve).
-These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and significant dichoptic masking observed using that method.
 The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (1, 9, 10).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (1, 9, 10).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
 However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, (34) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and (35) report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (30).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (28, 32, 33), though not for luminance decrements (32).
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+For example, Quaia et al.@Quaia2018 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and \href{mailto:Cajochen@Spitschan2019}{\nolinkurl{Cajochen@Spitschan2019}} report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (31).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (29, 33, 34), though not for luminance decrements (33).
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination.
 
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-(1) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (2).
+We \href{mailto:previously@Baker2017}{\nolinkurl{previously@Baker2017}} pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also (2)).
 This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (36, 37).
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or are otherwise phylogenetically older than binocular pattern vision.
 Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
@@
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but intend to investigate this directly in future neuroimaging work.
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (39, 40) are biased towards low spatial frequencies (41, 42), and relatively insensitive to stimulus orientation (39, 40, 43).
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (39, 40) are biased towards low spatial frequencies (41, 42), and relatively insensitive to stimulus orientation (39, 40) (though see (43)).
 As the blob regions are embedded within ocular dominance columns (39), they are also largely monocular (40, 44).
@@
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
-Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
-However our matching data (Figure \ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Fig.
+\ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
+However our matching data (Fig.
+\ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
 
@@
 
+\leavevmode\hypertarget{ref-Peirce2019}{}%
+20. J. Peirce\emph{et al.}, PsychoPy2: Experiments in behavior made easy. \emph{Behav Res Methods} \textbf{51}, 195--203 (2019).
+
 \leavevmode\hypertarget{ref-Kassner2014}{}%
-20.
+21.
 M.
@@
 \leavevmode\hypertarget{ref-Delorme2004}{}%
-21. A. Delorme, S. Makeig, EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).
+22. A. Delorme, S. Makeig, EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).
 
 \leavevmode\hypertarget{ref-Baker2021}{}%
-22. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
+23. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
 
 \leavevmode\hypertarget{ref-Victor1991}{}%
-23. J. D. Victor, J. Mast, A new statistic for steady-state evoked potentials. \emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).
+24. J. D. Victor, J. Mast, A new statistic for steady-state evoked potentials. \emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).
 
 \leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-24. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).
+25. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).
 
 \leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-25. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{J Vis} \textbf{16(11)}, 29 (2016).
+26. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{J Vis} \textbf{16(11)}, 29 (2016).
 
 \leavevmode\hypertarget{ref-Figueira2022}{}%
-26.
+27.
 J.
@@
 \leavevmode\hypertarget{ref-Schrodinger1926}{}%
-27. E. Schrödinger, ``Die gesichtsempfindungen.'' in \emph{Mueller-Pouillets Lehrbuch Der Physik (11th Ed.)}, (Vieweg: Braunschweig, 1926), pp. 456--560.
+28. E. Schrödinger, ``Die gesichtsempfindungen.'' in \emph{Mueller-Pouillets Lehrbuch Der Physik (11th Ed.)}, (Vieweg: Braunschweig, 1926), pp. 456--560.
 
 \leavevmode\hypertarget{ref-Baker2012}{}%
-28. D. H. Baker, S. A. Wallis, M. A. Georgeson, T. S. Meese, Nonlinearities in the binocular combination of luminance and contrast. \emph{Vision Res} \textbf{56}, 1--9 (2012).
+29. D. H. Baker, S. A. Wallis, M. A. Georgeson, T. S. Meese, Nonlinearities in the binocular combination of luminance and contrast. \emph{Vision Res} \textbf{56}, 1--9 (2012).
 
 \leavevmode\hypertarget{ref-Kingdom2015}{}%
-29. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15(5)}, 2 (2015).
+30. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15(5)}, 2 (2015).
 
 \leavevmode\hypertarget{ref-Baker2020}{}%
-30. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
+31. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
 
 \leavevmode\hypertarget{ref-Carpenter2017}{}%
-31. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).
+32. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).
 
 \leavevmode\hypertarget{ref-Anstis1998}{}%
-32. S. Anstis, A. Ho, Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}, 523--39 (1998).
+33. S. Anstis, A. Ho, Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}, 523--39 (1998).
 
 \leavevmode\hypertarget{ref-Levelt1965}{}%
-33. W. J. Levelt, Binocular brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).
+34. W. J. Levelt, Binocular brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).
 
 \leavevmode\hypertarget{ref-Quaia2018}{}%
-34. C. Quaia, L. M. Optican, B. G. Cumming, Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}, 7 (2018).
-
-\leavevmode\hypertarget{ref-Spitschan2019}{}%
-35. M. Spitschan, C. Cajochen, Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}, e12602 (2019).
+35. C. Quaia, L. M. Optican, B. G. Cumming, Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}, 7 (2018).
 

### 2023-02-03 manuscriptPLOSBIO.Rmd
Started formatting for PLOS Biology

--- 2023-02-02 manuscriptPNAS.Rmd
@@
 title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
+short title: "Binocular combination of flickering light"
 author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
 date: "Department of Psychology, University of York, UK"
+header-includes: \usepackage{setspace}\doublespacing
 output:
@@
 bibliography: references.bib
-csl: pnas.csl
+csl: plos-biology.csl
 ---
@@
 **Keywords:** Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
-
-**This PDF includes**:
-
-  Main Text (Abstract, Significance Statement, Introduction, Methods, Results, Discussion, Conclusions, Acknowledgments)
-
-  Figures 1 to 6
-
-  Table 1
+\newpage
 

### 2023-02-03 manuscriptPLOSBIO.tex
Started formatting for PLOS Biology

--- 2023-02-02 manuscriptPNAS.tex
@@
 \setcounter{secnumdepth}{5}
+\usepackage{setspace}\doublespacing
 
@@
 
-\textbf{This PDF includes}:
-
-Main Text (Abstract, Significance Statement, Introduction, Methods, Results, Discussion, Conclusions, Acknowledgments)
-
-Figures 1 to 6
-
-Table 1
-
 \hypertarget{abstract}{%
@@
 The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
-This involves a process of signal combination both within (1) and between (2) the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (3).
-Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (4).
-However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (5) and much less is known about the computations that operate in these subcortical pathways.
+This involves a process of signal combination both within {[}1{]} and between {[}2{]} the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established {[}3{]}.
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) {[}4{]}.
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels {[}5{]} and much less is known about the computations that operate in these subcortical pathways.
 Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
@@
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation(6, 7), with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2.
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (8, 9) and neural activity (1, 10) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (9, 11) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance' (12): perceived contrast does not change when one eye is opened and closed.
+This is known as binocular summation{[}6,7{]}, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2.
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) {[}8,9{]} and neural activity {[}1,10{]} are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision {[}9,11{]} advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance' {[}12{]}: perceived contrast does not change when one eye is opened and closed.
 
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (5).
-There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; (13)).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (5, 14--16).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (17), yet the computation that achieves this is unclear.
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink {[}5{]}.
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; {[}13{]}).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus {[}5,14--16{]}.
+To account for the consensual response, these brain regions must combine information from the left and right eyes {[}17{]}, yet the computation that achieves this is unclear.
 
@@
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Periodic flicker entrains both neural (18) and pupil (19) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Periodic flicker entrains both neural {[}18{]} and pupil {[}19{]} responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
@@
 All stimuli had a mean luminance of 42 cd/m\(^2\), and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
-All stimuli were presented using Psychopy (20) (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
+All stimuli were presented using Psychopy {[}20{]} (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
 
 EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany (21)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany {[}21{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (22).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox {[}22{]}.
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (23).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described previously (23).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic (24) that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}23{]}.
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described previously {[}23{]}.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic {[}24{]} that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (21), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}21{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (19).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (25, 26).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (27).
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis {[}19{]}.
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies {[}25,26{]}.
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis {[}27{]}.
 
@@
 
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.~(9).
-The second gain control stage was omitted, consistent with previous work (1), to simplify the model and reduce the number of free parameters.
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.~{[}9{]}.
+The second gain control stage was omitted, consistent with previous work {[}1{]}, to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 
-Despite being derived from the model proposed by Meese et al.~(9), the simplifications applied to this architecture make it very similar to other models (8, 11, 17, 28).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (29, 30).
+Despite being derived from the model proposed by Meese et al.~{[}9{]}, the simplifications applied to this architecture make it very similar to other models {[}8,11,17,28{]}.
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression {[}29,30{]}.
 Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (1).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (31).
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli {[}1{]}.
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation {[}31{]}.
 
-We implemented the model within a Bayesian framework using the Stan software (32).
+We implemented the model within a Bayesian framework using the Stan software {[}32{]}.
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (9, 29).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature {[}9,29{]}.
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (23) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) {[}23{]} comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
 The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
@@
 
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (1).
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli {[}1{]}.
 One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (19); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz {[}19{]}; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (33--35).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms {[}33--35{]}.
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (1, 9), and the peak location of our prior distribution (black curve).
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict {[}1,9{]}, and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and significant dichoptic masking observed using that method.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (1, 9, 10).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts {[}1,9,10{]}.
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
@@
 For example, Quaia et al.@Quaia2018 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and \href{mailto:Cajochen@Spitschan2019}{\nolinkurl{Cajochen@Spitschan2019}} report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (31).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (29, 33, 34), though not for luminance decrements (33).
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm {[}31{]}.
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments {[}29,33,34{]}, though not for luminance decrements {[}33{]}.
 Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination.
@@
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-We \href{mailto:previously@Baker2017}{\nolinkurl{previously@Baker2017}} pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also (2)).
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (36, 37).
+We \href{mailto:previously@Baker2017}{\nolinkurl{previously@Baker2017}} pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also {[}2{]}).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction {[}36,37{]}.
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (19).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (38).
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter {[}19{]}.
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms {[}38{]}.
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
@@
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (39, 40) are biased towards low spatial frequencies (41, 42), and relatively insensitive to stimulus orientation (39, 40) (though see (43)).
-As the blob regions are embedded within ocular dominance columns (39), they are also largely monocular (40, 44).
-More recent work has reported psychophysical evidence for unoriented chromatic (45) and achromatic (46) mechanisms, that also appear to be monocular.
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' {[}39,40{]} are biased towards low spatial frequencies {[}41,42{]}, and relatively insensitive to stimulus orientation {[}39,40{]} (though see {[}43{]}).
+As the blob regions are embedded within ocular dominance columns {[}39{]}, they are also largely monocular {[}40,44{]}.
+More recent work has reported psychophysical evidence for unoriented chromatic {[}45{]} and achromatic {[}46{]} mechanisms, that also appear to be monocular.
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
@@
 \leavevmode\hypertarget{ref-Baker2017}{}%
-1. D. H. Baker, A. R. Wade, Evidence for an optimal algorithm underlying signal combination in human visual cortex. \emph{Cereb Cortex} \textbf{27}, 254--264 (2017).
+1.
+Baker DH, Wade AR.
+Evidence for an optimal algorithm underlying signal combination in human visual cortex.
+Cereb Cortex.
+2017;27: 254--264.
+doi:\href{https://doi.org/10.1093/cercor/bhw395}{10.1093/cercor/bhw395}
 
 \leavevmode\hypertarget{ref-Ernst2002}{}%
-2. M. O. Ernst, M. S. Banks, Humans integrate visual and haptic information in a statistically optimal fashion. \emph{Nature} \textbf{415}, 429--33 (2002).
+2. Ernst MO, Banks MS. Humans integrate visual and haptic information in a statistically optimal fashion. Nature. 2002;415: 429--33. doi:\href{https://doi.org/10.1038/415429a}{10.1038/415429a}
 
 \leavevmode\hypertarget{ref-Hubel1962}{}%
-3. D. H. Hubel, T. N. Wiesel, Receptive fields, binocular interaction and functional architecture in the cat's visual cortex. \emph{J Physiol} \textbf{160}, 106--54 (1962).
+3.
+Hubel DH, Wiesel TN.
+Receptive fields, binocular interaction and functional architecture in the cat's visual cortex.
+J Physiol.
+1962;160: 106--54.
+doi:\href{https://doi.org/10.1113/jphysiol.1962.sp006837}{10.1113/jphysiol.1962.sp006837}
 
 \leavevmode\hypertarget{ref-Purves2008}{}%
-4. D. Purves\emph{et al.}, \emph{Principles of Cognitive Neuroscience} (Oxford University Press, 2008).
+4. Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, et al. Principles of Cognitive Neuroscience. Oxford University Press; 2008.
 
 \leavevmode\hypertarget{ref-McDougal2008}{}%
-5. D. H. McDougal, P. D. Gamlin, ``Pupillary control pathways.'' in \emph{The Senses: A Comprehensive Reference}, (Elsevier, 2008), pp. 521--536.
+5. McDougal DH, Gamlin PD. Pupillary control pathways. The senses: A comprehensive reference. Elsevier; 2008. pp. 521--536.
 
 \leavevmode\hypertarget{ref-Campbell1965}{}%
-6. F. W. Campbell, D. G. Green, Monocular versus binocular visual acuity. \emph{Nature} \textbf{208}, 191--2 (1965).
+6. Campbell FW, Green DG. Monocular versus binocular visual acuity. Nature. 1965;208: 191--2. doi:\href{https://doi.org/10.1038/208191a0}{10.1038/208191a0}
 
 \leavevmode\hypertarget{ref-Baker2018}{}%
-7. D. H. Baker, F. A. Lygo, T. S. Meese, M. A. Georgeson, Binocular summation revisited: Beyond \(\sqrt{2}\). \emph{Psychol Bull} \textbf{144}, 1186--1199 (2018).
+7. Baker DH, Lygo FA, Meese TS, Georgeson MA. Binocular summation revisited: Beyond \(\sqrt{2}\). Psychol Bull. 2018;144: 1186--1199. doi:\href{https://doi.org/10.1037/bul0000163}{10.1037/bul0000163}
 
 \leavevmode\hypertarget{ref-Legge1984}{}%
-8. G. E. Legge, Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}, 385--94 (1984).
+8. Legge GE. Binocular contrast summation--ii. Quadratic summation. Vision Res. 1984;24: 385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
 
 \leavevmode\hypertarget{ref-Meese2006}{}%
-9. T. S. Meese, M. A. Georgeson, D. H. Baker, Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}, 1224--43 (2006).
+9. Meese TS, Georgeson MA, Baker DH. Binocular contrast vision at and above threshold. J Vis. 2006;6: 1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
 \leavevmode\hypertarget{ref-Moradi2009}{}%
-10. F. Moradi, D. J. Heeger, Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}, 13 (2009).
+10. Moradi F, Heeger DJ. Inter-ocular contrast normalization in human visual cortex. J Vis. 2009;9(3): 13. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
 \leavevmode\hypertarget{ref-Ding2006}{}%
-11. J. Ding, G. Sperling, A gain-control theory of binocular combination. \emph{Proc Natl Acad Sci U S A} \textbf{103}, 1141--6 (2006).
+11. Ding J, Sperling G. A gain-control theory of binocular combination. Proc Natl Acad Sci U S A. 2006;103: 1141--6. doi:\href{https://doi.org/10.1073/pnas.0509629103}{10.1073/pnas.0509629103}
 
 \leavevmode\hypertarget{ref-Baker2007}{}%
-12. D. H. Baker, T. S. Meese, M. A. Georgeson, Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model. \emph{Spat Vis} \textbf{20}, 397--413 (2007).
+12.
+Baker DH, Meese TS, Georgeson MA.
+Binocular interaction: Contrast matching and contrast discrimination are predicted by the same model.
+Spat Vis.
+2007;20: 397--413.
+doi:\href{https://doi.org/10.1163/156856807781503622}{10.1163/156856807781503622}
 
@@
 13.
-H.
-J.
-Wyatt, J.
-F.
-Musselman, Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
-\emph{Vision Res} \textbf{21}, 513--25 (1981).
+Wyatt HJ, Musselman JF.
+Pupillary light reflex in humans: Evidence for an unbalanced pathway from nasal retina, and for signal cancellation in brainstem.
+Vision Res.
+1981;21: 513--25.
+doi:\href{https://doi.org/10.1016/0042-6989(81)90097-3}{10.1016/0042-6989(81)90097-3}
 
 \leavevmode\hypertarget{ref-Angee2021}{}%
-14. C. Angée, B. Nedelec, E. Erjavec, J.-M. Rozet, L. Fares Taie, Congenital microcoria: Clinical features and molecular genetics. \emph{Genes (Basel)} \textbf{12} (2021).
+14.
+Angée C, Nedelec B, Erjavec E, Rozet J-M, Fares Taie L.
+Congenital microcoria: Clinical features and molecular genetics.
+Genes (Basel).
+2021;12.
+doi:\href{https://doi.org/10.3390/genes12050624}{10.3390/genes12050624}
 
 \leavevmode\hypertarget{ref-Mathot2018}{}%
-15. S. Mathôt, Pupillometry: Psychology, physiology, and function. \emph{J Cogn} \textbf{1}, 16 (2018).
+15. Mathôt S. Pupillometry: Psychology, physiology, and function. J Cogn. 2018;1: 16. doi:\href{https://doi.org/10.5334/joc.18}{10.5334/joc.18}
 
 \leavevmode\hypertarget{ref-Wang2015}{}%
-16. C.-A. Wang, D. P. Munoz, A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size. \emph{Curr Opin Neurobiol} \textbf{33}, 134--40 (2015).
+16.
+Wang C-A, Munoz DP.
+A circuit for pupil orienting responses: Implications for cognitive modulation of pupil size.
+Curr Opin Neurobiol.
+2015;33: 134--40.
+doi:\href{https://doi.org/10.1016/j.conb.2015.03.018}{10.1016/j.conb.2015.03.018}
 
 \leavevmode\hypertarget{ref-Doesschate1967}{}%
-17. J. ten Doesschate, M. Alpern, Effect of photoexcitation of the two retinas on pupil size. \emph{J Neurophysiol} \textbf{30}, 562--76 (1967).
+17.
+Doesschate J ten, Alpern M.
+Effect of photoexcitation of the two retinas on pupil size.
+J Neurophysiol.
+1967;30: 562--76.
+doi:\href{https://doi.org/10.1152/jn.1967.30.3.562}{10.1152/jn.1967.30.3.562}
 
 \leavevmode\hypertarget{ref-Norcia2015}{}%
-18. A. M. Norcia, L. G. Appelbaum, J. M. Ales, B. R. Cottereau, B. Rossion, The steady-state visual evoked potential in vision research: A review. \emph{J Vis} \textbf{15(6)}, 4 (2015).
+18.
+Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
+The steady-state visual evoked potential in vision research: A review.
+J Vis.
+2015;15(6): 4.
+doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
 
 \leavevmode\hypertarget{ref-Spitschan2014}{}%
-19. M. Spitschan, S. Jain, D. H. Brainard, G. K. Aguirre, Opponent melanopsin and s-cone signals in the human pupillary light response. \emph{Proc Natl Acad Sci U S A} \textbf{111}, 15568--72 (2014).
+19.
+Spitschan M, Jain S, Brainard DH, Aguirre GK.
+Opponent melanopsin and s-cone signals in the human pupillary light response.
+Proc Natl Acad Sci U S A.
+2014;111: 15568--72.
+doi:\href{https://doi.org/10.1073/pnas.1400942111}{10.1073/pnas.1400942111}
 
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-20. J. Peirce\emph{et al.}, PsychoPy2: Experiments in behavior made easy. \emph{Behav Res Methods} \textbf{51}, 195--203 (2019).
+20.
+Peirce J, Gray JR, Simpson S, MacAskill M, Höchenberger R, Sogo H, et al.
+PsychoPy2: Experiments in behavior made easy.
+Behav Res Methods.
+2019;51: 195--203.
+doi:\href{https://doi.org/10.3758/s13428-018-01193-y}{10.3758/s13428-018-01193-y}
 
@@
 21.
-M.
-Kassner, W.
-Patera, A.
-Bulling, Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
-in \emph{Proceedings of the 2014 ACM International Joint Conference on Pervasive and Ubiquitous Computing: Adjunct Publication}, (UbiComp '14 Adjunct; ACM, 2014), pp.
+Kassner M, Patera W, Bulling A.
+Pupil: An open source platform for pervasive eye tracking and mobile gaze-based interaction.
+Proceedings of the 2014 ACM international joint conference on pervasive and ubiquitous computing: Adjunct publication.
+UbiComp '14 Adjunct; ACM; 2014.
+pp.
 1151--1160.
+doi:\href{https://doi.org/10.1145/2638728.2641695}{10.1145/2638728.2641695}
 
 \leavevmode\hypertarget{ref-Delorme2004}{}%
-22. A. Delorme, S. Makeig, EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}, 9--21 (2004).
+22.
+Delorme A, Makeig S.
+EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
+J Neurosci Methods.
+2004;134: 9--21.
+doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}
 
 \leavevmode\hypertarget{ref-Baker2021}{}%
-23. D. H. Baker, Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5} (2021).
+23. Baker DH. Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory. 2021;5. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
 
 \leavevmode\hypertarget{ref-Victor1991}{}%
-24. J. D. Victor, J. Mast, A new statistic for steady-state evoked potentials. \emph{Electroencephalogr Clin Neurophysiol} \textbf{78}, 378--88 (1991).
+24.
+Victor JD, Mast J.
+A new statistic for steady-state evoked potentials.
+Electroencephalogr Clin Neurophysiol.
+1991;78: 378--88.
+doi:\href{https://doi.org/10.1016/0013-4694(91)90099-p}{10.1016/0013-4694(91)90099-p}
 
 \leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-25. P. A. Barrionuevo\emph{et al.}, Assessing rod, cone, and melanopsin contributions to human pupil flicker responses. \emph{Invest Ophthalmol Vis Sci} \textbf{55}, 719--27 (2014).
+25.
+Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
+Assessing rod, cone, and melanopsin contributions to human pupil flicker responses.
+Invest Ophthalmol Vis Sci.
+2014;55: 719--27.
+doi:\href{https://doi.org/10.1167/iovs.13-13252}{10.1167/iovs.13-13252}
 
 \leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-26. P. A. Barrionuevo, D. Cao, Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response. \emph{J Vis} \textbf{16(11)}, 29 (2016).
+26.
+Barrionuevo PA, Cao D.
+Luminance and chromatic signals interact differently with melanopsin activation to control the pupil light response.
+J Vis.
+2016;16(11): 29.
+doi:\href{https://doi.org/10.1167/16.11.29}{10.1167/16.11.29}
 
@@
 27.
-J.
-S.
-B.
-Figueira, E.
-Kutlu, L.
-S.
-Scott, A.
-Keil, The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
-\emph{Dev Cogn Neurosci} \textbf{54}, 101066 (2022).
+Figueira JSB, Kutlu E, Scott LS, Keil A.
+The freqtag toolbox: A principled approach to analyzing electrophysiological time series in frequency tagging paradigms.
+Dev Cogn Neurosci.
+2022;54: 101066.
+doi:\href{https://doi.org/10.1016/j.dcn.2022.101066}{10.1016/j.dcn.2022.101066}
 
 \leavevmode\hypertarget{ref-Schrodinger1926}{}%
-28. E. Schrödinger, ``Die gesichtsempfindungen.'' in \emph{Mueller-Pouillets Lehrbuch Der Physik (11th Ed.)}, (Vieweg: Braunschweig, 1926), pp. 456--560.
+28. Schrödinger E. Die gesichtsempfindungen. Mueller-pouillets lehrbuch der physik (11th ed). Vieweg: Braunschweig; 1926. pp. 456--560.
 
 \leavevmode\hypertarget{ref-Baker2012}{}%
-29. D. H. Baker, S. A. Wallis, M. A. Georgeson, T. S. Meese, Nonlinearities in the binocular combination of luminance and contrast. \emph{Vision Res} \textbf{56}, 1--9 (2012).
+29.
+Baker DH, Wallis SA, Georgeson MA, Meese TS.
+Nonlinearities in the binocular combination of luminance and contrast.
+Vision Res.
+2012;56: 1--9.
+doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
 
 \leavevmode\hypertarget{ref-Kingdom2015}{}%
-30. F. A. A. Kingdom, L. Libenson, Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging. \emph{J Vis} \textbf{15(5)}, 2 (2015).
+30.
+Kingdom FAA, Libenson L.
+Dichoptic color saturation mixture: Binocular luminance contrast promotes perceptual averaging.
+J Vis.
+2015;15(5): 2.
+doi:\href{https://doi.org/10.1167/15.5.2}{10.1167/15.5.2}
 
 \leavevmode\hypertarget{ref-Baker2020}{}%
-31. D. H. Baker\emph{et al.}, Binaural summation of amplitude modulation involves weak interaural suppression. \emph{Sci Rep} \textbf{10}, 3560 (2020).
+31.
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+Binaural summation of amplitude modulation involves weak interaural suppression.
+Sci Rep.
+2020;10: 3560.
+doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
 
 \leavevmode\hypertarget{ref-Carpenter2017}{}%
-32. B. Carpenter\emph{et al.}, Stan: A probabilistic programming language. \emph{Journal of Statistical Software} \textbf{76}, 1--32 (2017).
+32.
+Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, et al.
+Stan: A probabilistic programming language.
+Journal of Statistical Software.
+2017;76: 1--32.
+doi:\href{https://doi.org/10.18637/jss.v076.i01}{10.18637/jss.v076.i01}
 
 \leavevmode\hypertarget{ref-Anstis1998}{}%
-33. S. Anstis, A. Ho, Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion. \emph{Vision Res} \textbf{38}, 523--39 (1998).
+33.
+Anstis S, Ho A.
+Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
+Vision Res.
+1998;38: 523--39.
+doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
 
 \leavevmode\hypertarget{ref-Levelt1965}{}%
-34. W. J. Levelt, Binocular brightness averaging and contour information. \emph{Br J Psychol} \textbf{56}, 1--13 (1965).
+34. Levelt WJ. Binocular brightness averaging and contour information. Br J Psychol. 1965;56: 1--13. doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}
 
 \leavevmode\hypertarget{ref-Quaia2018}{}%
-35. C. Quaia, L. M. Optican, B. G. Cumming, Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}, 7 (2018).
+35. Quaia C, Optican LM, Cumming BG. Binocular summation for reflexive eye movements. J Vis. 2018;18(4): 7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
 
 \leavevmode\hypertarget{ref-Li1994}{}%
-36. Z. Li, J. J. Atick, Efficient stereo coding in the multiscale representation. \emph{Network: Computation in Neural Systems} \textbf{5}, 157--174 (1994).
+36.
+Li Z, Atick JJ.
+Efficient stereo coding in the multiscale representation.
+Network: Computation in Neural Systems.
+1994;5: 157--174.
+doi:\href{https://doi.org/10.1088/0954-898X_5_2_003}{10.1088/0954-898X\_5\_2\_003}
 
 \leavevmode\hypertarget{ref-May2022}{}%
-37. K. May, L. Zhaoping, Li and Atick's theory of efficient binocular coding: A tutorial and mini-review. \emph{Vision Res} \textbf{201}, 107950 (2022).
+37.
+May K, Zhaoping L.
+Li and Atick's theory of efficient binocular coding: A tutorial and mini-review.
+Vision Res.
+2022;201: 107950.
+doi:\href{https://doi.org/10.1016/j.visres.2021.08.005}{10.1016/j.visres.2021.08.005}
 
 \leavevmode\hypertarget{ref-Bradley2008}{}%
-38. M. M. Bradley, L. Miccoli, M. A. Escrig, P. J. Lang, The pupil as a measure of emotional arousal and autonomic activation. \emph{Psychophysiology} \textbf{45}, 602--7 (2008).
+38.
+Bradley MM, Miccoli L, Escrig MA, Lang PJ.
+The pupil as a measure of emotional arousal and autonomic activation.
+Psychophysiology.
+2008;45: 602--7.
+doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
 
 \leavevmode\hypertarget{ref-Horton1981}{}%
-39. J. C. Horton, D. H. Hubel, Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey. \emph{Nature} \textbf{292}, 762--4 (1981).
+39.
+Horton JC, Hubel DH.
+Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
+Nature.
+1981;292: 762--4.
+doi:\href{https://doi.org/10.1038/292762a0}{10.1038/292762a0}
 
 \leavevmode\hypertarget{ref-Livingstone1984}{}%
-40. M. S. Livingstone, D. H. Hubel, Anatomy and physiology of a color system in the primate visual cortex. \emph{J Neurosci} \textbf{4}, 309--56 (1984).
+40.
+Livingstone MS, Hubel DH.
+Anatomy and physiology of a color system in the primate visual cortex.
+J Neurosci.
+1984;4: 309--56.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{10.1523/JNEUROSCI.04-01-00309.1984}
 
 \leavevmode\hypertarget{ref-Tootell1988}{}%
-41. R. B. Tootell, M. S. Silverman, S. L. Hamilton, E. Switkes, R. L. De Valois, Functional anatomy of macaque striate cortex. V. Spatial frequency. \emph{J Neurosci} \textbf{8}, 1610--24 (1988).
+41.
+Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
+Functional anatomy of macaque striate cortex.
+V.
+Spatial frequency.
+J Neurosci.
+1988;8: 1610--24.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{10.1523/JNEUROSCI.08-05-01610.1988}
 
@@
 42.
-D.
-P.
-Edwards, K.
-P.
-Purpura, E.
-Kaplan, Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
-\emph{Vision Res} \textbf{35}, 1501--23 (1995).
+Edwards DP, Purpura KP, Kaplan E.
+Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
+Vision Res.
+1995;35: 1501--23.
+doi:\href{https://doi.org/10.1016/0042-6989(94)00253-i}{10.1016/0042-6989(94)00253-i}
 
 \leavevmode\hypertarget{ref-Economides2011}{}%
-43. J. R. Economides, L. C. Sincich, D. L. Adams, J. C. Horton, Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex. \emph{Nat Neurosci} \textbf{14}, 1574--80 (2011).
+43.
+Economides JR, Sincich LC, Adams DL, Horton JC.
+Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
+Nat Neurosci.
+2011;14: 1574--80.
+doi:\href{https://doi.org/10.1038/nn.2958}{10.1038/nn.2958}
 
@@
 44.
-L.
-Tychsen, A.
-M.-F.
-Wong, A.
-Burkhalter, Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
-\emph{The Journal of Comparative Neurology} \textbf{474}, 261--275 (2004).
+Tychsen L, Wong AM-F, Burkhalter A.
+Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
+The Journal of Comparative Neurology.
+2004;474: 261--275.
+doi:\href{https://doi.org/10.1002/cne.20113}{10.1002/cne.20113}
 
@@
 45.
-M.
-Gheiratmand, T.
-S.
-Meese, K.
-T.
-Mullen, Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
-\emph{Journal of Vision} \textbf{13(1)}, 2 (2013).
+Gheiratmand M, Meese TS, Mullen KT.
+Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
+Journal of Vision.
+2013;13(1): 2.
+doi:\href{https://doi.org/10.1167/13.1.2}{10.1167/13.1.2}
 
@@
 46.
-T.
-S.
-Meese, D.
-H.
-Baker, A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-\emph{iPerception} \textbf{2}, 159--82 (2011).
+Meese TS, Baker DH.
+A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
+iPerception.
+2011;2: 159--82.
+doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
 

### 2023-02-08 manuscriptPLOSBIO.Rmd
Edited for PLOS Biology

--- 2023-02-02 manuscriptPNAS.Rmd
@@
 date: "Department of Psychology, University of York, UK"
+header-includes: 
+  - \usepackage{setspace}\doublespacing
+  - \usepackage{lineno}\linenumbers
 output:
@@
 ```
-Federico G. Segala, email: fgs502@york.ac.uk
-
-**Author contributions: Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
-**Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
-**Myat Aung**: Software, resources, writing - review & editing.
-**Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
-**Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
-
-**Competing interest declaration:** The authors declare no competing interests.
-
-**Classification:** Biological Sciences - Neuroscience
-
-**Keywords:** Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
-
-**This PDF includes**:
-
-  Main Text (Abstract, Significance Statement, Introduction, Methods, Results, Discussion, Conclusions, Acknowledgments)
-
-  Figures 1 to 6
-
-  Table 1
+**Short title**: "Binocular combination of flickering light"
+
+**Corresponding author**: Federico G. Segala, email: fgs502@york.ac.uk
+\newpage
 
@@
 
-# Significance Statement
-Please note that it should not exceed 120 words, but should be at least 50 words in length.
-
 # Introduction
@@
 The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways implement stronger interocular suppression than the canonical cortical pathway.
-
-# Methods
-
-## Participants
-
-Thirty (20 F, 10 M), twelve (7 F, 5 M) and ten (3 F, 7 M) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected-to-normal binocular vision, and gave written informed consent in accordance with the Declaration of Helsinki.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
-
-## Apparatus & stimuli
-
-The stimuli were two monocularly presented discs of achromatic flickering light with a diameter of 3.74 degrees, displayed against a black background.
-The same stimuli were used for all three experiments.
-Four dark red lines were added around each monocular disc to help with their fusion into a single binocular disc (see insert in Fig.
-\@ref(fig:pupildata)b for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants perceived a single fused disc.
-The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
-Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
-
-All stimuli had a mean luminance of 42 cd/m$^2$, and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
-Ltd., Japan).
-All stimuli were presented using Psychopy [@Peirce2019] (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
-
-EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-## Procedure
-
-Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
-This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
-
-### Experiment 1: simultaneous EEG and pupillometry
-
-The experiment was conducted in a windowless room, in which the only light source was the monitor.
-The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
-In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
-
-We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
-Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
-In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
-In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 2Hz, and the other eye's disc flickered at 1.6Hz.
-We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
-The rationale for flickering both eyes at 2Hz is that we can measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
-The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
-the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
-We counterbalanced presentation of the target stimulus across the left and right eyes.
-
-### Experiment 2: EEG responses across temporal frequency
-
-This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
-Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
-Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
-The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
-In each block, there were 20 trials in total with the same timing as for Experiment 1.
-
-### Experiment 3: temporal contrast matching
-
-The experiment was conducted in a darkened room with a blacked-out window.
-The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
-A two-interval contrast matching procedure was used to collect data.
-In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
-In the other interval, a target disc flickering at varying contrast levels was displayed.
-The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
-The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
-The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
-The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
-
-Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
-The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
-In each block, there were a total of 50 trials.
-No auditory feedback was given for this subjective task.
-
-## Data analysis
-
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
-The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
-The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
-All repetitions of each condition were then averaged for each electrode.
-They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
-Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.
-coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [@Baker2021].
-For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described previously @Baker2021.
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic @Victor1991 that can compare more than two conditions.
-
-A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-Finally, data were averaged across all participants to obtain the group results.
-Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis @Spitschan2014.
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [@Barrionuevo2014; @Barrionuevo2016].
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [@Figueira2022].
-
-To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
-We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
-Thresholds were averaged across participants in logarithmic (dB) units.
-
-For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
-
-## Computational model and parameter estimation
-
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
-[@Meese2006].
-The second gain control stage was omitted, consistent with previous work [@Baker2017], to simplify the model and reduce the number of free parameters.
-The response of the left eye's channel is given by:
-
-\begin{equation}
-\label{eq:respL}
-Resp_L = \frac{L^2}{Z + L + wR},
-\end{equation}
-
-with an equivalent expression for the right eye:
-
-\begin{equation}
-\label{eq:respR}
-Resp_R = \frac{R^2}{Z + R + wL}.
-\end{equation}
-
-In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respB}
-Resp_B = R_{max}(Resp_L + Resp_R) + n,
-\end{equation}
-
-where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
-The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
-
-Despite being derived from the model proposed by Meese et al.
-[@Meese2006], the simplifications applied to this architecture make it very similar to other models [@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [@Baker2012; @Kingdom2015].
-Our key parameter of interest is the weight of interocular suppression.
-Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
-Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
-
-We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
-This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
-We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
-The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants for our steady-state data, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
-\@ref(fig:modelfigure).
-We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
-
-## Preregistration, data and code availability
-
-We initially preregistered our main hypotheses and analysis intentions for the first experiment.
-We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
-We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
 
@@
 
-knitr::include_graphics(paste0(figdir,'pupildata.pdf'))
+knitr::include_graphics(paste0(figdir,'blank.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'EEGdata.pdf'))
+knitr::include_graphics(paste0(figdir,'blank.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'BSratios.pdf'))
+knitr::include_graphics(paste0(figdir,'blank.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'TFdata.pdf'))
+knitr::include_graphics(paste0(figdir,'blank.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'matchingdata.pdf'))
+knitr::include_graphics(paste0(figdir,'blank.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'modelfigure.pdf'))
+knitr::include_graphics(paste0(figdir,'blank.pdf'))
 
@@
 
-# Acknowledgements
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+# Methods
+
+## Participants
+
+Thirty (20 F, 10 M), twelve (7 F, 5 M) and ten (3 F, 7 M) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected-to-normal binocular vision, and gave written informed consent in accordance with the Declaration of Helsinki.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
+
+## Apparatus & stimuli
+
+The stimuli were two monocularly presented discs of achromatic flickering light with a diameter of 3.74 degrees, displayed against a black background.
+The same stimuli were used for all three experiments.
+Four dark red lines were added around each monocular disc to help with their fusion into a single binocular disc (see insert in Fig.
+\@ref(fig:pupildata)b for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants perceived a single fused disc.
+The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
+
+All stimuli had a mean luminance of 42 cd/m$^2$, and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
+Ltd., Japan).
+All stimuli were presented using Psychopy [@Peirce2019] (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
+
+EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+## Procedure
+
+Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
+This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
+
+### Experiment 1: simultaneous EEG and pupillometry
+
+The experiment was conducted in a windowless room, in which the only light source was the monitor.
+The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
+The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+
+We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
+In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
+In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 2Hz, and the other eye's disc flickered at 1.6Hz.
+We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
+The rationale for flickering both eyes at 2Hz is that we can measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
+The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
+the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
+We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+### Experiment 2: EEG responses across temporal frequency
+
+This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
+Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
+The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
+In each block, there were 20 trials in total with the same timing as for Experiment 1.
+
+### Experiment 3: temporal contrast matching
+
+The experiment was conducted in a darkened room with a blacked-out window.
+The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
+A two-interval contrast matching procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
+In the other interval, a target disc flickering at varying contrast levels was displayed.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
+The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
+
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
+The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
+In each block, there were a total of 50 trials.
+No auditory feedback was given for this subjective task.
+
+## Data analysis
+
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each electrode.
+They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
+Finally, these were averaged across participants to obtain the group results.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.
+coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [@Baker2021].
+For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described previously @Baker2021.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic @Victor1991 that can compare more than two conditions.
+
+A similar analysis pipeline was adopted for the pupillometry data.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+Finally, data were averaged across all participants to obtain the group results.
+Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis @Spitschan2014.
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [@Barrionuevo2014; @Barrionuevo2016].
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [@Figueira2022].
+
+To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
+We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
+Thresholds were averaged across participants in logarithmic (dB) units.
+
+For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
+
+## Computational model and parameter estimation
+
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
+[@Meese2006].
+The second gain control stage was omitted, consistent with previous work [@Baker2017], to simplify the model and reduce the number of free parameters.
+The response of the left eye's channel is given by:
+
+\begin{equation}
+\label{eq:respL}
+Resp_L = \frac{L^2}{Z + L + wR},
+\end{equation}
+
+with an equivalent expression for the right eye:
+
+\begin{equation}
+\label{eq:respR}
+Resp_R = \frac{R^2}{Z + R + wL}.
+\end{equation}
+
+In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+Resp_B = R_{max}(Resp_L + Resp_R) + n,
+\end{equation}
+
+where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
+The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
+
+Despite being derived from the model proposed by Meese et al.
+[@Meese2006], the simplifications applied to this architecture make it very similar to other models [@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [@Baker2012; @Kingdom2015].
+Our key parameter of interest is the weight of interocular suppression.
+Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
+Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
+
+We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+The models were fit using the individual data across all participants, independently for each data set.
+Because we used coherent averaging across participants for our steady-state data, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
+However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Fig.
+\@ref(fig:modelfigure).
+We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+
+## Preregistration, data and code availability
+
+We initially preregistered our main hypotheses and analysis intentions for the first experiment.
+We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then ran the main experiment, followed by two additional experiments that were not preregistered.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+
+# Author contributions
+
+**Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
+**Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
+**Myat Aung**: Software, resources, writing - review & editing.
+**Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
+**Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
 

### 2023-02-08 manuscriptPLOSBIO.tex
Edited for PLOS Biology

@@
 \usepackage{setspace}\doublespacing
+\usepackage{lineno}\linenumbers
 
@@
 
-Federico G. Segala, email: \href{mailto:fgs502@york.ac.uk}{\nolinkurl{fgs502@york.ac.uk}}
+\textbf{Short title}: ``Binocular combination of flickering light''
 
-\textbf{Author contributions: Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
-\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Myat Aung}: Software, resources, writing - review \& editing.
-\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
-
-\textbf{Competing interest declaration:} The authors declare no competing interests.
-
-\textbf{Classification:} Biological Sciences - Neuroscience
-
-\textbf{Keywords:} Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
+\textbf{Corresponding author}: Federico G. Segala, email: \href{mailto:fgs502@york.ac.uk}{\nolinkurl{fgs502@york.ac.uk}}
+\newpage
 
@@
 Ocularity invariance is therefore not a ubiquitous feature of visual processing, and the brain appears to repurpose a generic normalisation algorithm for different visual functions by adjusting the amount of interocular suppression.
-
-\hypertarget{significance-statement}{%
-\section{Significance Statement}\label{significance-statement}}
-
-Please note that it should not exceed 120 words, but should be at least 50 words in length.
 
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
+
+The pupillometry results for our first experiment are summarised in Fig.
+\ref{fig:pupildata}.
+The group average waveform for binocular presentation is shown in Fig.
+\ref{fig:pupildata}a.
+There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
+The average Fourier spectrum is displayed in Fig.
+\ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/blank}
+
+}
+
+\caption{Summary of pupillometry results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
+\end{figure}
+
+Fig.
+\ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
+The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) {[}20{]} comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
+
+In Fig.
+\ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Fig.
+\ref{fig:pupildata}c for comparison).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
+When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless{} 0.001).
+
+Fig.
+\ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
+The dichoptic cross condition does not show clear modulation with target contrast.
+
+Fig.
+\ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
+Fig.
+\ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Fig.
+\ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
+Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
+We therefore derived contrast response functions at both first and second harmonic frequencies.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/blank}
+
+}
+
+\caption{Summary of EEG results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
+Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Panels (f-h) are in the same format but for the second harmonic responses.
+Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
+\end{figure}
+
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Fig.
+\ref{fig:EEGdata}c) and second (Fig.
+\ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic (note that the absence of a main effect of condition is expected, given that there should be negligible differences between conditions at low contrasts, and any differences are therefore captured by the interaction term).
+For the cross-frequency conditions (Fig.
+\ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Fig.
+\ref{fig:EEGdata}e) and 3.2Hz (Fig.
+\ref{fig:EEGdata}h).
+This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
+
+Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
+Fig.
+\ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
+At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Fig.
+\ref{fig:pupildata} and \ref{fig:EEGdata}.
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/blank}
+
+}
+
+\caption{Ratio of binocular to monocular response for three data types.
+Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
+\end{figure}
+
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
+
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli {[}1{]}.
+One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
+We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz {[}19{]}; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+
+Results from the temporal frequency experiment are shown in Fig.
+\ref{fig:TFdata}.
+Fig.
+\ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
+However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
+Fig.
+\ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
+Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
+\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/blank}
+
+}
+
+\caption{Binocular facilitation at different temporal frequencies.
+Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
+Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
+Panel (c) shows the ratio of binocular to monocular responses.
+Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
+\end{figure}
+
+\hypertarget{experiment-3}{%
+\subsection{Experiment 3}\label{experiment-3}}
+
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms {[}21--23{]}.
+We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
+One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
+The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
+We tested 9 ratios of contrast between the left and right eyes.
+
+The results from the matching experiment are shown in Fig.
+\ref{fig:matchingdata}.
+Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
+For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
+The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Fig.
+\ref{fig:EEGdata}c,f).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/blank}
+
+}
+
+\caption{Contrast matching functions.
+Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
+This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
+\end{figure}
+
+\hypertarget{computational-modelling}{%
+\subsection{Computational modelling}\label{computational-modelling}}
+
+We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
+The model behaviour is displayed in Fig.
+\ref{fig:modelfigure}e-h, with empirical data replotted in Fig.
+\ref{fig:modelfigure}a-d for comparison.
+In general, the model captures the key characteristics of the empirical data.
+Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
+In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \ref{tab:paramtable}).
+This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
+This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
+
+We were particularly interested in comparing the weight of interocular suppression across data sets.
+We therefore plot the posterior distributions for this parameter for all four data sets (see Fig.
+\ref{fig:modelfigure}i).
+The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
+There is no overlap between the pupillometry distribution and any of the other three.
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict {[}1,9{]}, and the peak location of our prior distribution (black curve).
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and significant dichoptic masking observed using that method.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/blank}
+
+}
+
+\caption{Summary of computational modelling.
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
+Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
+Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
+The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:paramtable}Summary of median parameter values.}
+\centering
+\begin{tabular}[t]{l|c|c|c|c}
+\hline
+Data set & Z & k & w & Rmax\\
+\hline
+Pupillometry & 2.37 & 0.01 & 0.67 & 0.00023\\
+\hline
+EEG 1F & 2.59 & 0.15 & 0.02 & 0.0026\\
+\hline
+EEG 2F & 2.21 & 0.06 & 0.01 & 0.00404\\
+\hline
+Matching & 0.30 & 5.07 & 0.09 & -\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
+In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
+This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
+
+The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts {[}1,9,10{]}.
+Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
+However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
+For example, Quaia et al.@Quaia2018 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and \href{mailto:Cajochen@Spitschan2019}{\nolinkurl{Cajochen@Spitschan2019}} report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm {[}24{]}.
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments {[}21,22,25{]}, though not for luminance decrements {[}21{]}.
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination.
+
+Given the above, where does this leave our understanding of the overarching purpose of signal combination?
+We \href{mailto:previously@Baker2017}{\nolinkurl{previously@Baker2017}} pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also {[}2{]}).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction {[}26,27{]}.
+One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
+However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or are otherwise phylogenetically older than binocular pattern vision.
+Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
+Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
+
+Pupil size determines the total amount of light falling on the retina.
+It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
+We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter {[}19{]}.
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms {[}28{]}.
+We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
+Therefore we make the simplifying assumption that the two pathways are effectively distinct, but intend to investigate this directly in future neuroimaging work.
+
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' {[}29,30{]} are biased towards low spatial frequencies {[}31,32{]}, and relatively insensitive to stimulus orientation {[}29,30{]} (though see {[}33{]}).
+As the blob regions are embedded within ocular dominance columns {[}29{]}, they are also largely monocular {[}30,34{]}.
+More recent work has reported psychophysical evidence for unoriented chromatic {[}35{]} and achromatic {[}36{]} mechanisms, that also appear to be monocular.
+Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Fig.
+\ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
+However our matching data (Fig.
+\ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
+Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
+We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
+
 \hypertarget{methods}{%
@@
 All stimuli had a mean luminance of 42 cd/m\(^2\), and were presented on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
-All stimuli were presented using Psychopy {[}20{]} (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
+All stimuli were presented using Psychopy {[}37{]} (v3.0.7 for Experiments 1 and 2; v2022.1.1 for Experiment 3).
 
 EEG data were collected for Experiments 1 and 2 using a 64 electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany {[}21{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany {[}38{]}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox {[}22{]}.
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox {[}39{]}.
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}23{]}.
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described previously {[}23{]}.
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic {[}24{]} that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean {[}20{]}.
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described previously {[}20{]}.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic {[}40{]} that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}21{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software {[}38{]}, which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis {[}19{]}.
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies {[}25,26{]}.
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis {[}27{]}.
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies {[}41,42{]}.
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis {[}43{]}.
 
@@
 
-Despite being derived from the model proposed by Meese et al.~{[}9{]}, the simplifications applied to this architecture make it very similar to other models {[}8,11,17,28{]}.
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression {[}29,30{]}.
+Despite being derived from the model proposed by Meese et al.~{[}9{]}, the simplifications applied to this architecture make it very similar to other models {[}8,11,17,44{]}.
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression {[}25,45{]}.
 Our key parameter of interest is the weight of interocular suppression.
 Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli {[}1{]}.
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation {[}31{]}.
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation {[}24{]}.
 
-We implemented the model within a Bayesian framework using the Stan software {[}32{]}.
+We implemented the model within a Bayesian framework using the Stan software {[}46{]}.
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature {[}9,29{]}.
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature {[}9,25{]}.
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
 
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
-
-The pupillometry results for our first experiment are summarised in Fig.
-\ref{fig:pupildata}.
-The group average waveform for binocular presentation is shown in Fig.
-\ref{fig:pupildata}a.
-There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Fig.
-\ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
-These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/pupildata}
-
-}
-
-\caption{Summary of pupillometry results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
-Panels (c,d) show contrast response functions at 2Hz for different conditions.
-Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
-\end{figure}
-
-Fig.
-\ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
-Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
-The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) {[}23{]} comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
-The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
-
-In Fig.
-\ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Fig.
-\ref{fig:pupildata}c for comparison).
-When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
-When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless{} 0.001).
-
-Fig.
-\ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
-The dichoptic cross condition does not show clear modulation with target contrast.
-
-Fig.
-\ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
-Fig.
-\ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Fig.
-\ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
-Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
-We therefore derived contrast response functions at both first and second harmonic frequencies.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/EEGdata}
-
-}
-
-\caption{Summary of EEG results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
-Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
-Panels (c,d) show contrast response functions at 2Hz for different conditions.
-Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Panels (f-h) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
-\end{figure}
-
-When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Fig.
-\ref{fig:EEGdata}c) and second (Fig.
-\ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic (note that the absence of a main effect of condition is expected, given that there should be negligible differences between conditions at low contrasts, and any differences are therefore captured by the interaction term).
-For the cross-frequency conditions (Fig.
-\ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
-Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Fig.
-\ref{fig:EEGdata}e) and 3.2Hz (Fig.
-\ref{fig:EEGdata}h).
-This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
-
-Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
-Fig.
-\ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
-At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
-Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Fig.
-\ref{fig:pupildata} and \ref{fig:EEGdata}.
-A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/BSratios}
-
-}
-
-\caption{Ratio of binocular to monocular response for three data types.
-Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
-\end{figure}
-
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
-
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli {[}1{]}.
-One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
-We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz {[}19{]}; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
-
-Results from the temporal frequency experiment are shown in Fig.
-\ref{fig:TFdata}.
-Fig.
-\ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
-From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
-However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
-Fig.
-\ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
-Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
-\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/TFdata}
-
-}
-
-\caption{Binocular facilitation at different temporal frequencies.
-Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
-Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
-Panel (c) shows the ratio of binocular to monocular responses.
-Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
-\end{figure}
-
-\hypertarget{experiment-3}{%
-\subsection{Experiment 3}\label{experiment-3}}
-
-In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms {[}33--35{]}.
-We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
-One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
-The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
-We tested 9 ratios of contrast between the left and right eyes.
-
-The results from the matching experiment are shown in Fig.
-\ref{fig:matchingdata}.
-Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
-At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
-For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
-The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
-Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Fig.
-\ref{fig:EEGdata}c,f).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
-
-}
-
-\caption{Contrast matching functions.
-Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
-This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
-\end{figure}
-
-\hypertarget{computational-modelling}{%
-\subsection{Computational modelling}\label{computational-modelling}}
-
-We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Fig.
-\ref{fig:modelfigure}e-h, with empirical data replotted in Fig.
-\ref{fig:modelfigure}a-d for comparison.
-In general, the model captures the key characteristics of the empirical data.
-Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
-In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \ref{tab:paramtable}).
-This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
-This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
-
-We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Fig.
-\ref{fig:modelfigure}i).
-The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
-There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict {[}1,9{]}, and the peak location of our prior distribution (black curve).
-These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and significant dichoptic masking observed using that method.
-The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/modelfigure}
-
-}
-
-\caption{Summary of computational modelling.
-Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
-Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
-Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
-The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
-The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
-\end{figure}
-
-\begin{table}
-
-\caption{\label{tab:paramtable}Summary of median parameter values.}
-\centering
-\begin{tabular}[t]{l|c|c|c|c}
-\hline
-Data set & Z & k & w & Rmax\\
-\hline
-Pupillometry & 2.37 & 0.01 & 0.67 & 0.00023\\
-\hline
-EEG 1F & 2.59 & 0.15 & 0.02 & 0.0026\\
-\hline
-EEG 2F & 2.21 & 0.06 & 0.01 & 0.00404\\
-\hline
-Matching & 0.30 & 5.07 & 0.09 & -\\
-\hline
-\end{tabular}
-\end{table}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
-In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
-In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
-This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
-Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
-
-The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are universally consistent with strong interocular suppression and weak binocular facilitation at high contrasts {[}1,9,10{]}.
-Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
-However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, Quaia et al.@Quaia2018 observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and \href{mailto:Cajochen@Spitschan2019}{\nolinkurl{Cajochen@Spitschan2019}} report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm {[}31{]}.
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments {[}29,33,34{]}, though not for luminance decrements {[}33{]}.
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination.
-
-Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-We \href{mailto:previously@Baker2017}{\nolinkurl{previously@Baker2017}} pointed out that a model with strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also {[}2{]}).
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction {[}36,37{]}.
-One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or are otherwise phylogenetically older than binocular pattern vision.
-Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
-Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
-
-Pupil size determines the total amount of light falling on the retina.
-It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
-We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter {[}19{]}.
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms {[}38{]}.
-We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but intend to investigate this directly in future neuroimaging work.
-
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' {[}39,40{]} are biased towards low spatial frequencies {[}41,42{]}, and relatively insensitive to stimulus orientation {[}39,40{]} (though see {[}43{]}).
-As the blob regions are embedded within ocular dominance columns {[}39{]}, they are also largely monocular {[}40,44{]}.
-More recent work has reported psychophysical evidence for unoriented chromatic {[}45{]} and achromatic {[}46{]} mechanisms, that also appear to be monocular.
-Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
-Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Fig.
-\ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
-However our matching data (Fig.
-\ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
-Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
-Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
-We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
-
-\hypertarget{acknowledgements}{%
-\section{Acknowledgements}\label{acknowledgements}}
-
-Supported by Biotechnology and Biological Sciences Research Council grant BB/V007580/1 awarded to DHB and ARW, and Wellcome Trust grant 213616/Z/18/Z to AB.
+\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
+\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Myat Aung}: Software, resources, writing - review \& editing.
+\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
 
@@
 
+\leavevmode\hypertarget{ref-Baker2021}{}%
+20. Baker DH. Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory. 2021;5. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+
+\leavevmode\hypertarget{ref-Anstis1998}{}%
+21.
+Anstis S, Ho A.
+Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
+Vision Res.
+1998;38: 523--39.
+doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
+
+\leavevmode\hypertarget{ref-Levelt1965}{}%
+22. Levelt WJ. Binocular brightness averaging and contour information. Br J Psychol. 1965;56: 1--13. doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}
+
+\leavevmode\hypertarget{ref-Quaia2018}{}%
+23. Quaia C, Optican LM, Cumming BG. Binocular summation for reflexive eye movements. J Vis. 2018;18(4): 7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
+
+\leavevmode\hypertarget{ref-Baker2020}{}%
+24.
+Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
+Binaural summation of amplitude modulation involves weak interaural suppression.
+Sci Rep.
+2020;10: 3560.
+doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
+
+\leavevmode\hypertarget{ref-Baker2012}{}%
+25.
+Baker DH, Wallis SA, Georgeson MA, Meese TS.
+Nonlinearities in the binocular combination of luminance and contrast.
+Vision Res.
+2012;56: 1--9.
+doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
+
+\leavevmode\hypertarget{ref-Li1994}{}%
+26.
+Li Z, Atick JJ.
+Efficient stereo coding in the multiscale representation.
+Network: Computation in Neural Systems.
+1994;5: 157--174.
+doi:\href{https://doi.org/10.1088/0954-898X_5_2_003}{10.1088/0954-898X\_5\_2\_003}
+
+\leavevmode\hypertarget{ref-May2022}{}%
+27.
+May K, Zhaoping L.
+Li and Atick's theory of efficient binocular coding: A tutorial and mini-review.
+Vision Res.
+2022;201: 107950.
+doi:\href{https://doi.org/10.1016/j.visres.2021.08.005}{10.1016/j.visres.2021.08.005}
+
+\leavevmode\hypertarget{ref-Bradley2008}{}%
+28.
+Bradley MM, Miccoli L, Escrig MA, Lang PJ.
+The pupil as a measure of emotional arousal and autonomic activation.
+Psychophysiology.
+2008;45: 602--7.
+doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
+
+\leavevmode\hypertarget{ref-Horton1981}{}%
+29.
+Horton JC, Hubel DH.
+Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
+Nature.
+1981;292: 762--4.
+doi:\href{https://doi.org/10.1038/292762a0}{10.1038/292762a0}
+
+\leavevmode\hypertarget{ref-Livingstone1984}{}%
+30.
+Livingstone MS, Hubel DH.
+Anatomy and physiology of a color system in the primate visual cortex.
+J Neurosci.
+1984;4: 309--56.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{10.1523/JNEUROSCI.04-01-00309.1984}
+
+\leavevmode\hypertarget{ref-Tootell1988}{}%
+31.
+Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
+Functional anatomy of macaque striate cortex.
+V.
+Spatial frequency.
+J Neurosci.
+1988;8: 1610--24.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{10.1523/JNEUROSCI.08-05-01610.1988}
+
+\leavevmode\hypertarget{ref-Edwards1995}{}%
+32.
+Edwards DP, Purpura KP, Kaplan E.
+Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
+Vision Res.
+1995;35: 1501--23.
+doi:\href{https://doi.org/10.1016/0042-6989(94)00253-i}{10.1016/0042-6989(94)00253-i}
+
+\leavevmode\hypertarget{ref-Economides2011}{}%
+33.
+Economides JR, Sincich LC, Adams DL, Horton JC.
+Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
+Nat Neurosci.
+2011;14: 1574--80.
+doi:\href{https://doi.org/10.1038/nn.2958}{10.1038/nn.2958}
+
+\leavevmode\hypertarget{ref-Tychsen2004}{}%
+34.
+Tychsen L, Wong AM-F, Burkhalter A.
+Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
+The Journal of Comparative Neurology.
+2004;474: 261--275.
+doi:\href{https://doi.org/10.1002/cne.20113}{10.1002/cne.20113}
+
+\leavevmode\hypertarget{ref-Gheiratmand2013}{}%
+35.
+Gheiratmand M, Meese TS, Mullen KT.
+Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
+Journal of Vision.
+2013;13(1): 2.
+doi:\href{https://doi.org/10.1167/13.1.2}{10.1167/13.1.2}
+
+\leavevmode\hypertarget{ref-Meese2011}{}%
+36.
+Meese TS, Baker DH.
+A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
+iPerception.
+2011;2: 159--82.
+doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
+
 \leavevmode\hypertarget{ref-Peirce2019}{}%
-20.
+37.
 Peirce J, Gray JR, Simpson S, MacAskill M, Höchenberger R, Sogo H, et al.
@@
 \leavevmode\hypertarget{ref-Kassner2014}{}%
-21.
+38.
 Kassner M, Patera W, Bulling A.
@@
 \leavevmode\hypertarget{ref-Delorme2004}{}%
-22.
+39.
 Delorme A, Makeig S.
@@
 
-\leavevmode\hypertarget{ref-Baker2021}{}%
-23. Baker DH. Statistical analysis of periodic data in neuroscience. Neurons, Behavior, Data analysis, and Theory. 2021;5. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
-
 \leavevmode\hypertarget{ref-Victor1991}{}%
-24.
+40.
 Victor JD, Mast J.
@@
 \leavevmode\hypertarget{ref-Barrionuevo2014}{}%
-25.
+41.
 Barrionuevo PA, Nicandro N, McAnany JJ, Zele AJ, Gamlin P, Cao D.
@@
 \leavevmode\hypertarget{ref-Barrionuevo2016}{}%
-26.
+42.
 Barrionuevo PA, Cao D.
@@
 \leavevmode\hypertarget{ref-Figueira2022}{}%
-27.
+43.
 Figueira JSB, Kutlu E, Scott LS, Keil A.
@@
 \leavevmode\hypertarget{ref-Schrodinger1926}{}%
-28. Schrödinger E. Die gesichtsempfindungen. Mueller-pouillets lehrbuch der physik (11th ed). Vieweg: Braunschweig; 1926. pp. 456--560.
-
-\leavevmode\hypertarget{ref-Baker2012}{}%
-29.
-Baker DH, Wallis SA, Georgeson MA, Meese TS.
-Nonlinearities in the binocular combination of luminance and contrast.
-Vision Res.
-2012;56: 1--9.
-doi:\href{https://doi.org/10.1016/j.visres.2012.01.008}{10.1016/j.visres.2012.01.008}
+44. Schrödinger E. Die gesichtsempfindungen. Mueller-pouillets lehrbuch der physik (11th ed). Vieweg: Braunschweig; 1926. pp. 456--560.
 
 \leavevmode\hypertarget{ref-Kingdom2015}{}%
-30.
+45.
 Kingdom FAA, Libenson L.
@@
 
-\leavevmode\hypertarget{ref-Baker2020}{}%
-31.
-Baker DH, Vilidaite G, McClarnon E, Valkova E, Bruno A, Millman RE.
-Binaural summation of amplitude modulation involves weak interaural suppression.
-Sci Rep.
-2020;10: 3560.
-doi:\href{https://doi.org/10.1038/s41598-020-60602-5}{10.1038/s41598-020-60602-5}
-
 \leavevmode\hypertarget{ref-Carpenter2017}{}%
-32.
+46.
 Carpenter B, Gelman A, Hoffman MD, Lee D, Goodrich B, Betancourt M, et al.
@@
 
-\leavevmode\hypertarget{ref-Anstis1998}{}%
-33.
-Anstis S, Ho A.
-Nonlinear combination of luminance excursions during flicker, simultaneous contrast, afterimages and binocular fusion.
-Vision Res.
-1998;38: 523--39.
-doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
-
-\leavevmode\hypertarget{ref-Levelt1965}{}%
-34. Levelt WJ. Binocular brightness averaging and contour information. Br J Psychol. 1965;56: 1--13. doi:\href{https://doi.org/10.1111/j.2044-8295.1965.tb00939.x}{10.1111/j.2044-8295.1965.tb00939.x}
-
-\leavevmode\hypertarget{ref-Quaia2018}{}%
-35. Quaia C, Optican LM, Cumming BG. Binocular summation for reflexive eye movements. J Vis. 2018;18(4): 7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
-
-\leavevmode\hypertarget{ref-Li1994}{}%
-36.
-Li Z, Atick JJ.
-Efficient stereo coding in the multiscale representation.
-Network: Computation in Neural Systems.
-1994;5: 157--174.
-doi:\href{https://doi.org/10.1088/0954-898X_5_2_003}{10.1088/0954-898X\_5\_2\_003}
-
-\leavevmode\hypertarget{ref-May2022}{}%
-37.
-May K, Zhaoping L.
-Li and Atick's theory of efficient binocular coding: A tutorial and mini-review.
-Vision Res.
-2022;201: 107950.
-doi:\href{https://doi.org/10.1016/j.visres.2021.08.005}{10.1016/j.visres.2021.08.005}
-
-\leavevmode\hypertarget{ref-Bradley2008}{}%
-38.
-Bradley MM, Miccoli L, Escrig MA, Lang PJ.
-The pupil as a measure of emotional arousal and autonomic activation.
-Psychophysiology.
-2008;45: 602--7.
-doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
-
-\leavevmode\hypertarget{ref-Horton1981}{}%
-39.
-Horton JC, Hubel DH.
-Regular patchy distribution of cytochrome oxidase staining in primary visual cortex of macaque monkey.
-Nature.
-1981;292: 762--4.
-doi:\href{https://doi.org/10.1038/292762a0}{10.1038/292762a0}
-
-\leavevmode\hypertarget{ref-Livingstone1984}{}%
-40.
-Livingstone MS, Hubel DH.
-Anatomy and physiology of a color system in the primate visual cortex.
-J Neurosci.
-1984;4: 309--56.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.04-01-00309.1984}{10.1523/JNEUROSCI.04-01-00309.1984}
-
-\leavevmode\hypertarget{ref-Tootell1988}{}%
-41.
-Tootell RB, Silverman MS, Hamilton SL, Switkes E, De Valois RL.
-Functional anatomy of macaque striate cortex.
-V.
-Spatial frequency.
-J Neurosci.
-1988;8: 1610--24.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.08-05-01610.1988}{10.1523/JNEUROSCI.08-05-01610.1988}
-
-\leavevmode\hypertarget{ref-Edwards1995}{}%
-42.
-Edwards DP, Purpura KP, Kaplan E.
-Contrast sensitivity and spatial frequency response of primate cortical neurons in and around the cytochrome oxidase blobs.
-Vision Res.
-1995;35: 1501--23.
-doi:\href{https://doi.org/10.1016/0042-6989(94)00253-i}{10.1016/0042-6989(94)00253-i}
-
-\leavevmode\hypertarget{ref-Economides2011}{}%
-43.
-Economides JR, Sincich LC, Adams DL, Horton JC.
-Orientation tuning of cytochrome oxidase patches in macaque primary visual cortex.
-Nat Neurosci.
-2011;14: 1574--80.
-doi:\href{https://doi.org/10.1038/nn.2958}{10.1038/nn.2958}
-
-\leavevmode\hypertarget{ref-Tychsen2004}{}%
-44.
-Tychsen L, Wong AM-F, Burkhalter A.
-Paucity of horizontal connections for binocular vision in v1 of naturally strabismic macaques: Cytochrome oxidase compartment specificity.
-The Journal of Comparative Neurology.
-2004;474: 261--275.
-doi:\href{https://doi.org/10.1002/cne.20113}{10.1002/cne.20113}
-
-\leavevmode\hypertarget{ref-Gheiratmand2013}{}%
-45.
-Gheiratmand M, Meese TS, Mullen KT.
-Blobs versus bars: Psychophysical evidence supports two types of orientation response in human color vision.
-Journal of Vision.
-2013;13(1): 2.
-doi:\href{https://doi.org/10.1167/13.1.2}{10.1167/13.1.2}
-
-\leavevmode\hypertarget{ref-Meese2011}{}%
-46.
-Meese TS, Baker DH.
-A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-iPerception.
-2011;2: 159--82.
-doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
-
 \end{document}

### 2023-02-09 manuscriptPLOSBIO_InitialSubmission.Rmd
Additional edits to PLOS submission

--- 2023-02-08 manuscriptPLOSBIO.Rmd
@@
 
-knitr::include_graphics(paste0(figdir,'blank.pdf'))
+knitr::include_graphics(paste0(figdir,'pupildata.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'blank.pdf'))
+knitr::include_graphics(paste0(figdir,'EEGdata.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'blank.pdf'))
+knitr::include_graphics(paste0(figdir,'BSratios.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'blank.pdf'))
+knitr::include_graphics(paste0(figdir,'TFdata.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'blank.pdf'))
+knitr::include_graphics(paste0(figdir,'matchingdata.pdf'))
 
@@
 
-knitr::include_graphics(paste0(figdir,'blank.pdf'))
+knitr::include_graphics(paste0(figdir,'modelfigure.pdf'))
 

### 2023-03-30 manuscript.Rmd
Changed pupiltargets to pupilmasks

@@
 
-    temp <- c(pupilmasks[,,startindex+level],pupiltargets[,,startindex+level+5])
+    temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
         cartdata <- data.frame(Re(temp),Im(temp))

### 2023-06-03 manuscript.Rmd
Started eLife revisions

@@
     keep_tex: yes
-  pdf_document:
-    toc: no
-  word_document: default
+  word_document2: default
   html_document: default
@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 3  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
        }
+      }
 
@@
 
-    }
   }
@@
 
-    }
-
     save(file=paste0(datadir,'P',150+participant,'summary.RData'),list=c('cleanmeansE','meanspec'))
+    }
 
@@
 nChains <- 8
-ncores <- detectCores()/2  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
+ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
 options(mc.cores=ncores)

### 2023-06-03 manuscript.tex
Created rmd file specific for Nature and added Nature referencing style.
Started eLife revisions

--- 2023-01-10 manuscript.tex
@@
 A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, 2021) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
-The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,328) = 5.34, \(p\) \textless{} 0).
 
@@
 Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
-A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(2.96,121.48) = 6.18, \emph{p} \textless{} 0), no effect of data modality (F(2,82) = 5.55, \emph{p} = 0.01), but a highly significant interaction (F(5.04,206.46) = 6.38, \emph{p} \textless{} 0).
 
@@
 \hline
-Pupillometry & 2.37 & 0.01 & 0.67 & 0.00023\\
+Pupillometry & 2.40 & 0.01 & 0.66 & 0.00023\\
 \hline
-EEG 1F & 2.59 & 0.15 & 0.02 & 0.0026\\
+EEG 1F & 2.72 & 0.16 & 0.02 & 0.00261\\
 \hline
-EEG 2F & 2.21 & 0.06 & 0.01 & 0.00404\\
+EEG 2F & 2.23 & 0.06 & 0.01 & 0.00404\\
 \hline
-Matching & 0.30 & 5.07 & 0.09 & -\\
+Matching & 0.30 & 5.10 & 0.09 & -\\
 \hline
@@
 \textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
+
+\hypertarget{declaration-of-interests}{%
+\section{Declaration of interests}\label{declaration-of-interests}}
+
+The authors declare no competing interests.
 

### 2023-06-07 manuscript.Rmd
Added analysis of replication data

@@
 title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
-author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
-date: "Department of Psychology, University of York, UK"
+author: |
+ | Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker
+ | Department of Psychology, University of York, UK
+ | *eLife* (2023) https://doi.org/10.7554/eLife.87048
 output:
@@
 csl: elife.csl
+header-includes:
+- \usepackage{float}
+- \usepackage{float} \floatplacement{figure}{H}
+- \newcommand{\beginsupplement}{\setcounter{table}{0}
+- \renewcommand{\thetable}{A\arabic{table}}
+- \setcounter{figure}{0}
+- \renewcommand{\thefigure}{A\arabic{figure}}}
 ---
@@
 
-processdata <- 3  # this flag determines the amount of processing, with 4 levels:
+processdata <- 2  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
 # 1 - generate figures using the processed group data
-# 2 - average data across participants, do bootstrapping and modelling
+# 2 - average data across participants, do bootstrapping
 # 3 - download all raw data and analyse (requires 48GB of storage)
+
+domodelling <- 1    # if set to 1, run the Stan models (takes ~24 hours)
+
+# cut off for data inclusion (Mahalanobis distance for complex data)
+SDthresh <<- 3
+nbootstraps <<- 1000
 
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+# settings for sampler 
+numSavedSteps <- 1000    # total number of MCMC steps
+adaptSteps <- 1000  # Number of steps to "tune" the samplers
+burnInSteps <- 2000 
+thinSteps <- 10
+nChains <- 16
+ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
+options(mc.cores=ncores)
 
@@
 
+cleanup2D <- function(data){
+  # helper function to clean up complex data by removing any data points more than 
+  # SDthresh standard deviations from the mean (in Mahalanobis distance units)
+  cartdata <- data.frame(Re(data),Im(data))
+  output <- 0
+  if (sum(cartdata)!=0){
+    D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+    i <- which(D<SDthresh) 
+    output <- mean(temp[i])}
+return(output)}
+
+bootstrap2D <- function(data){
+  mbs <- data.frame(meanamp=0,lowerCI=0,upperCI=0)
+    cartdata <- data.frame(Re(data),Im(data))
+    if (sum(cartdata)!=0){
+      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+      i <- which(D<SDthresh) 
+    mbs <- amperrors(data[i],method='boot',quantiles=68,nresamples=nbootstraps)}
+return(mbs)}
+
 colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
@@
 if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
-
-# cut off for data inclusion (Mahalanobis distance for complex data)
-SDthresh <- 3
-nbootstraps <- 1000
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp1individualanalysis, include=FALSE, results='hide'}
 
@@
     temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
-        cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    cleanmeansP[cond,level] <- mean(temp[i])}
+    cleanmeansP[cond,level] <- cleanup2D(temp)
+}
 
     temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
-        cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    cleanmasksP[cond,level] <- mean(temp[i])}
+    cleanmasksP[cond,level] <- cleanup2D(temp)
 
@@
     temp <- c(EEGtargets[,ch,startindex+level],EEGtargets[,ch,startindex+level+5])
-            cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    cleanmeansE[ch,cond,level] <- mean(temp[i])}
+    cleanmeansE[ch,cond,level] <- cleanup2D(temp)
 
     temp <- c(EEGmasks[,ch,startindex+level],EEGmasks[,ch,startindex+level+5])
-                cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    cleanmasksE[ch,cond,level] <- mean(temp[i])}
+    cleanmasksE[ch,cond,level] <- cleanup2D(temp)
 
     temp <- c(EEGtargets2[,ch,startindex+level],EEGtargets2[,ch,startindex+level+5])
-                cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    cleanmeansE2[ch,cond,level] <- mean(temp[i])}
+    cleanmeansE2[ch,cond,level] <- cleanup2D(temp)
 
     temp <- c(EEGmasks2[,ch,startindex+level],EEGmasks2[,ch,startindex+level+5])
-                cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    cleanmasksE2[ch,cond,level] <- mean(temp[i])}   
-    }
-
+    cleanmasksE2[ch,cond,level] <- cleanup2D(temp) 
     }
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp1groupanalysis, include=FALSE, results='hide'}
 
@@
 
-d <- dir(datadir,pattern='*summary.RData',full.names=TRUE)
+d <- paste0('P',101:130,'summary.RData')
 
@@
 
-    load(d[s])
+    load(paste0(datadir,d[s]))
 
@@
     temp <- allmeansP[,cond,level]
-    cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+    mbs <- bootstrap2D(temp)
     cleanmeansP[cond,level] <- mbs$meanamp
@@
     cleanmeansPCI[2,cond,level] <- mbs$upperCI
-    }
 
     temp <- allmasksP[,cond,level]
-    cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-          mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+    mbs <- bootstrap2D(temp)
     cleanmasksP[cond,level] <- mbs$meanamp
@@
     cleanmasksPCI[2,cond,level] <- mbs$upperCI
-}
 
       temp <- apply(allmeansE[,electrodeindices,cond,level],1,mean)
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+      mbs <- bootstrap2D(temp)
     cleanmeansEav[cond,level] <- mbs$meanamp
@@
     cleanmeansEavCI[2,cond,level] <- mbs$upperCI
-      }
 
 temp <- apply(allmasksE[,electrodeindices,cond,level],1,mean)
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+mbs <- bootstrap2D(temp)
     cleanmasksEav[cond,level] <- mbs$meanamp
@@
     cleanmasksEavCI[2,cond,level] <- mbs$upperCI
-        }
 
 temp <- apply(allmeansE2[,electrodeindices,cond,level],1,mean)
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+mbs <- bootstrap2D(temp)
     cleanmeansE2av[cond,level] <- mbs$meanamp
@@
     cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
-        }
 
       temp <- apply(allmasksE2[,electrodeindices,cond,level],1,mean)
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+      mbs <- bootstrap2D(temp)
     cleanmasksE2av[cond,level] <- mbs$meanamp
@@
     cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
-        }
 
@@
       temp <- allmeansE[,ch,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+      mbs <- bootstrap2D(temp)
     cleanmeansE[ch,cond,level] <- mbs$meanamp
@@
     cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
-}
 
       temp <- allmasksE[,ch,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+      mbs <- bootstrap2D(temp)
     cleanmasksE[ch,cond,level] <- mbs$meanamp
@@
     cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
-        }
 
       temp <- allmeansE2[,ch,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+      mbs <- bootstrap2D(temp)
     cleanmeansE2[ch,cond,level] <- mbs$meanamp
@@
     cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
-        }
 
       temp <- allmasksE2[,ch,cond,level]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+      mbs <- bootstrap2D(temp)
     cleanmasksE2[ch,cond,level] <- mbs$meanamp
@@
     cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
-        }
 
@@
         temp <- allspectraP[,f]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+        mbs <- bootstrap2D(temp)
 meanspectraP[f] <- mbs$meanamp
@@
 meanspectraPCI[2,f] <- mbs$upperCI
-      }
 
         temp <- allspectraE[,f]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+        mbs <- bootstrap2D(temp)
 meanspectraE[f] <- mbs$meanamp
@@
 meanspectraECI[2,f] <- mbs$upperCI
-      }
+
 }
@@
 
-```{r include=FALSE, results='hide'}
+```{r createfig1, include=FALSE, results='hide'}
 
@@
 
+plotlims <- c(15,40,0,0.04) 
+ticklocsy <- seq(0,0.04,0.01)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
 par(pty="s")  # make axis square
@@
 }
-legend(22,0.03,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.028,'(e)',adj=0.5,cex=2.5)
+legend(22,0.04,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.038,'(e)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(-1,13,-1,0.5) 
+plotlims <- c(-1,13,-1.5,0.5) 
 ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
-ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklocsy <- seq(-1.5,0.5,0.5)    # locations of tick marks on y axis
 ticklabelsx <- ticklocsx        # set labels for x ticks
@@
 title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+title(ylab="Relative amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
 
@@
 
-lines(times, (sinewave/10)-0.9, col='black', lwd=3)
+lines(times, (sinewave/10)-1.4, col='black', lwd=3)
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r pupilstats, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r createfig2, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r eegstats, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r createfig3, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp2individualanalysis, include=FALSE, results='hide'}
 
@@
           temp <- temp[which(abs(temp)>0)]  
-          cartdata <- data.frame(Re(temp),Im(temp))
-          if (sum(cartdata)!=0){
-            D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-            i <- which(D<SDthresh) 
-            cleanmeansE[eye,cond] <- mean(temp[i])}
+          cleanmeansE[eye,cond] <- cleanup2D(temp)
 
@@
             temp <- temp[which(abs(temp)>0)]  
-            cartdata <- data.frame(Re(temp),Im(temp))
-            if (sum(cartdata)!=0){
-              D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-              i <- which(D<SDthresh) 
-              meanspec[eye,cond,f] <- mean(temp[i])}   
+            meanspec[eye,cond,f] <- cleanup2D(temp)
+
           }
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp2groupanalysis, include=FALSE, results='hide'}
 
@@
     temp <- allmeans[,cond,level]
-    cartdata <- data.frame(Re(temp),Im(temp))
-    if (sum(cartdata)!=0){
-      D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-      i <- which(D<SDthresh) 
-    mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+    mbs <- bootstrap2D(temp)
     cleanmeansTF[cond,level] <- mbs$meanamp
@@
     cleanmeansTFCI[2,cond,level] <- mbs$upperCI
-    }
 
@@
         temp <- allspec[,cond,level,f]
-      cartdata <- data.frame(Re(temp),Im(temp))
-      if (sum(cartdata)!=0){
-        D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-        i <- which(D<SDthresh) 
-mbs <- amperrors(temp[i],method='boot',quantiles=68,nresamples=nbootstraps)
+        mbs <- bootstrap2D(temp)
 meanspectraTF[cond,level,f] <- mbs$meanamp
@@
 }
-}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r createfig4, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r exp3analysis, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r makestanmodels, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r runstanmodels, include=FALSE, results='hide'}
 
@@
 
-if (processdata > 1){
-
-# settings for sampler 
-numSavedSteps <- 100000    # total number of MCMC steps
-adaptSteps <- 1000  # Number of steps to "tune" the samplers
-burnInSteps <- 2000 
-thinSteps <- 10
-nChains <- 8
-ncores <- 8  # because of multi-threading, this is usually double the true number of physical cores, so we halve the number as Stan can only use physical cores
-options(mc.cores=ncores)
+if (domodelling > 0){
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r makemodelfigure, include=FALSE, results='hide'}
 
@@
 
-plotlims <- c(15,40,0,0.04)
+plotlims <- c(15,40,0,0.03)
 ticklocsx <- contrastsdB    # locations of tick marks on x axis
 ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklocsy <- seq(0,0.04,0.01)    # locations of tick marks on y axis
+ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-legend(21,0.04,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.038,'(e)',adj=0.5,cex=2.5)
+legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.028,'(e)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(15,40,0,0.8)  
-ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+plotlims <- c(15,40,0,0.6)  
+ticklocsy <- seq(0,0.6,0.2)    # locations of tick marks on y axis
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-text(17,0.75,'(f)',adj=0.5,cex=2.5)
+text(17,0.55,'(f)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(15,40,0,0.8)  
-ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+plotlims <- c(15,40,0,1)  
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-text(17,0.75,'(g)',adj=0.5,cex=2.5)
+text(17,0.95,'(g)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(15,40,0,0.8)  
+plotlims <- c(15,40,0,0.6)  
 ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+ticklocsy <- seq(0,0.6,0.2)    # locations of tick marks on y axis
 ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
@@
 # legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.75,'(b)',adj=0.5,cex=2.5)
+text(17,0.55,'(b)',adj=0.5,cex=2.5)
 
@@
 postscript("edata2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+plotlims <- c(15,40,0,1)  
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy    # set labels for y ticks
 
@@
 # References
+
+<div id="refs"></div>
+
+# Appendix 1
+
+\beginsupplement
+
+```{r repindividualanalysis, include=FALSE, results='hide'}
+
+# (download and) analyse individual participant data for replication expt
+
+if (processdata > 2){
+
+legaltriggers <- 1:55
+
+timeseq <- seq(1/120,10,length.out=120*10)
+timeseq2 <- seq(1/120,14,length.out=120*14)
+EEGtimes <- seq(1/1000,10,1/1000)
+targetindex <- (2*10)+1
+maskindex <- (1.6*10)+1
+targetindex2 <- (2*2*10)+1
+maskindex2 <- (2*1.6*10)+1
+
+  for (participant in 1:12){
+
+    # only download and process data if this has not been done already for this participant
+    if (!file.exists(paste0(datadir,'P',200+participant,'summary.RData'))){
+
+      # if there is no directory for this participant's data
+      if (!file.exists(paste0(rawdir,'P',200+participant))){
+        dir.create(paste0(rawdir,'P',200+participant))
+
+       d <- dir(paste0(rawdir,'P',200+participant))
+
+       if (length(d)==0){
+
+         # if the tar file of this participant's data doesn't exist
+         if (!file.exists(paste0(rawdir,'P',200+participant,'.tar'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'sjymf'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name==paste0('P',200+participant,'.tar'))
+          osf_download(osffiles[fid,],rawdir,progress=TRUE)
+         }
+
+         # then unzip the tar file
+         untar(paste0(rawdir,'P',200+participant,'.tar'),exdir=paste0(rawdir,'P',100+participant))
+
+         # and delete the tar file to save storage space
+         file.remove(paste0(rawdir,'P',200+participant,'.tar'))
+       }
+      }
+
+      d <- dir(paste0(rawdir,'P',200+participant),full.names=TRUE)
+
+pupiltargets <- array(0,dim=c(3,2,60))
+pupiltargets2 <- array(0,dim=c(3,2,60))
+pupilmasks <- pupiltargets
+pupilmasks2 <- pupiltargets
+pupilwaveforms <- array(0,dim=c(3,2,60,120*14))
+pupilspectra <- array(0,dim=c(3,2,60,300))
+EEGtargets <- array(0,dim=c(3,64,60))
+EEGmasks <- EEGtargets
+EEGtargets2 <- EEGtargets
+EEGmasks2 <- EEGtargets
+EEGwaveforms <- array(0,dim=c(3,64,60,1000*14))
+EEGspectra <- array(0,dim=c(3,64,60,300))
+repcounterP <- 0*(1:60)
+
+psychopyfiles <- dir(path=paste0(rawdir,'P',200+participant),pattern='_block_', full.names = TRUE)
+infofiles <- dir(path=paste0(rawdir,'P',200+participant),pattern='*_info.csv', full.names = TRUE)
+EEGfiles <- dir(path=paste0(rawdir,'P',200+participant),pattern='*_EEG.csv.gz', full.names = TRUE)
+pupilfiles <- dir(path=paste0(rawdir,'P',200+participant),pattern='*_pupil_positions.csv', full.names = TRUE)
+annfiles <- dir(path=paste0(rawdir,'P',200+participant),pattern='*_annotations.csv', full.names = TRUE)
+
+for (block in 1:length(EEGfiles)){
+
+    infofile <- read.csv(infofiles[block])
+  temp <- substr(as.character(infofile[7,2]),1,16)
+  localstarttime <- as.numeric(temp)
+  adata <- read.csv(annfiles[block])
+
+    EEGdata <- read.csv(EEGfiles[block])
+    electrodes <- colnames(EEGdata)
+
+    triggertimes <- NULL
+    trialtypes <- NULL
+    counter <- 0
+    lasttrigger <- -10000
+    for (n in 1:nrow(EEGdata)){
+      if(EEGdata$Trigger[n] %in% legaltriggers){
+        if(n>(lasttrigger+10000)){
+        counter <- counter + 1
+        triggertimes[counter] <- n
+        trialtypes[counter] <- EEGdata$Trigger[n]
+        lasttrigger <- n
+      }}
+    }
+
+    trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
+    inclist <- NULL
+    for (t in 11:15){
+      i <- which(trialtypes==t)
+      inclist[t-10] <- i[2]
+    }
+    inclist <- inclist[which(!is.na(inclist))]
+    trialtypes[inclist] <- trialtypes[inclist] + 5
+
+    for (cond in 1:60){
+      for (ch in 1:64){
+        trial <- EEGdata[(triggertimes[cond]+(2001:12000)),ch+2]
+        fspec <- (fft(trial)/length(trial))
+        EEGtargets[block,ch,trialtypes[cond]] <- fspec[targetindex]
+        EEGmasks[block,ch,trialtypes[cond]] <- fspec[maskindex]
+        EEGtargets2[block,ch,trialtypes[cond]] <- fspec[targetindex2]
+        EEGmasks2[block,ch,trialtypes[cond]] <- fspec[maskindex2]
+        EEGspectra[block,ch,trialtypes[cond],1:300] <- fspec[1:300]
+
+        trial <- EEGdata[(triggertimes[cond]+(-999:13000)),ch+2]
+        EEGwaveforms[block,ch,trialtypes[cond],] <- trial - mean(trial[1:1000])
+      }}
+
+ trialtypes <- adata$condition_code[seq(1,120,2)]   
+ trialtimes <- (adata$timestamp[seq(1,120,2)] + adata$timestamp[seq(2,120,2)])/2
+
+    trialtypes[which(trialtypes>15)] <- trialtypes[which(trialtypes>15)] + 5
+    inclist <- NULL
+    for (t in 11:15){
+      i <- which(trialtypes==t)
+      inclist[t-10] <- i[2]
+    }
+    inclist <- inclist[which(!is.na(inclist))]
+    trialtypes[inclist] <- trialtypes[inclist] + 5
+
+  pdata <- read.csv(pupilfiles[block])
+  pdata2 <- pdata[,c(1,3,4,14)]
+  pdata2 <- pdata2[which(pdata2[,3]>0.2),]
+
+    for (trialno in 1:length(trialtypes)){
+      repcounterP[trialtypes[trialno]] <- repcounterP[trialtypes[trialno]] + 1
+      for (eye in 1:2){
+        eyedata <- pdata2[which(pdata2[,2]==(2-eye)),]      
+        a <- which(eyedata[,1]>trialtimes[trialno]+2)
+        b <- which(eyedata[,1]<(trialtimes[trialno]+12))
+        i <- intersect(a,b)
+        trial <- eyedata[i,]
+        trial <- trial[which(!is.na(trial[,4])),]
+        trial[,1] <- trial[,1] - trial[1,1]
+        if (nrow(trial)>3){
+          resampled <- interp1(trial[,1],trial[,4],timeseq,method='linear',extrap=TRUE)
+          fspec <- (fft(resampled)/length(resampled))
+          pupilspectra[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],1:300] <- fspec[1:300]
+          pupiltargets[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex]
+          pupilmasks[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex]
+          pupiltargets2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[targetindex2]
+          pupilmasks2[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno]] <- fspec[maskindex2]
+        }
+
+      a <- which(eyedata[,1]>(trialtimes[trialno]-1))
+      b <- which(eyedata[,1]<(trialtimes[trialno]+13))
+      i <- intersect(a,b)
+      trial <- eyedata[i,]
+      trial <- trial[which(!is.na(trial[,4])),]
+      trial[,1] <- trial[,1] - trial[1,1]
+      if (nrow(trial)>3){
+        resampled <- interp1(trial[,1],trial[,4],timeseq2,method='linear',extrap=TRUE)
+        pupilwaveforms[repcounterP[trialtypes[trialno]],eye,trialtypes[trialno],] <- resampled - mean(resampled[1:120])
+      }
+
+      }
+    }
+
+}
+
+cleanmeansP <- matrix(0,nrow=6,ncol=5)
+cleanmasksP <- matrix(0,nrow=6,ncol=5)
+cleanmeansE <- array(0,dim=c(64,6,5))
+cleanmasksE <- array(0,dim=c(64,6,5))
+cleanmeansE2 <- array(0,dim=c(64,6,5))
+cleanmasksE2 <- array(0,dim=c(64,6,5))
+
+for (cond in 1:6){
+  startindex <- (10*(cond-1))
+  for (level in 1:5){
+    temp <- c(pupiltargets[,,startindex+level],pupiltargets[,,startindex+level+5])
+    cleanmeansP[cond,level] <- cleanup2D(temp)
+
+    temp <- c(pupilmasks[,,startindex+level],pupilmasks[,,startindex+level+5])
+    cleanmasksP[cond,level] <- cleanup2D(temp)
+
+    for (ch in 1:64){
+    temp <- c(EEGtargets[,ch,startindex+level],EEGtargets[,ch,startindex+level+5])
+    cleanmeansE[ch,cond,level] <- cleanup2D(temp)
+
+    temp <- c(EEGmasks[,ch,startindex+level],EEGmasks[,ch,startindex+level+5])
+    cleanmasksE[ch,cond,level] <- cleanup2D(temp)
+
+    temp <- c(EEGtargets2[,ch,startindex+level],EEGtargets2[,ch,startindex+level+5])
+    cleanmeansE2[ch,cond,level] <- cleanup2D(temp)
+
+    temp <- c(EEGmasks2[,ch,startindex+level],EEGmasks2[,ch,startindex+level+5])
+    cleanmasksE2[ch,cond,level] <- cleanup2D(temp) 
+    }
+}
+}
+
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
+meanwavesE <- apply(EEGwaveforms[,electrodeindices,c(15,20),],4,mean,na.rm=TRUE)
+meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
+meanspectraE <- apply(EEGspectra[,electrodeindices,c(15,20),],4,mean,na.rm=TRUE)
+save(file=paste(datadir,'P',200+participant,'summary.RData',sep=''),list=c('cleanmeansP','cleanmeansE','cleanmeansE2','cleanmasksP','cleanmasksE','cleanmasksE2','meanspectraP','meanspectraE','meanwavesP','meanwavesE','electrodes'))
+
+      }
+
+      }
+
+  }
+
+```
+
+```{r repgroupanalysis, include=FALSE, results='hide'}
+
+# load in individual participant data and average, save group data
+
+if (processdata > 1){
+
+         if (!file.exists(paste0(datadir,'headerfile.csv'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'x8u4v'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='headerfile.csv')
+          osf_download(osffiles[fid,],datadir,progress=TRUE)
+          }
+
+  hdata <- read.csv(paste0(datadir,'headerfile.csv'))
+
+for (participant in 1:12){
+         # if the summary file of this participant's data doesn't exist
+         if (!file.exists(paste0(datadir,'P',200+participant,'summary.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name==paste0('P',200+participant,'summary.RData'))
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+}
+
+d <- paste0('P',201:212,'summary.RData')
+
+allmasksP <- array(0,dim=c(length(d),6,5))
+allmeansP <- allmasksP
+allmasksE <- array(0,dim=c(length(d),64,6,5))
+allmeansE <- allmasksE
+allmeansE2 <- allmeansE
+allmasksE2 <- allmasksE
+allspectraP <- array(0,dim=c(length(d),300))
+allspectraE <- array(0,dim=c(length(d),300))
+allwavesP <- array(0,dim=c(length(d),1680))
+allwavesE <- array(0,dim=c(length(d),14000))
+
+  for (s in 1:length(d)){
+
+    load(paste0(datadir,d[s]))
+
+  allmasksP[s,,] <- cleanmasksP
+  allmeansP[s,,] <- cleanmeansP
+  allspectraP[s,] <- meanspectraP
+  allspectraE[s,] <- meanspectraE
+  allwavesP[s,] <- meanwavesP
+  allwavesE[s,] <- meanwavesE
+  allmeansE[s,,,] <- cleanmeansE
+  allmasksE[s,,,] <- cleanmasksE
+  allmeansE2[s,,,] <- cleanmeansE2
+  allmasksE2[s,,,] <- cleanmasksE2
+
+  }
+
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+cleanmeansP <- matrix(0,nrow=6,ncol=5)
+cleanmeansPCI <- array(0,c(2,6,5))
+cleanmasksP <- matrix(0,nrow=6,ncol=5)
+cleanmasksPCI <- array(0,c(2,6,5))
+cleanmeansEav <- matrix(0,nrow=6,ncol=5)
+cleanmeansEavCI <- array(0,c(2,6,5))
+cleanmasksEav <- matrix(0,nrow=6,ncol=5)
+cleanmasksEavCI <- array(0,c(2,6,5))
+cleanmeansE2av <- matrix(0,nrow=6,ncol=5)
+cleanmeansE2avCI <- array(0,c(2,6,5))
+cleanmasksE2av <- matrix(0,nrow=6,ncol=5)
+cleanmasksE2avCI <- array(0,c(2,6,5))
+cleanmeansE <- array(0,dim=c(64,6,5))
+cleanmeansECI <- array(0,c(2,64,6,5))
+cleanmasksE <- array(0,dim=c(64,6,5))
+cleanmasksECI <- array(0,c(2,64,6,5))
+cleanmeansE2 <- array(0,dim=c(64,6,5))
+cleanmeansE2CI <- array(0,c(2,64,6,5))
+cleanmasksE2 <- array(0,dim=c(64,6,5))
+cleanmasksE2CI <- array(0,c(2,64,6,5))
+
+for (cond in 1:6){
+  for (level in 1:5){
+
+    temp <- allmeansP[,cond,level]
+    mbs <- bootstrap2D(temp)
+    cleanmeansP[cond,level] <- mbs$meanamp
+    cleanmeansPCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansPCI[2,cond,level] <- mbs$upperCI
+
+    temp <- allmasksP[,cond,level]
+    mbs <- bootstrap2D(temp)
+    cleanmasksP[cond,level] <- mbs$meanamp
+    cleanmasksPCI[1,cond,level] <- mbs$lowerCI
+    cleanmasksPCI[2,cond,level] <- mbs$upperCI
+
+      temp <- apply(allmeansE[,electrodeindices,cond,level],1,mean)
+      mbs <- bootstrap2D(temp)
+    cleanmeansEav[cond,level] <- mbs$meanamp
+    cleanmeansEavCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansEavCI[2,cond,level] <- mbs$upperCI
+
+temp <- apply(allmasksE[,electrodeindices,cond,level],1,mean)
+mbs <- bootstrap2D(temp)
+    cleanmasksEav[cond,level] <- mbs$meanamp
+    cleanmasksEavCI[1,cond,level] <- mbs$lowerCI
+    cleanmasksEavCI[2,cond,level] <- mbs$upperCI
+
+temp <- apply(allmeansE2[,electrodeindices,cond,level],1,mean)
+mbs <- bootstrap2D(temp)
+    cleanmeansE2av[cond,level] <- mbs$meanamp
+    cleanmeansE2avCI[1,cond,level] <- mbs$lowerCI
+    cleanmeansE2avCI[2,cond,level] <- mbs$upperCI
+
+      temp <- apply(allmasksE2[,electrodeindices,cond,level],1,mean)
+      mbs <- bootstrap2D(temp)
+    cleanmasksE2av[cond,level] <- mbs$meanamp
+    cleanmasksE2avCI[1,cond,level] <- mbs$lowerCI
+    cleanmasksE2avCI[2,cond,level] <- mbs$upperCI
+
+    for (ch in 1:64){
+
+      temp <- allmeansE[,ch,cond,level]
+      mbs <- bootstrap2D(temp)
+    cleanmeansE[ch,cond,level] <- mbs$meanamp
+    cleanmeansECI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmeansECI[2,ch,cond,level] <- mbs$upperCI
+
+      temp <- allmasksE[,ch,cond,level]
+      mbs <- bootstrap2D(temp)
+    cleanmasksE[ch,cond,level] <- mbs$meanamp
+    cleanmasksECI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmasksECI[2,ch,cond,level] <- mbs$upperCI
+
+      temp <- allmeansE2[,ch,cond,level]
+      mbs <- bootstrap2D(temp)
+    cleanmeansE2[ch,cond,level] <- mbs$meanamp
+    cleanmeansE2CI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmeansE2CI[2,ch,cond,level] <- mbs$upperCI
+
+      temp <- allmasksE2[,ch,cond,level]
+      mbs <- bootstrap2D(temp)
+    cleanmasksE2[ch,cond,level] <- mbs$meanamp
+    cleanmasksE2CI[1,ch,cond,level] <- mbs$lowerCI
+    cleanmasksE2CI[2,ch,cond,level] <- mbs$upperCI
+
+    }}}
+
+meanspectraP <- (1:300)*0
+meanspectraE <- (1:300)*0
+meanspectraPCI <- array(0,c(2,300))
+meanspectraECI <- array(0,c(2,300))
+
+for (f in 2:300){
+
+        temp <- allspectraP[,f]
+        mbs <- bootstrap2D(temp)
+meanspectraP[f] <- mbs$meanamp
+meanspectraPCI[1,f] <- mbs$lowerCI
+meanspectraPCI[2,f] <- mbs$upperCI
+
+        temp <- allspectraE[,f]
+        mbs <- bootstrap2D(temp)
+meanspectraE[f] <- mbs$meanamp
+meanspectraECI[1,f] <- mbs$lowerCI
+meanspectraECI[2,f] <- mbs$upperCI
+
+}
+
+meanwavesP <- NULL
+meanwavesE <- NULL
+meanwavesPCI <- array(0,dim=c(2,dim(allwavesP)[2]))
+meanwavesECI <- array(0,dim=c(2,dim(allwavesE)[2]))
+nsubjs <- dim(allwavesP)[1]
+for (t in 1:dim(allwavesP)[2]){
+  temp <- allwavesP[,t]
+  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
+  meanwavesP[t] <- mean(temp[i])
+  bspop <- NULL
+  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
+  meanwavesPCI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
+}
+
+for (t in 1:dim(allwavesE)[2]){
+    temp <- allwavesE[,t]
+  i <- which(abs(temp-mean(temp))<(SDthresh*sd(temp)))
+  meanwavesE[t] <- mean(temp[i])
+  bspop <- NULL
+  for (s in 1:nbootstraps){bspop[s] <- mean(sample(temp[i],length(i),replace=TRUE))}
+  meanwavesECI[,t] <- quantile(bspop,c(0.16,0.84),na.rm=TRUE)
+}
+
+save(file=paste0(datadir,'Replicationdata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2'))
+
+}
+
+```
+
+```{r createfigA1, include=FALSE, results='hide'}
+
+# generate plot showing the group pupillometry data
+
+         if (!file.exists(paste0(datadir,'Replicationdata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Replicationdata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(file=paste0(datadir,'Replicationdata.RData'))
+
+if (processdata > 0){
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+plotlims <- c(15,40,0,0.03) 
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("CRF1p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[cond,]),contrastsdB,cleanmeansPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(22,0.03,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF2p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+condlist <- c(1,5,6)
+pointlist <- c(21,24,25)
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansP[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansP[condlist[cond],]),contrastsdB,cleanmeansPCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)  
+  points(contrastsdB,abs(cleanmeansP[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(22,0.03,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(d)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF3p.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+plotlims <- c(15,40,0,0.04) 
+ticklocsy <- seq(0,0.04,0.01)    # locations of tick marks on y axis
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude at 1.6Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+for (cond in 4:6){
+  lines(contrastsdB,abs(cleanmasksP[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
+  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksP[cond,]),contrastsdB,cleanmasksPCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)    
+  points(contrastsdB,abs(cleanmasksP[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
+}
+legend(22,0.04,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.038,'(e)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("SpecP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+frequencies <- (0:299)/10
+
+plotlims <- c(1,6,0,0.03) 
+ticklocsx <- seq(1,6,1)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+polygon(frequencies[c(11:61,61:11)],c(meanspectraPCI[1,11:61],meanspectraPCI[2,61:11]),col=colpal[2],border=NA)
+
+lines(frequencies[11:61],abs(meanspectraP[11:61]), col=colpal[2], lwd=3, cex=0.5)
+
+text(1.1,0.028,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("timecourseP.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+times <- seq((1/120)-1,13,1/120)
+sinewave <- sin(2*times * 2*pi)
+sinewave[1:120] <- 0
+sinewave[1560:1680] <- 0
+
+plotlims <- c(-1,13,-1,0.5) 
+ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
+ticklocsy <- seq(-1,0.5,0.5)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Relative amplitude (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+filt <- butter(3,0.083)
+filtwaveP <- signal::filter(filt, meanwavesP)
+filtL <- signal::filter(filt,meanwavesPCI[1,])
+filtU <- signal::filter(filt,meanwavesPCI[2,])
+filtU[which(filtU>0.5)] <- 0.5  # crop upper error region at y-maximum
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
+
+lines(times, filtwaveP, col=colpal[2], lwd=1.5)
+
+lines(times, (sinewave/10)-0.9, col='black', lwd=3)
+
+text(-0.7,0.4,'(a)',adj=0.5,cex=2.5)
+
+dev.off()
+
+         if (!file.exists(paste0(localdir,'StimulusExample.png'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'tbema'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='StimulusExample.png')
+          osf_download(osffiles[fid,],localdir,progress=TRUE)
+         }
+
+stim <- readPNG('local/StimulusExample.png')
+
+  PostScriptTrace('CRF1p.ps')
+  p1 <- readPicture('CRF1p.ps.xml')
+  PostScriptTrace('CRF2p.ps')
+  p2 <- readPicture('CRF2p.ps.xml')
+  PostScriptTrace('CRF3p.ps')
+  p3 <- readPicture('CRF3p.ps.xml')
+  PostScriptTrace('SpecP.ps')
+  p4 <- readPicture('SpecP.ps.xml')
+  PostScriptTrace('timecourseP.ps')
+  p5 <- readPicture('timecourseP.ps.xml')
+
+    for (n in 1:length(p4@paths)){
+    temp <- class(p4@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p4@paths[n]$path@rgb))<765){p4@paths[n]$path@rgb <- addalpha(p4@paths[n]$path@rgb,alpha=0.2)}}}
+
+      for (n in 1:length(p5@paths)){
+    temp <- class(p5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p5@paths[n]$path@rgb))<765){p5@paths[n]$path@rgb <- addalpha(p5@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf(paste0(figdir,"pupildataRep.pdf"), bg="transparent", height = 10, width = 15)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  aspratio <- 10/15  # this is the aspect ratio of the output pdf
+  imwidth <- 0.2
+  xstart <- 0.85
+  ystart <- 0.72
+  rasterImage(stim,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  grid.picture(p1,x=0.17,y=0.25,width=0.32,height=1)
+  grid.picture(p2,x=0.5,y=0.25,width=0.32,height=1)
+  grid.picture(p3,x=0.83,y=0.25,width=0.32,height=1)
+  grid.picture(p5,x=0.25,y=0.7,width=0.5,height=1)
+  grid.picture(p4,x=0.75,y=0.7,width=0.5,height=1)
+
+  text(0.5,0.98,'Pupillometry',cex=4)
+
+  dev.off()
+
+  file.remove(c('CRF1p.ps','CRF2p.ps','CRF3p.ps','SpecP.ps','timecourseP.ps'))
+  file.remove(c('CRF1p.ps.xml','CRF2p.ps.xml','CRF3p.ps.xml','SpecP.ps.xml','timecourseP.ps.xml'))
+
+}
+
+```
+
+```{r createfigA2, include=FALSE, results='hide'}
+
+# generate plot showing the group EEG data
+
+contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+         if (!file.exists(paste0(datadir,'headerfile.csv'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'x8u4v'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='headerfile.csv')
+          osf_download(osffiles[fid,],datadir,progress=TRUE)
+          } 
+hdata <- read.csv(paste0(datadir,'headerfile.csv'))
+
+         if (!file.exists(paste0(datadir,'Replicationdata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Replicationdata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(file=paste0(datadir,'Replicationdata.RData'))
+
+electrodeindices <- match(targetelectrodes,electrodes)-2
+
+if (processdata > 0){
+
+plotlims <- c(15,40,0,0.5)  
+ticklocsx <- contrastsdB    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.5,0.1)    # locations of tick marks on y axis
+ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+postscript("CRF1e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansEav[cond,]),contrastsdB,cleanmeansEavCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansEav[cond,]),contrastsdB,cleanmeansEavCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(22,0.5,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.475,'(c)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF2e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
+title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,5,6)
+pointlist <- c(21,24,25)
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansEav[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
+  arrows(contrastsdB,abs(cleanmeansEav[condlist[cond],]),contrastsdB,cleanmeansEavCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansEav[condlist[cond],]),contrastsdB,cleanmeansEavCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansEav[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(22,0.5,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.475,'(d)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF3e.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV) at 1.6Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 4:6){
+  lines(contrastsdB,abs(cleanmasksEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
+  arrows(contrastsdB,abs(cleanmasksEav[cond,]),contrastsdB,cleanmasksEavCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksEav[cond,]),contrastsdB,cleanmasksEavCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksEav[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
+}
+legend(22,0.5,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.475,'(e)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF1e2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
+  arrows(contrastsdB,abs(cleanmeansE2av[cond,]),contrastsdB,cleanmeansE2avCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+
+  arrows(contrastsdB,abs(cleanmeansE2av[cond,]),contrastsdB,cleanmeansE2avCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+legend(22,0.5,c('Monocular','Binocular','Dichoptic'),pch=21:23,pt.bg=colpal[1:3],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.475,'(f)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF2e2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)   
+title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+condlist <- c(1,5,6)
+pointlist <- c(21,24,25)
+for (cond in 1:3){
+  lines(contrastsdB,abs(cleanmeansE2av[condlist[cond],]), col=colpal[condlist[cond]], lwd=3, cex=0.5)  
+  arrows(contrastsdB,abs(cleanmeansE2av[condlist[cond],]),contrastsdB,cleanmeansE2avCI[1,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmeansE2av[condlist[cond],]),contrastsdB,cleanmeansE2avCI[2,condlist[cond],],lwd=3,col=colpal[condlist[cond]],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmeansE2av[condlist[cond],]), pch = pointlist[cond], col='black', bg=colpal[condlist[cond]], cex=1.6, lwd=3)   
+}  
+legend(22,0.5,c('Monocular','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[condlist],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.475,'(g)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("CRF3e2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV) at 3.2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+for (cond in 4:6){
+  lines(contrastsdB,abs(cleanmasksE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)   
+  arrows(contrastsdB,abs(cleanmasksE2av[cond,]),contrastsdB,cleanmasksE2avCI[1,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  arrows(contrastsdB,abs(cleanmasksE2av[cond,]),contrastsdB,cleanmasksE2avCI[2,cond,],lwd=3,col=colpal[cond],length=0.05,angle=90)
+  points(contrastsdB,abs(cleanmasksE2av[cond,]), pch = pointlist[cond-3], col='black', bg=colpal[cond], cex=1.6, lwd=3) 
+}
+legend(22,0.5,c('Monocular 1.6Hz','Binocular cross','Dichoptic cross'),pch=pointlist,pt.bg=colpal[4:6],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.475,'(h)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("SpecE.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+frequencies <- (0:299)/10
+
+plotlims <- c(1,6,0,1) 
+ticklocsx <- seq(1,6,1)    # locations of tick marks on x axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+polygon(frequencies[c(11:61,61:11)],c(meanspectraECI[1,11:61],meanspectraECI[2,61:11]),col=colpal[2],border=NA)
+
+lines(frequencies[11:61],abs(meanspectraE[11:61]), col=colpal[2], lwd=3, cex=0.5)
+
+text(1.1,0.95,'(b)',adj=0.5,cex=2.5)
+
+dev.off()
+
+postscript("timecourseE.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 8)
+
+times <- seq((1/1000)-1,13,1/1000)
+sinewave <- sin(2*times * 2*pi)
+sinewave[1:1000] <- 0
+sinewave[13001:14000] <- 0
+
+plotlims <- c(-1,13,-10,20) 
+ticklocsx <- seq(-1,13,1)    # locations of tick marks on x axis
+ticklocsy <- seq(-10,20,10)    # locations of tick marks on y axis
+ticklabelsx <- ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+filt <- butter(3,0.083*0.12)
+filtwaveE <- signal::filter(filt, meanwavesE)
+filtU <- signal::filter(filt,meanwavesECI[1,])
+filtL <- signal::filter(filt,meanwavesECI[2,])
+polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=colpal[2],border=NA)
+
+lines(times, filtwaveE, col=colpal[2], lwd=1.5)
+
+lines(times, (sinewave*2.5)-7.5, col='black', lwd=3)
+
+text(-0.7,18,'(a)',adj=0.5,cex=2.5)
+
+dev.off()
+
+xpos <- 1:64
+ypos <- 1:64
+montageE <- toupper(as.character(hdata$Electrode))
+for (ch in 1:64){
+  i <- match(toupper(electrodes[ch+2]),montageE)
+  xpos[ch] <- hdata$X_position[i]
+  ypos[ch] <- hdata$Y_position[i]
+}
+
+ramp2 <- colorRamp(c("white",colpal[2]))  # create a ramp from one colour to another
+colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
+
+## Create data frame to be used for interpolation - the function needs columns labelled x, y, and z
+rmax <- 0.55   #specify a maximum boundary for the grid
+gridRes <- 100 #specify the interpolation grid resolution
+
+toplot <- abs(cleanmeansE[,2,5])
+toplot[which(is.na(toplot))] <- 0
+testDat<- data.frame(x = xpos, y = -ypos, z = toplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+
+tiff("head1.tiff", height = 600, width = 600, units="px", bg="white")
+
+plotlims <- c(-rmax,rmax,-rmax,rmax) 
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,1),add=TRUE,useRaster=TRUE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match(toupper(targetelectrodes),toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=2)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+dev.off()
+
+toplot <- abs(cleanmeansE2[,2,5])
+toplot[which(is.na(toplot))] <- 0
+testDat<- data.frame(x = xpos, y = -ypos, z = toplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+zo2[which(zo2>1)] <- 1
+
+tiff("head2.tiff", height = 600, width = 600, units="px", bg="white")
+
+plotlims <- c(-rmax,rmax,-rmax,rmax) 
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])  
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,1),add=TRUE,useRaster=TRUE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match(toupper(targetelectrodes),toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=2)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+dev.off()
+
+  PostScriptTrace('CRF1e.ps')
+  p1 <- readPicture('CRF1e.ps.xml')
+  PostScriptTrace('CRF2e.ps')
+  p2 <- readPicture('CRF2e.ps.xml')
+  PostScriptTrace('CRF3e.ps')
+  p3 <- readPicture('CRF3e.ps.xml')
+  PostScriptTrace('SpecE.ps')
+  p4 <- readPicture('SpecE.ps.xml')
+  PostScriptTrace('timecourseE.ps')
+  p5 <- readPicture('timecourseE.ps.xml')
+  PostScriptTrace('CRF1e2.ps')
+  p6 <- readPicture('CRF1e2.ps.xml')
+  PostScriptTrace('CRF2e2.ps')
+  p7 <- readPicture('CRF2e2.ps.xml')
+  PostScriptTrace('CRF3e2.ps')
+  p8 <- readPicture('CRF3e2.ps.xml')
+
+    for (n in 1:length(p4@paths)){
+    temp <- class(p4@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p4@paths[n]$path@rgb))<765){p4@paths[n]$path@rgb <- addalpha(p4@paths[n]$path@rgb,alpha=0.2)}}}
+
+      for (n in 1:length(p5@paths)){
+    temp <- class(p5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(p5@paths[n]$path@rgb))<765){p5@paths[n]$path@rgb <- addalpha(p5@paths[n]$path@rgb,alpha=0.2)}}}
+
+  h1 <- readTIFF('head1.tiff')
+  h2 <- readTIFF('head2.tiff')
+
+  pdf(paste0(figdir,"EEGdataRep.pdf"), bg="transparent", height = 15, width = 15)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  # insert the head plots first so the white border doesn't overlap the other graphs
+    aspratio <- 1  # this is the aspect ratio of the output pdf
+  imwidth <- 0.16
+  xstart <- 0.65
+  ystart <- 0.82
+  rasterImage(h1,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth) 
+  xstart <- 0.82
+  ystart <- 0.82
+  rasterImage(h2,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  grid.picture(p5,x=0.25,y=0.8,width=0.5,height=1)
+  grid.picture(p4,x=0.75,y=0.8,width=0.5,height=1)
+  grid.picture(p1,x=0.17,y=0.5,width=0.32,height=1)
+  grid.picture(p2,x=0.5,y=0.5,width=0.32,height=1)
+  grid.picture(p3,x=0.83,y=0.5,width=0.32,height=1)
+  grid.picture(p6,x=0.17,y=0.175,width=0.32,height=1)
+  grid.picture(p7,x=0.5,y=0.175,width=0.32,height=1)
+  grid.picture(p8,x=0.83,y=0.175,width=0.32,height=1)
+
+    text(0.5,1,'Electroencephalography',cex=4)
+
+  dev.off()
+
+  file.remove(c('CRF1e.ps','CRF2e.ps','CRF3e.ps','CRF1e2.ps','CRF2e2.ps','CRF3e2.ps','SpecE.ps','timecourseE.ps','head1.tiff','head2.tiff'))
+  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF3e.ps.xml','CRF1e2.ps.xml','CRF2e2.ps.xml','CRF3e2.ps.xml','SpecE.ps.xml','timecourseE.ps.xml'))
+
+}
+
+```

### 2023-06-07 manuscript.tex
Added analysis of replication data

@@
   pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
-  pdfauthor={Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker},
   hidelinks,
@@
 \title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
-\author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{Department of Psychology, University of York, UK}
+\author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
+Department of Psychology, University of York, UK\\
+\emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
+\date{}
 

### 2023-06-07 renameandupload.R

@@ -80,3 +80,32 @@ for (s in 1:12){
   
 }
 
+
+osfproject <- osf_retrieve_node("sjymf")
+componentlist <- osf_ls_nodes(osfproject)
+
+p <- getwd()
+
+for (s in 1:12){
+  
+  subj <- paste0('P',s+200)
+  
+  subjdir <- paste0('/Users/db900/Documents/git/PupillometryEEG/local/rawdata/',subj)
+  if (!file.exists(subjdir)){dir.create(subjdir)}
+  
+  setwd(subjdir)
+  
+  d <- dir(subjdir)
+  
+  tar(tarfile=paste0(subj,'.tar'),files=d,compression='gzip')
+  setwd(p)
+  
+  datafilesonOSF <- osf_ls_files(osfproject,n_max=300)
+  
+  if (!pmatch(paste0(subj,'.tar'),datafilesonOSF$name,nomatch=0)){
+    osf_upload(osfproject,paste0(subjdir,'/',subj,'.tar'),progress=TRUE)
+  }
+  
+  # unlink(subjdir,recursive=TRUE)
+  
+}

### 2023-06-09 manuscript.Rmd
Added lines at the beginning to link to figures (and not to captions) and to link to references.

@@
 bibliography: references.bib
+link-citations: true
 csl: elife.csl
@@
 - \renewcommand{\thefigure}{A\arabic{figure}}}
+- \usepackage{caption}
 ---
@@
 
-processdata <- 2  # this flag determines the amount of processing, with 4 levels:
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 
-domodelling <- 1    # if set to 1, run the Stan models (takes ~24 hours)
+domodelling <- 0    # if set to 1, run the Stan models (takes ~24 hours)
 

### 2023-06-09 manuscript.tex
Added lines at the beginning to link to figures (and not to captions) and to link to references.

--- 2023-01-12 manuscript.tex
@@
 \setcounter{secnumdepth}{5}
+\usepackage{float}
+\usepackage{float} \floatplacement{figure}{H}
+\newcommand{\beginsupplement}{\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}}
+\usepackage{caption}
 
 \title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
-\author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker}
-\date{Department of Psychology, University of York, UK}
+\author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
+Department of Psychology, University of York, UK\\
+\emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
+\date{}
 
@@
 The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
-This involves a process of signal combination both within (Baker and Wade, 2017) and between (Ernst and Banks, 2002) the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, 1962).
-Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
-However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, 2008) and much less is known about the computations that operate in these subcortical pathways.
+This involves a process of signal combination both within (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}) and between (Ernst and Banks, \protect\hyperlink{ref-Ernst2002}{2002}) the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}).
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., \protect\hyperlink{ref-Purves2008}{2008}).
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}) and much less is known about the computations that operate in these subcortical pathways.
 In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
@@
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., 2018; Campbell and Green, 1965).
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance' (Baker et al., 2007): perceived contrast does not change when one eye is opened and closed.
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., \protect\hyperlink{ref-Baker2018}{2018}; Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}).
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, \protect\hyperlink{ref-Legge1984}{1984}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) and neural activity (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}): perceived contrast does not change when one eye is opened and closed.
 
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, 2008).
-There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (1981)).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2008; Wang and Munoz, 2015).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the computation that achieves this is achieved is unclear.
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}).
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (\protect\hyperlink{ref-Wyatt1981}{1981})).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., \protect\hyperlink{ref-Angee2021}{2021}; Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}).
+To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, \protect\hyperlink{ref-Doesschate1967}{1967}), yet the computation that achieves this is achieved is unclear.
 
@@
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Periodic flicker entrains both neural (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}) and pupil (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
@@
 Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; Kassner et al.
-(2014)) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+(\protect\hyperlink{ref-Kassner2014}{2014})) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, \protect\hyperlink{ref-Delorme2004}{2004}).
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (2021).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (1991) that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, \protect\hyperlink{ref-Baker2021}{2021}).
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (\protect\hyperlink{ref-Baker2021}{2021}).
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (\protect\hyperlink{ref-Victor1991}{1991}) that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., 2014), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.~Spitschan et al., 2014).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., 2022).
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.~Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., \protect\hyperlink{ref-Figueira2022}{2022}).
 
@@
 To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
-(2006).
-The second gain control stage was omitted (consistent with Baker and Wade, 2017) to simplify the model and reduce the number of free parameters.
+(\protect\hyperlink{ref-Meese2006}{2006}).
+The second gain control stage was omitted (consistent with Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}) to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 Despite being derived from the model proposed by Meese et al.
-(2006), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
+(\protect\hyperlink{ref-Meese2006}{2006}), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Doesschate and Alpern, \protect\hyperlink{ref-Doesschate1967}{1967}; Legge, \protect\hyperlink{ref-Legge1984}{1984}; Schrödinger, \protect\hyperlink{ref-Schrodinger1926}{1926}).
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., \protect\hyperlink{ref-Baker2012}{2012}; Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
 Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, 2017).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., 2020).
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}).
 
-We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., 2017).
+We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., 2012; Meese et al., 2006).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., \protect\hyperlink{ref-Baker2012}{2012}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}).
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, 2021) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, \protect\hyperlink{ref-Baker2021}{2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
 The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
@@
 
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, 2017).
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
 One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, \protect\hyperlink{ref-Anstis1998}{1998}; Levelt, \protect\hyperlink{ref-Levelt1965}{1965}; Quaia et al., \protect\hyperlink{ref-Quaia2018}{2018}).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006), and the peak location of our prior distribution (black curve).
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}), and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
@@
 For example, Quaia et al.
-(2018) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (2019) report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., 2020).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, 1998; Baker et al., 2012; Levelt, 1965), though not for luminance decrements (Anstis and Ho, 1998).
+(\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, \protect\hyperlink{ref-Anstis1998}{1998}; Baker et al., \protect\hyperlink{ref-Baker2012}{2012}; Levelt, \protect\hyperlink{ref-Levelt1965}{1965}), though not for luminance decrements (Anstis and Ho, \protect\hyperlink{ref-Anstis1998}{1998}).
 Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
@@
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-Baker and Wade (2017) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, 2002).
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, 1994; May and Zhaoping, 2022).
+Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, \protect\hyperlink{ref-Ernst2002}{2002}).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, \protect\hyperlink{ref-Li1994}{1994}; May and Zhaoping, \protect\hyperlink{ref-May2022}{2022}).
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.~Spitschan et al., 2014).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.~Bradley et al., 2008).
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.~Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.~Bradley et al., \protect\hyperlink{ref-Bradley2008}{2008}).
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
@@
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, 1981; Livingstone and Hubel, 1984) are biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988), and relatively insensitive to stimulus orientation (Horton and Hubel, 1981; Livingstone and Hubel, 1984; though see Economides et al., 2011).
-As the blob regions are embedded within ocular dominance columns (Horton and Hubel, 1981), they are also largely monocular (Livingstone and Hubel, 1984; Tychsen et al., 2004).
-More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., 2013) and achromatic (Meese and Baker, 2011) mechanisms, that also appear to be monocular.
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, \protect\hyperlink{ref-Horton1981}{1981}; Livingstone and Hubel, \protect\hyperlink{ref-Livingstone1984}{1984}) are biased towards low spatial frequencies (Edwards et al., \protect\hyperlink{ref-Edwards1995}{1995}; Tootell et al., \protect\hyperlink{ref-Tootell1988}{1988}), and relatively insensitive to stimulus orientation (Horton and Hubel, \protect\hyperlink{ref-Horton1981}{1981}; Livingstone and Hubel, \protect\hyperlink{ref-Livingstone1984}{1984}; though see Economides et al., \protect\hyperlink{ref-Economides2011}{2011}).
+As the blob regions are embedded within ocular dominance columns (Horton and Hubel, \protect\hyperlink{ref-Horton1981}{1981}), they are also largely monocular (Livingstone and Hubel, \protect\hyperlink{ref-Livingstone1984}{1984}; Tychsen et al., \protect\hyperlink{ref-Tychsen2004}{2004}).
+More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., \protect\hyperlink{ref-Gheiratmand2013}{2013}) and achromatic (Meese and Baker, \protect\hyperlink{ref-Meese2011}{2011}) mechanisms, that also appear to be monocular.
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
@@
 \hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
+\section{References}\label{references}}
 
@@
 
+\hypertarget{appendix-1}{%
+\section{Appendix 1}\label{appendix-1}}
+
+\beginsupplement
+
 \end{document}

### 2023-06-10 manuscript.Rmd
Incorporated new model fits

@@
 # settings for sampler 
-numSavedSteps <- 1000    # total number of MCMC steps
+numSavedSteps <- 100000    # total number of MCMC steps
 adaptSteps <- 1000  # Number of steps to "tune" the samplers
@@
 
-plotlims <- c(15,40,0,0.03)
+plotlims <- c(15,40,0,0.04)
 ticklocsx <- contrastsdB    # locations of tick marks on x axis
 ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
+ticklocsy <- seq(0,0.04,0.01)    # locations of tick marks on y axis
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
 
@@
 
-legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.028,'(e)',adj=0.5,cex=2.5)
+legend(21,0.04,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
+
+text(17,0.037,'(e)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(15,40,0,0.6)  
-ticklocsy <- seq(0,0.6,0.2)    # locations of tick marks on y axis
+plotlims <- c(15,40,0,1)  
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
 ticklabelsy <- ticklocsy    # set labels for y ticks
@@
 
-text(17,0.55,'(f)',adj=0.5,cex=2.5)
+text(17,0.95,'(f)',adj=0.5,cex=2.5)
 
@@
 
-plotlims <- c(15,40,0,0.6)  
+plotlims <- c(15,40,0,1)  
 ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.6,0.2)    # locations of tick marks on y axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
 ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
@@
 # legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.55,'(b)',adj=0.5,cex=2.5)
+text(17,0.95,'(b)',adj=0.5,cex=2.5)
 
@@
 # legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.75,'(c)',adj=0.5,cex=2.5)
+text(17,0.95,'(c)',adj=0.5,cex=2.5)
 

### 2023-06-10 manuscript.tex
Incorporated new model fits

--- 2023-06-07 manuscript.tex
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{float}
+\usepackage{float} \floatplacement{figure}{H}
+\newcommand{\beginsupplement}{\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}}
+\usepackage{caption}
 \ifLuaTeX
@@
 The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
-This involves a process of signal combination both within (Baker and Wade, 2017) and between (Ernst and Banks, 2002) the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, 1962).
-Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., 2008).
-However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, 2008) and much less is known about the computations that operate in these subcortical pathways.
+This involves a process of signal combination both within (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}) and between (\protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}) the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}).
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (\protect\hyperlink{ref-Purves2008}{Purves et al., 2008}).
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (\protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}) and much less is known about the computations that operate in these subcortical pathways.
 In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
@@
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., 2018; Campbell and Green, 1965).
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (Legge, 1984; Meese et al., 2006) and neural activity (Baker and Wade, 2017; Moradi and Heeger, 2009) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (Ding and Sperling, 2006; Meese et al., 2006) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance' (Baker et al., 2007): perceived contrast does not change when one eye is opened and closed.
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}).
+This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (\protect\hyperlink{ref-Legge1984}{Legge, 1984}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) and neural activity (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (\protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}): perceived contrast does not change when one eye is opened and closed.
 
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, 2008).
-There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (1981)).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., 2021; Mathôt, 2018; McDougal and Gamlin, 2008; Wang and Munoz, 2015).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, 1967), yet the computation that achieves this is achieved is unclear.
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (\protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}).
+There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (\protect\hyperlink{ref-Wyatt1981}{1981})).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (\protect\hyperlink{ref-Angee2021}{Angée et al., 2021}; \protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}; \protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
+To account for the consensual response, these brain regions must combine information from the left and right eyes (\protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}), yet the computation that achieves this is achieved is unclear.
 
@@
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Periodic flicker entrains both neural (Norcia et al., 2015) and pupil (Spitschan et al., 2014) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Periodic flicker entrains both neural (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}) and pupil (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, 2004).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (\protect\hyperlink{ref-Delorme2004}{Delorme and Makeig, 2004}).
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, 2021).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (2021).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (1991) that can compare more than two conditions.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see \protect\hyperlink{ref-Baker2021}{Baker, 2021}).
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (\protect\hyperlink{ref-Baker2021}{2021}).
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (\protect\hyperlink{ref-Victor1991}{1991}) that can compare more than two conditions.
 
 A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., 2014), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
 The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
@@
 Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.
-Spitschan et al., 2014).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see Barrionuevo et al., 2014; Barrionuevo and Cao, 2016).
+\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}).
 Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
-Figueira et al., 2022).
+\protect\hyperlink{ref-Figueira2022}{Figueira et al., 2022}).
 
@@
 To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
-(2006).
-The second gain control stage was omitted (consistent with Baker and Wade, 2017) to simplify the model and reduce the number of free parameters.
+(\protect\hyperlink{ref-Meese2006}{2006}).
+The second gain control stage was omitted (consistent with \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}) to simplify the model and reduce the number of free parameters.
 The response of the left eye's channel is given by:
@@
 Despite being derived from the model proposed by Meese et al.
-(2006), the simplifications applied to this architecture make it very similar to other models (e.g.
-Ding and Sperling, 2006; Doesschate and Alpern, 1967; Legge, 1984; Schrödinger, 1926).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., 2012; Kingdom and Libenson, 2015).
+(\protect\hyperlink{ref-Meese2006}{2006}), the simplifications applied to this architecture make it very similar to other models (e.g.
+\protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}; \protect\hyperlink{ref-Schrodinger1926}{Schrödinger, 1926}).
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
 Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, 2017).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., 2020).
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
 
-We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., 2017).
+We implemented the model within a Bayesian framework using the Stan software (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}).
 This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., 2012; Meese et al., 2006).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (\protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}).
 We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, 2021) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
-The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,328) = 5.34, \(p\) \textless{} 0).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (\protect\hyperlink{ref-Baker2021}{Baker, 2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
 
@@
 Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
-A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(2.96,121.48) = 6.18, \emph{p} \textless{} 0), no effect of data modality (F(2,82) = 5.55, \emph{p} = 0.01), but a highly significant interaction (F(5.04,206.46) = 6.38, \emph{p} \textless{} 0).
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
 
@@
 
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, 2017).
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
 One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (Spitschan et al., 2014); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
-Anstis and Ho, 1998; Levelt, 1965; Quaia et al., 2018).
+\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}; \protect\hyperlink{ref-Quaia2018}{Quaia et al., 2018}).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, 2017; Meese et al., 2006), and the peak location of our prior distribution (black curve).
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}), and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
@@
 \hline
-Pupillometry & 2.40 & 0.01 & 0.66 & 0.00023\\
+Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
 \hline
-EEG 1F & 2.72 & 0.16 & 0.02 & 0.00261\\
+EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
 \hline
-EEG 2F & 2.23 & 0.06 & 0.01 & 0.00404\\
+EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
 \hline
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, 2017; Meese et al., 2006; Moradi and Heeger, 2009).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
@@
 For example, Quaia et al.
-(2018) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (2019) report a similar result in archival data on melatonin suppression due to light exposure.
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., 2020).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, 1998; Baker et al., 2012; Levelt, 1965), though not for luminance decrements (Anstis and Ho, 1998).
+(\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure.
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}), though not for luminance decrements (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}).
 Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
@@
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-Baker and Wade (2017) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, 2002).
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, 1994; May and Zhaoping, 2022).
+Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also \protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (\protect\hyperlink{ref-Li1994}{Li and Atick, 1994}; \protect\hyperlink{ref-May2022}{May and Zhaoping, 2022}).
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
@@
 However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.
-Spitschan et al., 2014).
+\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
 It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.
-Bradley et al., 2008).
+\protect\hyperlink{ref-Bradley2008}{Bradley et al., 2008}).
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
@@
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, 1981; Livingstone and Hubel, 1984) are biased towards low spatial frequencies (Edwards et al., 1995; Tootell et al., 1988), and relatively insensitive to stimulus orientation (Horton and Hubel, 1981; Livingstone and Hubel, 1984; though see Economides et al., 2011).
-As the blob regions are embedded within ocular dominance columns (Horton and Hubel, 1981), they are also largely monocular (Livingstone and Hubel, 1984; Tychsen et al., 2004).
-More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., 2013) and achromatic (Meese and Baker, 2011) mechanisms, that also appear to be monocular.
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}) are biased towards low spatial frequencies (\protect\hyperlink{ref-Edwards1995}{Edwards et al., 1995}; \protect\hyperlink{ref-Tootell1988}{Tootell et al., 1988}), and relatively insensitive to stimulus orientation (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; though see \protect\hyperlink{ref-Economides2011}{Economides et al., 2011}).
+As the blob regions are embedded within ocular dominance columns (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}), they are also largely monocular (\protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; \protect\hyperlink{ref-Tychsen2004}{Tychsen et al., 2004}).
+More recent work has reported psychophysical evidence for unoriented chromatic (\protect\hyperlink{ref-Gheiratmand2013}{Gheiratmand et al., 2013}) and achromatic (\protect\hyperlink{ref-Meese2011}{Meese and Baker, 2011}) mechanisms, that also appear to be monocular.
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.

### 2023-06-10 manuscript.Rmd
Added files for autobuild

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures

### 2023-06-10 manuscript.Rmd
Check automated figure construction

--- 2023-06-10 manuscript.Rmd
@@
 EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; @Kassner2014) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker [Pupil Labs GmbH, Berlin, Germany\; @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 

### 2023-06-10 manuscript.tex
Check automated figure construction

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; Kassner et al.
-(\protect\hyperlink{ref-Kassner2014}{2014})) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; \protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
 

### 2023-06-11 manuscript.Rmd
Trying to fix OSF download of headerfile
Trying to sort OSF auto downloading
Added small resource files to a new directory in the repository so they don't need to be downloaded from OSF

@@
 
+if (!file.exists(paste0(datadir,'headerfile.csv'))){
+# copy from resources folder
+file.copy('resources/headerfile.csv',paste0(datadir,'headerfile.csv'))
+}
+
+if (!file.exists(paste0(localdir,'StimulusExample.png'))){
+# copy from resources folder
+file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
+}
+
 ```

### 2023-06-11 manuscript.Rmd
Testing download of processed participant data

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 2  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures

### 2023-06-11 manuscript.Rmd
Downloading all preprocessed files in a zip for speed and avoiding OSF download errors for single files

@@
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','osfr') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','utils','osfr') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
+if (processdata>0){
 if (!file.exists(paste0(datadir,'headerfile.csv'))){
@@
 file.copy('resources/StimulusExample.png',paste0(localdir,'StimulusExample.png'))
+}
+}
+
+if (processdata==2){
+# if we're going to need the pre-processed files, download all in a zip file
+  if (!file.exists(paste0(datadir,'P101summary.RData'))){
+          osfnode <- '2qu6y'
+          osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)
+          fid <- which(osffiles$name=='allprocessed.zip')
+          osf_download(osffiles[fid,],localdir,progress=TRUE)
+          unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
+          d <- dir(paste0(localdir,'allprocessed'),full.names=TRUE)
+          file.copy(d,datadir)
+  }
 }

### 2023-06-11 manuscript.Rmd
Add processed data files to a local zip file in the repository to avoid having to download from OSF

@@
 } 
-
 if (!file.exists(paste0(localdir,'StimulusExample.png'))){
@@
 if (processdata==2){
-# if we're going to need the pre-processed files, download all in a zip file
+# if we're going to need the pre-processed files, extract from zip file
   if (!file.exists(paste0(datadir,'P101summary.RData'))){
+   if (file.exists('resources/allprocessed.zip')){file.copy('resources/allprocessed.zip',localdir)}
+   if (!file.exists('resources/allprocessed.zip')){ 
           osfnode <- '2qu6y'
@@
           osf_download(osffiles[fid,],localdir,progress=TRUE)
+   }
           unzip(paste0(localdir,'allprocessed.zip'),exdir=localdir)
@@
 ```
+
+Figures \@ref(fig:appendixfig1) and \@ref(fig:appendixfig2)
+
+```{r appendixfig1, fig.cap="S.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'pupildataRep.pdf'))
+
+```
+
+```{r appendixfig2, fig.cap="S.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'EEGdataRep.pdf'))
+
+```

### 2023-06-12 manuscript.Rmd
Started implementing reviewer suggestions

@@
 However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels [@McDougal2008] and much less is known about the computations that operate in these subcortical pathways.
-In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
+Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
@@
 This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between $\sqrt{2}$ and 2 [@Campbell1965; @Baker2018].
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) [@Legge1984; @Meese2006] and neural activity [@Moradi2009; @Baker2017] are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision [@Ding2006; @Meese2006] advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This advantage is lost at high stimulus contrasts, where both psychophysical performance (contrast discrimination thresholds) [@Legge1984; @Meese2006] and neural activity [@Moradi2009; @Baker2017] are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision [@Ding2006; @Meese2006] advocate a process of interocular suppression that normalizes the two eyes' inputs at high contrasts and negates the binocular advantage.
 This is consistent with our everyday experience of 'ocularity invariance' [@Baker2007]: perceived contrast does not change when one eye is opened and closed.
@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \@ref(fig:pupildata)b for an example of the fused stimulus).
+Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see insert in Figure \@ref(fig:pupildata)b for an example of the fused stimulus).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
@@
 
-Before each experiment, participants calibrated the stereoscope by adjusting the angle of the mirrors.
+Before each experiment, participants adjusted the angle of the stereoscope mirrors to achieve binocular fusion.
 This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
@@
 In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
-In the dichoptic condition the non-target eye saw a fixed contrast of 48\%.
+In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
 In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
@@
 In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
-In the other interval, a target disc flickering at varying contrast levels was displayed.
+In the other interval, a target disc was displayed, flickering at different contrast levels on each trial, but with a fixed interocular contrast ratio across the block.
 The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
@@
 @Spitschan2014].
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
+The Fourier approach is more robust to noise at other frequencies (which can make the phase and amplitude of a fitted sine wave unstable) and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
 Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
@@
 
-save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2'))
+save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2','allmasksP','allmasksE','allmasksE2'))
 
@@
 
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- allmasksP[p,4,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+    counter <- counter + 1
+    alldata[counter] <- allmasksP[p,5,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 2
+    allP[counter] <- p
+  }
+}
+
+monbinPstatsX2 <- anovacirc2way(alldata,allgroupA,allgroupB,allP)
+
+alldata <- NULL
+allgroupA <- NULL
+allgroupB <- NULL
+allP <- NULL
+counter <- 0
+for (p in 1:30){
+  for (lev in 1:5){
+    counter <- counter + 1
+    alldata[counter] <- allmasksP[p,4,lev]
+    allgroupA[counter] <- lev
+    allgroupB[counter] <- 1
+    allP[counter] <- p
+
+  }
+}
+
+mondichPstatsX2 <- anovacirc.test(alldata,allgroupA,allP)
+
 ```
@@
 Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum, with an inset image illustrating the stimulus appearance (upper right).
-Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Negative values indicate constriction relative to baseline, and positive values indicate dilation.
+Panel (b) shows the average Fourier spectrum (absolute amplitude values), with an inset image illustrating the stimulus appearance (upper right).
+Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions.
 Panel (e) shows contrast response functions at 1.6Hz for three conditions.
@@
 Figure \@ref(fig:pupildata)e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
-The dichoptic cross condition does not show clear modulation with target contrast.
+Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(`r monbinPstatsX2$dfAB`,`r monbinPstatsX2$dfR`) = `r round(monbinPstatsX2$FratioAB,digits=2)`, $p$ < 0.001).
+In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases [see e.g.
+@Busse2009]: F(`r mondichPstatsX2$dfM`,`r mondichPstatsX2$dfR`) = `r round(mondichPstatsX2$Fratio,digits=2)`, $p$ < 0.001).
 
@@
 ```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types.
-Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
+These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 1c, 2c and 2f.
+Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
 
@@
 
-```{r TFdata, fig.cap="Binocular facilitation at different temporal frequencies.
+```{r TFdata, fig.cap="Binocular facilitation at different temporal frequencies, measured using EEG.
 Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
@@
 ```{r matchingdata, fig.cap="Contrast matching functions.
-Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
+Dotted and dashed lines are predictions of canonical summation models involving linear combination (dotted) or a winner-take-all rule (dashed).
 Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
@@
 
-Pupil size determines the total amount of light falling on the retina.
+Pupil size affects the total amount of light falling on the retina.
 It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
@@
 monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
 

### 2023-06-12 manuscript.tex
Started implementing reviewer suggestions

@@
 However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (\protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}) and much less is known about the computations that operate in these subcortical pathways.
-In addition, our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
+Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
 
@@
 This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}).
-This advantage is lost at high stimulus intensities, where both psychophysical performance (contrast discrimination thresholds) (\protect\hyperlink{ref-Legge1984}{Legge, 1984}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) and neural activity (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (\protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) advocate a process of interocular suppression that normalizes the two eyes inputs at high contrasts and negates the binocular advantage.
+This advantage is lost at high stimulus contrasts, where both psychophysical performance (contrast discrimination thresholds) (\protect\hyperlink{ref-Legge1984}{Legge, 1984}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) and neural activity (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (\protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) advocate a process of interocular suppression that normalizes the two eyes' inputs at high contrasts and negates the binocular advantage.
 This is consistent with our everyday experience of `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}): perceived contrast does not change when one eye is opened and closed.
@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their fusion into one binocular disc (see insert in Figure \ref{fig:pupildata}b for an example of the fused stimulus).
+Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see insert in Figure \ref{fig:pupildata}b for an example of the fused stimulus).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
@@
 \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-The Fourier approach is more robust to noise at other frequencies and has been used in some previous studies (see \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}).
+The Fourier approach is more robust to noise at other frequencies (which can make the phase and amplitude of a fitted sine wave unstable) and has been used in some previous studies (see \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}).
 Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
@@
 Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Surprisingly there again appears to be a slight facilitation effect in the binocular cross condition, particularly at lower contrasts.
-The dichoptic cross condition does not show clear modulation with target contrast.
+Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(8,580) = 41.23, \(p\) \textless{} 0.001).
+In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.
+\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}): F(8,232) = 17, \(p\) \textless{} 0.001).
 
@@
 \caption{Ratio of binocular to monocular response for three data types.
-Each ratio is the average of ratios for N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
+These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 1c, 2c and 2f.
+Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
 \end{figure}
@@
 
-\caption{Binocular facilitation at different temporal frequencies.
+\caption{Binocular facilitation at different temporal frequencies, measured using EEG.
 Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
@@
 \caption{Contrast matching functions.
-Dotted and dashed lines are predictions of canonical summation models with a linear exponent (dotted) or an infinite exponent (dashed).
+Dotted and dashed lines are predictions of canonical summation models involving linear combination (dotted) or a winner-take-all rule (dashed).
 Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
@@
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the two pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
 
@@
 doi:\href{https://doi.org/10.1111/j.1469-8986.2008.00654.x}{10.1111/j.1469-8986.2008.00654.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
+Busse L, Wade AR, Carandini M.
+2009.
+Representation of concurrent stimuli by population activity in visual cortex.
+\emph{Neuron} \textbf{64}:931--942.
+doi:\href{https://doi.org/10.1016/j.neuron.2009.11.004}{10.1016/j.neuron.2009.11.004}
 
@@
 
+Figures \ref{fig:appendixfig1} and \ref{fig:appendixfig2}
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/pupildataRep}
+
+}
+
+\caption{S.}\label{fig:appendixfig1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/EEGdataRep}
+
+}
+
+\caption{S.}\label{fig:appendixfig2}
+\end{figure}
+
 \end{document}

### 2023-06-12 manuscript.Rmd
Implementing revisions

@@
 To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
+We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response [see @Spitschan2014], and the relatively higher-pass EEG response [@Regan1966].
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
 Periodic flicker entrains both neural [@Norcia2015] and pupil [@Spitschan2014] responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Relative to the response to a monocular signal, adding a signal in the other eye can either increase the response (facilitation) or reduce it (suppression).
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.
@@
 We initially preregistered our main hypotheses and analysis intentions for the first experiment.
-We then conducted a pilot study with N=12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then conducted a pilot study with N = 12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
 We then ran the main experiment, followed by two additional experiments that were not preregistered.
@@
 Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms [e.g.
-@Anstis1998; @Levelt1965; @Quaia2018].
+@Anstis1998; @Levelt1965; @Legge1981; @Quaia2018].
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 For example, @Quaia2018 observed a strong binocular facilitation (or 'supersummation') in the reflexive eye movement response to rapidly moving stimuli, and @Spitschan2019 report a similar result in archival data on melatonin suppression due to light exposure.
+Work on the accommodative response indicates that binocular combination there is approximately linear [@Flitcroft1992], and can even cancel when signals are in antiphase (we did not try this configuration here).
 In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm [@Baker2020].
@@
 
-Figures \@ref(fig:appendixfig1) and \@ref(fig:appendixfig2)
-
-```{r appendixfig1, fig.cap="S.", fig.align="center", echo=FALSE}
+We conducted a conceptual replication of Experiment 1 using an alternative system.
+We used a pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain), coupled to a binocular headset using liquid light guides.
+The light was imaged onto a circular diffuser for each eye (field size X deg) with the central 6 degrees masked off using a black occluder.
+Therefore the replication experiment involved peripheral stimulation, unlike the main experiment which stimulated the central ~4 degrees of the visual field.
+The mean luminance of the devices was $cd/m^2$.
+All conditions were otherwise as described for the main experiment, and we tested 12 participants in total.
+
+The pupillometry results are shown in Figure \@ref(fig:appendixfig1) and correspond closely to those from the main experiment (Figure \@ref(fig:pupildata)).
+The ratio of binocular to monocular responses in Figure \@ref(fig:appendixfig1)c is similar, and suppression is evident in Figure \@ref(fig:appendixfig1)d,e.
+Of particular interest is the presence of a slight response at the second harmonic (4Hz, Figure \@ref(fig:appendixfig1)b), which was not present in our original data.
+This may be because the driving signal is clearer when stimulating the periphery (note the clear waveform in Figure \@ref(fig:appendixfig1)a), or it might indicate additional nonlinearities not present in the fovea.
+
+```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for an overview of each panel.", fig.align="center", echo=FALSE}
 
@@
 
-```{r appendixfig2, fig.cap="S.", fig.align="center", echo=FALSE}
+The EEG results are shown in Figure \@ref(fig:appendixfig2).
+These still show a strong binocular facilitation effect at the highest contrast levels (Figure \@ref(fig:appendixfig2)c,f), but the contrast response function is less clear at both the first and second harmonics.
+We suspect that this is because the cortical representation of the peripheral visual field is primarily along the calcarine sulcus, which results in some cancellation of the steady-state signal.
+This results in weaker signals than we obtained for foveal stimulation (represented at the occipital pole) in the main experiment (see Figure \@ref(fig:EEGdata)).
+
+```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for an overview of each panel.", fig.align="center", echo=FALSE}
 

### 2023-06-12 manuscript.tex
Implementing revisions

@@
 To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
+We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response (see \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and the relatively higher-pass EEG response (\protect\hyperlink{ref-Regan1966}{Regan, 1966}).
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
 Periodic flicker entrains both neural (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}) and pupil (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Relative to the response to a monocular signal, adding a signal in the other eye can either increase the response (facilitation) or reduce it (suppression).
 We followed up our main experiment with additional exploration of the effect of stimulus frequency, and a psychophysical matching experiment measuring perceived flicker intensity (i.e.~temporal contrast).
@@
 Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
-\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}; \protect\hyperlink{ref-Quaia2018}{Quaia et al., 2018}).
+\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Legge1981}{Legge and Rubin, 1981}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}; \protect\hyperlink{ref-Quaia2018}{Quaia et al., 2018}).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 (\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure.
+Work on the accommodative response indicates that binocular combination there is approximately linear (\protect\hyperlink{ref-Flitcroft1992}{Flitcroft et al., 1992}), and can even cancel when signals are in antiphase (we did not try this configuration here).
 In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Flitcroft1992}{}}%
+Flitcroft DI, Judge SJ, Morley JW.
+1992.
+Binocular interactions in accommodation control: Effects of anisometropic stimuli.
+\emph{J Neurosci} \textbf{12}:188--203.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.12-01-00188.1992}{10.1523/JNEUROSCI.12-01-00188.1992}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Gheiratmand2013}{}}%
@@
 Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Legge1981}{}}%
+Legge GE, Rubin GS. 1981. Binocular interactions in suprathreshold contrast perception. \emph{Percept Psychophys} \textbf{30}:49--61. doi:\href{https://doi.org/10.3758/bf03206136}{10.3758/bf03206136}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Regan1966}{}}%
+Regan D.
+1966.
+Some characteristics of average steady-state and transient responses evoked by modulated light.
+\emph{Electroencephalogr Clin Neurophysiol} \textbf{20}:238--48.
+doi:\href{https://doi.org/10.1016/0013-4694(66)90088-5}{10.1016/0013-4694(66)90088-5}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Schrodinger1926}{}}%
@@
 
-Figures \ref{fig:appendixfig1} and \ref{fig:appendixfig2}
+We conducted a conceptual replication of Experiment 1 using an alternative system.
+We used a pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain), coupled to a binocular headset using liquid light guides.
+The light was imaged onto a circular diffuser for each eye (field size X deg) with the central 6 degrees masked off using a black occluder.
+Therefore the replication experiment involved peripheral stimulation, unlike the main experiment which stimulated the central \textasciitilde4 degrees of the visual field.
+The mean luminance of the devices was \(cd/m^2\).
+All conditions were otherwise as described for the main experiment, and we tested 12 participants in total.
+
+The pupillometry results are shown in Figure \ref{fig:appendixfig1} and correspond closely to those from the main experiment (Figure \ref{fig:pupildata}).
+The ratio of binocular to monocular responses in Figure \ref{fig:appendixfig1}c is similar, and suppression is evident in Figure \ref{fig:appendixfig1}d,e.
+Of particular interest is the presence of a slight response at the second harmonic (4Hz, Figure \ref{fig:appendixfig1}b), which was not present in our original data.
+This may be because the driving signal is clearer when stimulating the periphery (note the clear waveform in Figure \ref{fig:appendixfig1}a), or it might indicate additional nonlinearities not present in the fovea.
 
@@
 
-\caption{S.}\label{fig:appendixfig1}
+\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for an overview of each panel.}\label{fig:appendixfig1}
 \end{figure}
+
+The EEG results are shown in Figure \ref{fig:appendixfig2}.
+These still show a strong binocular facilitation effect at the highest contrast levels (Figure \ref{fig:appendixfig2}c,f), but the contrast response function is less clear at both the first and second harmonics.
+We suspect that this is because the cortical representation of the peripheral visual field is primarily along the calcarine sulcus, which results in some cancellation of the steady-state signal.
+This results in weaker signals than we obtained for foveal stimulation (represented at the occipital pole) in the main experiment (see Figure \ref{fig:EEGdata}).
 
@@
 
-\caption{S.}\label{fig:appendixfig2}
+\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for an overview of each panel.}\label{fig:appendixfig2}
 \end{figure}

### 2023-06-18 manuscript.Rmd
Implementing reviewer comments

@@
 The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+We confirmed in additional analyses that the monocular consensual pupil response was complete, justifying our pooling of data across the eyes.
 Finally, data were averaged across all participants to obtain the group results.
@@
 Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
-In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
-In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
+In the visual cortex response (indexed by EEG), the binocular combination of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+Evidence for this comes from the substantial binocular facilitation effect when comparing monocular and binocular responses, and the lack of a dichoptic suppression effect when the two eyes were stimulated at different frequencies.
+In the subcortical pathway (indexed by pupillometry), binocular combination is more non-linear, with evidence of interocular suppression.
+This was evidenced by a weaker binocular facilitation, and stronger dichoptic suppression, relative to the EEG data.
 This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
-Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
+Additionally, we found that perception of flickering light is consistent with a near-linear binocular summation process, consistent with the cortical (EEG) responses.
 
@@
 Previous studies investigating binocular combination of spatial patterns (i.e.
-sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts [@Baker2017; @Moradi2009; @Meese2006].
+sine wave grating stimuli) are generally consistent with strong interocular suppression and weak binocular facilitation at high contrasts [@Baker2017; @Moradi2009; @Meese2006] [however we note that facilitation as substantial as ours has been reported in previous EEG work by @Apkarian1981].
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
 However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, @Quaia2018 observed a strong binocular facilitation (or 'supersummation') in the reflexive eye movement response to rapidly moving stimuli, and @Spitschan2019 report a similar result in archival data on melatonin suppression due to light exposure.
+Using scleral search coils, @Quaia2018 observed a strong binocular facilitation (or 'supersummation') in the reflexive eye movement response to rapidly moving stimuli (also known as the ocular following response).
+@Spitschan2019 report a similar result in archival data on melatonin suppression due to light exposure (melatonin is a hormone released by the pineal gland that regulates sleep; its production is suppressed by light exposure and can be measured from saliva assays).
 Work on the accommodative response indicates that binocular combination there is approximately linear [@Flitcroft1992], and can even cancel when signals are in antiphase (we did not try this configuration here).
@@
 Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments [@Levelt1965; @Anstis1998; @Baker2012], though not for luminance decrements [@Anstis1998].
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination (or combination across multiple inputs in other senses).
 

### 2023-06-18 manuscript.tex
Implementing reviewer comments

@@
 Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
-In the visual cortex, the processing of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
-In the subcortical pathway, signal combination is more non-linear, with evidence of interocular suppression.
+In the visual cortex response (indexed by EEG), the binocular combination of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+Evidence for this comes from the substantial binocular facilitation effect when comparing monocular and binocular responses, and the lack of a dichoptic suppression effect when the two eyes were stimulated at different frequencies.
+In the subcortical pathway (indexed by pupillometry), binocular combination is more non-linear, with evidence of interocular suppression.
+This was evidenced by a weaker binocular facilitation, and stronger dichoptic suppression, relative to the EEG data.
 This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
-Additionally, we found that perception of flickering light is consistent with a near-linear summation process, consistent with the cortical (EEG) responses.
+Additionally, we found that perception of flickering light is consistent with a near-linear binocular summation process, consistent with the cortical (EEG) responses.
 
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are all consistent with strong interocular suppression and weak binocular facilitation at high contrasts (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are generally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) (however we note that facilitation as substantial as ours has been reported in previous EEG work by \protect\hyperlink{ref-Apkarian1981}{Apkarian et al., 1981}).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
 However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-For example, Quaia et al.
-(\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli, and Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure.
+Using scleral search coils, Quaia et al.
+(\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli (also known as the ocular following response).
+Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure (melatonin is a hormone released by the pineal gland that regulates sleep; its production is suppressed by light exposure and can be measured from saliva assays).
 Work on the accommodative response indicates that binocular combination there is approximately linear (\protect\hyperlink{ref-Flitcroft1992}{Flitcroft et al., 1992}), and can even cancel when signals are in antiphase (we did not try this configuration here).
@@
 Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}), though not for luminance decrements (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}).
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of sensory signal combination.
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination (or combination across multiple inputs in other senses).
 
@@
 doi:\href{https://doi.org/10.1016/s0042-6989(97)00167-3}{10.1016/s0042-6989(97)00167-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Apkarian1981}{}}%
+Apkarian PA, Nakayama K, Tyler CW.
+1981.
+Binocularity in the human visual evoked potential: Facilitation, summation and suppression.
+\emph{Electroencephalogr Clin Neurophysiol} \textbf{51}:32--48.
+doi:\href{https://doi.org/10.1016/0013-4694(81)91507-8}{10.1016/0013-4694(81)91507-8}
 

### 2023-06-20 manuscript.Rmd
Added new figure

@@
 To account for the consensual response, these brain regions must combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is achieved is unclear.
+The pupil response is temporally low-pass [@Spitschan2014], most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
 
@@
 
+```{r createmethodsfig, include=FALSE, results='hide'}
+
+if (processdata>0){
+
+           if (!file.exists(paste0(localdir,'StimulusExample.png'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'tbema'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='StimulusExample.png')
+          osf_download(osffiles[fid,],localdir,progress=TRUE)
+         }
+
+stim <- readPNG('local/StimulusExample.png')
+
+pdf("Figures/methodsfig.pdf", bg="transparent", height = 8, width = 8)
+
+contlist <- c(0.06,0.12,0.24,0.48,0.96)
+amp <- 0.5
+t <- seq(0,1,length=100)
+sinetarget <- sin(2 * t * 2*pi)*amp
+sinemask <- sin(1.6 * t * 2*pi)*amp
+
+colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
+symbollist <- c(21:23,21,24,25)
+ramp <- colorRamp(c("white", "black"))  # create a ramp from one colour to another
+greypal <- rgb(ramp(seq(0, 1, length = 5)), max = 255)   # index the ramp at ten points
+
+plotlims <- c(0.5,4.1,0.5,7)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+
+par(mar=c(0.1,0.1,0.1,0.1))
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+
+condlabels <- c('Monocular','Binocular','Dichoptic','Monocular cross','Binocular cross','Dichoptic cross')
+text(1.2,6:1,condlabels,pos=2,cex=1.2)
+
+text(c(2,3.5),7,c('Left eye','Right eye'),cex=1.6)
+
+points(rep(1.3,6),6:1, pch=symbollist, bg=colpal, cex=1.6, lwd=3)
+
+for (cont in 5:1){
+
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 6, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 5, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 4, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 2, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 1, col=greypal[cont], border=NA)
+
+  polygon(c(0,t,t[100])+3, c(0,sinetarget*contlist[cont],0) + 5, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+3, c(0,sinemask*contlist[cont],0) + 3, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+3, c(0,sinemask*contlist[cont],0) + 2, col=greypal[cont], border=NA)
+
+}
+
+for (cond in 1:6){lines(c(1.5,2.5),c(cond,cond),lty=2)}
+for (cond in 1:6){lines(c(3,4),c(cond,cond),lty=2)}
+
+lines(t+3, sinetarget*0.48 + 4, lwd=2)
+lines(t+3, sinemask*0.48 + 1, lwd=2)
+
+lines(t+3, sinetarget*0 + 6, lwd=2)
+lines(t+1.5, sinetarget*0 + 3, lwd=2)
+
+text(2.6,c(1,2,4,5,6),'2Hz',srt=270)
+text(4.1,c(4,5),'2Hz',srt=270)
+text(4.1,c(1,2,3),'1.6Hz',srt=270)
+
+text(2.6,3,'Mean',srt=270)
+text(4.1,6,'Mean',srt=270)
+
+imwidth <- 0.5
+xstart <- 0.4
+ystart <- 6.2
+rasterImage(stim,xstart,ystart,xstart+imwidth,ystart+imwidth*1.9)
+
+dev.off()
+
+}
+
+```
+
 The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see insert in Figure \@ref(fig:pupildata)b for an example of the fused stimulus).
+Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see upper left insert in Figure \@ref(fig:methodsfig) for an example of the fused stimulus).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
@@
 Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
-In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement (see upper rows of Figure \@ref(fig:methodsfig)).
 In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
 In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
-We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
+We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements (see lower rows of Figure \@ref(fig:methodsfig)).
 The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
@@
 We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+```{r methodsfig, fig.cap="Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1.
+Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
+Unshaded waveforms indicate mask stimuli, which were presented at a fixed contrast level of 48\\% regardless of the target contrast.
+Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
+The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
+The left and right eye assignments were counterbalanced across trials in the experiment (i.e.
+the monocular stimulus could be shown to either eye with equal probability).", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
+
+```
 
@@
 
-```{r createfig1, include=FALSE, results='hide'}
+```{r createpupilfig, include=FALSE, results='hide'}
 
@@
 dev.off()
-
-         if (!file.exists(paste0(localdir,'StimulusExample.png'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- 'tbema'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name=='StimulusExample.png')
-          osf_download(osffiles[fid,],localdir,progress=TRUE)
-         }
-
-stim <- readPNG('local/StimulusExample.png')
 
@@
   plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
-
-  aspratio <- 10/15  # this is the aspect ratio of the output pdf
-  imwidth <- 0.2
-  xstart <- 0.85
-  ystart <- 0.72
-  rasterImage(stim,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
 
@@
 Negative values indicate constriction relative to baseline, and positive values indicate dilation.
-Panel (b) shows the average Fourier spectrum (absolute amplitude values), with an inset image illustrating the stimulus appearance (upper right).
+Panel (b) shows the average Fourier spectrum (absolute amplitude values).
 Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions.
@@
 
-```{r createfig2, include=FALSE, results='hide'}
+```{r createEEGfig, include=FALSE, results='hide'}
 
@@
 
-```{r createfig3, include=FALSE, results='hide'}
+```{r createBSfig, include=FALSE, results='hide'}
 
@@
 
-```{r createfig4, include=FALSE, results='hide'}
+```{r createTFfig, include=FALSE, results='hide'}
 
@@
 Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
-At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the *x*- and *y*-axes), compared to a binocular target (points along the diagonal of *x*=*y*).
 For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.

### 2023-06-20 manuscript.tex
Added new figure

@@
 To account for the consensual response, these brain regions must combine information from the left and right eyes (\protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}), yet the computation that achieves this is achieved is unclear.
+The pupil response is temporally low-pass (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
 
@@
 The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see insert in Figure \ref{fig:pupildata}b for an example of the fused stimulus).
+Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see upper left insert in Figure \ref{fig:methodsfig} for an example of the fused stimulus).
 The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
@@
 Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
-In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement (see upper rows of Figure \ref{fig:methodsfig}).
 In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
 In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
-We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements.
+We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements (see lower rows of Figure \ref{fig:methodsfig}).
 The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
@@
 We counterbalanced presentation of the target stimulus across the left and right eyes.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/methodsfig}
+
+}
+
+\caption{Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1.
+Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
+Unshaded waveforms indicate mask stimuli, which were presented at a fixed contrast level of 48\% regardless of the target contrast.
+Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
+The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
+The left and right eye assignments were counterbalanced across trials in the experiment (i.e.
+the monocular stimulus could be shown to either eye with equal probability).}\label{fig:methodsfig}
+\end{figure}
 
@@
 Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
-At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the x- and y-axes), compared to a binocular target (points along the diagonal of x=y).
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the \emph{x}- and \emph{y}-axes), compared to a binocular target (points along the diagonal of \emph{x}=\emph{y}).
 For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.

### 2023-06-20 IManalysis.R

@@ -1,0 +1,294 @@
+
+# check which packages are installed, install the missing ones, and activate
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','utils','osfr') # list of CRAN packages
+missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
+if (length(missingpackages)>0){install.packages(missingpackages)}
+if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
+packagelist <- c(packagelist,'FourierStats')
+toinstall <- packagelist[which(!packagelist %in% (.packages()))]
+invisible(lapply(toinstall,library,character.only=TRUE))
+
+cleanup2D <- function(data){
+  # helper function to clean up complex data by removing any data points more than 
+  # SDthresh standard deviations from the mean (in Mahalanobis distance units)
+  cartdata <- data.frame(Re(data),Im(data))
+  output <- 0
+  if (sum(cartdata)!=0){
+    D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
+    i <- which(D<SDthresh) 
+    output <- mean(temp[i])}
+  return(output)}
+
+SDthresh <<- 3
+nbootstraps <<- 1000
+
+colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
+targetelectrodes <- c('Oz','POz','O1','O2')
+
+localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
+if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
+rawdir <- 'local/rawdata/'
+if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
+figdir <- 'Figures/'
+if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
+datadir <- 'local/spectra/'
+if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
+  
+  legaltriggers <- 1
+  
[…]

### 2023-06-21 manuscript.Rmd
Added IM figure

@@
 To account for the consensual response, these brain regions must combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is achieved is unclear.
-The pupil response is temporally low-pass [@Spitschan2014], most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
-
-To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
-We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response [see @Spitschan2014], and the relatively higher-pass EEG response [@Regan1966].
+The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass [@Barrionuevo2014; @Spitschan2014], most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
+
+To investigate the binocular combination of light, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
+We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response [see @Barrionuevo2014; @Spitschan2014], and the relatively higher-pass EEG response [@Regan1966].
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
@@
 
-All stimuli had a mean luminance of 42 cd/m$^2$ on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
+All stimuli had a mean luminance of 42 cd/m$^2$ and were displayed on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
 Ltd., Japan).
@@
 The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in a single session lasting 45 minutes in total, divided in three blocks of 15 minutes each.
+The experiment was carried out in a single session lasting 45 minutes in total, divided into three blocks of 15 minutes each.
 In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
@@
 In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
-In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
-We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements (see lower rows of Figure \@ref(fig:methodsfig)).
-The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
-The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.
-the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
-We counterbalanced presentation of the target stimulus across the left and right eyes.
+The rationale for including the monocular and binocular conditions is that they permit us to measure empirically any binocular facilitation, by comparing the response amplitudes across these two conditions.
+The rationale for including the dichoptic condition is that it provides additional contraints to computational models, and further explores the binocular contrast-response space [see @Baker2007].
+
+In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
+We chose this frequency because it was sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
+We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
+The rationale for the binocular cross condition is that it allows us to see the effects of suppression between the eyes without the additional complication of signal summation (which occurs when both eyes receive the same frequency), because the response of each eye can be resolved independently by frequency.
+Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
+A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \@ref(fig:methodsfig)).
+In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
 
@@
 Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
-Unshaded waveforms indicate mask stimuli, which were presented at a fixed contrast level of 48\\% regardless of the target contrast.
+Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\\% regardless of the target contrast.
 Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
@@
 Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
+Models from this family can handle both scalar contrast values and continuous waveforms [@Tsai2012] or images [@Meese2007] as inputs.
+For time-varying inputs, the calculations are performed at each time point, and the output waveform can then be analysed using Fourier analysis in the same way as for empirical data.
+This means that the model can make predictions for the entire Fourier spectrum, including harmonic and intermodulation responses that arise as a consequence of nonlinearities in the model [@Baker2017].
+However for computational tractability, we performed fitting here using scalar contrast values.
 
@@
     cleanmeansP[cond,level] <- cleanup2D(temp)
-}
 
@@
     cleanmasksE2[ch,cond,level] <- cleanup2D(temp) 
+    }
   }
@@
 meanspectraE <- apply(EEGspectra[,electrodeindices,c(15,20),],4,mean,na.rm=TRUE)
-save(file=paste(datadir,'P',100+participant,'summary.RData',sep=''),list=c('cleanmeansP','cleanmeansE','cleanmeansE2','cleanmasksP','cleanmasksE','cleanmasksE2','meanspectraP','meanspectraE','meanwavesP','meanwavesE','electrodes'))
+IMspectraP <- apply(pupilspectra[,,c(44,49,54,59),],4,mean,na.rm=TRUE)
+IMspectraE <- apply(EEGspectra[,electrodeindices,c(44,49,54,59),],4,mean,na.rm=TRUE)
+save(file=paste(datadir,'P',100+participant,'summary.RData',sep=''),list=c('cleanmeansP','cleanmeansE','cleanmeansE2','cleanmasksP','cleanmasksE','cleanmasksE2','meanspectraP','meanspectraE','meanwavesP','meanwavesE','electrodes','IMspectraP','IMspectraE'))
 
@@
 allspectraE <- array(0,dim=c(length(d),300))
+allspectraP_IM <- array(0,dim=c(length(d),300))
+allspectraE_IM <- array(0,dim=c(length(d),300))
 allwavesP <- array(0,dim=c(length(d),1680))
@@
   allspectraE[s,] <- meanspectraE
+  allspectraP_IM[s,] <- IMspectraP
+  allspectraE_IM[s,] <- IMspectraE  
   allwavesP[s,] <- meanwavesP
@@
 meanspectraECI <- array(0,c(2,300))
+meanspectraP_IM <- (1:300)*0
+meanspectraE_IM <- (1:300)*0
+meanspectraPCI_IM <- array(0,c(2,300))
+meanspectraECI_IM <- array(0,c(2,300))
 
@@
 meanspectraECI[2,f] <- mbs$upperCI
+
+        temp <- allspectraP_IM[,f]
+        mbs <- bootstrap2D(temp)
+meanspectraP_IM[f] <- mbs$meanamp
+meanspectraPCI_IM[1,f] <- mbs$lowerCI
+meanspectraPCI_IM[2,f] <- mbs$upperCI
+
+        temp <- allspectraE_IM[,f]
+        mbs <- bootstrap2D(temp)
+meanspectraE_IM[f] <- mbs$meanamp
+meanspectraECI_IM[1,f] <- mbs$lowerCI
+meanspectraECI_IM[2,f] <- mbs$upperCI
 
@@
 
-save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2','allmasksP','allmasksE','allmasksE2'))
+save(file=paste0(datadir,'Averagedata.RData'),list=c('cleanmeansP','cleanmeansPCI','cleanmasksP','cleanmasksPCI','cleanmeansEav','cleanmeansEavCI','cleanmasksEav','cleanmasksEavCI','cleanmeansE2av','cleanmeansE2avCI','cleanmasksE2av','cleanmasksE2avCI','cleanmeansE','cleanmeansECI','cleanmasksECI','cleanmeansE2','cleanmeansE2CI','cleanmasksE2','cleanmasksE2CI','meanspectraP','meanspectraPCI','meanspectraE','meanspectraECI','meanwavesP','meanwavesE','meanwavesPCI','meanwavesECI','electrodes','allmeansP','allmeansE','allmeansE2','allmasksP','allmasksE','allmasksE2','meanspectraP_IM','meanspectraPCI_IM','meanspectraE_IM','meanspectraECI_IM'))
 
@@
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Figure \@ref(fig:pupildata)b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz (though see Appendix 1).
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 Panel (b) shows the average Fourier spectrum (absolute amplitude values).
-Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions.
+Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 1).
 Panel (e) shows contrast response functions at 1.6Hz for three conditions.
@@
 
-Figure \@ref(fig:pupildata)c shows contrast response functions in response to stimuli flickering only at 2Hz.
-Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
+Figure \@ref(fig:pupildata)c shows contrast response functions driven by stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in the pupil response (to our knowledge this is the first time this has been demonstrated).
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
@@
 Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
-In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(`r monbinPstatsX2$dfAB`,`r monbinPstatsX2$dfR`) = `r round(monbinPstatsX2$FratioAB,digits=2)`, $p$ < 0.001).
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(`r monbinPstatsX2$dfAB`,`r monbinPstatsX2$dfR`) = `r round(monbinPstatsX2$FratioAB,digits=2)`, $p$ < 0.001.
 In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases [see e.g.
-@Busse2009]: F(`r mondichPstatsX2$dfM`,`r mondichPstatsX2$dfR`) = `r round(mondichPstatsX2$Fratio,digits=2)`, $p$ < 0.001).
+@Busse2009]: F(`r mondichPstatsX2$dfM`,`r mondichPstatsX2$dfR`) = `r round(mondichPstatsX2$Fratio,digits=2)`, $p$ < 0.001.
 
@@
 A $3 \times 5$ repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(`r round(ratioaov$ANOVA$DFn[2]*gg[2],digits=2)`,`r round(ratioaov$ANOVA$DFd[2]*gg[2],digits=2)`) = `r round(ratioaov$ANOVA$F[2],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[2],digits=3)`), no effect of data modality (F(`r ratioaov$ANOVA$DFn[1]`,`r ratioaov$ANOVA$DFd[1]`) = `r round(ratioaov$ANOVA$F[1],digits=2)`, \emph{p} = `r round(ratioaov$ANOVA$p[1],digits=2)`), but a highly significant interaction (F(`r round(ratioaov$ANOVA$DFn[3]*gg[3],digits=2)`,`r round(ratioaov$ANOVA$DFd[3]*gg[3],digits=2)`) = `r round(ratioaov$ANOVA$F[3],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[3],digits=4)`).
+All of the key results from Experiment 1 were subsequently replicated for peripheral stimulation (see Appendix 1).
 
@@
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz [@Spitschan2014]; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response substantially weaker above around 2Hz [@Barrionuevo2014; @Spitschan2014]; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 @Baker2017 point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs [see also @Ernst2002].
+Functionally, interocular suppression may therefore act to dynamically suppress noise, rendering binocular vision more stable.
 This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction [@Li1994; @May2022].
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+However the other examples of binocular combination discussed above are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
 Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
@@
 monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this more directly in future neuroimaging work.
 
@@
 Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.
-Figures \@ref(fig:BSratios) & \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
-However our matching data (Figure \@ref(fig:matchingdata)), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+Figures \@ref(fig:BSratios) & \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
+In the steady-state literature, one hallmark of a nonlinear system is the presence of intermodulation responses at the sums and differences of fundamental flicker frequencies [@Tsai2012].
+In Figure \@ref(fig:IMfig) we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \@ref(fig:pupildata)d,e and \@ref(fig:EEGdata)d,e).
+Consistent with the temporal properties of pupil responses and EEG, Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+
+``` {r createIMfig, include=FALSE, results='hide'}
+
+# generate plot showing the bin:mon ratio for three data sets
+
+if (processdata>0){
+         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Averagedata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(file=paste0(datadir,'Averagedata.RData'))
+
+frequencies <- (0:299)/10
+
+pdf("Figures/IMresponse.pdf", onefile = FALSE, paper = "special", height = 8, width = 6)
+
+par(mfcol = c(2,1))
+par(mar=c(3,4,0.5,1))
+
+plotlims <- c(0,6,0,0.06) 
+ticklocsx <- seq(0,6,1)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.05,0.01)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (mm)", col.lab=rgb(0,0,0), line=2, cex.lab=1.5)
+
+lines(c(0.4,0.4),c(0,0.05),lty=2,lwd=2,col='red')
+lines(c(2,2),c(0,0.05),lty=2,lwd=2,col='black')
+lines(c(1.6,1.6),c(0,0.05),lty=2,lwd=2,col='darkgreen')
+
+polygon(frequencies[c(2:61,61:2)],c(meanspectraPCI_IM[1,2:61],meanspectraPCI_IM[2,61:2]),col=addalpha(colpal[2],0.2),border=NA)
+
+lines(frequencies[2:61],abs(meanspectraP_IM[2:61]), col=colpal[2], lwd=3, cex=0.5)
+
+text(5.6,0.05,'(a)',adj=0.5,cex=1.5)
+text(0.4,0.053,'F1-F2',cex=1.2,adj=0.5,col='red')
+text(2,0.053,'F1',cex=1.2,adj=0.5,col='black')
+text(1.6,0.053,'F2',cex=1.2,adj=0.5,col='darkgreen')
+
+par(mar=c(3,4,0.5,1))
+plotlims <- c(0,6,0,0.35) 
+ticklocsx <- seq(0,6,1)    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.3,0.1)    # locations of tick marks on y axis
+ticklabelsx <-ticklocsx        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
+
+lines(c(3.6,3.6),c(0,0.3),lty=2,lwd=2,col='red')
+lines(c(2,2),c(0,0.3),lty=2,lwd=2,col='black')
+lines(c(1.6,1.6),c(0,0.3),lty=2,lwd=2,col='darkgreen')
+
+polygon(frequencies[c(3:61,61:3)],c(meanspectraECI_IM[1,3:61],meanspectraECI_IM[2,61:3]),col=addalpha(colpal[2],0.2),border=NA)
+
+lines(frequencies[3:61],abs(meanspectraE_IM[3:61]), col=colpal[2], lwd=3, cex=0.5)
+
+text(5.6,0.3,'(b)',adj=0.5,cex=1.5)
+text(3.6,0.32,'F1+F2',cex=1.2,adj=0.5,col='red')
+text(2,0.32,'F1',cex=1.2,adj=0.5,col='black')
+text(1.6,0.32,'F2',cex=1.2,adj=0.5,col='darkgreen')
+
+}
+
+```
+
+```{r IMfig, fig.cap="Summary of intermodulation responses in pupillometry (a) and EEG (b).
+The data are from the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\\%.
+Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies.
+Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.", out.width = '50%', fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'IMresponse.pdf'))
+
+```
 
@@
 We conducted a conceptual replication of Experiment 1 using an alternative system.
-We used a pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain), coupled to a binocular headset using liquid light guides.
-The light was imaged onto a circular diffuser for each eye (field size X deg) with the central 6 degrees masked off using a black occluder.
+A pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain) were coupled to a binocular headset using liquid light guides.
+The light was imaged onto a circular diffuser for each eye (field size 30 deg) with the central 8 degrees masked off using a black occluder.
 Therefore the replication experiment involved peripheral stimulation, unlike the main experiment which stimulated the central ~4 degrees of the visual field.
-The mean luminance of the devices was $cd/m^2$.
 All conditions were otherwise as described for the main experiment, and we tested 12 participants in total.
@@
 The ratio of binocular to monocular responses in Figure \@ref(fig:appendixfig1)c is similar, and suppression is evident in Figure \@ref(fig:appendixfig1)d,e.
-Of particular interest is the presence of a slight response at the second harmonic (4Hz, Figure \@ref(fig:appendixfig1)b), which was not present in our original data.
-This may be because the driving signal is clearer when stimulating the periphery (note the clear waveform in Figure \@ref(fig:appendixfig1)a), or it might indicate additional nonlinearities not present in the fovea.
-
-```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for an overview of each panel.", fig.align="center", echo=FALSE}
+Of particular interest is the existence of a slight response at the second harmonic (4Hz, Figure \@ref(fig:appendixfig1)b), which was not present in our original data.
+This may be because the driving signal is stronger when stimulating the periphery (note the clear waveform in Figure \@ref(fig:appendixfig1)a), or more robust to eye movements, or it might indicate additional nonlinearities not present in the fovea.
+
+```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.", fig.align="center", echo=FALSE}
 
@@
 
-```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for an overview of each panel.", fig.align="center", echo=FALSE}
+```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 3 for a description of each panel.", fig.align="center", echo=FALSE}
 

### 2023-06-21 manuscript.tex
Added IM figure

@@
 To account for the consensual response, these brain regions must combine information from the left and right eyes (\protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}), yet the computation that achieves this is achieved is unclear.
-The pupil response is temporally low-pass (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
-
-To address this shortcoming, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
-We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response (see \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and the relatively higher-pass EEG response (\protect\hyperlink{ref-Regan1966}{Regan, 1966}).
+The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
+
+To investigate the binocular combination of light, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
+We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response (see \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and the relatively higher-pass EEG response (\protect\hyperlink{ref-Regan1966}{Regan, 1966}).
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
@@
 
-All stimuli had a mean luminance of 42 cd/m\(^2\) on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
+All stimuli had a mean luminance of 42 cd/m\(^2\) and were displayed on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
 For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
@@
 In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
-In the remaining three conditions (termed the cross-frequency conditions) one eye's disc flickered at 1.6Hz, and the other eye's disc flickered at 2Hz.
-We also tested monocular (one eye sees 1.6Hz flicker, the other sees mean luminance), binocular (one eye sees each frequency at the target contrast) and dichoptic (target stimulus flickering at 2Hz, mask contrast of 48\% at 1.6Hz in the other eye) arrangements (see lower rows of Figure \ref{fig:methodsfig}).
-The rationale for flickering both eyes at 2Hz is that we can then measure summation behaviour between the eyes in the pupil and EEG response at 2Hz.
-The rationale for flickering the eyes at different frequencies is that this permits measurement of suppression between the eyes (i.e.~the reduction in the 2Hz response when a 1.6Hz mask component is added to the other eye).
-We counterbalanced presentation of the target stimulus across the left and right eyes.
+The rationale for including the monocular and binocular conditions is that they permit us to measure empirically any binocular facilitation, by comparing the response amplitudes across these two conditions.
+The rationale for including the dichoptic condition is that it provides additional contraints to computational models, and further explores the binocular contrast-response space (see \protect\hyperlink{ref-Baker2007}{Baker et al., 2007}).
+
+In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
+We chose this frequency because it was sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
+We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
+The rationale for the binocular cross condition is that it allows us to see the effects of suppression between the eyes without the additional complication of signal summation (which occurs when both eyes receive the same frequency), because the response of each eye can be resolved independently by frequency.
+Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
+A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \ref{fig:methodsfig}).
+In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
 
@@
 Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
-Unshaded waveforms indicate mask stimuli, which were presented at a fixed contrast level of 48\% regardless of the target contrast.
+Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\% regardless of the target contrast.
 Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
@@
 Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
+Models from this family can handle both scalar contrast values and continuous waveforms (\protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}) or images (\protect\hyperlink{ref-Meese2007}{Meese and Summers, 2007}) as inputs.
+For time-varying inputs, the calculations are performed at each time point, and the output waveform can then be analysed using Fourier analysis in the same way as for empirical data.
+This means that the model can make predictions for the entire Fourier spectrum, including harmonic and intermodulation responses that arise as a consequence of nonlinearities in the model (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+However for computational tractability, we performed fitting here using scalar contrast values.
 
@@
 There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz.
+The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz (though see Appendix 1).
 These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
@@
 
-Figure \ref{fig:pupildata}c shows contrast response functions in response to stimuli flickering only at 2Hz.
-Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in response (to our knowledge this is the first time this has been demonstrated).
+Figure \ref{fig:pupildata}c shows contrast response functions driven by stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in the pupil response (to our knowledge this is the first time this has been demonstrated).
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
@@
 Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
-In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(8,580) = 41.23, \(p\) \textless{} 0.001).
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(8,580) = 41.23, \(p\) \textless{} 0.001.
 In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}): F(8,232) = 17, \(p\) \textless{} 0.001).
+\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}): F(8,232) = 17, \(p\) \textless{} 0.001.
 
@@
 A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
+All of the key results from Experiment 1 were subsequently replicated for peripheral stimulation (see Appendix 1).
 
@@
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is negligible above around 2Hz (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response substantially weaker above around 2Hz (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also \protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}).
+Functionally, interocular suppression may therefore act to dynamically suppress noise, rendering binocular vision more stable.
 This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (\protect\hyperlink{ref-Li1994}{Li and Atick, 1994}; \protect\hyperlink{ref-May2022}{May and Zhaoping, 2022}).
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples given in the previous paragraph are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+However the other examples of binocular combination discussed above are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
 Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
@@
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this directly in future neuroimaging work.
+Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this more directly in future neuroimaging work.
 
@@
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
-Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than requiring binocular neurons.
-However our matching data (Figure \ref{fig:matchingdata}), as well as everyday perceptual experience, indicates that luminance signals must be combined physiologically at some stage, and that this process still involves weak or absent interocular suppression.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
+In the steady-state literature, one hallmark of a nonlinear system is the presence of intermodulation responses at the sums and differences of fundamental flicker frequencies (\protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
+In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
+Consistent with the temporal properties of pupil responses and EEG, Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/IMresponse}
+
+}
+
+\caption{Summary of intermodulation responses in pupillometry (a) and EEG (b).
+The data are from the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\%.
+Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies.
+Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.}\label{fig:IMfig}
+\end{figure}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Meese2007}{}}%
+Meese TS, Summers RJ.
+2007.
+Area summation in human vision at and above detection threshold.
+\emph{Proc Biol Sci} \textbf{274}:2891--900.
+doi:\href{https://doi.org/10.1098/rspb.2007.0957}{10.1098/rspb.2007.0957}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Tsai2012}{}}%
+Tsai JJ, Wade AR, Norcia AM.
+2012.
+Dynamics of normalization underlying masking in human visual cortex.
+\emph{J Neurosci} \textbf{32}:2783--9.
+doi:\href{https://doi.org/10.1523/JNEUROSCI.4485-11.2012}{10.1523/JNEUROSCI.4485-11.2012}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Tychsen2004}{}}%
@@
 We conducted a conceptual replication of Experiment 1 using an alternative system.
-We used a pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain), coupled to a binocular headset using liquid light guides.
-The light was imaged onto a circular diffuser for each eye (field size X deg) with the central 6 degrees masked off using a black occluder.
+A pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain) were coupled to a binocular headset using liquid light guides.
+The light was imaged onto a circular diffuser for each eye (field size 30 deg) with the central 8 degrees masked off using a black occluder.
 Therefore the replication experiment involved peripheral stimulation, unlike the main experiment which stimulated the central \textasciitilde4 degrees of the visual field.
-The mean luminance of the devices was \(cd/m^2\).
 All conditions were otherwise as described for the main experiment, and we tested 12 participants in total.
@@
 The ratio of binocular to monocular responses in Figure \ref{fig:appendixfig1}c is similar, and suppression is evident in Figure \ref{fig:appendixfig1}d,e.
-Of particular interest is the presence of a slight response at the second harmonic (4Hz, Figure \ref{fig:appendixfig1}b), which was not present in our original data.
-This may be because the driving signal is clearer when stimulating the periphery (note the clear waveform in Figure \ref{fig:appendixfig1}a), or it might indicate additional nonlinearities not present in the fovea.
+Of particular interest is the existence of a slight response at the second harmonic (4Hz, Figure \ref{fig:appendixfig1}b), which was not present in our original data.
+This may be because the driving signal is stronger when stimulating the periphery (note the clear waveform in Figure \ref{fig:appendixfig1}a), or more robust to eye movements, or it might indicate additional nonlinearities not present in the fovea.
 
@@
 
-\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for an overview of each panel.}\label{fig:appendixfig1}
+\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.}\label{fig:appendixfig1}
 \end{figure}
@@
 
-\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for an overview of each panel.}\label{fig:appendixfig2}
+\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 3 for a description of each panel.}\label{fig:appendixfig2}
 \end{figure}

### 2023-06-21 IManalysis.R

@@ -1,294 +1,0 @@
-
-# check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','utils','osfr') # list of CRAN packages
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
-if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
-packagelist <- c(packagelist,'FourierStats')
-toinstall <- packagelist[which(!packagelist %in% (.packages()))]
-invisible(lapply(toinstall,library,character.only=TRUE))
-
-cleanup2D <- function(data){
-  # helper function to clean up complex data by removing any data points more than 
-  # SDthresh standard deviations from the mean (in Mahalanobis distance units)
-  cartdata <- data.frame(Re(data),Im(data))
-  output <- 0
-  if (sum(cartdata)!=0){
-    D <- sqrt(stats::mahalanobis(cartdata, colMeans(cartdata), cov(cartdata)))
-    i <- which(D<SDthresh) 
-    output <- mean(temp[i])}
-  return(output)}
-
-SDthresh <<- 3
-nbootstraps <<- 1000
-
-colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
-targetelectrodes <- c('Oz','POz','O1','O2')
-
-localdir <- 'local/'    # all files are stored in the project directory /local/ which git is told to ignore
-if (!file.exists(localdir)){dir.create(localdir)}   # create a local directory to store data and outputs
-rawdir <- 'local/rawdata/'
-if (!file.exists(rawdir)){dir.create(rawdir)}   # create a local directory to store raw data
-figdir <- 'Figures/'
-if (!file.exists(figdir)){dir.create(figdir)}   # create a local directory to store figures
-datadir <- 'local/spectra/'
-if (!file.exists(datadir)){dir.create(datadir)}   # create a local directory to store processed data
-  
-  legaltriggers <- 1
-  
[…]

### 2023-06-21 manuscript.Rmd
Test full pipeline from raw data

@@
 
-```{r IMfig, fig.cap="Summary of intermodulation responses in pupillometry (a) and EEG (b).
-The data are from the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\\%.
-Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies.
+```{r IMfig, fig.cap="Summary of intermodulation responses in pupillometry (a) and EEG (b) data.
+The data are pooled across the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\\%.
+Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies (red).
 Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.", out.width = '50%', fig.align="center", echo=FALSE}

### 2023-06-22 manuscript.Rmd
Added option to delete raw data files after use - necessary because Github Actions otherwise doesn't have enough space

@@
 # 3 - download all raw data and analyse (requires 48GB of storage)
+cleanupraw <- 1  # if downloading raw data, delete once processed to save space
 
@@
 
+ if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
       }
@@
     save(file=paste0(datadir,'P',150+participant,'summary.RData'),list=c('cleanmeansE','meanspec'))
+    if (cleanupraw==1){file.remove(d)}  # delete raw data files to save space
     }
@@
 
+ if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
+
       }

### 2023-06-22 manuscript.Rmd
Testing auto-download of appendix data

@@
 
-processdata <- 3  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 # (download and) analyse individual participant data for replication expt
+processdata <- 3
 
@@
          # then unzip the tar file
-         untar(paste0(rawdir,'P',200+participant,'.tar'),exdir=paste0(rawdir,'P',100+participant))
+         untar(paste0(rawdir,'P',200+participant,'.tar'),exdir=paste0(rawdir,'P',200+participant))
 

### 2023-06-22 manuscript.Rmd
Trying again

@@
 Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.
-Figures \@ref(fig:BSratios) & \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
-In the steady-state literature, one hallmark of a nonlinear system is the presence of intermodulation responses at the sums and differences of fundamental flicker frequencies [@Tsai2012].
+Figures \@ref(fig:BSratios) \& \@ref(fig:TFdata)) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
+We therefore performed an additional analysis to investigate this possibility.
+
+In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies [@Tsai2012].
 In Figure \@ref(fig:IMfig) we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \@ref(fig:pupildata)d,e and \@ref(fig:EEGdata)d,e).
-Consistent with the temporal properties of pupil responses and EEG, Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+Consistent with the temporal properties of pupil responses and EEG activity, Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line).
 The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+Indeed, our model architecture makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@].
 

### 2023-06-22 manuscript.Rmd
Fixed error with IM figure

@@
 # 3 - download all raw data and analyse (requires 48GB of storage)
-cleanupraw <- 1  # if downloading raw data, delete once processed to save space
+cleanupraw <- 0  # if downloading raw data, delete once processed to save space
 
@@
 
-In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry; see Figure \@ref(fig:BSratios)).
 Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms [e.g.
@@
 Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this more directly in future neuroimaging work.
+Using fMRI to simultaneously image cortical and subcortical brain regions will also allow us to check that the differences we report here are not a consequence of the different measurement techniques we used (pupillometry and EEG).
 
@@
 The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
-Indeed, our model architecture makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@].
+Indeed, our model architecture makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@Dougherty2019].
 
@@
 
+dev.off()
 }
@@
 # (download and) analyse individual participant data for replication expt
-processdata <- 3
 
@@
 
-         if (!file.exists(paste0(localdir,'StimulusExample.png'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- 'tbema'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name=='StimulusExample.png')
-          osf_download(osffiles[fid,],localdir,progress=TRUE)
-         }
-
-stim <- readPNG('local/StimulusExample.png')
-
   PostScriptTrace('CRF1p.ps')

### 2023-06-22 manuscript.tex
Fixed error with IM figure

@@
 
-In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry).
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry; see Figure \ref{fig:BSratios}).
 Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
@@
 Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
-In the steady-state literature, one hallmark of a nonlinear system is the presence of intermodulation responses at the sums and differences of fundamental flicker frequencies (\protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
+We therefore performed an additional analysis to investigate this possibility.
+
+In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (\protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
 In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
-Consistent with the temporal properties of pupil responses and EEG, Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+Consistent with the temporal properties of pupil responses and EEG activity, Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
 The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+Indeed, our model architecture makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}).
 
@@
 
-\caption{Summary of intermodulation responses in pupillometry (a) and EEG (b).
-The data are from the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\%.
-Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies.
+\caption{Summary of intermodulation responses in pupillometry (a) and EEG (b) data.
+The data are pooled across the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\%.
+Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies (red).
 Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.}\label{fig:IMfig}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Dougherty2019}{}}%
+Dougherty K, Cox MA, Westerberg JA, Maier A.
+2019.
+Binocular modulation of monocular V1 neurons.
+\emph{Curr Biol} \textbf{29}:381--391.e4.
+doi:\href{https://doi.org/10.1016/j.cub.2018.12.004}{10.1016/j.cub.2018.12.004}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Economides2011}{}}%

### 2023-06-22 manuscript.Rmd
Trying full build from raw data (no modelling)

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 3  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 # 3 - download all raw data and analyse (requires 48GB of storage)
-cleanupraw <- 0  # if downloading raw data, delete once processed to save space
+cleanupraw <- 1  # if downloading raw data, delete once processed to save space
 

### 2023-06-23 manuscript.Rmd
Added co-author, further edits

--- 2023-06-22 manuscript.Rmd
@@
 author: |
- | Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker
+ | Federico G. Segala, Aurelio Bruno, Joel T. Martin, 
+ | Myat T. Aung, Alex R. Wade & Daniel H. Baker
  | Department of Psychology, University of York, UK
@@
 # check which packages are installed, install the missing ones, and activate
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','coda','parallel','utils','osfr') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','png','tiff','pals','ez','gtools','signal','boot','quickpsy','rstan','rstatix','coda','parallel','utils','osfr') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
-We chose this frequency because it was sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
+We chose this frequency because it is sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
 We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
@@
 Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
-A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \@ref(fig:methodsfig)).
+A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \@ref(fig:methodsfig).
 In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
@@
 The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
-In each block, there were a total of 50 trials.
+In each block, there was a total of 50 trials.
 No auditory feedback was given for this subjective task.
@@
 The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \@ref(fig:modelfigure).
+We used coherent averaging to combine the data across participants, but this was not implemented in the model, so to compensate we corrected the group-level model by scaling the estimated noise parameter ($n$) by the square root of the number of participants ($n_{group} = \frac{n}{\sqrt{30}}$).
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A $2\times5$ repeated measures $ANOVA^2_{circ}$ [@Baker2021] comparing these conditions revealed a significant main effect of target contrast (F(`r monbinPstats$dfA`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioA,digits=2)`, $p$ < 0.001), a significant effect of condition (F(`r monbinPstats$dfB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioB,digits=2)`, $p$ < 0.001), and a significant interaction (F(`r monbinPstats$dfAB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioAB,digits=2)`, $p$ < 0.001).
-The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(`r dichA2c$dfM`,`r dichA2c$dfR`) = `r round(dichA2c$Fratio,digits=2)`, $p$ < `r round(dichA2c$pval,digits=3)`).
+A $2\times5$ repeated measures $ANOVA^2_{circ}$ [@Baker2021] comparing these conditions revealed a significant main effect of target contrast (F(`r monbinPstats$dfA`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioA,digits=2)`, $p$ `r p_format(monbinPstats$pvalA,digits=3,accuracy=0.001)`), a significant effect of condition (F(`r monbinPstats$dfB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioB,digits=2)`, $p$ `r p_format(monbinPstats$pvalB,digits=3,accuracy=0.001)`), and a significant interaction (F(`r monbinPstats$dfAB`,`r monbinPstats$dfR`) = `r round(monbinPstats$FratioAB,digits=2)`, $p$ `r p_format(monbinPstats$pvalAB,digits=3,accuracy=0.001)`).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(`r dichA2c$dfM`,`r dichA2c$dfR`) = `r round(dichA2c$Fratio,digits=2)`, $p$ < `r p_format(dichA2c$pval,digits=1,accuracy=0.001)`).
 
 In Figure \@ref(fig:pupildata)d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \@ref(fig:pupildata)c for comparison).
-When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(`r monbinPstatsX$dfAB`,`r monbinPstatsX$dfR`) = `r round(monbinPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
-When the 1.6Hz component had a fixed contrast of 48% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(`r mondichPstatsX$dfAB`,`r mondichPstatsX$dfR`) = `r round(mondichPstatsX$FratioAB,digits=2)`, $p$ < 0.001).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(`r monbinPstatsX$dfAB`,`r monbinPstatsX$dfR`) = `r round(monbinPstatsX$FratioAB,digits=2)`, $p$ `r p_format(monbinPstatsX$pvalAB,digits=3,accuracy=0.001)`).
+When the 1.6Hz component had a fixed contrast of 48% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(`r mondichPstatsX$dfAB`,`r mondichPstatsX$dfR`) = `r round(mondichPstatsX$FratioAB,digits=2)`, $p$ `r p_format(mondichPstatsX$pvalAB,digits=3,accuracy=0.001)`).
 
@@
 Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
-In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(`r monbinPstatsX2$dfAB`,`r monbinPstatsX2$dfR`) = `r round(monbinPstatsX2$FratioAB,digits=2)`, $p$ < 0.001.
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles) (interaction effect: F(`r monbinPstatsX2$dfAB`,`r monbinPstatsX2$dfR`) = `r round(monbinPstatsX2$FratioAB,digits=2)`, $p$ `r p_format(monbinPstatsX2$pvalAB,digits=3,accuracy=0.001)`).
 In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases [see e.g.
-@Busse2009]: F(`r mondichPstatsX2$dfM`,`r mondichPstatsX2$dfR`) = `r round(mondichPstatsX2$Fratio,digits=2)`, $p$ < 0.001.
+@Busse2009] (main effect of target contrast F(`r mondichPstatsX2$dfM`,`r mondichPstatsX2$dfR`) = `r round(mondichPstatsX2$Fratio,digits=2)`, $p$ `r p_format(mondichPstatsX2$pval,digits=3,accuracy=0.001)`).
 
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \@ref(fig:EEGdata)c) and second (Figure \@ref(fig:EEGdata)f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ < 0.001) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ < 0.001), but no effect of condition ($p$ = `r round(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
+Analysis of variance on the complex values ($ANOVA^2_{circ}$) revealed a main effect of contrast (F(`r monbinEstats$dfA`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioA,digits=2)`, $p$ `r p_format(monbinEstats$pvalA,digits=3,accuracy=0.001)`) and an interaction effect (F(`r monbinEstats$dfAB`,`r monbinEstats$dfR`) = `r round(monbinEstats$FratioAB,digits=2)`, $p$ `r p_format(monbinEstats$pvalAB,digits=3,accuracy=0.001)`), but no effect of condition ($p$ = `r p_format(monbinEstats$pvalB,digits=2)`) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \@ref(fig:EEGdata)d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \@ref(fig:pupildata) and \@ref(fig:EEGdata).
-A $3 \times 5$ repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(`r round(ratioaov$ANOVA$DFn[2]*gg[2],digits=2)`,`r round(ratioaov$ANOVA$DFd[2]*gg[2],digits=2)`) = `r round(ratioaov$ANOVA$F[2],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[2],digits=3)`), no effect of data modality (F(`r ratioaov$ANOVA$DFn[1]`,`r ratioaov$ANOVA$DFd[1]`) = `r round(ratioaov$ANOVA$F[1],digits=2)`, \emph{p} = `r round(ratioaov$ANOVA$p[1],digits=2)`), but a highly significant interaction (F(`r round(ratioaov$ANOVA$DFn[3]*gg[3],digits=2)`,`r round(ratioaov$ANOVA$DFd[3]*gg[3],digits=2)`) = `r round(ratioaov$ANOVA$F[3],digits=2)`, \emph{p} < `r round(ratioaov$ANOVA$p[3],digits=4)`).
+A $3 \times 5$ repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(`r round(ratioaov$ANOVA$DFn[2]*gg[2],digits=2)`,`r round(ratioaov$ANOVA$DFd[2]*gg[2],digits=2)`) = `r round(ratioaov$ANOVA$F[2],digits=2)`, \emph{p} <`r p_format(ratioaov$ANOVA$p[2],digits=1,accuracy=0.001)`), no effect of data modality (F(`r ratioaov$ANOVA$DFn[1]`,`r ratioaov$ANOVA$DFd[1]`) = `r round(ratioaov$ANOVA$F[1],digits=2)`, \emph{p} = `r p_format(ratioaov$ANOVA$p[1],digits=2)`), but a highly significant interaction (F(`r round(ratioaov$ANOVA$DFn[3]*gg[3],digits=2)`,`r round(ratioaov$ANOVA$DFd[3]*gg[3],digits=2)`) = `r round(ratioaov$ANOVA$F[3],digits=2)`, \emph{p} `r p_format(ratioaov$ANOVA$p[3],digits=3,accuracy=0.001)`).
 All of the key results from Experiment 1 were subsequently replicated for peripheral stimulation (see Appendix 1).
@@
 ```{r BSratios, fig.cap="Ratio of binocular to monocular response for three data types.
-These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 1c, 2c and 2f.
+These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f.
 Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
@@
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response substantially weaker above around 2Hz [@Barrionuevo2014; @Spitschan2014]; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is substantially weaker above around 2Hz [@Barrionuevo2014; @Spitschan2014]; note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
-One stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
+On each trial, one stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
 The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
-We tested 9 ratios of contrast between the left and right eyes.
+We tested 9 ratios of target contrast between the left and right eyes.
 
@@
 The model behaviour is displayed in Figure \@ref(fig:modelfigure)e-h, with empirical data replotted in Figure \@ref(fig:modelfigure)a-d for comparison.
-In general, the model captures the key characteristics of the empirical data.
-Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
-In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \@ref(tab:paramtable)).
-This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
-This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
-
+In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Table \@ref(tab:paramtable).
 We were particularly interested in comparing the weight of interocular suppression across data sets.
@@
 k <- pupilRmax
-n <- pupilK
+n <- pupilK/sqrt(30)
 q <- 2
@@
 k <- EEGRmax
-n <- EEGK
+n <- EEGK/sqrt(30)
 q <- 2
@@
 k <- EEG2Rmax
-n <- EEG2K
+n <- EEG2K/sqrt(30)
 q <- 2
@@
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples of binocular combination discussed above are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit less from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+However the other examples of binocular combination discussed above are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit more from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
 Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
@@
 Pupil size affects the total amount of light falling on the retina.
-It is therefore the case that fluctuations in pupil diameter have a downstream effect on the signals reaching cortex.
+It is therefore the case that fluctuations in pupil diameter will have a downstream effect on the signals reaching cortex.
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
@@
 In Figure \@ref(fig:IMfig) we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \@ref(fig:pupildata)d,e and \@ref(fig:EEGdata)d,e).
-Consistent with the temporal properties of pupil responses and EEG activity, Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line).
-The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
-Indeed, our model architecture makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@Dougherty2019].
+Figure \@ref(fig:IMfig)a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \@ref(fig:IMfig)b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods.
+The presence of  intermodulation terms is predicted by nonlinear gain control models of the type considered here [@Tsai2012; @Baker2017], and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+Indeed, our model architecture [@Meese2006] makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology [@Dougherty2019].
 
@@
 **Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
+**Joel Martin**: Software, resources, writing - review & editing.
 **Myat Aung**: Software, resources, writing - review & editing.
@@
 Of particular interest is the existence of a slight response at the second harmonic (4Hz, Figure \@ref(fig:appendixfig1)b), which was not present in our original data.
-This may be because the driving signal is stronger when stimulating the periphery (note the clear waveform in Figure \@ref(fig:appendixfig1)a), or more robust to eye movements, or it might indicate additional nonlinearities not present in the fovea.
+This may be because the driving signal is stronger when stimulating the periphery (note the clear waveform in Figure \@ref(fig:appendixfig1)a), or more robust to eye movements, or it might indicate additional nonlinearities not present at the fovea.
 

### 2023-06-23 manuscript.tex
Added co-author, further edits

@@
 \title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
-\author{Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
+\author{Federico G. Segala, Aurelio Bruno, Joel T. Martin,\\
+Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
 Department of Psychology, University of York, UK\\
@@
 Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
-A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \ref{fig:methodsfig}).
+A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \ref{fig:methodsfig}.
 In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
@@
 The experiment was divided into 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
-In each block, there were a total of 50 trials.
+In each block, there was a total of 50 trials.
 No auditory feedback was given for this subjective task.
@@
 The models were fit using the individual data across all participants, independently for each data set.
-Because we used coherent averaging across participants, the group average amplitudes are shifted vertically relative to the model predictions, which are based on hierarchical fits to the individual participant amplitudes (put another way, the model does not implement coherent averaging).
-However it is clear that the character of the model in all cases gives a good representation of the data, as can be seen in Figure \ref{fig:modelfigure}.
+We used coherent averaging to combine the data across participants, but this was not implemented in the model, so to compensate we corrected the group-level model by scaling the estimated noise parameter (\(n\)) by the square root of the number of participants (\(n_{group} = \frac{n}{\sqrt{30}}\)).
 We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (\protect\hyperlink{ref-Baker2021}{Baker, 2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless{} 0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless{} 0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless{} 0.001).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (\protect\hyperlink{ref-Baker2021}{Baker, 2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless0.001).
 The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
@@
 In Figure \ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \ref{fig:pupildata}c for comparison).
-When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless{} 0.001).
-When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless{} 0.001).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless0.001).
+When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless0.001).
 
@@
 Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
-In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles): F(8,580) = 41.23, \(p\) \textless{} 0.001.
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles) (interaction effect: F(8,580) = 41.23, \(p\) \textless0.001).
 In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}): F(8,232) = 17, \(p\) \textless{} 0.001.
+\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}) (main effect of target contrast F(8,232) = 17, \(p\) \textless0.001).
 
@@
 When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless{} 0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless{} 0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
 For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
@@
 Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
-A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless{} 0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless{} \ensuremath{3\times 10^{-4}}).
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless0.001).
 All of the key results from Experiment 1 were subsequently replicated for peripheral stimulation (see Appendix 1).
@@
 \caption{Ratio of binocular to monocular response for three data types.
-These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 1c, 2c and 2f.
+These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f.
 Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
@@
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response substantially weaker above around 2Hz (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is substantially weaker above around 2Hz (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 The model behaviour is displayed in Figure \ref{fig:modelfigure}e-h, with empirical data replotted in Figure \ref{fig:modelfigure}a-d for comparison.
-In general, the model captures the key characteristics of the empirical data.
-Note that there are some minor discrepancies, which are a consequence of the hierarchical nature of the modelling.
-In brief, the model is fitted to the amplitudes for each participant, and group-level parameter estimates are derived based on these fits (see Table \ref{tab:paramtable}).
-This procedure discards the phase information, whereas the empirical averages are coherently averaged across participants (retaining phase information).
-This explains the amplitude differences between model and data, particularly at low target contrast levels, but is of little consequence for the pattern of relative responses across conditions, which is our main focus here.
-
+In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Table \ref{tab:paramtable}.
 We were particularly interested in comparing the weight of interocular suppression across data sets.
@@
 In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
-Consistent with the temporal properties of pupil responses and EEG activity, Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
-The presence of these intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
-Indeed, our model architecture makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}).
+Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods.
+The presence of intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+Indeed, our model architecture (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}).
 
@@
 \textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
+\textbf{Joel Martin}: Software, resources, writing - review \& editing.
 \textbf{Myat Aung}: Software, resources, writing - review \& editing.
@@
 Of particular interest is the existence of a slight response at the second harmonic (4Hz, Figure \ref{fig:appendixfig1}b), which was not present in our original data.
-This may be because the driving signal is stronger when stimulating the periphery (note the clear waveform in Figure \ref{fig:appendixfig1}a), or more robust to eye movements, or it might indicate additional nonlinearities not present in the fovea.
+This may be because the driving signal is stronger when stimulating the periphery (note the clear waveform in Figure \ref{fig:appendixfig1}a), or more robust to eye movements, or it might indicate additional nonlinearities not present at the fovea.
 

### 2023-06-24 manuscript.Rmd
Added reference to Baitch & Levi 1988

@@
 
-In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies [@Tsai2012].
+In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies [@Baitch1988; @Tsai2012].
 In Figure \@ref(fig:IMfig) we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \@ref(fig:pupildata)d,e and \@ref(fig:EEGdata)d,e).

### 2023-06-24 resources/STLabProtocol.py
Add STLab protocol /JTM

@@ -1,0 +1,391 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Script to run monocular and binocular targeted photoreceptor experiments.
+
+
+@author: jtm
+"""
+import os
+import os.path as op
+import shutil
+import glob
+from time import sleep
+import pickle
+
+import pandas as pd
+import parallel
+from pyplr.pupil import PupilCore
+from pyplr.stlabscene import SpectraTuneLabScene
+from pyplr.protocol import timer
+
+import make_stimuli
+
+
+#-------------------------------#
+#    Experiment configuration   #
+#-------------------------------#
+# Experiments to choose from
+EXPERIMENTS_TO_RUN = dict(
+    enumerate(['S-cone', 'M-cone', 'L-cone', 'Melanopsin', 'L-M', 'Luminance']))
+
+# Experiment pauses at end of trial if this file exists
+PAUSEFILE = op.join(op.expanduser('~'), 'PAUSEFILE')
+
+# Timing parameters in s
+ADAPTATION_PERIOD = 2*60
+INCLUDE_ADAPTATION_PERIOD = True
+STIMULUS_DURATION = 12
+
+# Experiment parameters
+DOUBLE_TRIALS = False
+
+# Set to 1. to run all 60 trials
+FRAC_TRIALS = 1.0
+
+# inter-trial interval
+ITI = 3
+
+# Hardware flags
+USE_STLAB = True
+USE_PUPIL_CORE = True
+USE_EEG = False
+
+#-------------------------------#
+# Functions
+
+
+class OverwriteError(Exception):
+    pass
+
+
+def choose_experiment():
+    print('Which experiment to run?\n')
+    print(*EXPERIMENTS_TO_RUN.items(), sep='\n')
+    experiment = ''
+    while experiment not in EXPERIMENTS_TO_RUN.keys():
+        experiment = int(input('\n> Enter the number: '))
+        if experiment not in EXPERIMENTS_TO_RUN.keys():
+            print('Enter a valid experiment...')
+    return EXPERIMENTS_TO_RUN[experiment]
+
+#-------------------------------#
+
+
+def main():
+    try:
+        print('\n')
+        print(f"{'='*80 : ^80}")
+        print(f"{'MonBin Photoreceptors': ^80}")
+        print(f"{'='*80 : ^80}")
+        print('\n')
+        sleep(.1)
+
+        # Ask experimenter to choose the experiment
+        experiment = choose_experiment()
+
+        # Ask for subject ID and block number
[…]

### 2023-06-24 resources/STLabProtocol.py
Add files /JTM

@@ -203,7 +203,7 @@ def main():
             pcore.command(f'R {op.abspath(subject_dir)}')
 
         # Get conditions, double up and randomise
-        trials = pd.read_csv('datasource.csv')
+        trials = pd.read_csv('STLabDatasource.csv')
 
         if not DOUBLE_TRIALS:
             trials = (trials.sample(frac=FRAC_TRIALS)

### 2023-06-24 resources/make_luminance_stims.py

@@ -1,0 +1,286 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Sat Jun 11 16:37:42 2022
+
+@author: jtm545
+
+Script to make the stimuli for the MonBin1 experiment. 
+
+"""
+
+import os
+import os.path as op
+from itertools import product
+from pprint import pprint
+import pickle
+from datetime import datetime
+
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+from pyplr import stlabhelp
+from pysilsub.problems import SilentSubstitutionProblem as SSP
+from pysilsub.CIE import get_CIE_1924_photopic_vl
+
+LUMENS_PER_WATT = 683
+
+
+# %% ~~~ PLOT STYLE ~~~
+
+plt.style.use('seaborn')
+plt.rcParams['font.size'] = 14
+plt.rcParams['font.family'] = 'Helvetica'
+
+# %% ~~~ CONSTANTS ~~~
+
+MINTENSITY = 0
+MAXTENSITY = 4095
+BACKGROUND = MAXTENSITY/2
+Fs = 100  # STLAB switching time
+VL = get_CIE_1924_photopic_vl()
+
+# %% ~~~ MAKE FOLDERS FOR OUTPUT ~~~
+
+STIM_FOLDER = './LuminanceTest/stims/'
+if not op.exists(STIM_FOLDER):
+    os.makedirs(STIM_FOLDER)
+
+STLAB_1_STIM_FOLDER = op.join(STIM_FOLDER, 'STLAB_1/')
+if not op.exists(STLAB_1_STIM_FOLDER):
+    os.mkdir(STLAB_1_STIM_FOLDER)
+    
+STLAB_2_STIM_FOLDER = op.join(STIM_FOLDER, 'STLAB_2/')
+if not op.exists(STLAB_2_STIM_FOLDER):
+    os.mkdir(STLAB_2_STIM_FOLDER)
+    
+CALIBRATION_FOLDER = './calibration/'
+if not op.exists(CALIBRATION_FOLDER):
+    os.mkdir(CALIBRATION_FOLDER)
+
+GAMMA_FOLDER = op.join(CALIBRATION_FOLDER, 'gamma/')
+if not op.exists(GAMMA_FOLDER):
+    os.mkdir(op.join(GAMMA_FOLDER))
+
+#%% ~~~ CALIBRATION ~~~ #
+
+# Load predictive models for each device.
[…]

### 2023-06-26 manuscript.Rmd
Simplified presentation of model figure

@@
 
+  contrastsdB <- 20*log10(c(6,12,24,48,96))
+
+         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='Averagedata.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(file=paste0(datadir,'Averagedata.RData'))
+
+         if (!file.exists(paste0(datadir,'meanmatching.RData'))){
+           # download it from OSF
+           if (!exists('osffilesP')){
+           osfnode <- '2qu6y'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffilesP <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffilesP$name=='meanmatching.RData')
+          osf_download(osffilesP[fid,],datadir,progress=TRUE)
+         }
+
+load(paste0(datadir,'meanmatching.RData'))
+
   nchains <- dim(pupilsamples)[2]
@@
 
-text(9,0.58,'(i)',cex=1.25,adj=0.5)
+text(9,0.58,'(e)',cex=2.5,adj=0.5)
 
@@
 
-legend(21,0.04,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.037,'(e)',adj=0.5,cex=2.5)
+for (cond in 1:3){
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+cond <- 6
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)
+
+legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+text(17,0.028,'(a)',adj=0.5,cex=2.5)
 
@@
 
-# legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.95,'(f)',adj=0.5,cex=2.5)
+for (cond in 1:3){
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+cond <- 6
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points
+
+text(17,0.95,'(b)',adj=0.5,cex=2.5)
 
@@
 
-# legend(21,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),lwd=3,col=colpal[condlist],box.lwd=2)
-
-text(17,0.95,'(g)',adj=0.5,cex=2.5)
+for (cond in 1:3){
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+}  
+cond <- 6
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)
+
+text(17,0.95,'(c)',adj=0.5,cex=2.5)
 
@@
 
-legend(62,95,c('48% match','24% match'),col=colpal[2:1],lwd=3,pt.cex=2,box.lwd=2)
-
-legend(45,125,c('Winner-take-all','Linear summation'),lty=2:3,box.lwd=2)
-
-text(10,117.5,'(h)',adj=0.5,cex=2.5)
-
-dev.off()
-
-contrastsdB <- 20*log10(c(6,12,24,48,96))
-
-         if (!file.exists(paste0(datadir,'Averagedata.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '2qu6y'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name=='Averagedata.RData')
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-
-load(file=paste0(datadir,'Averagedata.RData'))
-
-plotlims <- c(15,40,0,0.03) 
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.03,0.01)    # locations of tick marks on y axis
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-postscript("pdata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude at 2Hz (mm)", col.lab=rgb(0,0,0), line=1.8, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-cond <- 6
-  lines(contrastsdB,abs(cleanmeansP[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-
-legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.028,'(a)',adj=0.5,cex=2.5)
-
-dev.off()
-
-plotlims <- c(15,40,0,1)  
-ticklocsx <- contrastsdB    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
-ticklabelsx <-c(6,12,24,48,96)        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-postscript("edata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (µV) at 2Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-cond <- 6
-  lines(contrastsdB,abs(cleanmeansEav[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-
-# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.95,'(b)',adj=0.5,cex=2.5)
-
-dev.off()
-
-postscript("edata2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-plotlims <- c(15,40,0,1)  
-ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
-ticklabelsy <- ticklocsy    # set labels for y ticks
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)  
-title(ylab="Amplitude (µV) at 4Hz", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-for (cond in 1:3){
-  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-}  
-cond <- 6
-  lines(contrastsdB,abs(cleanmeansE2av[cond,]), col=colpal[cond], lwd=3, cex=0.5)
-  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
-
-# legend(22,0.8,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
-text(17,0.95,'(c)',adj=0.5,cex=2.5)
-
-dev.off()
-
-         if (!file.exists(paste0(datadir,'meanmatching.RData'))){
-           # download it from OSF
-           if (!exists('osffilesP')){
-           osfnode <- '2qu6y'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffilesP <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffilesP$name=='meanmatching.RData')
-          osf_download(osffilesP[fid,],datadir,progress=TRUE)
-         }
-
-load(paste0(datadir,'meanmatching.RData'))
-
-postscript("matchingdata.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5.5, width = 5.5)
-
-plotlims <- c(0,125,0,125)  
-ticklocs <- seq(0,125,25)   
 ratiosL <- c(1, 1, 1, 1, 1, 0.75, 0.5, 0.25, 0)
 ratiosR <- c(0, 0.25, 0.5, 0.75, 1, 1, 1, 1, 1)
-
-par(pty="s")  # make axis square
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocs, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-axis(2, at=ticklocs, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklocs, side = 1, at=ticklocs)     # add the tick labels
-mtext(text = ticklocs, side = 2, at=ticklocs, line=0.2, las=1)
-title(xlab="Right eye contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Left eye contrast (%)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(c(0,24),c(24,24),lty=2)
-lines(c(0,48),c(48,48),lty=2)
-lines(c(24,24),c(0,24),lty=2)
-lines(c(48,48),c(0,48),lty=2)
-lines(c(0,96),c(96,0),lty=3)
-lines(c(0,48),c(48,0),lty=3)
-
-for (matchlev in 1:2){
-lines(ratiosR*10^(meanthresh[matchlev,]/20),ratiosL*10^(meanthresh[matchlev,]/20),pch=16,col=colpal[matchlev],lwd=3)}
 
@@
   points(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),pch=16,cex=2,col=colpal[matchlev])
-
-  # if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])<42){
-  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
-  # }
-  # 
-  # # plot as an arrow if exceeding the axis limits
-  # if ((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])>42){
-  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),125,ratiosL[cond]*10^((SEthresh[matchlev,cond]+meanthresh[matchlev,cond])/20),length=0.035, angle=45, lwd=2)
-  # }
-
-  # arrows(ratiosR[cond]*10^(meanthresh[matchlev,cond]/20),ratiosL[cond]*10^(meanthresh[matchlev,cond]/20),ratiosR[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),ratiosL[cond]*10^((meanthresh[matchlev,cond]-SEthresh[matchlev,cond])/20),length=0.015, angle=90, lwd=2)
-}
-}
+}}
+
+legend(62,95,c('48% match','24% match'),col=colpal[2:1],lwd=3,pch=16,pt.cex=2,box.lwd=2)
+
+legend(45,125,c('Winner-take-all','Linear summation'),lty=2:3,box.lwd=2)
 
 text(10,117.5,'(d)',adj=0.5,cex=2.5)
-
-legend(75,95,c('48% match','24% match'),pch=16,col=colpal[2:1],pt.cex=2,box.lwd=2)
-
-legend(45.75,125,c('Winner-take-all','Linear summation'),lty=2:3,box.lwd=2)
 
@@
 
-  PostScriptTrace('pdata.ps')
-  p6 <- readPicture('pdata.ps.xml')
-  PostScriptTrace('edata.ps')
-  p7 <- readPicture('edata.ps.xml')
-  PostScriptTrace('edata2.ps')
-  p8 <- readPicture('edata2.ps.xml')
-  PostScriptTrace('matchingdata.ps')
-  p9 <- readPicture('matchingdata.ps.xml')
-
     for (n in 1:length(p5@paths)){
@@
 
-  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 10, width = 30)
+  pdf(paste0(figdir,"modelfigure.pdf"), bg="transparent", height = 5, width = 25)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-  grid.picture(p1,x=1/12,y=0.25,width=1/6,height=1)
-  grid.picture(p2,x=3/12,y=0.25,width=1/6,height=1)
-  grid.picture(p3,x=5/12,y=0.25,width=1/6,height=1)
-  grid.picture(p4,x=7/12,y=0.25,width=1/6,height=1)
-
-  grid.picture(p5,x=5/6,y=0.5,width=1/3,height=1)
-
-  grid.picture(p6,x=1/12,y=0.75,width=1/6,height=1)
-  grid.picture(p7,x=3/12,y=0.75,width=1/6,height=1)
-  grid.picture(p8,x=5/12,y=0.75,width=1/6,height=1)
-  grid.picture(p9,x=7/12,y=0.75,width=1/6,height=1)
-
-  dev.off()
-
-  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','matchingdata.ps','pdata.ps','edata.ps','edata2.ps','posteriors.ps'))
-  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','matchingdata.ps.xml','pdata.ps.xml','edata.ps.xml','edata2.ps.xml','posteriors.ps.xml'))
+  grid.picture(p1,x=1/10,y=0.5,width=0.2,height=1)
+  grid.picture(p2,x=3/10,y=0.5,width=0.2,height=1)
+  grid.picture(p3,x=5/10,y=0.5,width=0.2,height=1)
+  grid.picture(p4,x=7/10,y=0.5,width=0.2,height=1)
+  grid.picture(p5,x=9/10,y=0.5,width=0.2,height=1)
+
+  dev.off()
+
+  file.remove(c('CRF1e.ps','CRF2e.ps','CRF1p.ps','matchingmodel.ps','posteriors.ps'))
+  file.remove(c('CRF1e.ps.xml','CRF2e.ps.xml','CRF1p.ps.xml','matchingmodel.ps.xml','posteriors.ps.xml'))
 

### 2023-06-26 manuscript.tex
Simplified presentation of model figure

@@
 
-In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (\protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
+In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (\protect\hyperlink{ref-Baitch1988}{Baitch and Levi, 1988}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
 In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Baitch1988}{}}%
+Baitch LW, Levi DM.
+1988.
+Evidence for nonlinear binocular interactions in human visual cortex.
+\emph{Vision Res} \textbf{28}:1139--43.
+doi:\href{https://doi.org/10.1016/0042-6989(88)90140-x}{10.1016/0042-6989(88)90140-x}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%

### 2023-06-26 manuscript.Rmd
Added references and other minor tweaks

@@
 Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus [@Angee2021; @Mathot2018; @McDougal2008; @Wang2015].
-To account for the consensual response, these brain regions must combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is achieved is unclear.
-The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass [@Barrionuevo2014; @Spitschan2014], most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
+To account for the consensual response, these brain regions must combine information from the left and right eyes [@Doesschate1967], yet the computation that achieves this is unclear.
+The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass [@Barrionuevo2014; @Spitschan2014], most likely due to the mechanical limitations of the iris sphincter and dilator muscles [@Privitera2006].
 
@@
 We fitted a computational model to the data from Experiments 1 & 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \@ref(fig:modelfigure)e-h, with empirical data replotted in Figure \@ref(fig:modelfigure)a-d for comparison.
+The model behaviour is displayed in Figure \@ref(fig:modelfigure)a-d, with empirical data superimposed for comparison.
 In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Table \@ref(tab:paramtable).
 We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \@ref(fig:modelfigure)i).
+We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \@ref(fig:modelfigure)e).
 The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
@@
 for (cond in 1:3){
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 20+cond, col=colpal[cond], bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
 }  
 cond <- 6
-  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)
-
-legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
+  points(contrastsdB,abs(cleanmeansP[cond,]), pch = 25, col=colpal[cond], bg=colpal[cond], cex=1.6, lwd=3)
+
+legend(21,0.03,c('Monocular','Binocular','Dichoptic','Dichoptic cross'),pch=c(21:23,25),pt.bg=colpal[c(1:3,6)],lwd=3,lty=1,col=colpal[c(1:3,6)],pt.lwd=3,pt.cex=1.6,box.lwd=2)
 text(17,0.028,'(a)',adj=0.5,cex=2.5)
@@
 for (cond in 1:3){
-  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 20+cond, col=colpal[cond], bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
 }  
 cond <- 6
-  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points
+  points(contrastsdB,abs(cleanmeansEav[cond,]), pch = 25, col=colpal[cond], bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points
 
@@
 for (cond in 1:3){
-  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col='black', bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 20+cond, col=colpal[cond], bg=colpal[cond], cex=1.6, lwd=3)   # draw the data points themselves
 }  
 cond <- 6
-  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 25, col='black', bg=colpal[cond], cex=1.6, lwd=3)
+  points(contrastsdB,abs(cleanmeansE2av[cond,]), pch = 25, col=colpal[cond], bg=colpal[cond], cex=1.6, lwd=3)
 
@@
 ```{r modelfigure, fig.cap="Summary of computational modelling.
-Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
-Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
-Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments, with curves showing model behaviour generated using the median group-level parameter values.
+Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
 The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
@@
 
-We conducted a conceptual replication of Experiment 1 using an alternative system.
+We conducted a conceptual replication of Experiment 1 using an alternative system of hardware and software [@Martin2022; @Martin2023].
 A pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain) were coupled to a binocular headset using liquid light guides.

### 2023-06-26 manuscript.tex
Added references and other minor tweaks

@@
 Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (\protect\hyperlink{ref-Angee2021}{Angée et al., 2021}; \protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}; \protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (\protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}), yet the computation that achieves this is achieved is unclear.
-The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles.
+To account for the consensual response, these brain regions must combine information from the left and right eyes (\protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}), yet the computation that achieves this is unclear.
+The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles (\protect\hyperlink{ref-Privitera2006}{Privitera and Stark, 2006}).
 
@@
 We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \ref{fig:modelfigure}e-h, with empirical data replotted in Figure \ref{fig:modelfigure}a-d for comparison.
+The model behaviour is displayed in Figure \ref{fig:modelfigure}a-d, with empirical data superimposed for comparison.
 In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Table \ref{tab:paramtable}.
 We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}i).
+We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}e).
 The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
@@
 \caption{Summary of computational modelling.
-Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments.
-Panels (e-h) show model behaviour for the same conditions, generated using the median group-level parameter values.
-Panel (i) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments, with curves showing model behaviour generated using the median group-level parameter values.
+Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
 The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
+Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
+2023.
+PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and non-visual photoreception research.
+\emph{Journal of Vision} \textbf{In press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
+Martin JT, Pinto J, Bulte D, Spitschan M.
+2022.
+PyPlr: A versatile, integrated system of hardware and software for researching the human pupillary light reflex.
+\emph{Behav Res Methods} \textbf{54}:2720--2739.
+doi:\href{https://doi.org/10.3758/s13428-021-01759-3}{10.3758/s13428-021-01759-3}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Mathot2018}{}}%
@@
 doi:\href{https://doi.org/10.1167/15.6.4}{10.1167/15.6.4}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Privitera2006}{}}%
+Privitera CM, Stark LW.
+2006.
+A binocular pupil model for simulation of relative afferent pupil defects and the swinging flashlight test.
+\emph{Biol Cybern} \textbf{94}:215--24.
+doi:\href{https://doi.org/10.1007/s00422-005-0042-8}{10.1007/s00422-005-0042-8}
 
@@
 
-We conducted a conceptual replication of Experiment 1 using an alternative system.
+We conducted a conceptual replication of Experiment 1 using an alternative system of hardware and software (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}, \protect\hyperlink{ref-Martin2022}{2022}).
 A pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain) were coupled to a binocular headset using liquid light guides.

### 2023-06-30 manuscript.Rmd
Fixed a typo in the Fig 4 caption

@@
 These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f.
-Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
+Each value is the average ratio across N=30 participants, and error bars indicate bootstrapped standard errors.", fig.align="center", out.width = '50%', echo=FALSE}
 

### 2023-08-28 manuscript.Rmd
Changed position of methods according to eLife guidelines

@@
 
-# Methods
-
-## Participants
-
-Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
-
-## Apparatus & stimuli
-
-```{r createmethodsfig, include=FALSE, results='hide'}
-
-if (processdata>0){
-
-           if (!file.exists(paste0(localdir,'StimulusExample.png'))){
-           # download it from OSF
-           if (!exists('osffiles')){
-           osfnode <- 'tbema'
-           osfproject <- osf_retrieve_node(osfnode)
-          osffiles <- osf_ls_files(osfproject,n_max=300)}
-          fid <- which(osffiles$name=='StimulusExample.png')
-          osf_download(osffiles[fid,],localdir,progress=TRUE)
-         }
-
-stim <- readPNG('local/StimulusExample.png')
-
-pdf("Figures/methodsfig.pdf", bg="transparent", height = 8, width = 8)
-
-contlist <- c(0.06,0.12,0.24,0.48,0.96)
-amp <- 0.5
-t <- seq(0,1,length=100)
-sinetarget <- sin(2 * t * 2*pi)*amp
-sinemask <- sin(1.6 * t * 2*pi)*amp
-
-colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
-symbollist <- c(21:23,21,24,25)
-ramp <- colorRamp(c("white", "black"))  # create a ramp from one colour to another
-greypal <- rgb(ramp(seq(0, 1, length = 5)), max = 255)   # index the ramp at ten points
-
-plotlims <- c(0.5,4.1,0.5,7)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-
-par(mar=c(0.1,0.1,0.1,0.1))
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
-
-condlabels <- c('Monocular','Binocular','Dichoptic','Monocular cross','Binocular cross','Dichoptic cross')
-text(1.2,6:1,condlabels,pos=2,cex=1.2)
-
-text(c(2,3.5),7,c('Left eye','Right eye'),cex=1.6)
-
-points(rep(1.3,6),6:1, pch=symbollist, bg=colpal, cex=1.6, lwd=3)
-
-for (cont in 5:1){
-
-  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 6, col=greypal[cont], border=NA)
-  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 5, col=greypal[cont], border=NA)
-  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 4, col=greypal[cont], border=NA)
-  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 2, col=greypal[cont], border=NA)
-  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 1, col=greypal[cont], border=NA)
-
-  polygon(c(0,t,t[100])+3, c(0,sinetarget*contlist[cont],0) + 5, col=greypal[cont], border=NA)
-  polygon(c(0,t,t[100])+3, c(0,sinemask*contlist[cont],0) + 3, col=greypal[cont], border=NA)
-  polygon(c(0,t,t[100])+3, c(0,sinemask*contlist[cont],0) + 2, col=greypal[cont], border=NA)
-
-}
-
-for (cond in 1:6){lines(c(1.5,2.5),c(cond,cond),lty=2)}
-for (cond in 1:6){lines(c(3,4),c(cond,cond),lty=2)}
-
-lines(t+3, sinetarget*0.48 + 4, lwd=2)
-lines(t+3, sinemask*0.48 + 1, lwd=2)
-
-lines(t+3, sinetarget*0 + 6, lwd=2)
-lines(t+1.5, sinetarget*0 + 3, lwd=2)
-
-text(2.6,c(1,2,4,5,6),'2Hz',srt=270)
-text(4.1,c(4,5),'2Hz',srt=270)
-text(4.1,c(1,2,3),'1.6Hz',srt=270)
-
-text(2.6,3,'Mean',srt=270)
-text(4.1,6,'Mean',srt=270)
-
-imwidth <- 0.5
-xstart <- 0.4
-ystart <- 6.2
-rasterImage(stim,xstart,ystart,xstart+imwidth,ystart+imwidth*1.9)
-
-dev.off()
-
-}
-
-```
-
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
-The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see upper left insert in Figure \@ref(fig:methodsfig) for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
-The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
-Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
-
-All stimuli had a mean luminance of 42 cd/m$^2$ and were displayed on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
-Ltd., Japan).
-For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
-For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
-
-EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker [Pupil Labs GmbH, Berlin, Germany\; @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-## Procedure
-
-Before each experiment, participants adjusted the angle of the stereoscope mirrors to achieve binocular fusion.
-This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
-
-### Experiment 1: simultaneous EEG and pupillometry
-
-The experiment was conducted in a windowless room, in which the only light source was the monitor.
-The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in a single session lasting 45 minutes in total, divided into three blocks of 15 minutes each.
-In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
-
-We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
-Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
-In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement (see upper rows of Figure \@ref(fig:methodsfig)).
-In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
-The rationale for including the monocular and binocular conditions is that they permit us to measure empirically any binocular facilitation, by comparing the response amplitudes across these two conditions.
-The rationale for including the dichoptic condition is that it provides additional contraints to computational models, and further explores the binocular contrast-response space [see @Baker2007].
-
-In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
-We chose this frequency because it is sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
-We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
-The rationale for the binocular cross condition is that it allows us to see the effects of suppression between the eyes without the additional complication of signal summation (which occurs when both eyes receive the same frequency), because the response of each eye can be resolved independently by frequency.
-Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
-A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \@ref(fig:methodsfig).
-In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
-
-```{r methodsfig, fig.cap="Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1.
-Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
-Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\\% regardless of the target contrast.
-Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
-The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
-The left and right eye assignments were counterbalanced across trials in the experiment (i.e.
-the monocular stimulus could be shown to either eye with equal probability).", fig.align="center", echo=FALSE}
-
-knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
-
-```
-
-### Experiment 2: EEG responses across temporal frequency
-
-This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
-Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
-Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
-The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
-In each block, there were 20 trials in total with the same timing as for Experiment 1.
-
-### Experiment 3: temporal contrast matching
-
-The experiment was conducted in a darkened room with a blacked-out window.
-The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
-A two-interval contrast matching procedure was used to collect data.
-In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
-In the other interval, a target disc was displayed, flickering at different contrast levels on each trial, but with a fixed interocular contrast ratio across the block.
-The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
-The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
-The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
-The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
-
-Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
-The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
-In each block, there was a total of 50 trials.
-No auditory feedback was given for this subjective task.
-
-## Data analysis
-
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
-The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
-The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
-All repetitions of each condition were then averaged for each electrode.
-They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
-Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.
-coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
-For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021.
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.
-
-A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-We confirmed in additional analyses that the monocular consensual pupil response was complete, justifying our pooling of data across the eyes.
-Finally, data were averaged across all participants to obtain the group results.
-Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis [e.g.
-@Spitschan2014].
-The Fourier approach is more robust to noise at other frequencies (which can make the phase and amplitude of a fitted sine wave unstable) and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
-@Figueira2022].
-
-To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
-We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
-Thresholds were averaged across participants in logarithmic (dB) units.
-
-For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
-
-## Computational model and parameter estimation
-
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by @Meese2006.
-The second gain control stage was omitted [consistent with @Baker2017] to simplify the model and reduce the number of free parameters.
-The response of the left eye's channel is given by:
-
-\begin{equation}
-\label{eq:respL}
-Resp_L = \frac{L^2}{Z + L + wR},
-\end{equation}
-
-with an equivalent expression for the right eye:
-
-\begin{equation}
-\label{eq:respR}
-Resp_R = \frac{R^2}{Z + R + wL}.
-\end{equation}
-
-In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respB}
-Resp_B = R_{max}(Resp_L + Resp_R) + n,
-\end{equation}
-
-where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
-The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
-
-Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
-@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
-Our key parameter of interest is the weight of interocular suppression.
-Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
-Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
-Models from this family can handle both scalar contrast values and continuous waveforms [@Tsai2012] or images [@Meese2007] as inputs.
-For time-varying inputs, the calculations are performed at each time point, and the output waveform can then be analysed using Fourier analysis in the same way as for empirical data.
-This means that the model can make predictions for the entire Fourier spectrum, including harmonic and intermodulation responses that arise as a consequence of nonlinearities in the model [@Baker2017].
-However for computational tractability, we performed fitting here using scalar contrast values.
-
-We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
-This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
-We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
-The models were fit using the individual data across all participants, independently for each data set.
-We used coherent averaging to combine the data across participants, but this was not implemented in the model, so to compensate we corrected the group-level model by scaling the estimated noise parameter ($n$) by the square root of the number of participants ($n_{group} = \frac{n}{\sqrt{30}}$).
-We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
-
-## Preregistration, data and code availability
-
-We initially preregistered our main hypotheses and analysis intentions for the first experiment.
-We then conducted a pilot study with N = 12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
-We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
-
 # Results
@@
 
+# Methods
+
+## Participants
+
+Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
+
+## Apparatus & stimuli
+
+```{r createmethodsfig, include=FALSE, results='hide'}
+
+if (processdata>0){
+
+           if (!file.exists(paste0(localdir,'StimulusExample.png'))){
+           # download it from OSF
+           if (!exists('osffiles')){
+           osfnode <- 'tbema'
+           osfproject <- osf_retrieve_node(osfnode)
+          osffiles <- osf_ls_files(osfproject,n_max=300)}
+          fid <- which(osffiles$name=='StimulusExample.png')
+          osf_download(osffiles[fid,],localdir,progress=TRUE)
+         }
+
+stim <- readPNG('local/StimulusExample.png')
+
+pdf("Figures/methodsfig.pdf", bg="transparent", height = 8, width = 8)
+
+contlist <- c(0.06,0.12,0.24,0.48,0.96)
+amp <- 0.5
+t <- seq(0,1,length=100)
+sinetarget <- sin(2 * t * 2*pi)*amp
+sinemask <- sin(1.6 * t * 2*pi)*amp
+
+colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
+symbollist <- c(21:23,21,24,25)
+ramp <- colorRamp(c("white", "black"))  # create a ramp from one colour to another
+greypal <- rgb(ramp(seq(0, 1, length = 5)), max = 255)   # index the ramp at ten points
+
+plotlims <- c(0.5,4.1,0.5,7)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+
+par(mar=c(0.1,0.1,0.1,0.1))
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   # create an empty axis of the correct dimensions
+
+condlabels <- c('Monocular','Binocular','Dichoptic','Monocular cross','Binocular cross','Dichoptic cross')
+text(1.2,6:1,condlabels,pos=2,cex=1.2)
+
+text(c(2,3.5),7,c('Left eye','Right eye'),cex=1.6)
+
+points(rep(1.3,6),6:1, pch=symbollist, bg=colpal, cex=1.6, lwd=3)
+
+for (cont in 5:1){
+
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 6, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 5, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 4, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 2, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+1.5, c(0,sinetarget*contlist[cont],0) + 1, col=greypal[cont], border=NA)
+
+  polygon(c(0,t,t[100])+3, c(0,sinetarget*contlist[cont],0) + 5, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+3, c(0,sinemask*contlist[cont],0) + 3, col=greypal[cont], border=NA)
+  polygon(c(0,t,t[100])+3, c(0,sinemask*contlist[cont],0) + 2, col=greypal[cont], border=NA)
+
+}
+
+for (cond in 1:6){lines(c(1.5,2.5),c(cond,cond),lty=2)}
+for (cond in 1:6){lines(c(3,4),c(cond,cond),lty=2)}
+
+lines(t+3, sinetarget*0.48 + 4, lwd=2)
+lines(t+3, sinemask*0.48 + 1, lwd=2)
+
+lines(t+3, sinetarget*0 + 6, lwd=2)
+lines(t+1.5, sinetarget*0 + 3, lwd=2)
+
+text(2.6,c(1,2,4,5,6),'2Hz',srt=270)
+text(4.1,c(4,5),'2Hz',srt=270)
+text(4.1,c(1,2,3),'1.6Hz',srt=270)
+
+text(2.6,3,'Mean',srt=270)
+text(4.1,6,'Mean',srt=270)
+
+imwidth <- 0.5
+xstart <- 0.4
+ystart <- 6.2
+rasterImage(stim,xstart,ystart,xstart+imwidth,ystart+imwidth*1.9)
+
+dev.off()
+
+}
+
+```
+
+The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The same stimuli were used for all three experiments.
+Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see upper left insert in Figure \@ref(fig:methodsfig) for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
+
+All stimuli had a mean luminance of 42 cd/m$^2$ and were displayed on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.
+Ltd., Japan).
+For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
+For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+
+EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker [Pupil Labs GmbH, Berlin, Germany\; @Kassner2014] running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+## Procedure
+
+Before each experiment, participants adjusted the angle of the stereoscope mirrors to achieve binocular fusion.
+This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
+
+### Experiment 1: simultaneous EEG and pupillometry
+
+The experiment was conducted in a windowless room, in which the only light source was the monitor.
+The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
+The experiment was carried out in a single session lasting 45 minutes in total, divided into three blocks of 15 minutes each.
+In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+
+We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement (see upper rows of Figure \@ref(fig:methodsfig)).
+In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
+The rationale for including the monocular and binocular conditions is that they permit us to measure empirically any binocular facilitation, by comparing the response amplitudes across these two conditions.
+The rationale for including the dichoptic condition is that it provides additional contraints to computational models, and further explores the binocular contrast-response space [see @Baker2007].
+
+In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
+We chose this frequency because it is sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
+We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
+The rationale for the binocular cross condition is that it allows us to see the effects of suppression between the eyes without the additional complication of signal summation (which occurs when both eyes receive the same frequency), because the response of each eye can be resolved independently by frequency.
+Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
+A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \@ref(fig:methodsfig).
+In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
+
+```{r methodsfig, fig.cap="Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1.
+Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
+Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\\% regardless of the target contrast.
+Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
+The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
+The left and right eye assignments were counterbalanced across trials in the experiment (i.e.
+the monocular stimulus could be shown to either eye with equal probability).", fig.align="center", echo=FALSE}
+
+knitr::include_graphics(paste0(figdir,'methodsfig.pdf'))
+
+```
+
+### Experiment 2: EEG responses across temporal frequency
+
+This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
+Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
+The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
+In each block, there were 20 trials in total with the same timing as for Experiment 1.
+
+### Experiment 3: temporal contrast matching
+
+The experiment was conducted in a darkened room with a blacked-out window.
+The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
+A two-interval contrast matching procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
+In the other interval, a target disc was displayed, flickering at different contrast levels on each trial, but with a fixed interocular contrast ratio across the block.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
+The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
+
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
+The experiment was divided into 54 blocks (3 repetitions $\times$ 2 standard contrasts $\times$ 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
+In each block, there was a total of 50 trials.
+No auditory feedback was given for this subjective task.
+
+## Data analysis
+
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each electrode.
+They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
+Finally, these were averaged across participants to obtain the group results.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.
+coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding $D$ = `r SDthresh` from the complex-valued mean [see @Baker2021].
+For statistical comparisons of complex-valued data, we use the $ANOVA^2_{circ}$ statistic described by @Baker2021.
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the $T^2_{circ}$ statistic of @Victor1991 that can compare more than two conditions.
+
+A similar analysis pipeline was adopted for the pupillometry data.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software [@Kassner2014], which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+We confirmed in additional analyses that the monocular consensual pupil response was complete, justifying our pooling of data across the eyes.
+Finally, data were averaged across all participants to obtain the group results.
+Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis [e.g.
+@Spitschan2014].
+The Fourier approach is more robust to noise at other frequencies (which can make the phase and amplitude of a fitted sine wave unstable) and has been used in some previous studies [see @Barrionuevo2014; @Barrionuevo2016].
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis [e.g.
+@Figueira2022].
+
+To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
+We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
+Thresholds were averaged across participants in logarithmic (dB) units.
+
+For all experiments, we used a bootstrapping procedure with `r nbootstraps` iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
+
+## Computational model and parameter estimation
+
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by @Meese2006.
+The second gain control stage was omitted [consistent with @Baker2017] to simplify the model and reduce the number of free parameters.
+The response of the left eye's channel is given by:
+
+\begin{equation}
+\label{eq:respL}
+Resp_L = \frac{L^2}{Z + L + wR},
+\end{equation}
+
+with an equivalent expression for the right eye:
+
+\begin{equation}
+\label{eq:respR}
+Resp_R = \frac{R^2}{Z + R + wL}.
+\end{equation}
+
+In both equations, _L_ and _R_ are the contrast signals from the left and right eyes, _Z_ is a saturation constant that shifts the contrast-response function laterally, and _w_ is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+Resp_B = R_{max}(Resp_L + Resp_R) + n,
+\end{equation}
+
+where _n_ is a noise parameter, and $R_{max}$ scales the overall response amplitude.
+The $R_{max}$ parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
+
+Despite being derived from the model proposed by @Meese2006, the simplifications applied to this architecture make it very similar to other models [e.g.
+@Ding2006; @Legge1984; @Schrodinger1926; @Doesschate1967].
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression [see @Baker2012; @Kingdom2015].
+Our key parameter of interest is the weight of interocular suppression.
+Large values around $w$ = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli [@Baker2017].
+Low values around $w$ = 0 produce substantial, near-linear binocular facilitation [@Baker2020].
+Models from this family can handle both scalar contrast values and continuous waveforms [@Tsai2012] or images [@Meese2007] as inputs.
+For time-varying inputs, the calculations are performed at each time point, and the output waveform can then be analysed using Fourier analysis in the same way as for empirical data.
+This means that the model can make predictions for the entire Fourier spectrum, including harmonic and intermodulation responses that arise as a consequence of nonlinearities in the model [@Baker2017].
+However for computational tractability, we performed fitting here using scalar contrast values.
+
+We implemented the model within a Bayesian framework using the Stan software [@Carpenter2017].
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, $w$, and the other free model parameters $R_{max}$, $Z$ and $n$.
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for $w$ and $R_{max}$, and 5 and 2 for $Z$ and $n$, with these values chosen based on previous literature [@Meese2006; @Baker2012].
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+The models were fit using the individual data across all participants, independently for each data set.
+We used coherent averaging to combine the data across participants, but this was not implemented in the model, so to compensate we corrected the group-level model by scaling the estimated noise parameter ($n$) by the square root of the number of participants ($n_{group} = \frac{n}{\sqrt{30}}$).
+We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+
+## Preregistration, data and code availability
+
+We initially preregistered our main hypotheses and analysis intentions for the first experiment.
+We then conducted a pilot study with N = 12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then ran the main experiment, followed by two additional experiments that were not preregistered.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: https://doi.org/10.17605/OSF.IO/TBEMA.
+
 # Acknowledgements

### 2023-08-28 manuscript.tex
Changed position of methods according to eLife guidelines

@@
 ]{article}
-\usepackage{amsmath,amssymb}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
+\usepackage{longtable,booktabs}
 % Correct order of tables after \paragraph or \subparagraph
@@
 \setcounter{secnumdepth}{5}
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{float}
@@
 \usepackage{caption}
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={Different rules for binocular combination of luminance flicker in cortical and subcortical pathways},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
 
@@
 The brain must combine information across multiple sensory inputs to derive a coherent percept of the external world.
-This involves a process of signal combination both within (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}) and between (\protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}) the senses.
-Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (\protect\hyperlink{ref-Hubel1962}{Hubel and Wiesel, 1962}).
-Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (\protect\hyperlink{ref-Purves2008}{Purves et al., 2008}).
-However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (\protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}) and much less is known about the computations that operate in these subcortical pathways.
+This involves a process of signal combination both within (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}) and between (Ernst and Banks, \protect\hyperlink{ref-Ernst2002}{2002}) the senses.
+Binocular vision is a useful test case for signal combination, as the inputs to the two eyes overlap substantially (in species with forward-facing eyes), and the neural locus is well-established (Hubel and Wiesel, \protect\hyperlink{ref-Hubel1962}{1962}).
+Much of our knowledge about binocular combination derives from studies on the contrast response of the `canonical' visual pathway, in which signals pass from the eyes to primary visual cortex (V1), via the lateral geniculate nucleus (LGN) (Purves et al., \protect\hyperlink{ref-Purves2008}{2008}).
+However, signals are also combined across the eyes in the network of subcortical nuclei that govern pupil diameter in response to absolute light levels (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}) and much less is known about the computations that operate in these subcortical pathways.
 Our primary purpose here is to investigate the computations governing signal combination in these two anatomically distinct pathways in response to luminance changes.
@@
 For pattern vision, binocular presentation confers greater sensitivity to low contrast targets than monocular presentation.
-This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (\protect\hyperlink{ref-Baker2018}{Baker et al., 2018}; \protect\hyperlink{ref-Campbell1965}{Campbell and Green, 1965}).
-This advantage is lost at high stimulus contrasts, where both psychophysical performance (contrast discrimination thresholds) (\protect\hyperlink{ref-Legge1984}{Legge, 1984}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) and neural activity (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) are approximately equal for monocular and binocular presentation.
-Contemporary models of binocular vision (\protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) advocate a process of interocular suppression that normalizes the two eyes' inputs at high contrasts and negates the binocular advantage.
-This is consistent with our everyday experience of `ocularity invariance' (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}): perceived contrast does not change when one eye is opened and closed.
-
-The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (\protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}).
+This is known as binocular summation, with summation ratios (the relative improvement under binocular presentation) at detection threshold lying between \(\sqrt{2}\) and 2 (Baker et al., \protect\hyperlink{ref-Baker2018}{2018}; Campbell and Green, \protect\hyperlink{ref-Campbell1965}{1965}).
+This advantage is lost at high stimulus contrasts, where both psychophysical performance (contrast discrimination thresholds) (Legge, \protect\hyperlink{ref-Legge1984}{1984}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) and neural activity (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}) are approximately equal for monocular and binocular presentation.
+Contemporary models of binocular vision (Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) advocate a process of interocular suppression that normalizes the two eyes' inputs at high contrasts and negates the binocular advantage.
+This is consistent with our everyday experience of `ocularity invariance' (Baker et al., \protect\hyperlink{ref-Baker2007}{2007}): perceived contrast does not change when one eye is opened and closed.
+
+The pupillary light reflex is an automatic constriction of the iris sphincter muscles in response to increases in light levels, which causes the pupil to shrink (McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}).
 There is a clear binocular component to this reflex, as stimulation of one eye still causes constriction of the other eye's pupil (termed the consensual response; Wyatt and Musselman (\protect\hyperlink{ref-Wyatt1981}{1981})).
-Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (\protect\hyperlink{ref-Angee2021}{Angée et al., 2021}; \protect\hyperlink{ref-Mathot2018}{Mathôt, 2018}; \protect\hyperlink{ref-McDougal2008}{McDougal and Gamlin, 2008}; \protect\hyperlink{ref-Wang2015}{Wang and Munoz, 2015}).
-To account for the consensual response, these brain regions must combine information from the left and right eyes (\protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}), yet the computation that achieves this is unclear.
-The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles (\protect\hyperlink{ref-Privitera2006}{Privitera and Stark, 2006}).
+Importantly, the neuroanatomical pathway involved completely bypasses the canonical cortical pathway (retina to V1), instead involving a network of subcortical nuclei, including the Pretectal Olivary nucleus, Superior Cervical ganglion, and Edinger-Westphal nucleus (Angée et al., \protect\hyperlink{ref-Angee2021}{2021}; Mathôt, \protect\hyperlink{ref-Mathot2018}{2018}; McDougal and Gamlin, \protect\hyperlink{ref-McDougal2008}{2008}; Wang and Munoz, \protect\hyperlink{ref-Wang2015}{2015}).
+To account for the consensual response, these brain regions must combine information from the left and right eyes (Doesschate and Alpern, \protect\hyperlink{ref-Doesschate1967}{1967}), yet the computation that achieves this is unclear.
+The pupil response can be modulated by periodic changes in luminance, and is temporally low-pass (Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), most likely due to the mechanical limitations of the iris sphincter and dilator muscles (Privitera and Stark, \protect\hyperlink{ref-Privitera2006}{2006}).
 
 To investigate the binocular combination of light, we designed an experiment that allowed us to simultaneously record electrophysiological and pupillometric responses to monocular and binocular stimuli.
-We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response (see \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}), and the relatively higher-pass EEG response (\protect\hyperlink{ref-Regan1966}{Regan, 1966}).
+We chose a primary flicker frequency of 2Hz as a compromise between the low-pass pupil response (see Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}), and the relatively higher-pass EEG response (Regan, \protect\hyperlink{ref-Regan1966}{1966}).
 This novel paradigm allowed us to probe both cortical (using EEG) and subcortical (using a binocular eyetracker) pathways simultaneously in response to flickering light, and make quantitative comparisons between them.
-Periodic flicker entrains both neural (\protect\hyperlink{ref-Norcia2015}{Norcia et al., 2015}) and pupil (\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
+Periodic flicker entrains both neural (Norcia et al., \protect\hyperlink{ref-Norcia2015}{2015}) and pupil (Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}) responses at the flicker frequency, enabling precise estimation of response amplitudes in the Fourier domain.
 Relative to the response to a monocular signal, adding a signal in the other eye can either increase the response (facilitation) or reduce it (suppression).
@@
 The results are interpreted using a hierarchical Bayesian computational model of binocular vision, and reveal that subcortical pathways implement stronger interocular suppression than the canonical cortical pathway.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
-All participants had normal or corrected to normal binocular vision, and gave written informed consent.
-Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
-
-\hypertarget{apparatus-stimuli}{%
-\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
-
-The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
-The same stimuli were used for all three experiments.
-Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see upper left insert in Figure \ref{fig:methodsfig} for an example of the fused stimulus).
-The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
-The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
-Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
-
-All stimuli had a mean luminance of 42 cd/m\(^2\) and were displayed on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
-For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
-For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
-
-EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
-Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; \protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-Before each experiment, participants adjusted the angle of the stereoscope mirrors to achieve binocular fusion.
-This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
-
-\hypertarget{experiment-1-simultaneous-eeg-and-pupillometry}{%
-\subsubsection{Experiment 1: simultaneous EEG and pupillometry}\label{experiment-1-simultaneous-eeg-and-pupillometry}}
-
-The experiment was conducted in a windowless room, in which the only light source was the monitor.
-The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
-The experiment was carried out in a single session lasting 45 minutes in total, divided into three blocks of 15 minutes each.
-In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
-The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
-
-We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
-Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
-In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement (see upper rows of Figure \ref{fig:methodsfig}).
-In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
-The rationale for including the monocular and binocular conditions is that they permit us to measure empirically any binocular facilitation, by comparing the response amplitudes across these two conditions.
-The rationale for including the dichoptic condition is that it provides additional contraints to computational models, and further explores the binocular contrast-response space (see \protect\hyperlink{ref-Baker2007}{Baker et al., 2007}).
-
-In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
-We chose this frequency because it is sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
-We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
-The rationale for the binocular cross condition is that it allows us to see the effects of suppression between the eyes without the additional complication of signal summation (which occurs when both eyes receive the same frequency), because the response of each eye can be resolved independently by frequency.
-Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
-A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \ref{fig:methodsfig}.
-In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/methodsfig}
-
-}
-
-\caption{Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1.
-Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
-Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\% regardless of the target contrast.
-Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
-The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
-The left and right eye assignments were counterbalanced across trials in the experiment (i.e.
-the monocular stimulus could be shown to either eye with equal probability).}\label{fig:methodsfig}
-\end{figure}
-
-\hypertarget{experiment-2-eeg-responses-across-temporal-frequency}{%
-\subsubsection{Experiment 2: EEG responses across temporal frequency}\label{experiment-2-eeg-responses-across-temporal-frequency}}
-
-This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
-Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
-Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
-The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
-In each block, there were 20 trials in total with the same timing as for Experiment 1.
-
-\hypertarget{experiment-3-temporal-contrast-matching}{%
-\subsubsection{Experiment 3: temporal contrast matching}\label{experiment-3-temporal-contrast-matching}}
-
-The experiment was conducted in a darkened room with a blacked-out window.
-The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
-A two-interval contrast matching procedure was used to collect data.
-In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
-In the other interval, a target disc was displayed, flickering at different contrast levels on each trial, but with a fixed interocular contrast ratio across the block.
-The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
-The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
-The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
-After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
-The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
-
-Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
-The experiment was divided into 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
-In each block, there was a total of 50 trials.
-No auditory feedback was given for this subjective task.
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (\protect\hyperlink{ref-Delorme2004}{Delorme and Makeig, 2004}).
-The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
-The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
-All repetitions of each condition were then averaged for each electrode.
-They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
-Finally, these were averaged across participants to obtain the group results.
-All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see \protect\hyperlink{ref-Baker2021}{Baker, 2021}).
-For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (\protect\hyperlink{ref-Baker2021}{2021}).
-This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (\protect\hyperlink{ref-Victor1991}{1991}) that can compare more than two conditions.
-
-A similar analysis pipeline was adopted for the pupillometry data.
-The data were converted from mp4 videos to a csv text file using the Pupil Player software (\protect\hyperlink{ref-Kassner2014}{Kassner et al., 2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
-The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
-We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
-The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
-We confirmed in additional analyses that the monocular consensual pupil response was complete, justifying our pooling of data across the eyes.
-Finally, data were averaged across all participants to obtain the group results.
-Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
-Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.
-\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-The Fourier approach is more robust to noise at other frequencies (which can make the phase and amplitude of a fitted sine wave unstable) and has been used in some previous studies (see \protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Barrionuevo2016}{Barrionuevo and Cao, 2016}).
-Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.
-\protect\hyperlink{ref-Figueira2022}{Figueira et al., 2022}).
-
-To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
-We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
-Thresholds were averaged across participants in logarithmic (dB) units.
-
-For all experiments, we used a bootstrapping procedure with 1000 iterations to estimate standard errors across participants.
-All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
-
-\hypertarget{computational-model-and-parameter-estimation}{%
-\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
-
-To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}).
-The second gain control stage was omitted (consistent with \protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}) to simplify the model and reduce the number of free parameters.
-The response of the left eye's channel is given by:
-
-\begin{equation}
-\label{eq:respL}
-Resp_L = \frac{L^2}{Z + L + wR},
-\end{equation}
-
-with an equivalent expression for the right eye:
-
-\begin{equation}
-\label{eq:respR}
-Resp_R = \frac{R^2}{Z + R + wL}.
-\end{equation}
-
-In both equations, \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \emph{w} is the weight of suppression from the other eye.
-
-The responses from the two eyes are then summed binocularly:
-
-\begin{equation}
-\label{eq:respB}
-Resp_B = R_{max}(Resp_L + Resp_R) + n,
-\end{equation}
-
-where \emph{n} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
-The \(R_{max}\) parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
-
-Despite being derived from the model proposed by Meese et al.
-(\protect\hyperlink{ref-Meese2006}{2006}), the simplifications applied to this architecture make it very similar to other models (e.g.
-\protect\hyperlink{ref-Ding2006}{Ding and Sperling, 2006}; \protect\hyperlink{ref-Doesschate1967}{Doesschate and Alpern, 1967}; \protect\hyperlink{ref-Legge1984}{Legge, 1984}; \protect\hyperlink{ref-Schrodinger1926}{Schrödinger, 1926}).
-In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Kingdom2015}{Kingdom and Libenson, 2015}).
-Our key parameter of interest is the weight of interocular suppression.
-Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
-Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
-Models from this family can handle both scalar contrast values and continuous waveforms (\protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}) or images (\protect\hyperlink{ref-Meese2007}{Meese and Summers, 2007}) as inputs.
-For time-varying inputs, the calculations are performed at each time point, and the output waveform can then be analysed using Fourier analysis in the same way as for empirical data.
-This means that the model can make predictions for the entire Fourier spectrum, including harmonic and intermodulation responses that arise as a consequence of nonlinearities in the model (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
-However for computational tractability, we performed fitting here using scalar contrast values.
-
-We implemented the model within a Bayesian framework using the Stan software (\protect\hyperlink{ref-Carpenter2017}{Carpenter et al., 2017}).
-This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
-The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (\protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}).
-We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
-The models were fit using the individual data across all participants, independently for each data set.
-We used coherent averaging to combine the data across participants, but this was not implemented in the model, so to compensate we corrected the group-level model by scaling the estimated noise parameter (\(n\)) by the square root of the number of participants (\(n_{group} = \frac{n}{\sqrt{30}}\)).
-We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
-
-\hypertarget{preregistration-data-and-code-availability}{%
-\subsection{Preregistration, data and code availability}\label{preregistration-data-and-code-availability}}
-
-We initially preregistered our main hypotheses and analysis intentions for the first experiment.
-We then conducted a pilot study with N = 12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
-We then ran the main experiment, followed by two additional experiments that were not preregistered.
-The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
@@
 The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (\protect\hyperlink{ref-Baker2021}{Baker, 2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless0.001).
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (Baker, \protect\hyperlink{ref-Baker2021}{2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless0.001).
 The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
@@
 In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles) (interaction effect: F(8,580) = 41.23, \(p\) \textless0.001).
-In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}) (main effect of target contrast F(8,232) = 17, \(p\) \textless0.001).
+In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.~Busse et al., \protect\hyperlink{ref-Busse2009}{2009}) (main effect of target contrast F(8,232) = 17, \(p\) \textless0.001).
 
@@
 These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f.
-Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
+Each value is the average ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
 \end{figure}
@@
 
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
 One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
 We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is substantially weaker above around 2Hz (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+Only EEG data were collected for this experiment, as the pupil response is substantially weaker above around 2Hz (Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}; Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
 
@@
 In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry; see Figure \ref{fig:BSratios}).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
-\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Legge1981}{Legge and Rubin, 1981}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}; \protect\hyperlink{ref-Quaia2018}{Quaia et al., 2018}).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.~Anstis and Ho, \protect\hyperlink{ref-Anstis1998}{1998}; Legge and Rubin, \protect\hyperlink{ref-Legge1981}{1981}; Levelt, \protect\hyperlink{ref-Levelt1965}{1965}; Quaia et al., \protect\hyperlink{ref-Quaia2018}{2018}).
 We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
@@
 There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}), and the peak location of our prior distribution (black curve).
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}), and the peak location of our prior distribution (black curve).
 These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
@@
 The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are generally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) (however we note that facilitation as substantial as ours has been reported in previous EEG work by \protect\hyperlink{ref-Apkarian1981}{Apkarian et al., 1981}).
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are generally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}; Moradi and Heeger, \protect\hyperlink{ref-Moradi2009}{2009}) (however we note that facilitation as substantial as ours has been reported in previous EEG work by Apkarian et al., \protect\hyperlink{ref-Apkarian1981}{1981}).
 Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
@@
 Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure (melatonin is a hormone released by the pineal gland that regulates sleep; its production is suppressed by light exposure and can be measured from saliva assays).
-Work on the accommodative response indicates that binocular combination there is approximately linear (\protect\hyperlink{ref-Flitcroft1992}{Flitcroft et al., 1992}), and can even cancel when signals are in antiphase (we did not try this configuration here).
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}), though not for luminance decrements (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}).
+Work on the accommodative response indicates that binocular combination there is approximately linear (Flitcroft et al., \protect\hyperlink{ref-Flitcroft1992}{1992}), and can even cancel when signals are in antiphase (we did not try this configuration here).
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (Anstis and Ho, \protect\hyperlink{ref-Anstis1998}{1998}; Baker et al., \protect\hyperlink{ref-Baker2012}{2012}; Levelt, \protect\hyperlink{ref-Levelt1965}{1965}), though not for luminance decrements (Anstis and Ho, \protect\hyperlink{ref-Anstis1998}{1998}).
 Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination (or combination across multiple inputs in other senses).
@@
 Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also \protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}).
+Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also Ernst and Banks, \protect\hyperlink{ref-Ernst2002}{2002}).
 Functionally, interocular suppression may therefore act to dynamically suppress noise, rendering binocular vision more stable.
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (\protect\hyperlink{ref-Li1994}{Li and Atick, 1994}; \protect\hyperlink{ref-May2022}{May and Zhaoping, 2022}).
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (Li and Atick, \protect\hyperlink{ref-Li1994}{1994}; May and Zhaoping, \protect\hyperlink{ref-May2022}{2022}).
 One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
@@
 We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.
-\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.
-\protect\hyperlink{ref-Bradley2008}{Bradley et al., 2008}).
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.~Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.~Bradley et al., \protect\hyperlink{ref-Bradley2008}{2008}).
 We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
@@
 
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}) are biased towards low spatial frequencies (\protect\hyperlink{ref-Edwards1995}{Edwards et al., 1995}; \protect\hyperlink{ref-Tootell1988}{Tootell et al., 1988}), and relatively insensitive to stimulus orientation (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; though see \protect\hyperlink{ref-Economides2011}{Economides et al., 2011}).
-As the blob regions are embedded within ocular dominance columns (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}), they are also largely monocular (\protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; \protect\hyperlink{ref-Tychsen2004}{Tychsen et al., 2004}).
-More recent work has reported psychophysical evidence for unoriented chromatic (\protect\hyperlink{ref-Gheiratmand2013}{Gheiratmand et al., 2013}) and achromatic (\protect\hyperlink{ref-Meese2011}{Meese and Baker, 2011}) mechanisms, that also appear to be monocular.
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (Horton and Hubel, \protect\hyperlink{ref-Horton1981}{1981}; Livingstone and Hubel, \protect\hyperlink{ref-Livingstone1984}{1984}) are biased towards low spatial frequencies (Edwards et al., \protect\hyperlink{ref-Edwards1995}{1995}; Tootell et al., \protect\hyperlink{ref-Tootell1988}{1988}), and relatively insensitive to stimulus orientation (Horton and Hubel, \protect\hyperlink{ref-Horton1981}{1981}; Livingstone and Hubel, \protect\hyperlink{ref-Livingstone1984}{1984}; though see Economides et al., \protect\hyperlink{ref-Economides2011}{2011}).
+As the blob regions are embedded within ocular dominance columns (Horton and Hubel, \protect\hyperlink{ref-Horton1981}{1981}), they are also largely monocular (Livingstone and Hubel, \protect\hyperlink{ref-Livingstone1984}{1984}; Tychsen et al., \protect\hyperlink{ref-Tychsen2004}{2004}).
+More recent work has reported psychophysical evidence for unoriented chromatic (Gheiratmand et al., \protect\hyperlink{ref-Gheiratmand2013}{2013}) and achromatic (Meese and Baker, \protect\hyperlink{ref-Meese2011}{2011}) mechanisms, that also appear to be monocular.
 Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
@@
 
-In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (\protect\hyperlink{ref-Baitch1988}{Baitch and Levi, 1988}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
+In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (Baitch and Levi, \protect\hyperlink{ref-Baitch1988}{1988}; Tsai et al., \protect\hyperlink{ref-Tsai2012}{2012}).
 In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
@@
 It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods.
-The presence of intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
-Indeed, our model architecture (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}).
+The presence of intermodulation terms is predicted by nonlinear gain control models of the type considered here (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}; Tsai et al., \protect\hyperlink{ref-Tsai2012}{2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+Indeed, our model architecture (Meese et al., \protect\hyperlink{ref-Meese2006}{2006}) makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (Dougherty et al., \protect\hyperlink{ref-Dougherty2019}{2019}).
 
@@
 We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Thirty (20 females), twelve (7 females) and ten (3 females) adult participants, whose ages ranged from 18 to 45, were recruited for Experiments 1, 2 and 3 respectively.
+All participants had normal or corrected to normal binocular vision, and gave written informed consent.
+Our procedures were approved by the Ethics Committee of the Department of Psychology at the University of York (identification number 792).
+
+\hypertarget{apparatus-stimuli}{%
+\subsection{Apparatus \& stimuli}\label{apparatus-stimuli}}
+
+The stimuli were two discs of achromatic flickering light with a diameter of 3.74 degrees, presented on a black background.
+The same stimuli were used for all three experiments.
+Four dark red lines were added around both discs to help with their perceptual fusion, giving the appearance of a single binocular disc (see upper left insert in Figure \ref{fig:methodsfig} for an example of the fused stimulus).
+The discs were viewed through a four-mirror stereoscope, which used front silvered mirrors to avoid internal reflections, and meant that participants saw a single fused disc.
+The use of a stereoscope allowed us to modulate the stimuli in three different ocular configurations: monocular, binocular, and dichoptic.
+Note that during monocular presentation of flicker, the unstimulated eye still saw the static (non-flickering) disc of mean luminance.
+
+All stimuli had a mean luminance of 42 cd/m\(^2\) and were displayed on an Iiyama VisionMaster™ Pro 510 display (800 x 600 pixels, 60 Hz refresh rate), which was gamma corrected using a Minolta LS-110 photometer (Minolta Camera Co.~Ltd., Japan).
+For experiments 1 and 2, the stimuli were presented using Psychopy (v3.0.7).
+For experiment 3, the stimuli were presented using Psychopy (v2022.1.1).
+
+EEG data were collected for Experiments 1 and 2 using a 64-electrode ANT WaveGuard cap and the signals were recorded at 1 kHz using the ASA software (ANT Neuro, Netherlands).
+Pupillometry data were collected for Experiment 1 using a binocular Pupil Core eye-tracker (Pupil Labs GmbH, Berlin, Germany; Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}) running at 120 Hz, and the signals were recorded with the Pupil Capture software.
+
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+Before each experiment, participants adjusted the angle of the stereoscope mirrors to achieve binocular fusion.
+This was done so that they would perceive the two discs as one fused disc when looking at the screen through the stereoscope.
+
+\hypertarget{experiment-1-simultaneous-eeg-and-pupillometry}{%
+\subsubsection{Experiment 1: simultaneous EEG and pupillometry}\label{experiment-1-simultaneous-eeg-and-pupillometry}}
+
+The experiment was conducted in a windowless room, in which the only light source was the monitor.
+The participants sat at 99 cm from the monitor and the total optical viewing distance (through the stereoscope) was 107 cm.
+The experiment was carried out in a single session lasting 45 minutes in total, divided into three blocks of 15 minutes each.
+In each block, there were 60 trials lasting 15 seconds each (12s of stimulus presentation, with an interstimulus interval of 3s).
+The participants were given no task other than to look at the fixation cross in the middle of the disc while trying to minimise their blinking during the presentation period.
+
+We included six distinct ocular conditions, each at five temporal contrast levels (combined factorially) relative to the mean luminance: 6, 12, 24, 48 and 96\%.
+Contrast was defined as temporal Michelson contrast; the difference between maximum and minimum luminances, scaled by the mean and expressed as a percentage.
+In the first three conditions, the discs flickered at 2 Hz, in either a monocular, binocular, or dichoptic arrangement (see upper rows of Figure \ref{fig:methodsfig}).
+In the dichoptic condition the non-target eye saw a fixed temporal contrast of 48\%.
+The rationale for including the monocular and binocular conditions is that they permit us to measure empirically any binocular facilitation, by comparing the response amplitudes across these two conditions.
+The rationale for including the dichoptic condition is that it provides additional contraints to computational models, and further explores the binocular contrast-response space (see Baker et al., \protect\hyperlink{ref-Baker2007}{2007}).
+
+In the remaining three conditions (termed the cross-frequency conditions) an additional flicker frequency of 1.6Hz was introduced.
+We chose this frequency because it is sufficiently well-isolated from the target frequency (2Hz) in the Fourier spectrum for 10-second trials.
+We repeated the monocular condition with this stimulus (one eye sees 1.6Hz flicker, the other sees mean luminance), as well as testing in a binocular cross configuration (one eye sees each frequency at the target contrast).
+The rationale for the binocular cross condition is that it allows us to see the effects of suppression between the eyes without the additional complication of signal summation (which occurs when both eyes receive the same frequency), because the response of each eye can be resolved independently by frequency.
+Finally, in the dichoptic cross condition, one eye saw the target stimulus flickering at 2Hz, the other eye saw flicker at 1.6Hz with a contrast of 48\% - again this reveals the presence of suppression (by comparison with the 2Hz monocular condition).
+A schematic overview of the cross-frequency conditions is shown in the lower rows of Figure \ref{fig:methodsfig}.
+In all conditions, we counterbalanced presentation of the target stimulus across the left and right eyes.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/methodsfig}
+
+}
+
+\caption{Schematic diagram illustrating the ocular arrangements, and temporal waveforms of the luminance modulations used in Experiment 1.
+Shaded waveforms indicate a target stimulus, that was presented at one of five contrasts on each trial (denoted by the shading levels).
+Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\% regardless of the target contrast.
+Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
+The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
+The left and right eye assignments were counterbalanced across trials in the experiment (i.e.
+the monocular stimulus could be shown to either eye with equal probability).}\label{fig:methodsfig}
+\end{figure}
+
+\hypertarget{experiment-2-eeg-responses-across-temporal-frequency}{%
+\subsubsection{Experiment 2: EEG responses across temporal frequency}\label{experiment-2-eeg-responses-across-temporal-frequency}}
+
+This experiment used the same equipment set up as Experiment 1, except that the eye tracker was not used.
+Unlike the first experiment, only one contrast level was used (96\%) and the discs were set to flicker at five different frequencies (2, 4, 8, 16 and 30 Hz).
+Only two ocular configurations, monocular and binocular, were included, with the latter having both discs flickering at the same frequency.
+The experiment was carried out in one session lasting 25 minutes in total, divided into five blocks of 5 minutes each.
+In each block, there were 20 trials in total with the same timing as for Experiment 1.
+
+\hypertarget{experiment-3-temporal-contrast-matching}{%
+\subsubsection{Experiment 3: temporal contrast matching}\label{experiment-3-temporal-contrast-matching}}
+
+The experiment was conducted in a darkened room with a blacked-out window.
+The display equipment (monitor and stereoscope) were the same as for the two previous experiments, but no EEG or pupillometry data were collected.
+A two-interval contrast matching procedure was used to collect data.
+In one interval, participants were presented with a standard fused disc that flickered at a set contrast level (either 24 or 48\%), which was selected by the experimenter at the beginning of each block.
+In the other interval, a target disc was displayed, flickering at different contrast levels on each trial, but with a fixed interocular contrast ratio across the block.
+The contrast level of the target was controlled by a 1-up, 1-down staircase moving in logarithmic (dB) steps of contrast.
+The ratio of flicker amplitudes in the left and right eyes was varied across blocks and was set to be 0, 0.25, 0.5, 0.75 or 1 (9 distinct conditions).
+The standard and target discs were displayed for 1 second each, with an interstimulus interval of 0.5 seconds.
+After both discs had appeared on screen, the participants had to indicate which interval they perceived as having the more intense flicker.
+The intervals were randomly ordered, and all discs flickered at a frequency of 2 Hz (two cycles in sine phase).
+
+Due to its long duration (approximately 3 hours in total), the participants completed the experiment across multiple sessions initiated at their own convenience.
+The experiment was divided into 54 blocks (3 repetitions \(\times\) 2 standard contrasts \(\times\) 9 target ratios), which lasted on average 3 minutes each, depending on the response speed of the participant.
+In each block, there was a total of 50 trials.
+No auditory feedback was given for this subjective task.
+
+\hypertarget{data-analysis}{%
+\subsection{Data analysis}\label{data-analysis}}
+
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, \protect\hyperlink{ref-Delorme2004}{2004}).
+The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
+The Fourier transform of each waveform was calculated, and the complex spectrum stored in a matrix.
+All repetitions of each condition were then averaged for each electrode.
+They were then averaged across four occipital electrodes (\emph{POz}, \emph{Oz}, \emph{O1}, \emph{O2}), to obtain individual results.
+Finally, these were averaged across participants to obtain the group results.
+All averaging was performed in the complex domain and therefore retained the phase information (i.e.~coherent averaging), and at each stage we excluded data points with a Mahalanobis distance exceeding \(D\) = 3 from the complex-valued mean (see Baker, \protect\hyperlink{ref-Baker2021}{2021}).
+For statistical comparisons of complex-valued data, we use the \(ANOVA^2_{circ}\) statistic described by Baker (\protect\hyperlink{ref-Baker2021}{2021}).
+This is a multivariate extension of ANOVA that assumes equal variance of the real and imaginary Fourier components, or equivalently, an extension of the \(T^2_{circ}\) statistic of Victor and Mast (\protect\hyperlink{ref-Victor1991}{1991}) that can compare more than two conditions.
+
+A similar analysis pipeline was adopted for the pupillometry data.
+The data were converted from mp4 videos to a csv text file using the Pupil Player software (Kassner et al., \protect\hyperlink{ref-Kassner2014}{2014}), which estimated pupil diameter for each eye on each frame using a 3D model of the eyeball.
+The individual data were then loaded into R for analysis, where again a ten-second waveform for each trial in each eye was extracted (excluding the first two seconds after stimulus onset).
+We interpolated across any dropped or missing frames to ensure regular and continuous sampling over time.
+The Fourier transform was calculated for each waveform, and all repetitions of each condition were pooled across eye and then averaged.
+We confirmed in additional analyses that the monocular consensual pupil response was complete, justifying our pooling of data across the eyes.
+Finally, data were averaged across all participants to obtain the group results.
+Again, we used coherent averaging, and excluded outlying data points in the same way as for the EEG data.
+Note that previous pupillometry studies using luminance flicker have tended to fit a single sine-wave at the fundamental frequency, rather than using Fourier analysis (e.g.~Spitschan et al., \protect\hyperlink{ref-Spitschan2014}{2014}).
+The Fourier approach is more robust to noise at other frequencies (which can make the phase and amplitude of a fitted sine wave unstable) and has been used in some previous studies (see Barrionuevo et al., \protect\hyperlink{ref-Barrionuevo2014}{2014}; Barrionuevo and Cao, \protect\hyperlink{ref-Barrionuevo2016}{2016}).
+Additionally, it makes the pupillometry analysis consistent with standard practice in steady-state EEG analysis (e.g.~Figueira et al., \protect\hyperlink{ref-Figueira2022}{2022}).
+
+To analyse the matching data, we pooled the trial responses across all repetitions of a given condition for each participant.
+We then fitted a cumulative normal psychometric function to estimate the point of subjective equality at the 50\% level.
+Thresholds were averaged across participants in logarithmic (dB) units.
+
+For all experiments, we used a bootstrapping procedure with 1000 iterations to estimate standard errors across participants.
+All analysis and figure construction was conducted using a single R-script, available online, making this study fully computationally reproducible.
+
+\hypertarget{computational-model-and-parameter-estimation}{%
+\subsection{Computational model and parameter estimation}\label{computational-model-and-parameter-estimation}}
+
+To describe our data, we chose a model of binocular contrast gain control with the same general form as the first stage of the model proposed by Meese et al.
+(\protect\hyperlink{ref-Meese2006}{2006}).
+The second gain control stage was omitted (consistent with Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}) to simplify the model and reduce the number of free parameters.
+The response of the left eye's channel is given by:
+
+\begin{equation}
+\label{eq:respL}
+Resp_L = \frac{L^2}{Z + L + wR},
+\end{equation}
+
+with an equivalent expression for the right eye:
+
+\begin{equation}
+\label{eq:respR}
+Resp_R = \frac{R^2}{Z + R + wL}.
+\end{equation}
+
+In both equations, \emph{L} and \emph{R} are the contrast signals from the left and right eyes, \emph{Z} is a saturation constant that shifts the contrast-response function laterally, and \emph{w} is the weight of suppression from the other eye.
+
+The responses from the two eyes are then summed binocularly:
+
+\begin{equation}
+\label{eq:respB}
+Resp_B = R_{max}(Resp_L + Resp_R) + n,
+\end{equation}
+
+where \emph{n} is a noise parameter, and \(R_{max}\) scales the overall response amplitude.
+The \(R_{max}\) parameter was omitted when modelling the contrast matching data, as it has no effect in this paradigm.
+
+Despite being derived from the model proposed by Meese et al.
+(\protect\hyperlink{ref-Meese2006}{2006}), the simplifications applied to this architecture make it very similar to other models (e.g.~Ding and Sperling, \protect\hyperlink{ref-Ding2006}{2006}; Doesschate and Alpern, \protect\hyperlink{ref-Doesschate1967}{1967}; Legge, \protect\hyperlink{ref-Legge1984}{1984}; Schrödinger, \protect\hyperlink{ref-Schrodinger1926}{1926}).
+In particular we fixed the numerator exponent at 2 in our model, because otherwise this value tends to trade off with the weight of interocular suppression (see Baker et al., \protect\hyperlink{ref-Baker2012}{2012}; Kingdom and Libenson, \protect\hyperlink{ref-Kingdom2015}{2015}).
+Our key parameter of interest is the weight of interocular suppression.
+Large values around \(w\) = 1 result in a very small or nonexistent binocular advantage at suprathreshold contrasts, consistent with previous work using grating stimuli (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
+Low values around \(w\) = 0 produce substantial, near-linear binocular facilitation (Baker et al., \protect\hyperlink{ref-Baker2020}{2020}).
+Models from this family can handle both scalar contrast values and continuous waveforms (Tsai et al., \protect\hyperlink{ref-Tsai2012}{2012}) or images (Meese and Summers, \protect\hyperlink{ref-Meese2007}{2007}) as inputs.
+For time-varying inputs, the calculations are performed at each time point, and the output waveform can then be analysed using Fourier analysis in the same way as for empirical data.
+This means that the model can make predictions for the entire Fourier spectrum, including harmonic and intermodulation responses that arise as a consequence of nonlinearities in the model (Baker and Wade, \protect\hyperlink{ref-Baker2017}{2017}).
+However for computational tractability, we performed fitting here using scalar contrast values.
+
+We implemented the model within a Bayesian framework using the Stan software (Carpenter et al., \protect\hyperlink{ref-Carpenter2017}{2017}).
+This allowed us to estimate group-level posterior parameter distributions for the weight of interocular suppression, \(w\), and the other free model parameters \(R_{max}\), \(Z\) and \(n\).
+The prior distributions for all parameters were Gaussian, with means and standard deviations of 1 and 0.5 for \(w\) and \(R_{max}\), and 5 and 2 for \(Z\) and \(n\), with these values chosen based on previous literature (Baker et al., \protect\hyperlink{ref-Baker2012}{2012}; Meese et al., \protect\hyperlink{ref-Meese2006}{2006}).
+We sampled from a Student's t-distribution for the amplitudes in the pupillometry and EEG experiments, and from a Bernoulli distribution for the single trial matching data.
+The models were fit using the individual data across all participants, independently for each data set.
+We used coherent averaging to combine the data across participants, but this was not implemented in the model, so to compensate we corrected the group-level model by scaling the estimated noise parameter (\(n\)) by the square root of the number of participants (\(n_{group} = \frac{n}{\sqrt{30}}\)).
+We took posterior samples at over a million steps for each data set, using a computer cluster, and retained 10\% of samples for plotting.
+
+\hypertarget{preregistration-data-and-code-availability}{%
+\subsection{Preregistration, data and code availability}\label{preregistration-data-and-code-availability}}
+
+We initially preregistered our main hypotheses and analysis intentions for the first experiment.
+We then conducted a pilot study with N = 12 participants, before making some minor changes to the stimulus (we added dim red lines to aid binocular fusion).
+We then ran the main experiment, followed by two additional experiments that were not preregistered.
+The preregistration document, raw data files, and experimental and analysis code, are available on the project repository: \url{https://doi.org/10.17605/OSF.IO/TBEMA}.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Apkarian1981}{}}%
+\leavevmode\hypertarget{ref-Apkarian1981}{}%
 Apkarian PA, Nakayama K, Tyler CW.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Baitch1988}{}}%
+\leavevmode\hypertarget{ref-Baitch1988}{}%
 Baitch LW, Levi DM.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Busse2009}{}}%
+\leavevmode\hypertarget{ref-Busse2009}{}%
 Busse L, Wade AR, Carandini M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dougherty2019}{}}%
+\leavevmode\hypertarget{ref-Dougherty2019}{}%
 Dougherty K, Cox MA, Westerberg JA, Maier A.
 2019.
-Binocular modulation of monocular V1 neurons.
+Binocular modulation of monocular v1 neurons.
 \emph{Curr Biol} \textbf{29}:381--391.e4.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Flitcroft1992}{}}%
+\leavevmode\hypertarget{ref-Flitcroft1992}{}%
 Flitcroft DI, Judge SJ, Morley JW.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1984}{}}%
-Legge GE. 1984. Binocular contrast summation--II. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Legge1981}{}}%
+\leavevmode\hypertarget{ref-Legge1984}{}%
+Legge GE. 1984. Binocular contrast summation--ii. Quadratic summation. \emph{Vision Res} \textbf{24}:385--94. doi:\href{https://doi.org/10.1016/0042-6989(84)90064-6}{10.1016/0042-6989(84)90064-6}
+
+\leavevmode\hypertarget{ref-Legge1981}{}%
 Legge GE, Rubin GS. 1981. Binocular interactions in suprathreshold contrast perception. \emph{Percept Psychophys} \textbf{30}:49--61. doi:\href{https://doi.org/10.3758/bf03206136}{10.3758/bf03206136}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Levelt1965}{}}%
+\leavevmode\hypertarget{ref-Levelt1965}{}%
 Levelt WJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2023}{}}%
+\leavevmode\hypertarget{ref-Martin2023}{}%
 Martin JT, Boynton GM, Baker DH, Wade AR, Spitschan M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Martin2022}{}}%
+\leavevmode\hypertarget{ref-Martin2022}{}%
 Martin JT, Pinto J, Bulte D, Spitschan M.
@@
 A reevaluation of achromatic spatio-temporal vision: Nonoriented filters are monocular, they adapt, and can be used for decision making at high flicker speeds.
-\emph{{iPerception}} \textbf{2}:159--82.
+\emph{iPerception} \textbf{2}:159--82.
 doi:\href{https://doi.org/10.1068/i0416}{10.1068/i0416}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2006}{}}%
+\leavevmode\hypertarget{ref-Meese2006}{}%
 Meese TS, Georgeson MA, Baker DH. 2006. Binocular contrast vision at and above threshold. \emph{J Vis} \textbf{6}:1224--43. doi:\href{https://doi.org/10.1167/6.11.7}{10.1167/6.11.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Meese2007}{}}%
+\leavevmode\hypertarget{ref-Meese2007}{}%
 Meese TS, Summers RJ.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Moradi2009}{}}%
+\leavevmode\hypertarget{ref-Moradi2009}{}%
 Moradi F, Heeger DJ. 2009. Inter-ocular contrast normalization in human visual cortex. \emph{J Vis} \textbf{9(3)}:13. doi:\href{https://doi.org/10.1167/9.3.13}{10.1167/9.3.13}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Norcia2015}{}}%
+\leavevmode\hypertarget{ref-Norcia2015}{}%
 Norcia AM, Appelbaum LG, Ales JM, Cottereau BR, Rossion B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Privitera2006}{}}%
+\leavevmode\hypertarget{ref-Privitera2006}{}%
 Privitera CM, Stark LW.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Purves2008}{}}%
-Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of {Cognitive} {Neuroscience}. Oxford University Press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Quaia2018}{}}%
+\leavevmode\hypertarget{ref-Purves2008}{}%
+Purves D, Brannon EM, Cabeza R, LaBar KS, Huettel SA, Platt ML, Woldorff MG. 2008. Principles of Cognitive Neuroscience. Oxford University Press.
+
+\leavevmode\hypertarget{ref-Quaia2018}{}%
 Quaia C, Optican LM, Cumming BG. 2018. Binocular summation for reflexive eye movements. \emph{J Vis} \textbf{18(4)}:7. doi:\href{https://doi.org/10.1167/18.4.7}{10.1167/18.4.7}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Regan1966}{}}%
+\leavevmode\hypertarget{ref-Regan1966}{}%
 Regan D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Schrodinger1926}{}}%
+\leavevmode\hypertarget{ref-Schrodinger1926}{}%
 Schrödinger E. 1926. Die gesichtsempfindungen.Mueller-Pouillets Lehrbuch Der Physik (11th Ed.). Vieweg: Braunschweig. pp. 456--560.
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2019}{}}%
+\leavevmode\hypertarget{ref-Spitschan2019}{}%
 Spitschan M, Cajochen C. 2019. Binocular facilitation in light-mediated melatonin suppression? \emph{J Pineal Res} \textbf{67}:e12602. doi:\href{https://doi.org/10.1111/jpi.12602}{10.1111/jpi.12602}
 
-\leavevmode\vadjust pre{\hypertarget{ref-Spitschan2014}{}}%
+\leavevmode\hypertarget{ref-Spitschan2014}{}%
 Spitschan M, Jain S, Brainard DH, Aguirre GK.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Tsai2012}{}}%
+\leavevmode\hypertarget{ref-Tsai2012}{}%
 Tsai JJ, Wade AR, Norcia AM.
@@
 
-\end{CSLReferences}
-
 \hypertarget{appendix-1}{%
@@
 
-We conducted a conceptual replication of Experiment 1 using an alternative system of hardware and software (\protect\hyperlink{ref-Martin2023}{Martin et al., 2023}, \protect\hyperlink{ref-Martin2022}{2022}).
+We conducted a conceptual replication of Experiment 1 using an alternative system of hardware and software (Martin et al., \protect\hyperlink{ref-Martin2023}{2023}, \protect\hyperlink{ref-Martin2022}{2022}).
 A pair of Spectra Tune Lab multiprimary devices (LEDmotive Technologies LLC, Barcelona, Spain) were coupled to a binocular headset using liquid light guides.

### 2023-08-28 manuscript.Rmd
Updater authors' inofrmation

@@
 author: |
- | Federico G. Segala, Aurelio Bruno, Joel T. Martin, 
- | Myat T. Aung, Alex R. Wade & Daniel H. Baker
- | Department of Psychology, University of York, UK
+ | Federico G. Segala$^1$, Aurelio Bruno$^2$, Joel T. Martin$^1$, Myat T. Aung$^1$, Alex R. Wade$^1$
+ | & Daniel H. Baker$^1$
  | *eLife* (2023) https://doi.org/10.7554/eLife.87048
@@
 
+$^1$Department of Psychology, University of York, York, UK. YO10 5DD  
+$^2$School of Psychology and Vision Sciences, University of Leicester, Leicester, UK. LE1 7RH
+
+Address for correspondence: Federico G. Segala, [fgs502\@york.ac.uk](fgs502@york.ac.uk)
+
 # Abstract

### 2023-08-29 manuscript.Rmd
Minor updates to figure cross-references in captions.

@@
 Panel (b) shows the average Fourier spectrum (absolute amplitude values).
-Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 1).
+Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 8).
 Panel (e) shows contrast response functions at 1.6Hz for three conditions.
@@
 
-colnames(tabledata) <- c('Data set','Z','k','w','Rmax')
+colnames(tabledata) <- c('Data set','Z','n','w','Rmax')
 kable(tabledata, align='lcccc',caption = 'Summary of median parameter values.')
@@
 Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\\% regardless of the target contrast.
-Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
+Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 1 and 2.
 The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
@@
 
-```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.", fig.align="center", echo=FALSE}
+```{r appendixfig1, fig.cap="Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for a description of each panel.", fig.align="center", echo=FALSE}
 
@@
 
-```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 3 for a description of each panel.", fig.align="center", echo=FALSE}
+```{r appendixfig2, fig.cap="Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.", fig.align="center", echo=FALSE}
 

### 2023-08-29 manuscript.tex
Updater authors' inofrmation
Minor updates to figure cross-references in captions.

--- 2023-06-26 manuscript.tex
@@
 \title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
-\author{Federico G. Segala, Aurelio Bruno, Joel T. Martin,\\
-Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
-Department of Psychology, University of York, UK\\
+\author{Federico G. Segala\(^1\), Aurelio Bruno\(^2\), Joel T. Martin\(^1\), Myat T. Aung\(^1\), Alex R. Wade\(^1\)\\
+\& Daniel H. Baker\(^1\)\\
 \emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
@@
 
+\(^1\)Department of Psychology, University of York, York, UK. YO10 5DD\\
+\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, UK. LE1 7RH
+
+Address for correspondence: Federico G. Segala, \url{fgs502@york.ac.uk}
+
 \hypertarget{abstract}{%
@@
 
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\hypertarget{experiment-1}{%
+\subsection{Experiment 1}\label{experiment-1}}
+
+The pupillometry results are summarised in Figure \ref{fig:pupildata}.
+The group average waveform for binocular presentation is shown in Figure \ref{fig:pupildata}a.
+There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
+The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz (though see Appendix 1).
+These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/pupildata}
+
+}
+
+\caption{Summary of pupillometry results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
+Negative values indicate constriction relative to baseline, and positive values indicate dilation.
+Panel (b) shows the average Fourier spectrum (absolute amplitude values).
+Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 8).
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
+\end{figure}
+
+Figure \ref{fig:pupildata}c shows contrast response functions driven by stimuli flickering only at 2Hz.
+Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in the pupil response (to our knowledge this is the first time this has been demonstrated).
+The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
+A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (\protect\hyperlink{ref-Baker2021}{Baker, 2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless0.001).
+The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
+
+In Figure \ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \ref{fig:pupildata}c for comparison).
+When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless0.001).
+When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless0.001).
+
+Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
+Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
+In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles) (interaction effect: F(8,580) = 41.23, \(p\) \textless0.001).
+In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.
+\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}) (main effect of target contrast F(8,232) = 17, \(p\) \textless0.001).
+
+Figure \ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
+Figure \ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Figure \ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
+Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
+We therefore calculated contrast response functions at both first and second harmonic frequencies.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/EEGdata}
+
+}
+
+\caption{Summary of EEG results for N=30 participants.
+Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
+Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
+Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
+Panels (c,d) show contrast response functions at 2Hz for different conditions.
+Panel (e) shows contrast response functions at 1.6Hz for three conditions.
+Panels (f-h) are in the same format but for the second harmonic responses.
+Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
+\end{figure}
+
+When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
+Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
+For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
+Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \ref{fig:EEGdata}e) and 3.2Hz (Figure \ref{fig:EEGdata}h).
+This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
+
+Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
+Figure \ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
+At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
+Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
+A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless0.001).
+All of the key results from Experiment 1 were subsequently replicated for peripheral stimulation (see Appendix 1).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/BSratios}
+
+}
+
+\caption{Ratio of binocular to monocular response for three data types.
+These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f.
+Each value is the average ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
+\end{figure}
+
+\hypertarget{experiment-2}{%
+\subsection{Experiment 2}\label{experiment-2}}
+
+The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
+One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
+We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
+Only EEG data were collected for this experiment, as the pupil response is substantially weaker above around 2Hz (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
+
+Results from the temporal frequency experiment are shown in Figure \ref{fig:TFdata}.
+Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
+From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
+However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
+Figure \ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
+Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
+\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/TFdata}
+
+}
+
+\caption{Binocular facilitation at different temporal frequencies, measured using EEG.
+Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
+Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
+Panel (c) shows the ratio of binocular to monocular responses.
+Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
+\end{figure}
+
+\hypertarget{experiment-3}{%
+\subsection{Experiment 3}\label{experiment-3}}
+
+In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry; see Figure \ref{fig:BSratios}).
+Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
+\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Legge1981}{Legge and Rubin, 1981}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}; \protect\hyperlink{ref-Quaia2018}{Quaia et al., 2018}).
+We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
+On each trial, one stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
+The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
+We tested 9 ratios of target contrast between the left and right eyes.
+
+The results from the matching experiment are shown in Figure \ref{fig:matchingdata}.
+Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
+At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the \emph{x}- and \emph{y}-axes), compared to a binocular target (points along the diagonal of \emph{x}=\emph{y}).
+For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
+The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
+Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \ref{fig:EEGdata}c,f).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
+
+}
+
+\caption{Contrast matching functions.
+Dotted and dashed lines are predictions of canonical summation models involving linear combination (dotted) or a winner-take-all rule (dashed).
+Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
+Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
+This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
+\end{figure}
+
+\hypertarget{computational-modelling}{%
+\subsection{Computational modelling}\label{computational-modelling}}
+
+We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
+The model behaviour is displayed in Figure \ref{fig:modelfigure}a-d, with empirical data superimposed for comparison.
+In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Table \ref{tab:paramtable}.
+We were particularly interested in comparing the weight of interocular suppression across data sets.
+We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}e).
+The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
+There is no overlap between the pupillometry distribution and any of the other three.
+All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}), and the peak location of our prior distribution (black curve).
+These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
+The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/modelfigure}
+
+}
+
+\caption{Summary of computational modelling.
+Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments, with curves showing model behaviour generated using the median group-level parameter values.
+Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
+The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
+The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
+\end{figure}
+
+\begin{table}
+
+\caption{\label{tab:paramtable}Summary of median parameter values.}
+\centering
+\begin{tabular}[t]{l|c|c|c|c}
+\hline
+Data set & Z & n & w & Rmax\\
+\hline
+Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
+\hline
+EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
+\hline
+EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
+\hline
+Matching & 0.30 & 5.10 & 0.09 & -\\
+\hline
+\end{tabular}
+\end{table}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
+In the visual cortex response (indexed by EEG), the binocular combination of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
+Evidence for this comes from the substantial binocular facilitation effect when comparing monocular and binocular responses, and the lack of a dichoptic suppression effect when the two eyes were stimulated at different frequencies.
+In the subcortical pathway (indexed by pupillometry), binocular combination is more non-linear, with evidence of interocular suppression.
+This was evidenced by a weaker binocular facilitation, and stronger dichoptic suppression, relative to the EEG data.
+This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
+Additionally, we found that perception of flickering light is consistent with a near-linear binocular summation process, consistent with the cortical (EEG) responses.
+
+The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
+Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are generally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) (however we note that facilitation as substantial as ours has been reported in previous EEG work by \protect\hyperlink{ref-Apkarian1981}{Apkarian et al., 1981}).
+Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
+However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
+Using scleral search coils, Quaia et al.
+(\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli (also known as the ocular following response).
+Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure (melatonin is a hormone released by the pineal gland that regulates sleep; its production is suppressed by light exposure and can be measured from saliva assays).
+Work on the accommodative response indicates that binocular combination there is approximately linear (\protect\hyperlink{ref-Flitcroft1992}{Flitcroft et al., 1992}), and can even cancel when signals are in antiphase (we did not try this configuration here).
+In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
+Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}), though not for luminance decrements (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}).
+Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination (or combination across multiple inputs in other senses).
+
+Given the above, where does this leave our understanding of the overarching purpose of signal combination?
+Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also \protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}).
+Functionally, interocular suppression may therefore act to dynamically suppress noise, rendering binocular vision more stable.
+This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (\protect\hyperlink{ref-Li1994}{Li and Atick, 1994}; \protect\hyperlink{ref-May2022}{May and Zhaoping, 2022}).
+One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
+However the other examples of binocular combination discussed above are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit more from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
+Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
+Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
+
+Pupil size affects the total amount of light falling on the retina.
+It is therefore the case that fluctuations in pupil diameter will have a downstream effect on the signals reaching cortex.
+We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
+However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.
+\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
+It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.
+\protect\hyperlink{ref-Bradley2008}{Bradley et al., 2008}).
+We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
+Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this more directly in future neuroimaging work.
+Using fMRI to simultaneously image cortical and subcortical brain regions will also allow us to check that the differences we report here are not a consequence of the different measurement techniques we used (pupillometry and EEG).
+
+Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}) are biased towards low spatial frequencies (\protect\hyperlink{ref-Edwards1995}{Edwards et al., 1995}; \protect\hyperlink{ref-Tootell1988}{Tootell et al., 1988}), and relatively insensitive to stimulus orientation (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; though see \protect\hyperlink{ref-Economides2011}{Economides et al., 2011}).
+As the blob regions are embedded within ocular dominance columns (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}), they are also largely monocular (\protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; \protect\hyperlink{ref-Tychsen2004}{Tychsen et al., 2004}).
+More recent work has reported psychophysical evidence for unoriented chromatic (\protect\hyperlink{ref-Gheiratmand2013}{Gheiratmand et al., 2013}) and achromatic (\protect\hyperlink{ref-Meese2011}{Meese and Baker, 2011}) mechanisms, that also appear to be monocular.
+Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
+Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
+We therefore performed an additional analysis to investigate this possibility.
+
+In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (\protect\hyperlink{ref-Baitch1988}{Baitch and Levi, 1988}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
+In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
+Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
+It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods.
+The presence of intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
+Indeed, our model architecture (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{Figures/IMresponse}
+
+}
+
+\caption{Summary of intermodulation responses in pupillometry (a) and EEG (b) data.
+The data are pooled across the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\%.
+Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies (red).
+Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.}\label{fig:IMfig}
+\end{figure}
+
+\hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
+
+We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
+Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
+Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
+We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
+
 \hypertarget{methods}{%
@@
 Unshaded waveforms indicate mask stimuli, that were presented at a fixed contrast level of 48\% regardless of the target contrast.
-Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 2 and 3.
+Each waveform corresponds to a 1 second period of a 12 second trial, and coloured symbols are for consistency with Figures 1 and 2.
 The icon in the upper left corner illustrates the stimulus appearance (a luminous disc against a black background).
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{experiment-1}{%
-\subsection{Experiment 1}\label{experiment-1}}
-
-The pupillometry results are summarised in Figure \ref{fig:pupildata}.
-The group average waveform for binocular presentation is shown in Figure \ref{fig:pupildata}a.
-There is a substantial pupil constriction at stimulus onset, followed by visible oscillations at the flicker frequency (2Hz, see waveform at foot).
-The average Fourier spectrum is displayed in Figure \ref{fig:pupildata}b, and shows a clear spike at 2 Hz, but no evidence of a second harmonic response at 4Hz (though see Appendix 1).
-These results demonstrate that our paradigm can evoke measurable steady-state pupil responses at 2Hz.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/pupildata}
-
-}
-
-\caption{Summary of pupillometry results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Negative values indicate constriction relative to baseline, and positive values indicate dilation.
-Panel (b) shows the average Fourier spectrum (absolute amplitude values).
-Panels (c,d) show contrast response functions for pupil diameter at 2Hz for different conditions (illustrated in Figure 1).
-Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:pupildata}
-\end{figure}
-
-Figure \ref{fig:pupildata}c shows contrast response functions driven by stimuli flickering only at 2Hz.
-Response amplitudes increased monotonically with target contrast, confirming that our paradigm is suitable for measuring contrast-dependent differences in the pupil response (to our knowledge this is the first time this has been demonstrated).
-The amplitude of the binocular condition (blue squares) is consistently greater than that of the monocular condition (red circles) across all target contrasts.
-A \(2\times5\) repeated measures \(ANOVA^2_{circ}\) (\protect\hyperlink{ref-Baker2021}{Baker, 2021}) comparing these conditions revealed a significant main effect of target contrast (F(8,580) = 16.79, \(p\) \textless0.001), a significant effect of condition (F(2,580) = 11.04, \(p\) \textless0.001), and a significant interaction (F(8,580) = 56.25, \(p\) \textless0.001).
-The dichoptic condition begins at a much higher amplitude, owing to binocular combination of the target and high (48\%) contrast mask, and then increases slightly with increasing target contrast (main effect of target contrast: F(8,232) = 3.03, \(p\) \textless{} 0.003).
-
-In Figure \ref{fig:pupildata}d, we plot responses to monocular target stimuli flickering at 2Hz, when the other eye viewed stimuli flickering at 1.6Hz (the red monocular-only data are replotted from Figure \ref{fig:pupildata}c for comparison).
-When the 1.6Hz component had the same contrast as the target (the binocular cross condition, shown in purple) responses were facilitated slightly at low contrasts, and suppressed at the highest target contrasts (interaction between contrast and condition: F(8,580) = 52.94, \(p\) \textless0.001).
-When the 1.6Hz component had a fixed contrast of 48\% (the dichoptic cross condition, shown in yellow), responses were suppressed slightly across the contrast range (interaction between contrast and condition: F(8,580) = 62.05, \(p\) \textless0.001).
-
-Figure \ref{fig:pupildata}e shows responses at 1.6Hz, for the same conditions, as well as for a condition in which a monocular stimulus flickered at 1.6Hz (grey circles).
-Here we find strong suppression in both the binocular cross (purple triangles) and dichoptic cross (yellow triangles) conditions.
-In the binocular cross condition, the amplitudes are reduced relative to the monocular condition (grey circles) (interaction effect: F(8,580) = 41.23, \(p\) \textless0.001).
-In the dichoptic cross condition, increasing the 2Hz target contrast suppresses the response to the 1.6Hz mask, and the function decreases (see e.g.
-\protect\hyperlink{ref-Busse2009}{Busse et al., 2009}) (main effect of target contrast F(8,232) = 17, \(p\) \textless0.001).
-
-Figure \ref{fig:EEGdata} shows equivalent results, measured contemporaneously using EEG.
-Figure \ref{fig:EEGdata}a shows the group average waveform for binocular presentation, and Figure \ref{fig:EEGdata}b shows the Fourier spectrum for binocular presentation, both averaged across four posterior electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}, marked on the inset scalp plots).
-Unlike for the pupillometry data, there are clear responses at both the first harmonic frequency (2Hz), and also the second harmonic frequency (4Hz).
-We therefore calculated contrast response functions at both first and second harmonic frequencies.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/EEGdata}
-
-}
-
-\caption{Summary of EEG results for N=30 participants.
-Panel (a) shows a group average waveform for binocular presentation (low pass filtered at 5Hz), with the driving signal plotted at the foot.
-Panel (b) shows the average Fourier spectrum, and inset scalp distributions.
-Black dots on the scalp plots indicate electrodes Oz, POz, O1 and O2.
-Panels (c,d) show contrast response functions at 2Hz for different conditions.
-Panel (e) shows contrast response functions at 1.6Hz for three conditions.
-Panels (f-h) are in the same format but for the second harmonic responses.
-Shaded regions and error bars indicate bootstrapped standard errors.}\label{fig:EEGdata}
-\end{figure}
-
-When stimuli in both eyes flicker at 2Hz, the binocular responses at the first (Figure \ref{fig:EEGdata}c) and second (Figure \ref{fig:EEGdata}f) harmonics are substantially greater than the monocular responses, particularly at high contrasts.
-Analysis of variance on the complex values (\(ANOVA^2_{circ}\)) revealed a main effect of contrast (F(8,580) = 4.38, \(p\) \textless0.001) and an interaction effect (F(8,580) = 61.58, \(p\) \textless0.001), but no effect of condition (\(p\) = 0.13) at the first harmonic, with a similar pattern of results obtained at the second harmonic.
-For the cross-frequency conditions (Figure \ref{fig:EEGdata}d,g), there was no appreciable effect of adding a 1.6Hz component on the response at 2Hz or 4Hz (no effect of condition, and no interaction).
-Similarly, there were no clear interocular interactions between frequencies in the responses at 1.6Hz (Figure \ref{fig:EEGdata}e) and 3.2Hz (Figure \ref{fig:EEGdata}h).
-This pattern of results suggests that processing of temporal luminance modulations happens in a more linear way in visual cortex (indexed by EEG), compared with subcortical pathways (indexed by pupillometry), and shows no evidence of interocular suppression.
-
-Finally, we calculated the ratio of binocular to monocular responses across the three data types from Experiment 1.
-Figure \ref{fig:BSratios} shows that these ratios are approximately \(\sqrt2\) across the low-to-intermediate contrast range for all three data types.
-At higher contrasts, we see ratios of 2 or higher for the EEG data, but much weaker ratios near 1 for the pupillometry data.
-Note that the ratios here are calculated on a per-participant basis and then averaged, rather than being the ratios of the average values shown in Figures \ref{fig:pupildata} and \ref{fig:EEGdata}.
-A \(3 \times 5\) repeated measures ANOVA on the logarithmic (dB) ratios found a main effect of contrast (F(3.08,89.28) = 4.53, \emph{p} \textless0.002), no effect of data modality (F(2,58) = 0.75, \emph{p} = 0.48), but a highly significant interaction (F(5.54,160.67) = 3.84, \emph{p} \textless0.001).
-All of the key results from Experiment 1 were subsequently replicated for peripheral stimulation (see Appendix 1).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/BSratios}
-
-}
-
-\caption{Ratio of binocular to monocular response for three data types.
-These were calculated by dividing the binocular response by the monocular response at each contrast level, using the data underlying Figures 2c, 3c and 3f.
-Each value is the average of ratio across N=30 participants, and error bars indicate bootstrapped standard errors.}\label{fig:BSratios}
-\end{figure}
-
-\hypertarget{experiment-2}{%
-\subsection{Experiment 2}\label{experiment-2}}
-
-The strong binocular facilitation and weak interocular suppression in the EEG data from Experiment 1 was very different from previous findings on binocular combination using steady-state EEG with grating stimuli (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}).
-One possible explanation is that the lower temporal frequency used here (2Hz, vs 5 or 7Hz in previous work) might be responsible for this difference.
-We therefore ran a second experiment to compare monocular and binocular responses at a range of temporal frequencies.
-Only EEG data were collected for this experiment, as the pupil response is substantially weaker above around 2Hz (\protect\hyperlink{ref-Barrionuevo2014}{Barrionuevo et al., 2014}; \protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}); note that we originally chose 2Hz because it produces measurable signals for both EEG and pupillometry, yet is unfortunately optimal for neither.
-
-Results from the temporal frequency experiment are shown in Figure \ref{fig:TFdata}.
-Figure \ref{fig:TFdata}a shows the Fourier spectra for responses to binocular flicker at 5 different frequencies (2, 4, 8, 16, and 30 Hz).
-From 2 to 16 Hz, clear signals are observed at each fundamental frequency, and typically also their higher harmonics (integer multiples of the fundamental).
-However, at 30 Hz (upper row), the responses recorded were not demonstrably above the noise baseline.
-Figure \ref{fig:TFdata}b compares the monocular and binocular responses at each stimulation frequency.
-Here we replicate the substantial summation effect across frequencies up to and including 16Hz (Fig.
-\ref{fig:TFdata}c), demonstrating that strong binocular facilitation in the EEG data of Experiment 1 cannot be attributed to our use of 2Hz flicker.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/TFdata}
-
-}
-
-\caption{Binocular facilitation at different temporal frequencies, measured using EEG.
-Panel (a) shows Fourier spectra for responses to binocular flicker at 5 different frequencies (offset vertically for clarity).
-Panel (b) shows the response at each stimulation frequency for monocular (red circles) and binocular (blue squares) presentation.
-Panel (c) shows the ratio of binocular to monocular responses.
-Error bars and shaded regions indicate bootstrapped standard errors across N=12 participants.}\label{fig:TFdata}
-\end{figure}
-
-\hypertarget{experiment-3}{%
-\subsection{Experiment 3}\label{experiment-3}}
-
-In Experiment 1 we found evidence of stronger binocular facilitation for cortical responses to luminance flicker (measured using EEG), compared with subcortical responses (measured using pupillometry; see Figure \ref{fig:BSratios}).
-Since perception is dependent on cortical responses, these results provide a clear prediction for perceived contrast judgements indexed by psychophysical contrast matching paradigms (e.g.
-\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Legge1981}{Legge and Rubin, 1981}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}; \protect\hyperlink{ref-Quaia2018}{Quaia et al., 2018}).
-We therefore conducted such an experiment, in which participants judged which of two stimuli had the greater perceived amplitude of flicker.
-On each trial, one stimulus was a matching stimulus, that had a fixed binocular flicker amplitude of either 24\% or 48\% (temporal) contrast.
-The other stimulus was a target stimulus, the contrast of which was controlled by a staircase algorithm.
-We tested 9 ratios of target contrast between the left and right eyes.
-
-The results from the matching experiment are shown in Figure \ref{fig:matchingdata}.
-Each data point indicates the contrast levels required in each eye that were perceptually equivalent to the binocular 24\% (red circles) and 48\% (blue circles) matching contrasts.
-At both matching contrasts, we see a very substantial increase in the physical contrast required for a monocular target (data points along the \emph{x}- and \emph{y}-axes), compared to a binocular target (points along the diagonal of \emph{x}=\emph{y}).
-For example with a 48\% match, the monocular targets required contrasts close to 100\%, whereas binocular targets required a contrast of around 50\%.
-The data points between these extremes also fall close to the predictions of a linear summation model (diagonal dotted lines), and are inconsistent with a winner-takes-all (or MAX) model (dashed lines).
-Overall, these matching results are consistent with the approximately linear summation effects observed in the EEG data of Experiment 1 (Figure \ref{fig:EEGdata}c,f).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/matchingdata}
-
-}
-
-\caption{Contrast matching functions.
-Dotted and dashed lines are predictions of canonical summation models involving linear combination (dotted) or a winner-take-all rule (dashed).
-Error bars indicate the standard error across participants (N=10), and are constrained along radial lines converging at the origin.
-Note that, for the {48\%} match, the data point on the x axis falls higher than {100\%} contrast.
-This is because the psychometric function fits for some individuals were interpolated such that the PSE fell above {100\%}, shifting the mean slightly above that value.}\label{fig:matchingdata}
-\end{figure}
-
-\hypertarget{computational-modelling}{%
-\subsection{Computational modelling}\label{computational-modelling}}
-
-We fitted a computational model to the data from Experiments 1 \& 3 using a hierarchical Bayesian approach.
-The model behaviour is displayed in Figure \ref{fig:modelfigure}a-d, with empirical data superimposed for comparison.
-In general, the model captures the key characteristics of the empirical data, with group-level parameter estimates provided in Table \ref{tab:paramtable}.
-We were particularly interested in comparing the weight of interocular suppression across data sets.
-We therefore plot the posterior distributions for this parameter for all four data sets (see Figure \ref{fig:modelfigure}e).
-The key finding is that the pupillometry results (green distribution) display a much greater weight of interocular suppression compared with the other data sets (grey, purple and yellow distributions).
-There is no overlap between the pupillometry distribution and any of the other three.
-All four distributions are also meaningfully below a weight of 1 -- the value that previous work using grating stimuli would predict (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}), and the peak location of our prior distribution (black curve).
-These results offer an explanation of the empirical data: the strong interocular suppression for the pupillometry data is consistent with the weak binocular facilitation, and measurable dichoptic masking observed using that method.
-The weaker suppression for the other experiments is consistent with the near-linear binocular facilitation effects, and absent dichoptic masking.
-
-\begin{figure}
-
-{\centering \includegraphics{Figures/modelfigure}
-
-}
-
-\caption{Summary of computational modelling.
-Panels (a-d) show empirical data from key conditions, replotted from earlier figures for the pupillometry (a), first harmonic EEG responses (b), second harmonic EEG responses (c) and contrast matching (d) experiments, with curves showing model behaviour generated using the median group-level parameter values.
-Panel (e) shows the posterior probability distributions of the interocular suppression parameter for each of the four model fits.
-The pupillometry distribution (green) is centred about a substantially higher suppressive weight than for the other data types (note the logarithmic x-axis).
-The black curve shows the (scaled) prior distribution for the weight parameter.}\label{fig:modelfigure}
-\end{figure}
-
-\begin{table}
-
-\caption{\label{tab:paramtable}Summary of median parameter values.}
-\centering
-\begin{tabular}[t]{l|c|c|c|c}
-\hline
-Data set & Z & k & w & Rmax\\
-\hline
-Pupillometry & 3.44 & 0.01 & 0.61 & 0.00023\\
-\hline
-EEG 1F & 2.62 & 0.15 & 0.02 & 0.00336\\
-\hline
-EEG 2F & 3.71 & 0.07 & 0.02 & 0.0031\\
-\hline
-Matching & 0.30 & 5.10 & 0.09 & -\\
-\hline
-\end{tabular}
-\end{table}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Using a novel paradigm that combines EEG and pupillometry, we found surprising results for the binocular integration of flickering light.
-In the visual cortex response (indexed by EEG), the binocular combination of spatially-uniform temporal luminance modulations seems to happen approximately linearly, with no evidence of interocular suppression.
-Evidence for this comes from the substantial binocular facilitation effect when comparing monocular and binocular responses, and the lack of a dichoptic suppression effect when the two eyes were stimulated at different frequencies.
-In the subcortical pathway (indexed by pupillometry), binocular combination is more non-linear, with evidence of interocular suppression.
-This was evidenced by a weaker binocular facilitation, and stronger dichoptic suppression, relative to the EEG data.
-This pattern of results was confirmed by computational modelling, which showed a much greater suppressive weight for the pupillometry data compared to the EEG data.
-Additionally, we found that perception of flickering light is consistent with a near-linear binocular summation process, consistent with the cortical (EEG) responses.
-
-The results of our main experiment were unexpected for both the pupillometry and the EEG measures.
-Previous studies investigating binocular combination of spatial patterns (i.e.~sine wave grating stimuli) are generally consistent with strong interocular suppression and weak binocular facilitation at high contrasts (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Meese2006}{Meese et al., 2006}; \protect\hyperlink{ref-Moradi2009}{Moradi and Heeger, 2009}) (however we note that facilitation as substantial as ours has been reported in previous EEG work by \protect\hyperlink{ref-Apkarian1981}{Apkarian et al., 1981}).
-Our second experiment ruled out the possibility that these differences were due to the lower temporal frequency (2Hz) used here.
-However, there is evidence of more extensive binocular facilitation for a range of other stimuli.
-Using scleral search coils, Quaia et al.
-(\protect\hyperlink{ref-Quaia2018}{2018}) observed a strong binocular facilitation (or `supersummation') in the reflexive eye movement response to rapidly moving stimuli (also known as the ocular following response).
-Spitschan and Cajochen (\protect\hyperlink{ref-Spitschan2019}{2019}) report a similar result in archival data on melatonin suppression due to light exposure (melatonin is a hormone released by the pineal gland that regulates sleep; its production is suppressed by light exposure and can be measured from saliva assays).
-Work on the accommodative response indicates that binocular combination there is approximately linear (\protect\hyperlink{ref-Flitcroft1992}{Flitcroft et al., 1992}), and can even cancel when signals are in antiphase (we did not try this configuration here).
-In the auditory system, interaural suppression of amplitude modulation also appears to be weak when measured using a similar steady-state paradigm (\protect\hyperlink{ref-Baker2020}{Baker et al., 2020}).
-Finally, psychophysical matching experiments using static stimuli also show near-linear behaviour for luminance increments (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}; \protect\hyperlink{ref-Baker2012}{Baker et al., 2012}; \protect\hyperlink{ref-Levelt1965}{Levelt, 1965}), though not for luminance decrements (\protect\hyperlink{ref-Anstis1998}{Anstis and Ho, 1998}).
-Overall, this suggests that strong interocular normalization may be specific to spatial pattern vision, and not a general feature of binocular signal combination (or combination across multiple inputs in other senses).
-
-Given the above, where does this leave our understanding of the overarching purpose of signal combination?
-Baker and Wade (\protect\hyperlink{ref-Baker2017}{2017}) point out that strong suppression between channels that are subsequently summed is equivalent to a Kalman filter, which is the optimal method for combining two noisy inputs (see also \protect\hyperlink{ref-Ernst2002}{Ernst and Banks, 2002}).
-Functionally, interocular suppression may therefore act to dynamically suppress noise, rendering binocular vision more stable.
-This account has intuitive appeal, and is consistent with other models that propose binocular combination as a means of redundancy reduction (\protect\hyperlink{ref-Li1994}{Li and Atick, 1994}; \protect\hyperlink{ref-May2022}{May and Zhaoping, 2022}).
-One possibility is that optimal combination is useful for visual perception --- a critical system for interacting with the local environment --- and is therefore worth devoting the additional resource of inhibitory wiring between ocular channels.
-However the other examples of binocular combination discussed above are primarily physiological responses (pupil size, eye movements, hormone release) that may benefit more from an increased signal-to-noise ratio, or otherwise be phylogenetically older than binocular pattern vision.
-Conceptualised another way, the brain can repurpose a generic architecture for different situational demands by adjusting parameter values (here the weight of interocular suppression) to achieve different outcomes.
-Our future work in this area intends to compare binocular combination for specific photoreceptor pathways, including different cone classes, and intrinsically photoreceptive retinal ganglion cells.
-
-Pupil size affects the total amount of light falling on the retina.
-It is therefore the case that fluctuations in pupil diameter will have a downstream effect on the signals reaching cortex.
-We did not incorporate such interactions into our computational model, though in principle this might be worthwhile.
-However we anticipate than any such effects would be small, since pupil modulations at 2Hz are in the order of 2\% of overall diameter (e.g.
-\protect\hyperlink{ref-Spitschan2014}{Spitschan et al., 2014}).
-It is also the case that cortical activity can modulate pupil diameter, usually through arousal and attention mechanisms (e.g.
-\protect\hyperlink{ref-Bradley2008}{Bradley et al., 2008}).
-We think it unlikely that these temporally coarse processes would have a differential effect on e.g.~monocular and binocular stimulation conditions in our experiment, and any fluctuations during an experimental session (perhaps owing to fatigue) will be equivalent for our comparisons of interest.
-Therefore we make the simplifying assumption that the pupil and perceptual pathways are effectively distinct, but hope to investigate this more directly in future neuroimaging work.
-Using fMRI to simultaneously image cortical and subcortical brain regions will also allow us to check that the differences we report here are not a consequence of the different measurement techniques we used (pupillometry and EEG).
-
-Classic studies investigating the neurophysiological architecture of V1 reported that cells in cytochrome-oxidase `blobs' (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}) are biased towards low spatial frequencies (\protect\hyperlink{ref-Edwards1995}{Edwards et al., 1995}; \protect\hyperlink{ref-Tootell1988}{Tootell et al., 1988}), and relatively insensitive to stimulus orientation (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}; \protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; though see \protect\hyperlink{ref-Economides2011}{Economides et al., 2011}).
-As the blob regions are embedded within ocular dominance columns (\protect\hyperlink{ref-Horton1981}{Horton and Hubel, 1981}), they are also largely monocular (\protect\hyperlink{ref-Livingstone1984}{Livingstone and Hubel, 1984}; \protect\hyperlink{ref-Tychsen2004}{Tychsen et al., 2004}).
-More recent work has reported psychophysical evidence for unoriented chromatic (\protect\hyperlink{ref-Gheiratmand2013}{Gheiratmand et al., 2013}) and achromatic (\protect\hyperlink{ref-Meese2011}{Meese and Baker, 2011}) mechanisms, that also appear to be monocular.
-Our use of luminance flicker might preferentially stimulate these mechanisms, perhaps explaining why our EEG data show little evidence of binocular interactions.
-Indeed, our EEG results could potentially be explained by a model involving entirely non-interacting monocular channels, with the binocular facilitation effects we find (e.g.~Figures \ref{fig:BSratios} \& \ref{fig:TFdata}) owing to additivity of the electrophysiological response across independent monocular cells, rather than within binocular neurons.
-We therefore performed an additional analysis to investigate this possibility.
-
-In the steady-state literature, one hallmark of a nonlinear system that pools inputs is the presence of intermodulation responses at the sums and differences of the fundamental flicker frequencies (\protect\hyperlink{ref-Baitch1988}{Baitch and Levi, 1988}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
-In Figure \ref{fig:IMfig} we plot the amplitude spectra of conditions from Experiment 1 in which the two eyes were stimulated at different frequencies (2Hz and 1.6Hz) but at the same contrast (48\%; these correspond to the binocular cross and dichoptic cross conditions in Figures \ref{fig:pupildata}d,e and \ref{fig:EEGdata}d,e).
-Figure \ref{fig:IMfig}a reveals a strong intermodulation difference response at 0.4Hz (red dashed line), and Figure \ref{fig:IMfig}b reveals an intermodulation sum response at 3.6Hz (red dashed line).
-It seems likely that the absence of a sum response for pupillometry data, and of a difference responses for the EEG data, is a consequence of the temporal constraints of these methods.
-The presence of intermodulation terms is predicted by nonlinear gain control models of the type considered here (\protect\hyperlink{ref-Baker2017}{Baker and Wade, 2017}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}), and indicates that the processing of monocular flicker signals is not fully linear prior to the point at which they are combined across the eyes.
-Indeed, our model architecture (\protect\hyperlink{ref-Meese2006}{Meese et al., 2006}) makes specific predictions about the location of interocular suppression - it impacts before binocular combination, consistent with results from primate physiology (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{Figures/IMresponse}
-
-}
-
-\caption{Summary of intermodulation responses in pupillometry (a) and EEG (b) data.
-The data are pooled across the binocular cross and dichoptic cross conditions of Experiment 1, with a target contrast of 48\%.
-Vertical dashed lines indicate the fundamental flicker frequencies of 2Hz (F1; black) and 1.6Hz (F2; green), and the intermodulation difference (F1-F2 = 0.4Hz) and sum (F1+F2 = 3.6Hz) frequencies (red).
-Data are averaged across N = 30 participants, and shaded regions indicate ±1 standard error.}\label{fig:IMfig}
-\end{figure}
-
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
-
-We have demonstrated that binocular combination of flickering light differs between cortical and subcortical pathways.
-Flicker was also associated with substantially weaker interocular suppression, and stronger binocular facilitation, compared to combination of spatial luminance modulations in visual cortex.
-Our computational framework for understanding signal combination permits direct comparisons between disparate experimental paradigms and data types.
-We anticipate that this will help elucidate the constraints the brain faces when combining different types of signals to govern perception, action and biological function.
-
 \hypertarget{acknowledgements}{%
@@
 
-\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.}\label{fig:appendixfig1}
+\caption{Summary of pupillometry results for N = 12 participants, for peripheral stimulation. See Figure 1 for a description of each panel.}\label{fig:appendixfig1}
 \end{figure}
@@
 
-\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 3 for a description of each panel.}\label{fig:appendixfig2}
+\caption{Summary of steady-state EEG results for N = 12 participants, for peripheral stimulation. See Figure 2 for a description of each panel.}\label{fig:appendixfig2}
 \end{figure}

### 2023-09-08 manuscript.Rmd
Amended information

@@
  | & Daniel H. Baker$^1$
- | *eLife* (2023) https://doi.org/10.7554/eLife.87048
 output:
@@
 
-# Author contributions
-
-**Federico Segala**: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review & editing, visualization.
-**Aurelio Bruno**: Conceptualization, writing - review & editing, supervision, project administration, funding acquisition.
-**Joel Martin**: Software, resources, writing - review & editing.
-**Myat Aung**: Software, resources, writing - review & editing.
-**Alex Wade**: Conceptualization, methodology, resources, writing - review & editing, supervision, project administration, funding acquisition.
-**Daniel Baker**: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review & editing, visualization, supervision, project administration, funding acquisition.
-
 # Declaration of interests

### 2023-09-08 manuscript.tex
Amended information

--- 2023-08-28 manuscript.tex
@@
 \title{Different rules for binocular combination of luminance flicker in cortical and subcortical pathways}
-\author{Federico G. Segala, Aurelio Bruno, Joel T. Martin,\\
-Myat T. Aung, Alex R. Wade \& Daniel H. Baker\\
-Department of Psychology, University of York, UK\\
-\emph{eLife} (2023) \url{https://doi.org/10.7554/eLife.87048}}
+\author{Federico G. Segala\(^1\), Aurelio Bruno\(^2\), Joel T. Martin\(^1\), Myat T. Aung\(^1\), Alex R. Wade\(^1\)\\
+\& Daniel H. Baker\(^1\)}
 \date{}
@@
 \maketitle
+
+\(^1\)Department of Psychology, University of York, York, UK. YO10 5DD\\
+\(^2\)School of Psychology and Vision Sciences, University of Leicester, Leicester, UK. LE1 7RH
+
+Address for correspondence: Federico G. Segala, \url{fgs502@york.ac.uk}
 
@@
 \hline
-Data set & Z & k & w & Rmax\\
+Data set & Z & n & w & Rmax\\
 \hline
@@
 
-\hypertarget{author-contributions}{%
-\section{Author contributions}\label{author-contributions}}
-
-\textbf{Federico Segala}: Methodology, software, formal analysis, investigation, data curation, writing - original draft, writing - review \& editing, visualization.
-\textbf{Aurelio Bruno}: Conceptualization, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Joel Martin}: Software, resources, writing - review \& editing.
-\textbf{Myat Aung}: Software, resources, writing - review \& editing.
-\textbf{Alex Wade}: Conceptualization, methodology, resources, writing - review \& editing, supervision, project administration, funding acquisition.
-\textbf{Daniel Baker}: Conceptualization, methodology, software, formal analysis, investigation, resources, data curation, writing - original draft, writing - review \& editing, visualization, supervision, project administration, funding acquisition.
-
 \hypertarget{declaration-of-interests}{%
@@
 2023.
-PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and non-visual photoreception research.
-\emph{Journal of Vision} \textbf{In press}.
+PySilSub: An open-source python toolbox for implementing the method of silent substitution in vision and nonvisual photoreception research.
+\emph{Journal of Vision} \textbf{23}:10.
+doi:\href{https://doi.org/10.1167/jov.23.7.10}{10.1167/jov.23.7.10}
 

### 2023-09-08 manuscript.Rmd
Added github repo

@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox [@Delorme2004].
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script (available at: https://github.com/bakerdh/PupillometryEEG/; @Segala2023) and components of the EEGlab toolbox [@Delorme2004].
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).

### 2023-09-08 manuscript.tex
Added github repo

@@
 
-EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script and components of the EEGlab toolbox (Delorme and Makeig, \protect\hyperlink{ref-Delorme2004}{2004}).
+EEG data were converted from the ANT-EEProbe format to a compressed csv text file using a custom Matlab script (available at: \url{https://github.com/bakerdh/PupillometryEEG/}; Segala et al.
+(\protect\hyperlink{ref-Segala2023}{2023})) and components of the EEGlab toolbox (Delorme and Makeig, \protect\hyperlink{ref-Delorme2004}{2004}).
 The data for each participant were then loaded into R for analysis, where a ten-second waveform for each trial at each electrode was extracted (omitting the first two seconds).
@@
 
+\leavevmode\hypertarget{ref-Segala2023}{}%
+Segala FG, Bruno A, Martin JT, Aung MT, Wade AR, Baker DH.
+2023.
+Different rules for binocular combination of luminance flicker in cortical and subcortical pathways (code).
+Github.
+Https://github.com/bakerdh/pupillometryeeg/.
+F3181b1.
+
 \leavevmode\hypertarget{ref-Spitschan2019}{}%
